% This is the main point of entry to the blueprint.
% Add chapters of the blueprint here.
% This file is not meant to be built. Build src/web.tex or src/print.text instead.

% Note: still have to upstream section ~> chapter and subsection ~> section to Overleaf
% Replace spaces by dashes in labels using search&replace (leave out `, keep space)
% `((\\label|\\ref|\\eqref|\\uses|\\proves)\{([^ \n},]|,\n? *[a-zA-Z])*) `
% to
% `$1-`
%
\title{Carleson operators on doubling metric measure spaces}

\date{\today}

\maketitle

\begin{abstract}
    We prove a new generalization of a theorem of Carleson, namely bounds for a generalized Carleson operator on doubling metric measure spaces.
    Additionally, we explicitly reduce Carleson's classical result on pointwise convergence of Fourier series to this new theorem.
    Both proofs are presented in great detail, suitable as a blueprint for computer verification using the current capabilities of the software package Lean.
    Note that even Carleson's classical result has not yet been computer-verified.
\end{abstract}

\tableofcontents

\textbf{Acknowledgements}: We greatly appreciate the help by anyone proof reading this blueprint or helping with the formalization process.

\chapter{Introduction}

In \cite{carleson}, L. Carleson addressed a classical question regarding the convergence of Fourier series of continuous functions by proving their pointwise convergence almost everywhere. \Cref{classical-Carleson} represents a version of this result.

Let $f$ be a complex valued, $2\pi$-periodic bounded Borel measurable function on the real line, and for an integer $n$, define the Fourier coefficient as
\begin{equation}
    \widehat{f}_n:=\frac {1}{2\pi} \int_0^{2\pi} f(x) e^{- i nx} dx .
\end{equation}
Define the partial Fourier sum for $N\ge 0$ as
\begin{equation}
    S_Nf(x):=\sum_{n=-N}^N \widehat{f}_n e^{i nx}\ .
\end{equation}

\begin{theorem}[classical Carleson]
\label{classical-Carleson}
\leanok
\lean{classical_carleson}
\uses{smooth-approximation, convergence-for-smooth,
control-approximation-effect}
Let $f$ be a $2\pi$-periodic complex-valued uniformly continuous function on $\mathbb{R}$ satisfying the bound $|f(x)|\le 1$ for all $x\in \mathbb{R}$. For all $0<\epsilon<1$, there exists a Borel set $E\subset [0,2\pi]$ with Lebesgue measure $|E|\le \epsilon$ and a positive integer $N_0$ such that for all $x\in [0,2\pi]\setminus E$ and all integers $N>N_0$, we have
\begin{equation}\label{aeconv}
|f(x)-S_N f(x)|\le \epsilon.
\end{equation}
\end{theorem}

Note that mere continuity implies uniform continuity in the setting of this theorem. By applying this theorem with a sequence of $\epsilon_n:= 2^{-n}\delta$ for $n\ge 1$ and taking the union of corresponding exceptional sets $E_n$, we see that outside a set of measure $\delta$, the partial Fourier sums converge pointwise for $N\to \infty$. Applying this with a sequence of $\delta$ shrinking to zero and taking the intersection of the corresponding exceptional sets, which has measure zero, we see that the Fourier series converges outside a set of measure zero.

The purpose of this paper is twofold. On the one hand, it prepares computer verification of \Cref{classical-Carleson} by presenting a very detailed proof as a blueprint for coding in Lean. We pass through a bound for a generalization of the so-called Carleson operator to doubling metric measure spaces. This generalization is new, and proving these bounds constitutes the second purpose of this paper. This generalization incorporates several results from the recent literature, most prominently bounds for the polynomial Carleson operator of V. Lie \cite{lie-polynomial} as well as its generalization \cite{zk-polynomial}. A computer verification of our theorem will also entail a computer verification for the bulk of the work in these results.


We proceed to introduce the setup for our general theorem.
We carry a multi purpose parameter, a natural number
\begin{equation}
    a\ge 4
\end{equation} in our notation that as it gets larger will allow more general applications but will worsen the constants in the estimates.



A doubling metric measure space $(X,\rho,\mu, a)$ is a complete
and locally compact metric space $(X,\rho)$
equipped with a $\sigma$-finite non-zero Radon--Borel measure $\mu$ that satisfies the doubling condition that for all $x\in X$ and all $R>0$ we have
\begin{equation}\label{doublingx}
    \mu(B(x,2R))\le 2^a\mu(B(x,R))\,,
\end{equation}
where we have denoted by $B(x,R)$ the open ball of radius $R$ centred at $x$:
\begin{equation}\label{eq-define-ball}
 B(x,R):=\{y\in X: \rho(x,y)<R\}. \end{equation}

A collection $\Mf$ of real valued continuous functions on the doubling metric measure space $(X,\rho,\mu,a)$ is called compatible, if there is a point $o\in X$ where all the functions are equal to $0$, and if there exists for each ball $B \subset X$ a metric $d_B$ on $\Mf$, such that the following five properties \eqref{osccontrol}, \eqref{firstdb}, \eqref{monotonedb}, \eqref{seconddb}, and \eqref{thirddb} are satisfied. For every ball $B \subset X$
\begin{equation}\label{osccontrol}
    \sup_{x,y\in B}|\mfa(x)-{\mfa(y)}- \mfb(x)+{\mfb(y)}| \le d_{B}(\mfa,\mfb)\,.
\end{equation}
For any two balls $B_1=B(x_1,R)$, $B_2= B(x_2,2R)$ in $X$ with $x_1\in B_2$ and any $\mfa,\mfb\in \Mf$,
\begin{equation}\label{firstdb}
    d_{B_2}(\mfa,\mfb)\le 2^a d_{B_1}(\mfa,\mfb) .
\end{equation}
For any two balls $B_1, B_2$ in $X$ with $B_1 \subset B_2$ and any $\mfa, \mfb \in \Mf$
\begin{equation}\label{monotonedb}
    d_{B_1}(\mfa,\mfb) \le d_{B_2}(\mfa, \mfb)
\end{equation}
and for any two balls
$B_1=B(x_1,R)$, $B_2= B(x_2,2^aR)$
with $B_1\subset B_2$, and $\mfa,\mfb\in \Mf$,
\begin{equation}\label{seconddb}
    2d_{B_1}(\mfa,\mfb)
\le d_{B_2}(\mfa,\mfb) .
\end{equation}
For every ball $B$ in $X$ and every $d_B$-ball $\tilde B$ of radius $2R$ in $\Mf$, there is a collection $\mathcal{B}$ of
at most $2^a$ many $d_B$-balls of radius $R$ covering $\tilde B$, that is,
\begin{equation}\label{thirddb}
    \tilde B\subset \bigcup \mathcal{B}.
\end{equation}


Further, a compatible collection $\Mf$ is called cancellative, if
for any ball $B$ in $X$ of radius $R$, any Lipschitz function $\varphi: X\to \C$
supported on $B$, and any $\mfa,\mfb\in \Mf$ we have
\begin{equation}
    \label{eq-vdc-cond}
    |\int_B e(\mfa(x)-{\mfb(x)}) \varphi(x) d\mu(x)|\le 2^a \mu(B)\|\varphi\|_{\Lip(B)}
(1+d_B(\mfa,\mfb))^{-\frac{1}{a}},
\end{equation}
where $\|\cdot\|_{\Lip(B)}$ denotes the inhomogeneous Lipschitz norm on $B$:
$$
    \|\varphi\|_{\Lip(B)} = \sup_{x \in B} |\varphi(x)| + R \sup_{x,y \in B, x \neq y} \frac{|\varphi(x) - \varphi(y)|}{\rho(x,y)}\,.
$$




A one-sided Calder\'on--Zygmund kernel $K$ on the doubling metric measure space $(X, \rho, \mu, a)$ is a measurable function
 \begin{equation}\label{eqkernel0}
K:X\times X\to \mathbb{C}
 \end{equation}
such that for all $x,y',y\in X$ with $x\neq y$, we have
\begin{equation}\label{eqkernel-size}
    |K(x,y)| \leq \frac{2^{a^3}}{V(x,y)}
  \end{equation}
 and if $2\rho(y,y') \leq \rho(x,y)$, then
  \begin{equation}
  \label{eqkernel-y-smooth}
       |K(x,y) - K(x,y')| \leq \left(\frac{\rho(y,y')}{\rho(x,y)}\right)^{\frac{1}{a}}\frac{2^{a^3}}{V(x,y)},
\end{equation}
where \[V(x,y):=\mu(B(x,\rho(x,y))).\]
Define the maximally truncated non-tangential singular integral $T_{*}$ associated with $K$ by
\begin{equation}
    \label{def-tang-unm-op}
    T_{*}f(x):=\sup_{R_1 < R_2} \sup_{\rho(x,x')<R_1} \left|\int_{R_1< \rho(x',y) < R_2} K(x',y) f(y) \, \mathrm{d}\mu(y) \right|\,.
\end{equation}
We define the generalized Carleson operator $T$ by
 \begin{equation}
        \label{def-main-op}
        Tf(x):=\sup_{\mfa\in\Mf} \sup_{0 < R_1 < R_2}\left| \int_{R_1 < \rho(x,y) < R_2} K(x,y) f(y) e(\mfa(y)) \, \mathrm{d}\mu(y) \right|\, ,
\end{equation}
where $e(r)=e^{ir}$.

Our main result is the following restricted weak type estimate for $T$ in the range $1<q\le 2$, which by interpolation techniques recovers $L^q$ estimates for the open range
$1<q<2$.
\begin{theorem}[metric space Carleson]
\label{metric-space-Carleson}
\uses{R-truncation}
    For all integers $a \ge 4$ and real numbers $1<q\le 2$
    the following holds.
    Let $(X,\rho,\mu,a)$ be a doubling metric measure space. Let $\Mf$ be a
    cancellative compatible collection of functions and let $K$ be a one-sided Calder\'on--Zygmund kernel on $(X,\rho,\mu,a)$. Assume that for every bounded measurable function $g$ on $X$ supported on a set of finite measure we have
    \begin{equation}\label{nontanbound}
        \|T_{*}g\|_{2} \leq 2^{a^3} \|g\|_2\,,
    \end{equation}
    where $T_{*}$ is defined in
\eqref{def-tang-unm-op}.
    Then for all Borel sets $F$ and $G$ in $X$ and
    all Borel functions $f:X\to \C$ with
    $|f|\le \mathbf{1}_F$, we have, with $T$ defined in \eqref{def-main-op},
    \begin{equation}
    \label{resweak}
        \left|\int_{G} T f \, \mathrm{d}\mu\right| \leq \frac{2^{450a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}\, .
        \end{equation}
\end{theorem}

In the one-dimensional Euclidean setting, with $K$ representing the Hilbert kernel:
\begin{equation*}
K(x,y)=(x-y)^{-1}
\end{equation*}
and $\Mf$ denoting the class of linear functions, the operator \eqref{def-main-op} is the classical Carleson operator, which plays a crucial role in proving the almost everywhere convergence of Fourier series \cite{carleson}, \cite{fefferman}, \cite{lacey-thiele}. The supremum in $R_1$ and $R_2$ is often omitted in classical treatments, but considering the maximal truncations can easily be reduced to the case without these truncations.

By replacing $\Mf$ with the class of polynomials vanishing at $0$ up to some fixed but arbitrary degree, we obtain the polynomial Carleson operator of Lie \cite{lie-quadratic} (quadratic case) and \cite{lie-polynomial}. The case of the class of polynomials with vanishing linear coefficient is simpler and was estimated in \cite{stein-wainger}. The polynomial Carleson operator was generalized to the high-dimensional Euclidean setting in \cite{zk-polynomial} for $K$ being a Calder\'on-Zygmund kernel with some H\"older regularity.

Doubling metric measure spaces are instances of spaces of homogeneous type. Indeed, by changing from a quasi-metric to an equivalent metric, every space of homogeneous type can be viewed as a doubling metric measure space (cf. \cite{MaciasSegovia}). Spaces of homogeneous type were introduced by \cite{MR0499948} as a natural setting for Calder\'on-Zygmund theory. We refer to the textbook \cite{stein-book} for an account of these spaces.

Our concept of a compatible collection $\Mf$ as a natural class of phase functions on a doubling metric measure space does not appear in \cite{stein-book} but is implicitly anticipated in \cite{zk-polynomial} and subsequent work of \cite{mnatsakanyan}, who proves a Carleson-type theorem for the Malmquist-Takenaka series, which leads to classes of phases related to Blaschke products. A generalization of \eqref{def-main-op} from the previously mentioned Euclidean setting into the anisotropic setting that was suggested in \cite{zk-polynomial} is included in our theory. The polynomial Carleson operator also plays a role in the study of maximally modulated singular Radon transforms along the parabola, see \cite{ramos} and \cite{becker2024maximal}.

For the proof of \Cref{metric-space-Carleson}, we largely follow \cite{zk-polynomial}, which in turn was inspired by \cite{lie-polynomial}. We make suitable modifications to adapt to our more general setting and have made a few technical improvements in the proof. In particular, in \Cref{overviewsection}, we explicitly divide the main work of the proof into mutually independent sections \ref{thmfromproplinear}, \ref{christsection}, \ref{proptopropprop}, \ref{antichainboundary}, \ref{treesection}, \ref{liphoel}, and \ref{sec-hlm}. Some of these sections follow a similar pattern, starting with a subsection dividing the proof into further mutually independent subsections. This modularization of our proof was strongly endorsed in personal communication by the author of \cite{zk-polynomial}.

\noindent \textit{Acknowledgement.}
L.B., F.v.D., R.S., and C.T. were funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy -- EXC-2047/1 -- 390685813.
L.B. , R.S., and C.T. were also supported by SFB 1060.
A.J. is funded by the T\"UBITAK (Scientific and Technological Research Council of T\"urkiye) under Grant Number 123F122.

\chapter{Proof of Metric Space Carleson, overview}
\label{overviewsection}

This section organizes the proof of \Cref{metric-space-Carleson} into sections \ref{thmfromproplinear}, \ref{christsection}, \ref{proptopropprop}, \ref{antichainboundary}, \ref{treesection}, \ref{liphoel}, and \ref{sec-hlm}. These sections are mutually independent except for referring to the statements formulated in the present section. \Cref{thmfromproplinear} proves the main \Cref{metric-space-Carleson}, while sections \ref{christsection}, \ref{proptopropprop}, \ref{antichainboundary}, \ref{treesection}, \ref{liphoel}, and \ref{sec-hlm} each prove one proposition that is stated in the present section. The present section also introduces all definitions used across these sections.

\Cref{global-auxiliary-lemmas} proves some auxiliary lemmas that are used in more than one of the sections 3-9.

Let $a, q$ be given as in \Cref{metric-space-Carleson}.




Define
\begin{equation}\label{defineD}
D:= 2^{100 a^2}\, ,
\end{equation}
\begin{equation}\label{definekappa}
\kappa:= 2^{-10a}\,,
\end{equation}
and
\begin{equation}
    \label{defineZ}
    Z := 2^{12a}\,.
\end{equation}
Let
 $\psi:\R \to \R$ be the unique compactly supported, piece-wise linear, continuous function with corners precisely at $\frac 1{4D}$, $\frac 1{2D}$, $\frac 14$ and $\frac 12$ which satisfies
 \begin{equation}
    \label{eq-psisum}
    \sum_{s\in \mathbb{Z}} \psi(D^{-s}x)=1
\end{equation}
for all $x>0$. This function vanishes outside $[\frac1{4D},\frac 12]$, is constant one on
$[\frac1{2D},\frac 14]$, and is Lipschitz
with constant $4D$.







Let a doubling metric measure space $(X,\rho,\mu, a)$ be given.
Let a cancellative compatible collection $\Mf$ of functions on $X$ be given.
Let $o\in X$ be a point such that $\mfa(o)=0$
for all $\mfa\in \Mf$.







Let a one-sided Calder\'on--Zygmund kernel $K$ on $X$ be given so that the operator $T_*$ defined in \eqref{def-tang-unm-op}
satisfies
\eqref{nontanbound}. Let $T$ be the corresponding operator as defined in \eqref{def-main-op}.


For $s\in\mathbb{Z}$, we define
\begin{equation}\label{defks}
    K_s(x,y):=K(x,y)\psi(D^{-s}\rho(x,y))\,,
\end{equation}
so that for each $x, y \in X$ with $x\neq y$ we have
$$K(x,y)=\sum_{s\in\mathbb{Z}}K_s(x,y).$$

In \Cref{thmfromproplinear}, we prove \Cref{metric-space-Carleson}
from its finitary version, \Cref{finitary-Carleson} below. Recall
that a function from a measure space to a finite set is measurable if the pre-image of each of the elements in the range is measurable.


\begin{proposition}[finitary Carleson]
\label{finitary-Carleson}
\leanok
\lean{finitary_carleson}
\uses{discrete-Carleson, grid-existence, tile-structure, tile-sum-operator}
Let ${\sigma_1},\sigma_2\colon X\to \mathbb{Z}$ be measurable functions with finite range and ${\sigma_1}\leq \sigma_2$. Let $\tQ\colon X\to \Mf$ be a measurable function with finite range. Let $F,G$ be bounded Borel sets in $X$. Then there is a Borel set $G'$ in $X$ with $2\mu(G')\leq \mu(G)$ such that
for all Borel functions $f:X\to \C$ with $|f|\le \mathbf{1}_F$.
\begin{equation*}
    \int_{G \setminus G'} \left|\sum_{s={\sigma_1}(x)}^{{\sigma_2}(x)} \int K_s(x,y) f(y) e(\tQ(x)(y)) \, \mathrm{d}\mu(y) \right| \mathrm{d}\mu(x)
\end{equation*}
\begin{equation}
    \label{eq-linearized}
    \le \frac{2^{440a^3}}{(q-1)^4} \mu(G)^{1-\frac{1}{q}}
     \mu(F)^{\frac 1 q}\,.
\end{equation}
\end{proposition}
Let measurable functions ${\sigma_1}\leq \sigma_2\colon X\to \mathbb{Z}$ with finite range be given. Let a measurable function
$\tQ\colon X\to \Mf$ with finite range
be given.
Let bounded Borel sets $F,G$ in $X$ be given.
Let $S$ be the smallest integer such that the ranges of
$\sigma_1$ and $\sigma_2$ are contained in $[-S,S]$ and $F$ and $G$ are contained
in the ball $B(o, D^S)$.

In \Cref{christsection}, we prove \Cref{finitary-Carleson} using a
bound for a dyadic model formulated in \Cref{discrete-Carleson} below.

A grid structure $(\mathcal{D}, c, s)$ on $X$ consists of a finite collection $\mathcal{D}$ of Borel
sets in $X$ called dyadic cubes, a surjective function $s\colon \mathcal{D}\to [-S, S]$
called scale function, and a function $c:\mathcal{D}\to X$
called center function such that the five properties
\eqref{coverdyadic}, \eqref{dyadicproperty}, \eqref{coverball},
\eqref{eq-vol-sp-cube}, and \eqref{eq-small-boundary} hold.

For each dyadic cube $I$ and each $-S\le k<s(I)$ we have
\begin{equation}\label{coverdyadic}
I\subset \bigcup_{J\in \mathcal {D}: s(J)=k}J\, .
\end{equation}
Any two non-disjoint dyadic cubes $I,J$ with $s(I)\le s(J)$ satisfy
\begin{equation}\label{dyadicproperty}
I\subset J.
\end{equation}
For any $x\in B(o,D^S)$, and every $k\in[-S,S]$, there
is a dyadic cube $I$ with $s(I)=k$ and
\begin{equation}\label{coverball}
x\in I.
\end{equation}
For any dyadic cube $I$,
 \begin{equation}
        \label{eq-vol-sp-cube}
        c(I)\in B(c(I), \frac{1}{4} D^{s(I)}) \subset I \subset B(c(I), 4 D^{s(I)})\,.
    \end{equation}
For any dyadic cube $I$ and any $t$ with $tD^{s(I)} \ge D^{-S}$,
\begin{equation}
        \label{eq-small-boundary}
        % Note(Georges Gonthier): The D in the RHS can be replaced by 2.
        % We can do the same in the statement and proof of {boundary-measure}.
        \mu(\{x \in I \ : \ \rho(x, X \setminus I) \leq t D^{s(I)}\}) \le D t^\kappa \mu(I)\,.
    \end{equation}







A tile structure $(\fP,\scI,\fc,\fcc,\pc,\ps)$
for a given grid structure $(\mathcal{D}, c, s)$
is a finite set $\fP$ of elements called tiles with five maps
\begin{align*}
\scI&\colon \fP\to {\mathcal{D}}\\
\fc&\colon \fP\to \mathcal{P}(\Mf) \\
\fcc &\colon \fP\to \Mf\\
\pc &\colon \fP\to X\\
\ps &\colon \fP\to \mathbb{Z}
\end{align*}
with $\scI$ surjective and $\mathcal{P}(\Mf)$ denoting the power set of $\Mf$ such that the five properties \eqref{eq-dis-freq-cover}, \eqref{eq-freq-dyadic},
\eqref{eq-freq-comp-ball}, \eqref{tilecenter}, and
\eqref{tilescale} hold.
For each dyadic cube $I$, the restriction of the map $\Omega$ to the set
\begin{equation}\label{injective}
    \fP(I)=\{\fp: \scI(\fp) =I\}
\end{equation}
is injective
and we have the disjoint covering property (we use the union symbol with dot on top to denote a disjoint union)
\begin{equation}\label{eq-dis-freq-cover}
\tQ(X)\subset \dot{\bigcup}_{\fp\in \fP(I)}\fc(\fp).
\end{equation}
For any tiles $\fp,\fq$ with $\scI(\fp)\subset \scI(\fq)$ and $\fc(\fp) \cap \fc(\fq) \neq \emptyset$ we have
\begin{equation} \label{eq-freq-dyadic}
\fc(\fq)\subset \fc(\fp) .
\end{equation}
For each tile $\fp$,
        \begin{equation}\label{eq-freq-comp-ball}
        \fcc(\fp)\in B_{\fp}(\fcc(\fp), 0.2) \subset \fc(\fp) \subset B_{\fp}(\fcc(\fp),1)\,,
        \end{equation}
        where
\begin{equation}
    B_{\fp} (\mfa, R) := \{\mfb \in \Mf \, : \, d_{\fp}(\mfa, \mfb) < R\,\} ,
\end{equation}
 and
\begin{equation}\label{defdp}
d_{\fp} := d_{B(\pc(\fp),\frac 14 D^{\ps(\fp)})}\, .
\end{equation}
We have for each tile $\fp$
\begin{equation}\label{tilecenter}
    \pc(\fp)=c(\scI(\fp)),
\end{equation}
\begin{equation}\label{tilescale}
    \ps(\fp)=s(\scI(\fp)).
\end{equation}


\begin{proposition}[discrete Carleson]
\label{discrete-Carleson}
\leanok
\lean{discrete_carleson}
\uses{exceptional-set, forest-union, forest-complement}
Let $(\mathcal{D}, c, s)$ be a grid structure and \begin{equation*}
    (\fP,\scI,\fc,\fcc,\pc,\ps)
\end{equation*}
a tile structure for this grid structure.
Define for $\fp\in \fP$
\begin{equation}\label{defineep}
    E(\fp)=\{x\in \scI(\fp): \tQ(x)\in \fc(\fp) , {\sigma_1}(x)\le \ps(\fp)\le {\sigma_2}(x)\}
\end{equation}
and
\begin{equation}\label{definetp}
    T_{\fp} f(x)= \mathbf{1}_{E(\fp)}(x) \int K_{\ps(\fp)}(x,y) f(y) e(\tQ(x)(y)-\tQ(x)(x))\, d\mu(y).
\end{equation}
Then there exists a Borel set $G'$ with $2\mu(G') \leq \mu(G)$ such that for all Borel functions $f:X\to \C$ with $|f|\le \mathbf{1}_F$
we have
\begin{equation}
    \label{disclesssim}
   \int_{G \setminus G'} \left| \sum_{\fp \in \fP} T_{\fp} f (x) \right| \, \mathrm{d}\mu(x) \le \frac{2^{440a^3}}{(q-1)^4} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}\,.
\end{equation}
\end{proposition}









The proof of \Cref{discrete-Carleson} is done in \Cref{proptopropprop}
by a reduction to two further propositions that we state below.


Fix a grid structure $(\mathcal{D}, c, s)$ and a tile structure $(\fP,\scI,\fc,\fcc,\pc,\ps)$
for this grid structure.

We define the relation
\begin{equation}\label{straightorder}
    \fp\le \fp'
\end{equation}
 on $\fP\times \fP$ meaning
$\scI(\fp)\subset \scI(\fp')$ and
$\Omega(\fp')\subset \Omega(\fp)$.
We further define for $\lambda,\lambda' >0$
the relation
\begin{equation}\label{wiggleorder}
    \lambda \fp \lesssim \lambda' \fp'
\end{equation}
on $\fP\times \fP$ meaning
$\scI(\fp)\subset \scI(\fp')$ and
\begin{equation}
    B_{\fp'}(\fcc(\fp'),\lambda' )
    \subset B_{\fp}(\fcc(\fp),\lambda )\, .
\end{equation}



Define for a tile $\fp$ and $\lambda>0$
\begin{equation}\label{definee1}
    E_1(\fp):=\{x\in \scI(\fp)\cap G: \tQ(x)\in \fc(\fp)\}\, ,
\end{equation}
\begin{equation}\label{definee2}
    E_2(\lambda, \fp):=\{x\in \scI(\fp)\cap G: \tQ(x)\in B_{\fp}(\fcc(\fp), \lambda)\}\, .
\end{equation}



Given a subset $\fP'$ of $\fP$, we define
$\fP(\fP')$ to be the set of
all $\fp \in \fP$ such that there exist $\fp' \in \fP'$ with $\scI(\fp)\subset \scI(\fp')$. Define the densities
\begin{equation}\label{definedens1}
    {\dens}_1(\fP') := \sup_{\fp'\in \fP'}\sup_{\lambda \geq 2} \lambda^{-a} \sup_{\fp \in \fP(\fP'), \lambda \fp' \lesssim \lambda \fp}
    \frac{\mu({E}_2(\lambda, \fp))}{\mu(\scI(\fp))}\, ,
\end{equation}
\begin{equation}\label{definedens2}
    {\dens}_2(\fP') := \sup_{\fp'\in \fP'}
    \sup_{r\ge 4D^{\ps(\fp)}}
    \frac{\mu(F\cap B(\pc(\fp),r))}{\mu(B(\pc(\fp),r))}\, .
\end{equation}





An antichain is a subset $\mathfrak{A}$
of $\fP$ such that for any distinct $\fp,\fq\in \mathfrak{A}$ we do not have have $\fp\le \fq$.

The following proposition is proved in \Cref{antichainboundary}.

\begin{proposition}[antichain operator]
\label{antichain-operator}
\leanok
\lean{antichain_operator}

\uses{dens2-antichain,dens1-antichain}
For any antichain $\mathfrak{A} $ and for all $f:X\to \C$ with $|f|\le \mathbf{1}_F$ and all $g:X\to\C$ with $|g| \le \mathbf{1}_G$
\begin{equation} \label{eq-antiprop}
    |\int \overline{g(x)} \sum_{\fp \in \mathfrak{A}} T_{\fp} f(x)\, d\mu(x)|
\end{equation}
\begin{equation}
    \le \frac{2^{150a^3}}{q-1} \dens_1(\mathfrak{A})^{\frac {q-1}{8a^4}}\dens_2(\mathfrak{A})^{\frac 1{q}-\frac 12} \|f\|_2 \|g\|_2\, .
\end{equation}
\end{proposition}

Let $n\ge 0$.
An $n$-forest is a pair $(\fU, \mathfrak{T})$
where $\fU$ is a subset of $\fP$
and $\mathfrak{T}$ is a map assigning to
each $\fu\in \fU$ a nonempty set $\fT (\fu)\subset \fP$ called tree
such that the following properties
\eqref{forest1}, \eqref{forest2},
\eqref{forest3},
\eqref{forest4},
\eqref{forest5}, and
\eqref{forest6}
hold.

For each $\fu\in \fU$ and each $\fp\in \fT(\fu)$
we have
\begin{equation}\label{forest1}
4\fp\lesssim 1\fu.
\end{equation}
For each $\fu \in \fU$ and each $\fp,\fp''\in \fT(\fu)$ and $\fp'\in \fP$
we have
\begin{equation}\label{forest2}
    \fp, \fp'' \in \mathfrak{T}(\fu), \fp \leq \fp' \leq \fp'' \implies \fp' \in \mathfrak{T}(\fu).
\end{equation}
We have
\begin{equation}\label{forest3}
   \|\sum_{\fu\in \fU} \mathbf{1}_{\scI(\fu)}\|_\infty \leq 2^n\,.
\end{equation}
We have for every $\fu\in \fU$
\begin{equation}\label{forest4}
\dens_1(\fT(\fu))\le 2^{4a + 1-n}\, .
\end{equation}
We have for $\fu, \fu'\in \fU$ with $\fu\neq \fu'$ and $\fp\in \fT(\fu')$ with $\scI(\fp)\subset \scI(\fu)$ that
\begin{equation}\label{forest5}
d_{\fp}(\fcc(\fp), \fcc(\fu))>2^{Z(n+1)}\, .
\end{equation}
We have for every $\fu\in \fU$ and $\fp\in \fT(\fu)$ that
\begin{equation}\label{forest6}
B(\pc(\fp), 8D^{\ps(\fp)})\subset \scI(\fu).
\end{equation}


The following proposition is proved in \Cref{treesection}.
\begin{proposition}[forest operator]
\label{forest-operator}
\leanok
\lean{forest_operator}
\uses{forest-row-decomposition,row-bound,row-correlation,disjoint-row-support}
For any $n\ge 0$ and any $n$-forest $(\fU,\fT)$ we have for all $f: X \to \mathbb{C}$ with $|f| \le \mathbf{1}_F$ and all bounded $g$ with bounded support
$$
    | \int \overline{g(x)} \sum_{\fu\in \fU} \sum_{\fp\in \fT(\fu)} T_{\fp} f(x) \, \mathrm{d}\mu(x)|
$$
$$
    \le
    2^{432a^3}2^{-\frac{q-1}{q} n} \dens_2\left(\bigcup_{\fu\in \fU}\fT(\fu)\right)^{\frac{1}{q}-\frac{1}{2}} \|f\|_2 \|g\|_2 \,.
$$
\end{proposition}

\Cref{metric-space-Carleson} is formulated at the level of generality
for general kernels satisfying the mere H\"older regularity condition \eqref{eqkernel-y-smooth}. On the other hand, the cancellative condition \eqref{eq-vdc-cond} is a testing condition against more regular,
namely Lipschitz functions. To bridge the gap, we follow \cite{zk-polynomial} to observe a variant of \eqref{eq-vdc-cond} that we formulate
in the following proposition proved in \Cref{liphoel}.


Define
\begin{equation}
    \tau:=\frac 1a\, .
\end{equation}
Define for any open ball $B$ of radius $R$ in $X$ the $L^\infty$-normalized $\tau$-H\"older norm by
\begin{equation}
    \label{eq-Holder-norm}
    \|\varphi\|_{C^\tau(B)} = \sup_{x \in B} |\varphi(x)| + R^\tau \sup_{x,y \in B, x \neq y} \frac{|\varphi(x) - \varphi(y)|}{\rho(x,y)^\tau}\,.
\end{equation}


\begin{proposition}[Holder van der Corput]
    \label{Holder-van-der-Corput}
    \leanok
    \lean{holder_van_der_corput}
    \uses{Lipschitz-Holder-approximation}
     Let $z\in X$ and $R>0$ and set $B=B(z,R)$.
     Let $\varphi: X \to \mathbb{C}$ by
     supported on $B$ and satisfy $\|{\varphi}\|_{C^\tau(B)}<\infty$.
     Let $\mfa, \mfb \in \Mf$. Then
    \begin{equation}
        \label{eq-vdc-cond-tau-2}
        |\int e(\mfa(x)-{\mfb(x)})\varphi(x) dx|\le
         2^{8a} \mu(B) \|{\varphi}\|_{C^\tau(B)}
       (1 + d_{B}(\mfa,\mfb))^{-\frac{1}{2a^2+a^3}}
    \,.
    \end{equation}
\end{proposition}

We further formulate a classical Vitali covering result
and maximal function estimate that we need throughout several sections.
This following proposition will typically be applied to the absolute value of a complex valued function and be proved in \Cref{sec-hlm}. By a ball $B$ we mean a set $B(x,r)$ with $x\in X$
and $r>0$ as defined in \eqref{eq-define-ball}.
For a finite collection $\mathcal{B}$ of balls in $X$
and $1\le p< \infty$ define the measurable function $M_{\mathcal{B},p}u$ on $X$ by
\begin{equation}\label{def-hlm}
M_{\mathcal{B},p}u(x):=\left(\sup_{B\in \mathcal{B}} \frac{\mathbf{1}_{B}(x)}{\mu(B)}\int _{B} |u(y)|^p\, d\mu(y)\right)^\frac 1p\, .
\end{equation}
Define further $M_{\mathcal{B}}:=M_{\mathcal{B},1}$.

\begin{proposition}[Hardy--Littlewood]
\label{Hardy-Littlewood}
\leanok
\lean{measure_biUnion_le_lintegral, maximalFunction_lt_top, snorm_maximalFunction, M_lt_top,
  laverage_le_M, snorm_M_le}
\uses{layer-cake-representation,covering-separable-space}
   Let $\mathcal{B}$ be a finite collection of balls in $X$.
If for some $\lambda>0$ and some measurable function $u:X\to [0,\infty)$ we have
\begin{equation}\label{eq-ball-assumption}
\int_{B} u(x)\, d\mu(x)\ge \lambda \mu(B)
\end{equation}
   for each $B\in \mathcal{B}$,
   then
   \begin{equation}\label{eq-besico}
\lambda \mu(\bigcup \mathcal{B}) \le 2^{2a}\int_X u(x)\, d\mu(x)\, .
\end{equation}
For every measurable function $v$
and $1\le p_1<p_2$ we have
\begin{equation}\label{eq-hlm}
    \|M_{\mathcal{B},p_1} v\|_{p_2}\le 2^{2a}\frac{p_2}{p_2-p_1} \|v\|_{p_2}\, .
\end{equation}
Moreover, given any measurable bounded function $w: X \to \C$ there exists a measurable function $Mw: X \to [0, \infty)$ such that the following \eqref{eq-ball-av} and \eqref{eq-hlm-2} hold. For each ball $B \subset X$ and each $x \in B$
\begin{equation}
    \label{eq-ball-av}
    \frac{1}{\mu(B)} \int_{B} |w(y)| \, \mathrm{d}\mu(y) \le Mw(x)
\end{equation}
and for all $1 \le p_1 < p_2 \le \infty$
\begin{equation}
    \label{eq-hlm-2}
    \|M(w^{p_1})^{\frac{1}{p_1}}\|_{p_2} \le 2^{4a} \frac{p_2}{p_2-p_1}\|w\|_{p_2}\,.
\end{equation}

\end{proposition}

This completes the overview of the proof of \Cref{metric-space-Carleson}.

\section{Auxiliary lemmas}
\label{global-auxiliary-lemmas}
We close this section by recording some auxiliary lemmas about the objects defined in \Cref{overviewsection}, which will be used in multiple sections to follow.

First, we record an estimate for the metrical entropy numbers of balls in the space $\Mf$ equipped with any of the metrics $d_B$, following from the doubling property \eqref{thirddb}.

\begin{lemma}[ball metric entropy]
    \label{ball-metric-entropy}
    \leanok
    \lean{Î˜.mk_le_of_le_dist}
    Let $B' \subset X$ be a ball. Let $r > 0$, $\mfa \in \Mf$ and $k \in \mathbb{N}$. Suppose that $\mathcal{Z} \subset B_{B'}(\mfa, r2^k)$ satisfies that for all $z, z' \in \mathcal{Z}$ with $z \ne z'$, we have $d_{B'}(z,z') \ge r$. Then
    $$
        |\mathcal{Z}| \le 2^{ka}\,.
    $$
\end{lemma}

\begin{proof}
    By applying property \eqref{thirddb} $k$ times, we obtain a collection $\mathcal{Z}' \subset \Mf$ with $|\mathcal{Z}'| = 2^{ka}$ and
    $$
        B_{B'}(\mfa,r2^k) \subset \bigcup_{z' \in \mathcal{Z}'} B_{B'}(z', \frac{r}{2})\,.
    $$
    Then each $z \in \mathcal{Z}$ is contained in one of the balls $B(z', \frac{r}{2})$, but by the separation assumption no such ball contains more than one element of $\mathcal{Z}$. Thus $|\mathcal{Z}| \le |\mathcal{Z}'| = 2^{ka}$.
\end{proof}

The next lemma concerns monotonicity of the metrics $d_{B(c(I), \frac 14 D^{s(I)})}$ with respect to inclusion of cubes $I$ in a grid.

\begin{lemma}[monotone cube metrics]
    \label{monotone-cube-metrics}
    \leanok
    \lean{ð““.dist_mono, ð““.dist_strictMono}
    Let $(\mathcal{D}, c, s)$ be a grid structure. Denote for cubes $I \in \mathcal{D}$
    $$
        I^\circ := B(c(I), \frac{1}{4} D^{s(I)})\,.
    $$
    Let $I, J \in \mathcal{D}$ with $I \subset J$.
    Then for all $\mfa, \mfb \in\Mf$ we have
    $$
        d_{I^\circ}(\mfa, \mfb) \le d_{J^\circ}(\mfa, \mfb)\,,
    $$
    and if $I \ne J$ then we have
    $$
        d_{I^\circ}(\mfa, \mfb) \le 2^{-95a} d_{J^\circ}(\mfa, \mfb)\,.
    $$
\end{lemma}

\begin{proof}
    If $s(I) \ge s(J)$ then \eqref{dyadicproperty} and the assumption $I\subset J$ imply $I = J$. Then the lemma holds by reflexivity.

    If $s(J) \ge s(I)+1$, then using the monotonicity property \eqref{monotonedb}, \eqref{defineD} and \eqref{seconddb}, we get
    \begin{equation}
    \label{eq-dIJ-est}
        d_{I^\circ}(\mfa, \mfb) \le d_{B(c(I), 4 D^{s(I)})}(\mfa, \mfb) \le 2^{-100a} d_{B(c(I), 4D^{s(J)})}(\mfa, \mfb)\,.
    \end{equation}
    Using \eqref{eq-vol-sp-cube}, together with the inclusion $I \subset J$, we obtain
    $$
        c(I) \in I \subset J \subset B(c(J), 4 D^{s(J)})
    $$
    and consequently by the triangle inequality
    $$
        B(c(I), 4 D^{s(J)}) \subset B(c(J), 8 D^{s(J)})\,.
    $$
    Using this together with the monotonicity property \eqref{monotonedb} and \eqref{firstdb} in \eqref{eq-dIJ-est}, we obtain
    \begin{align*}
        d_{I^\circ}(\mfa, \mfb) &\le 2^{-100a} d_{B(c(J), 8D^{s(J)})}(\mfa, \mfb)\\
        &\le 2^{-100a + 5a} d_{B(c(J), \frac{1}{4}D^{s(J)})}(\mfa, \mfb)\\
        &= 2^{-95a}d_{J^\circ}(\mfa, \mfb)\,.
    \end{align*}
    This proves the second inequality claimed in the Lemma, from which the first follows since $a \ge 4$ and hence $2^{-95a} \le 1$.
\end{proof}

We also record the following basic estimates for the kernels $K_s$.

\begin{lemma}[kernel summand]
\label{kernel-summand}
\leanok
\lean{dist_mem_Icc_of_Ks_ne_zero, norm_Ks_le, norm_Ks_sub_Ks_le}
    Let $-S\le s\le S$ and $x,y,y'\in X$.
    If $K_s(x,y)\neq 0$, then we have
    \begin{equation}\label{supp-Ks}
      \frac{1}{4} D^{s-1} \leq \rho(x,y) \leq \frac{1}{2} D^s\, .
    \end{equation}
    We have
    \begin{equation}
       \label{eq-Ks-size}
        |K_s(x,y)|\le \frac{2^{102 a^3}}{\mu(B(x, D^{s}))}\,
    \end{equation}
    and
    \begin{equation}
        \label{eq-Ks-smooth}
        |K_s(x,y)-K_s(x, y')|\le \frac{2^{150a^3}}{\mu(B(x, D^{s}))}
        \left(\frac{ \rho(y,y')}{D^s}\right)^{\frac 1a}\,.
    \end{equation}
\end{lemma}

\begin{proof}
    By Definition \eqref{defks}, the function $K_s$ is the product of
    $K$ with a function which is supported in the set of all
    $x,y$ satisfying \eqref{supp-Ks}. This proves
    \eqref{supp-Ks}.

    Using \eqref{eqkernel-size} and the lower bound in \eqref{supp-Ks}
    we obtain
    \begin{equation}
        |K_s(x,y)|\le \frac{2^{a^3}}{\mu(B(x,\frac 14 D^{s-1}))}
    \end{equation}
    Using $D=2^{100a^2}$
    and the doubling property \eqref{doublingx} $2 +100a^2$ times estimates
    the last display by
    \begin{equation}
        \label{eq-Ks-aux}
        \le \frac{2^{2a+101a^3}}{\mu(B(x, D^{s}))}\, .
    \end{equation}
    Using $a\ge 4$ proves \eqref{eq-Ks-size}.

    If $2\rho(y,y') \le \rho(x,y)$, we obtain similarly with \eqref{eqkernel-y-smooth} and the lower bound in
    \eqref{supp-Ks}
    \begin{equation}
        |K_s(x,y)-K_s(x, y')|\le \frac{2^{a^3}}{\mu(B(x, \frac 14 D^{s-1}))}
        \left(\frac{ \rho(y,y')}{\frac 14 D^{s-1}}\right)^{\frac 1a}\,.
    \end{equation}
    As above, this is estimated by
    \begin{equation}
       \le \frac{4D 2^{2a+101a^3}}{\mu(B(x, D^{s}))}
        \left(\frac{ \rho(y,y')}{D^{s}}\right)^{\frac 1a}
         = \frac{2^{2+2a+100a^2+101a^3}}{\mu(B(x, D^{s}))}
        \left(\frac{ \rho(y,y')}{D^{s}}\right)^{\frac 1a}\,.
    \end{equation}
    Using $a\ge 4$, this proves \eqref{eq-Ks-smooth} in the case $2\rho(y,y') \le \rho(x,y)$. If $2\rho(y,y') > \rho(x,y)$, then by the lower bound in \eqref{supp-Ks} $2\rho(y,y') > \frac{1}{8}D^s$. Then \eqref{eq-Ks-smooth} follows from the triangle inequality, \eqref{eq-Ks-size} and $a \ge 4$.
\end{proof}


\chapter{Proof of Metric Space Carleson}
\label{thmfromproplinear}


Let Borel sets $F$, $G$ in $X$ be given.
We have that
\begin{equation}
    X=\bigcup_{R>0}B(o,R),
\end{equation} because every point of $X$
has finite distance from $o$.
\begin{lemma}[R truncation]
\label{R-truncation}
 \uses{S-truncation}
For all integers $R>0$
$$
    \int \mathbf{1}_{G\cap B(o,R)}
    \sup_{1/R<R_1<R_2<R}\sup_{\mfa\in\Mf}
    \left| T_{R_1,R_2,\mfa} \mathbf{1}_{F}(x) \right|\, d\mu(x)
$$
\begin{equation} \label{Rcut}
    \leq \frac{2^{450a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}},
\end{equation}
where
\begin{equation}\label{TRR}
    T_{R_1,R_2,\mfa} f(x)=
    \int_{R_1 < \rho(x,y) < R_2} K(x,y) f(y) e(\mfa(y)) \, \mathrm{d}\mu(y) .
\end{equation}
\end{lemma}

We first show how \Cref{R-truncation} implies \Cref{metric-space-Carleson}. As $R$ tends to $\infty$, the integrand of the left-hand side of \eqref{Rcut} grows monotonically toward the integrand of the left-hand side of \eqref{resweak} for all $x$. By Lebesgue's monotone convergence theorem, the left-hand side of \eqref{Rcut} converges to the left-hand side of \eqref{resweak}. This verifies \Cref{metric-space-Carleson}.

It remains to prove \Cref{R-truncation}. Fix an integer $R>0$. By replacing $G$ with $G\cap B(o,R)$ if necessary, it suffices to show \eqref{Rcut} under the assumption that $G$ is contained in $B(o,R)$. We make this assumption. For every $x\in G$, the domain of integration in \eqref{TRR} is contained in $B(o,2R)$. By replacing $F$ with $F\cap B(o,2R)$ if necessary, it suffices to show \eqref{Rcut} under the assumption that $F$ is contained in $B(o,2R)$. We make this assumption.

Using the definition \eqref{defks} of $K_s$ and the partition of unity \eqref{eq-psisum}, we express \eqref{TRR} as the sum of
\begin{equation}\label{middles}
{T}_{1,s_1,s_2,\mfa}f(x):=\sum_{s_1 \le s\le s_2}
\int K_s(x,y) f(y) e(\mfa(y)) \, \mathrm{d}\mu(y)
\end{equation}
and
\begin{equation}\label{boundarys}
\sum_{s=s_1-2,s_1-1, s_2+1, s_2+2}
\int_{R_1 < \rho(x,y) < R_2} K_s(x,y) f(y) e(\mfa(y)) \,
 \mathrm{d}\mu(y),
\end{equation}
where $s_1$ is the smallest integer such that $D^{s_1-2}R_2>\frac 1{4D}$ and $s_2$ is the largest integer such that $D^{s_2+2}R_1<\frac 12$. We restrict the summation index $s$ by excluding summands with $s<s_1-2$ or $s>s_2+2$ because for these summands, the function $K_s$ vanishes on the domain of integration. We also omit the restriction in the integral for the summands in \eqref{middles} because in these summands, the support of $K_s$ is contained in the set described by this restriction.



We apply the triangle inequality and estimate the versions of \eqref{Rcut} separately with $T_{R_1,R_2,\mfa}$ replaced by \eqref{middles} and by each summand of \eqref{boundarys}. To handle the case \eqref{middles}, we employ the following lemma. Here, we utilize the fact that if $\frac 1R\le R_1\le R_2\le R$, then $s_1$ and $s_2$ as in \eqref{middles} are in an interval $[-S,S]$ for some sufficiently large $S$ depending on $R$.


\begin{lemma}[S truncation]
\label{S-truncation}
\uses{Hardy-Littlewood,kernel-summand,finitary-S-truncation}
For all integers $S>0$
$$
    \int \mathbf{1}_{G}(x)
    \max_{-S<s_1\le s_2<S}\sup_{\mfa\in\Mf}
    \left| T_{1, s_1,s_2,\mfa} \mathbf{1}_{F}(x) \right|\, d\mu(x)
$$
\begin{equation} \label{Scut}
    \leq \frac{2^{446a^3}}{(q-1)^5} \mu(G)^{1 - \frac{1}{q}} \mu(F)^{\frac{1}{q}},
\end{equation}
where $T_{1, s_1,s_2,\mfa}$ is defined in \eqref{middles}.
\end{lemma}

To reduce \Cref{R-truncation} to \Cref{S-truncation}, we need estimates for the summands in \eqref{boundarys}. Using \Cref{kernel-summand}, we obtain for arbitrary $s$ the inequality
\begin{multline}
\left|\int_{R_1 < \rho(x,y) < R_2} K_s(x,y) f(y) e(\mfa(y)) \, \mathrm{d}\mu(y)\right|\\
\leq \frac{2^{102 a^3}}{\mu(B(x, D^{s}))}
 \int_{B(x, D^s)} \mathbf{1}_F(y) \, \mathrm{d}\mu(y)
\leq 2^{102 a^3} M\mathbf{1}_F(x),
\end{multline}
where $M\mathbf{1}_F$ is as defined in \Cref{Hardy-Littlewood}.
Now, the left-hand side of \eqref{Rcut}, with $T_{R_1,R_2,\mfa}$ replaced by a summand of \eqref{boundarys}, can be estimated using H\"older's inequality and \Cref{Hardy-Littlewood} by
$$
    2^{102 a^3}\int \mathbf{1}_{G}(x) M\mathbf{1}_F(x)\, d\mu(x)
    \leq \frac{2^{102 a^3+4a}q}{q-1}\mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}\,.
$$
Applying the triangle inequality to estimate the left-hand side of \eqref{Rcut} by contributions from the summands in \eqref{middles} and \eqref{boundarys}, using \Cref{S-truncation} to control the first term, and the above to estimate the contribution from the four summands in \eqref{boundarys}, combined with $a\geq 4$ and $q < 2$, completes the reduction of \Cref{R-truncation} to \Cref{S-truncation}.

It remains to prove \Cref{S-truncation}. Fix $S>0$.
\begin{lemma}[finitary S truncation]
\label{finitary-S-truncation}
\uses{linearized-truncation}
For all finite sets $\tilde{\Mf}\subset \Mf$
$$
    \int \mathbf{1}_{G}(x)
    \max_{-S<s_1\le s_2<S}\sup_{\mfa\in\tilde{\Mf}}
    \left| T_{1, s_1,s_2,\mfa} \mathbf{1}_{F}(x) \right|\, d\mu(x)
$$
\begin{equation} \label{Sqcut}
\leq \frac{2^{445a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}\,.
\end{equation}
\end{lemma}

We reduce \Cref{S-truncation} to \Cref{finitary-S-truncation}.
By the Lebesgue monotone convergence theorem,
applied to an increasing sequence of finite sets $\tilde{\Mf}$, inequality \eqref{Sqcut}
continues to hold for countable $\tilde{\Mf}$.

Let $\epsilon=\frac{1}{2S+1}$. Pick some $\mfa_0 \in \Mf$.
For $k \ge 0$, let the set $\tilde{\Mf}_k$ be a subset of $B_{B(o,2R)}(\mfa_0, k)$ of maximal size, such that for all $\mfa, \mfb \in \tilde{\Mf}_k$, it holds that $d_{B(o, 2R)}(\mfa, \mfb) \ge \epsilon$. Such a set exists, since by \Cref{ball-metric-entropy} there exists an upper bound for the size of such subsets in $B_{B(o, 2R)}(\mfa_0, k)$. Define
$$
    \tilde{\Mf} := \bigcup_{k \in \mathbb{N}} \tilde{\Mf}_k\,.
$$
Then the set $\tilde{\Mf}$ is at most countable, and it has the property that for any $\mfb \in \Mf$, there exists $\mfa \in \tilde{\Mf}$ with
$$
    d_{B(o, 2R)}(\mfb, \mfa) < \epsilon\,.
$$

For every $\mfa\in \Mf$, we have
\begin{equation}
\left| T_{1, s_1,s_2,\mfa} \mathbf{1}_{F}(x)\right|=
\left|\sum_{s_1 \le s\le s_2}
\int K_s(x,y) f(y) e(\mfa(y)-{\mfa(x)}) \, \mathrm{d}\mu(y)\right|
\end{equation}
Moreover, there is a $\tilde{\mfa}
\in \tilde{\Mf}$ with $d_{B(o,2R)}(\mfa,\tilde{\mfa})\le \epsilon$. Hence,
\begin{align*}
    &\left| T_{1, s_1,s_2,\mfa} \mathbf{1}_{F}(x)\right|-\left|T_{1, s_1,s_2,\tilde{\mfa}} \mathbf{1}_{F}(x) \right|\\
  &\leq\sum_{s_1 \le s\le s_2} \int |K_s(x,y)| \mathbf{1}_F(y) |e(\mfa(y)-{\mfa(x)})-e({\tilde{\mfa}(y)}-{\tilde{\mfa}(x)})| \, \mathrm{d}\mu(y)\\
    &\leq \sum_{s_1 \le s\le s_2} \epsilon \int |K_s(x,y)| \mathbf{1}_F(y) \, \mathrm{d}\mu(y)
\end{align*}
Using \Cref{kernel-summand}, we can estimate the above expression by
\begin{align*}
    &\sum_{s_1 \le s\le s_2} \frac{2^{102 a^3}}{\mu(B(x, D^{s}))}
\epsilon \int_{B(x, D^s)} \mathbf{1}_F(y) \, \mathrm{d}\mu(y)\\
    &\leq (2S+1)\epsilon 2^{102 a^3} M\mathbf{1}_F(x)\le 2^{102 a^3}M\mathbf{1}_F(x)
\end{align*}
We estimate the left-hand-side of \eqref{Scut} by
the sum of left-hand-side of \eqref{Sqcut} and
\begin{align*}
    &\int \mathbf{1}_{G}(x)
\max_{-S<s_1\le s_2<S}\sup_{\mfa\in {\Mf}}
\inf_{\tilde{\mfa}\in\tilde{\Mf}}
(| T_{1, s_1,s_2,\mfa}|-|T_{1, s_1,s_2,\tilde{\mfa}} |)\mathbf{1}_{F}(x)\, d\mu(x)\,,\\
\end{align*}
which, as we have just shown, is estimated by
\begin{align*}
     &2^{102 a^3}\int \mathbf{1}_{G}(x)
M\mathbf{1}_{F}(x)\, d\mu(x).
\end{align*}
By H\"older's inequality and \Cref{Hardy-Littlewood}
 (more precisely, \eqref{eq-hlm-2} with $p=q$), the above is no greater than
\begin{align*}
&\frac{2^{102 a^3+4a}q}{q-1} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}.
\end{align*}
Combining this with \Cref{finitary-S-truncation} and the fact that
\begin{align*}
    \frac{2^{102 a^3+4a}q}{q-1}\leq \frac{2^{445a^3}}{(q-1)^5}
\end{align*}
proves \Cref{S-truncation}.

It remains to prove \Cref{finitary-S-truncation}.
Fix a finite set
$\tilde{\Mf}$.
\begin{lemma}[linearized truncation]
\label{linearized-truncation}
\uses{finitary-Carleson}
Let $\sigma_1,\sigma_2\colon X\to \mathbb{Z}$ be measurable functions with finite range
$[-S,S]$ and $\sigma_1\leq \sigma_2$.
Let $\tQ\colon X\to {\tilde{\Mf}}$ be a measurable function. Then we have
\begin{equation} \label{Sqlin}
    \int \mathbf{1}_{G}(x)
    \left| {T}_{2,\sigma_1,\sigma_2,\tQ}\mathbf{1}_F(x)\right|\, d\mu(x)
    \le \frac{2^{445a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}},
\end{equation}
with
\begin{equation}\label{middles1}
    {T}_{2,\sigma_1,\sigma_2,\tQ}f(x)=\sum_{\sigma_1(x) \le s\le \sigma_2(x)}
    \int K_s(x,y) f(y) e(\tQ(x)(y) - \tQ(x)(x)) \, \mathrm{d}\mu(y)\,.
\end{equation}
\end{lemma}

We reduce \Cref{finitary-S-truncation} to
\Cref{linearized-truncation}.
For each $x$, let $\sigma_1(x)$ be the
minimal element $s'\in [-S,S]$ such that
\[\max_{s'\leq s_2<S}\max_{\mfa\in\tilde{\Mf}}
| T_{1, s',s_2,\mfa} \mathbf{1}_{F}(x)|
=
\max_{-S<s_1\le s_2<S}\max_{\mfa\in\tilde{\Mf}}
| {T}_{1, s_1,s_2,\mfa} \mathbf{1}_{F}(x)|:={T}_{1, x}.
\]
Similarly, let ${\sigma}_2(x)$ be the
minimal element $s''\in [-S,S]$ such that
\[\max_{\mfa\in\tilde{\Mf}}
| {T}_{1, {\sigma}_1(x), s'',\mfa} \mathbf{1}_{F}(x)|
=
{T}_{1,x}\,.
\]
Finally, choose a total order of the finite set $\tilde{\Mf}$
and let $\tQ(x)$ be the minimal element $\mfa$ with respect to this order such that
\[
| {T}_{1, {\sigma}_1(x),{\sigma}_2(x),\mfa} \mathbf{1}_{F}(x)| = {T}_{1,x}\,.
\]
With these choices, and noting that
\begin{equation*}
{T}_{1, {\sigma}_1(x),{\sigma}_2(x),\tQ(x)} \mathbf{1}_{F}(x)={T}_{2, {\sigma}_1,{\sigma}_2,\tQ} \mathbf{1}_{F}(x),
\end{equation*}
we conclude that the left-hand side of \eqref{Sqcut}
and \eqref{Sqlin} are equal. Thus, \Cref{finitary-S-truncation}
follows from \Cref{linearized-truncation}.

It remains to prove \Cref{linearized-truncation}.
Fix $\sigma_1$, $\sigma_2$,
and $\tQ$ as in the lemma.
Applying \Cref{finitary-Carleson} recursively, we obtain
a sequence of sets $G_n$ with $G_0=G$ and,
for each $n\ge 0$, $\mu(G_{n})\le 2^{-n} \mu(G)$ and
\begin{equation*}
    \int \mathbf{1}_{G_{n}\setminus G_{n+1}}(x)
    \left| {T}_{2,\sigma_1,\sigma_2, \tQ} \mathbf{1}_{F}(x) \right|\, d\mu(x)
\end{equation*}
\begin{equation}
    \le \frac{2^{440a^3}}{(q-1)^4} \mu(G_n)^{1 - \frac{1}{q}} \mu(F)^{\frac{1}{q}},
\end{equation}
Adding the first $n$ of these inequalities, we obtain by bounding a geometric series
    \begin{equation} \label{Sqcut2}
    \int \mathbf{1}_{G\setminus G_{n}}(x)
\left| {T}_{2,\sigma_1,\sigma_2, \tQ}\mathbf{1}_F(x) \right|\, d\mu(x)
\le \frac{2^{445a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}.
\end{equation}
As the integrand is bounded by
\begin{equation}\mathbf{1}_{G\setminus G_{n}}(x)
\sum_{-S<s_1\le s_2<S}\sum_{\mfa\in\tilde{\Mf}}
\left| {T}_{1,s_1, s_2, \mfa} \mathbf{1}_{F}(x) \right|,
\end{equation}
which by interchange of summation and integration is seen to be integrable, we obtain by Lebesgue's dominated convergence theorem
 \begin{equation} \label{Sqcut3}
    \int \mathbf{1}_{G}(x)
\left| {T}_{2,\sigma_1,\sigma_2, \tQ}\mathbf{1}_F(x) \right|\, d\mu(x)
\le \frac{2^{445a^3}}{(q-1)^5} \mu(G)^{1-\frac{1}{q}} \mu(F)^{\frac{1}{q}}.
\end{equation}



This completes the proof of \Cref{linearized-truncation}
and thus \Cref{metric-space-Carleson}.

\chapter{Proof of Finitary Carleson}
\label{christsection}

To prove Proposition
\ref{finitary-Carleson}, we already fixed in \Cref{overviewsection}
measurable functions ${\sigma_1},\sigma_2, \tQ$ and Borel sets $F,G$. We have also
defined $S$ to be the smallest
integer such that the ranges of
$\sigma_1$ and $\sigma_2$ are contained in $[-S,S]$ and $F$ and $G$ are contained
in the ball $B(o, D^S)$.


The proof of the next lemma is done in \Cref{subsecdyadic},
following the construction of dyadic cubes in \cite[\S 3]{christ1990b}.

\begin{lemma}[grid existence]
\label{grid-existence}
\leanok
\lean{grid_existence}
\uses{counting-balls,boundary-measure} There exists a grid structure $(\mathcal{D}, c,s)$.
\end{lemma}




The next lemma, which we prove in \Cref{subsectiles}, should be compared
with the construction in \cite[Lemma 2.12]{zk-polynomial}.

\begin{lemma}[tile structure]
\label{tile-structure}
\leanok
\lean{tile_existence}
 \uses{ball-metric-entropy,frequency-ball-cover,disjoint-frequency-cubes,frequency-cube-cover}
    For a given grid structure $(\mathcal{D}, c,s)$, there exists a tile structure
    $(\fP,\scI,\fc,\fcc,\pc,\ps)$.
\end{lemma}

Choose a grid structure $(\mathcal{D}, c,s)$ with \Cref{grid-existence} and a tile structure for this
grid structure $(\fP,\scI,\fc,\fcc,\pc,\ps)$ with \Cref{tile-structure}.
Applying \Cref{discrete-Carleson}, we obtain a Borel set $G'$ in $X$ with $2\mu(G')\leq \mu(G)$ such that for all Borel functions $f:X\to \C$ with $|f|\le \mathbf{1}_F$
we have \eqref{disclesssim}.

\begin{lemma}[tile sum operator]
\label{tile-sum-operator}
\leanok
\lean{tile_sum_operator, integrable_tile_sum_operator}
We have for all $x\in G\setminus G'$
\begin{equation}\label{eq-sump}
    \sum_{\fp\in \fP}T_{\fp} f(x)= \sum_{s=\sigma_1(x)}^{\sigma_2(x)}
    \int K_{s}(x,y) f(y) e(\tQ(x)(y)-\tQ(x)(x))\, d\mu(y).
\end{equation}
\end{lemma}
\begin{proof}
Fix $x\in G\setminus G'$.
Sorting the tiles $\fp$ on the left-hand-side of \eqref{eq-sump} by the value $\ps(\fp)\in [-S,S]$,
it suffices to prove for every $-S\le s\le S$ that
\begin{equation}\label{outsump}
    \sum_{\fp\in \fP: \ps(\fp)=s}T_{\fp} f(x)=0
\end{equation}
 if $s\not\in [\sigma_1(x), \sigma_2(x)]$ and
\begin{equation}\label{insump}
    \sum_{\fp\in \fP: \ps(\fp)=s}T_{\fp} f(x)=
    \int K_{s}(x,y) f(y) e(\tQ(x)(y) - \tQ(x)(x))\, d\mu(y).
\end{equation}
if $s\in [\sigma_1(x),\sigma_2(x)]$.
If $s\not\in [\sigma_1(x), \sigma_2(x)]$, then by definition of $E(\fp)$ we have
$x\not\in E(\fp)$ for any $\fp$ with $\ps(\fp)=s$ and thus $T_{\fp} f(x)=0$. This proves
\eqref{outsump}.

Now assume $s\in [\sigma_1(x),\sigma_2(x)]$.
By \eqref{coverball} and $G\subset B(o,D^S)$, there is at least
one $I\in \mathcal{D}$ with $s(I)=s$ and $x\in I$.
By \eqref{dyadicproperty}, this $I$ is unique. By \eqref{eq-dis-freq-cover}, there is precisely one $\fp\in \fP(I)$ such that
$\tQ(x)\in \fc(\fp)$. Hence there is precisely one $\fp\in \fP$ with $\ps(\fp)=s$ such that
$x\in E(\fp)$. For this $\fp$, the value $T_{\fp}(x)$ by its definition in \eqref{definetp}
equals the right-hand side of \eqref{insump}. This proves the lemma.
\end{proof}

We use this to prove \Cref{finitary-Carleson}.
\begin{proof}[Proof of \Cref{finitary-Carleson}]
\proves{finitary-Carleson}
We now estimate with \Cref{tile-sum-operator} and \Cref{discrete-Carleson}
\begin{equation}
 \int_{G \setminus G'} \left|\sum_{s={\sigma_1}(x)}^{{\sigma_2}(x)} \int K_s(x,y) f(y) e(\tQ(x)(y)) \, \mathrm{d}\mu(y)\right| \mathrm{d}\mu(x)
\end{equation}
\begin{equation}
 =\int_{G \setminus G'} \left|\sum_{s={\sigma_1}(x)}^{{\sigma_2}(x)} \int K_s(x,y) f(y) e(\tQ(x)(y) - \tQ(x)(x))\mathrm{d}\mu(y)\right| \mathrm{d}\mu(x)
\end{equation}
\begin{equation}
 =\int_{G \setminus G'} \left|\sum_{\fp\in \fP}T_{\fp} f(x)\right| \mathrm{d}\mu(x)
 \le \frac{2^{440a^3}}{(q-1)^4} \mu(G)^{1 - \frac{1}{q}} \mu(F)^{\frac{1}{q}} \,.
\end{equation}
This proves \eqref{eq-linearized} for the chosen set $G'$ and arbitrary $f$ and thus completes the proof of Proposition
\ref{finitary-Carleson}.
\end{proof}


\section{Proof of Grid Existence Lemma}
\label{subsecdyadic}

We begin with the construction of the centers of the dyadic cubes.
\begin{lemma}[counting balls]
\label{counting-balls}
Let $-S\le k\le S$. Consider $Y\subset X$ such that for any $y\in Y$, we have
\begin{equation}\label{ybinb}
  y\in B(o,4D^S-D^k),
\end{equation}
furthermore, for any $y'\in Y$ with $y\neq y'$, we have
\begin{equation} \label{eq-disj-yballs}
    B(y,D^k)\cap B(y',D^k)=\emptyset.
\end{equation}
Then the cardinality of $Y$ is bounded by
\begin{equation}\label{boundY}
    |Y|\le 2^{3a + 200Sa^3}\, .
\end{equation}
\end{lemma}


\begin{proof}
Let $k$ and $Y$ be given. By applying the doubling property \eqref{doublingx} inductively, we have for each integer $j\ge 0$
\begin{equation}\label{jballs}
    \mu(B(y,2^{j}D^k))\le 2^{aj} \mu(B(y,D^k))\, .
\end{equation}
Since $X$ is the union of the balls $B(y,2^{j}D^k)$ and $\mu$ is not zero, at least one of the balls $B(y,2^{j}D^k)$ has positive measure, thus $B(y,D^k)$ has positive measure.

Applying \eqref{jballs} for $j' = \ln_2(8D^{2S}) = 3 + 2S \cdot 100a^2$ by \eqref{defineD}, using $-S\le k\le S$, $y\in B(o,4D^S)$, and the triangle inequality, we have
\begin{equation}
    B(o, 4D^S) \subset B(y, 8D^S) \subset B(y,2^{j'}D^k) \, .
\end{equation}
Using the disjointedness of the balls in \eqref{eq-disj-yballs}, \eqref{ybinb}, and the triangle inequality for $\rho$, we obtain
\begin{equation}
|Y|\mu(B(o,4D^S))\le 2^{j'a}\sum_{y\in Y}\mu(B(y,D^k))
\end{equation}
\begin{equation}
\le
2^{j'a}\mu(\bigcup_{y\in Y}B(y,D^k))
\le 2^{j'a}\mu(o,4D^S)\, .
\end{equation}
As $\mu(o,4D^S)$ is not zero, the lemma follows.
\end{proof}

For each $-S\le k\le S$, let $Y_k$ be a set of
maximal cardinality in $X$ such that $Y=Y_k$ satisfies
the properties \eqref{ybinb} and \eqref{eq-disj-yballs}.
By the upper bound of \Cref{counting-balls}, such a set exists.

For each $-S\le k\le S$, choose an enumeration of the points in the finite set $Y_k$ and thus a total
order $<$ on $Y_{k}$.

\begin{lemma}[cover big ball]
\label{cover-big-ball}
  For each $-S\le k\le S$, the ball
  $B(o, 4D^S-D^k)$ is contained
  in the union of the balls $B(y,2D^k)$ with $y\in Y_k$.
\end{lemma}

\begin{proof}
Let $x$ be any point of $B(o, 4D^S-D^k)$. By maximality of $|Y_k|$, the ball
$B(x, D^k)$ intersects one of the balls
$B(y, D^k)$ with $y\in Y_k$. By the triangle
inequality, $x\in B(y,2D^k)$.
\end{proof}

Define the set
\begin{equation}
    \mathcal{C}:= \{(y,k): -S\le k\le S, y\in Y_k\}\,
\end{equation}
We totally order the set $\mathcal{C}$ lexicographically by setting
$(y,k)<(y',k')$ if $k< k'$ or both $k=k'$ and $y<y'$.
In what follows, we define recursively in the sense of this order a function
\begin{equation}
    (I_1,I_2,I_3): \mathcal{C}\to \mathcal{P}(X)\times \mathcal{P}(X)\times \mathcal{P}(X)\, .
\end{equation}


Assume the sets ${I}_j(y',k')$ have already been defined for $j=1,2,3$ if $k'<k$ and if $k=k'$ and $y'<y$.




If $k=-S$, define for $j\in \{1,2\}$ the set
${I}_j(y,k)$ to be $B(y,jD^{-S})$.
If $-S<k$, define for $j\in \{1,2\}$
and $y\in Y_k$ the set ${I}_j(y,k)$ to be
\begin{equation}\label{defineij}
\bigcup\{I_3(y',k-1):
y'\in Y_{k-1}\cap B(y,jD^k)\}.
\end{equation}
Define for {$-S\leq k\leq S$} and $y\in Y_k$
\begin{equation}\label{definei3}
I_3(y,k):={I_1}(y,k)\cup \left[{I_2}(y,k)\setminus \left[X_k\cup \bigcup\{I_3(y',k):y'\in Y_{k}, y'<y\})\right]\right]
\end{equation}
with
\begin{equation}
      X_{k}:=\bigcup\{I_1(y', k):y'\in Y_{k}\}.
\end{equation}


\begin{lemma}[basic grid structure]
\label{basic-grid-structure}
\uses{cover-big-ball}
   For each $-S\le k\le S$ and $1\le j\le 3$
   the following holds.

   If $j\neq 2$ and for some $x\in X$ and $y_1,y_2\in Y_k$ we have
   \begin{equation}\label{disji}
       x\in I_j(y_1,k)\cap I_j(y_2,k),
   \end{equation}
then $y_1=y_2$.

   If $j\neq 1$, then
\begin{equation}\label{unioni}
B(o, 4D^S-2D^k)\subset \bigcup_{y\in Y_k} I_j(y,k)\, .
\end{equation}
We have for each $y\in Y_k$,
   \begin{equation}\label{squeezedyadic}
    B(y,\frac 12 D^k) \subset I_3(y,k)\subset
     B(y,4D^k).
\end{equation}



\end{lemma}

\begin{proof}
We prove these statements simultaneously by induction on the ordered set of pairs $(y,k)$. Let $-S\le k\le S$.

We first consider \eqref{disji} for $j=1$. If $k=-S$, disjointedness of the sets $I_1(y,-S)$ follows by definition of $I_1$ and $Y_k$. If $k>-S$, assume $x$ is in $I_1(y_m,k)$ for $m=1,2$. Then, for $m=1,2$, there is $z_m\in Y_{k-1}\cap B(y_m,D^k)$ with $x\in I_3(z_m,k-1)$. Using \eqref{disji} inductively for $j=3$, we conclude $z_1=z_2$. This implies that the balls $B(y_1, D^k)$ and $B(y_2, D^k)$ intersect. By construction of $Y_k$, this implies $y_1=y_2$. This proves \eqref{disji} for $j=1$.

We next consider \eqref{disji} for $j=3$. Assume $x$ is in $I_3(y_m,k)$ for $m=1,2$ and $y_m\in Y_k$. If $x$ is in $X_k$, then by definition \eqref{definei3}, $x\in I_1(y_m,k)$ for $m=1,2$. As we have already shown \eqref{disji} for $j=1$, we conclude $y_1=y_2$. This completes the proof in case $x\in X_k$, and we may assume $x$ is not in $X_k$. By definition \eqref{definei3}, $x$ is not in $I_3(z,k)$ for any $z$ with $z<y_1$ or $z<y_2$. Hence, neither $y_1<y_2$ nor $y_2<y_1$, and by totality of the order of $Y_k$, we have $y_1=y_2$. This completes the proof of \eqref{disji} for $j=3$.

We show \eqref{unioni} for $j=2$. In case $k=-S$, this follows from \Cref{cover-big-ball}. Assume $k>-S$. Let $x$ be a point of $B(o, 4D^S-2D^k)$. By induction, there is $y'\in Y_{k-1}$ such that $x\in I_3(y',k-1)$. Using the inductive statement \eqref{squeezedyadic}, we obtain $x\in B(y',4D^{k-1})$. As $D>4$, by applying the triangle inequality with the points, $o$, $x$, and $y'$, we obtain that $y'\in B(o, 4D^S-D^k)$. By \Cref{cover-big-ball}, $y'$ is in $B(y,2D^k)$ for some $y\in Y_k$. It follows that $x\in I_2(y,k)$. This proves \eqref{unioni} for $j=2$.

We show \eqref{unioni} for $j=3$. Let $x\in B(o, 4D^S-2D^k)$. In case $x\in X_k$, then by definition of $X_k$ we have $x\in I_1(y,k)$ for some $y\in Y_k$ and thus $x\in I_3(y,k)$. We may thus assume $x\not\in X_k$. As we have already seen \eqref{unioni} for $j=2$, there is $y\in Y_k$ such that $x\in I_2(y,k)$. We may assume this $y$ is minimal with respect to the order in $Y_k$. Then $x\in I_3(y,k)$. This proves \eqref{unioni} for $j=3$.

Next, we show the first inclusion in \eqref{squeezedyadic}. Let $x\in B(y,\frac 12 D^k)$. As $I_1(y,k)\subset I_3(y,k)$, it suffices to show $x\in I_1(y,k)$. If $k=-S$, this follows immediately from the assumption on $x$ and the definition of $I_1$. Assume $k>-S$. By the inductive statement \eqref{unioni} and $D>4$, there is a $y'\in Y_{k-1}$ such that $x\in I_3(y',k-1)$. By the inductive statement \eqref{squeezedyadic}, we conclude $x\in B(y',4D^{k-1})$. By the triangle inequality with points $x$, $y$, $y'$, and $D>4$, we have $y'\in B(y,D^k)$. It follows by definition \eqref{defineij} that $I_3(y',k-1)\subset I_1(y,k)$, and thus $x\in I_3(y,k)$. This proves the first inclusion in \eqref{squeezedyadic}.

We show the second inclusion in \eqref{squeezedyadic}. Let $x\in I_3(y,k)$. As $I_1(y,k)\subset I_2(y,k)$ directly from the definition \eqref{defineij}, it follows by definition \eqref{definei3} that $x\in I_2(y,k)$. By definition \eqref{defineij}, there is $y'\in Y_{k-1}\cap B(y,2D^k)$ with $x\in I_3(y',k-1)$. By induction, $x\in B(y', 4D^{k-1})$. By the triangle inequality applied to the points $x,y',y$ and $D>4$, we conclude $x\in B(y,4D^k)$. This shows the second inclusion in \eqref{squeezedyadic} and completes the proof of the lemma.
\end{proof}

\begin{lemma}[cover by cubes]
\label{cover-by-cubes}
Let $-S\le l\le k\le S$ and
$y\in Y_k$.
We have
\begin{equation}\label{3coverdyadic}
   I_3(y,k)\subset \bigcup_{y'\in Y_l} I_3(y',l)\, .
\end{equation}
\end{lemma}
\begin{proof}

Let $-S\le l\le k\le S$ and $y\in Y_k$.
If $l=k$, the inclusion \eqref{3coverdyadic}
is true from the definition of set union.
We may then assume inductively that $k>l$ and the statement of the lemma is true if $k$ is replaced by $k-1$.
Let $x\in I_3(y,k)$.
By definition \eqref{definei3}, $x\in I_j(y,k)$
for some $j\in \{1,2\}$. By \eqref{defineij},
$x\in I_3(w,k-1)$ for some $w\in Y_{k-1}$.
We conclude \eqref{3coverdyadic} by induction.
\end{proof}

\begin{lemma}[dyadic property]
\label{dyadic-property}
\uses{basic-grid-structure, cover-by-cubes}
Let $-S\le l\le k\le S$ and $y\in Y_k$ and $y'\in Y_l$ with
$I_3(y',l)\cap I_3(y,k)\neq \emptyset$. Then
\begin{equation}
    \label{3dyadicproperty}
I_3(y',l)\subset I_3(y,k).
\end{equation}


\end{lemma}

\begin{proof}
Let $l,k,y,y'$ be as in the lemma. Pick $x\in I_3(y',l)\cap I_3(y,k)$. Assume first $l=k$. By \eqref{disji} of \Cref{basic-grid-structure}, we conclude $y'=y$, and thus \eqref{3dyadicproperty}. Now assume $l<k$. By induction, we may assume that the statement of the lemma is proven for $k-1$ in place of $k$.

By \Cref{cover-by-cubes}, there is a $y''\in Y_{k-1}$ such that $x\in I_3(y'',k-1)$. By induction, we have $I_3(y',l)\subset I_3(y'',k-1)$. If $l=k-1$, then by the disjointedness property of \Cref{basic-grid-structure}, we see that $y'=y''$, and hence \eqref{3dyadicproperty} follows. For $l<k-1$, it remains to prove
\begin{equation}\label{wyclaim}
I_3(y'',k-1)\subset I_3(y,k).
\end{equation}
We make a case distinction and assume first $x\in X_k$. By Definition \eqref{definei3}, we have $x\in I_1(y,k)$. By Definition \eqref{defineij}, there is a $v\in Y_{k-1}\cap B(y,D^k)$ with $x\in I_3(v,k-1)$. By \eqref{disji} of \Cref{basic-grid-structure}, we have $v=y''$. By Definition \eqref{defineij}, we then have $I_3(y'',k-1)\subset I_1(y,k)$. Then \eqref{wyclaim} follows by Definition \eqref{definei3} in the given case.

Assume now the case $x\notin X_k$. By \eqref{definei3}, we have $x\in I_2(y,k)$. Moreover, for any $u<y$ in $Y_k$, we have $x\not\in I_3(u,k)$. Let $u<y$. By transitivity of the order in $Y_k$, we conclude $x\not \in I_2(u,k)$. By \eqref{defineij} and the disjointedness property of \Cref{basic-grid-structure}, we have $I_3(y'',k-1)\cap I_2(u,k)= \emptyset$. Similarly, $I_3(y'',k-1)\cap I_1(u,k)= \emptyset$. Hence $I_3(y'',k-1)\cap I_3(u,k)=\emptyset$. As $u<y$ was arbitrary, we conclude with \eqref{definei3} the claim in the given case. This completes the proof of \eqref{wyclaim}, and thus also \eqref{3dyadicproperty}.
\end{proof}




For $-S\le k'\le k\le S$ and $y'\in Y_{k'}$, $y\in Y_k$
write $(y',k'|y,k)$ if $I_3(y',k')\subset I_3(y,k)$ and
\begin{equation}\label{bdcond}
    \inf_{x\in X\setminus I_3(y,k)}\rho(y',x)<6D^{k'}\, .
\end{equation}


\begin{lemma}[transitive boundary]
\label{transitive-boundary}
\uses{dyadic-property}
Assume $-S\le k''< k'< k\le S$ and
$y''\in Y_{k''}$, $y'\in Y_{k'}$, $y\in Y_k$.
Assume there is $x\in X$ such that
\begin{equation}
x\in I_3(y'',k'')\cap I_3(y',k')\cap I_3(y,k)\, .
\end{equation}
If $(y'',k''|y,k)$, the also
$(y'',k''|y',k')$ and $(y',k'|y,k)$
\end{lemma}

\begin{proof}
As $x\in I_3(y'',k'')\cap I_3(y',k')$ and $k''< k'$, we have by \Cref{dyadic-property} that
$I_3(y'',k'')\subset I_3(y',k')$. Similarly,
$I_3(y',k')\subset I_3(y,k)$.
Pick $x'\in X\setminus I_3(y,k)$ such that
\begin{equation}\label{yppxp}
    \rho(y'',x')< 6D^{k''}\, ,
\end{equation}
which exists as $(y'',k''|y,k)$. As
$x'\in X\setminus I_3(y',k')$ as well, we conclude
$(y'',k''| y',k')$.
By the triangle inequality, we have
\begin{equation}
\rho(y',x')\le \rho(y',x)+\rho(x,y'')+\rho(y'',x')
\end{equation}
Using the choice of $x$ and \eqref{squeezedyadic}
as well as \eqref{yppxp}, we estimate this by
\begin{equation}
< 4D^{k'}+4D^{k''}+6D^{k''}\le 6D^{k'}\, ,
\end{equation}
where we have used $D>5$ and $k''<k'$.
We conclude $(y',k'|y,k)$.
\end{proof}


\begin{lemma}[small boundary]
\label{small-boundary}
\uses{transitive-boundary}
 Let $K = 2^{4a+1}$. For each $-S+K\le k\le S$ and $y\in Y_k$ we have
    \begin{equation}
        \label{new-small-boundary}
        \sum_{z\in Y_{k-K}: (z,k-K|y,k)}\mu(I_3(z,k-K)) \le \frac 12 \mu(I_3(y,k))\,.
    \end{equation}
\end{lemma}

\begin{proof}
Let $K$ be as in the lemma. Let $-S+K\le k\le S$ and $y\in Y_k$.

Pick $k'$ so that $k-K\le k'\le k$.
For each $y''\in Y_{k-K}$ with $(y'',k-K| y,k)$,
by \Cref{cover-by-cubes} and \Cref{dyadic-property}, there is a unique $y'\in Y_{k'}$ such that
\begin{equation}\label{4.31}
    I_3(y'',k-K)\subset I_3(y',k')\subset I_3(y,k)\, .
\end{equation}
Using \Cref{transitive-boundary}, $(y',k'|y,k)$.

We conclude using the disjointedness property of
\Cref{basic-grid-structure} that
\begin{equation}\label{scalecompare}
    \sum_{y'': (y'',k-K|y,k)}\mu(I_3(y'',k-K))
   \le
\sum_{y': (y',k'|y,k)}
\mu(I_3(y',k')) \, .
   \end{equation}
Adding over $k-K<k'\le k$, and using
\[\mu(I_3(y',k'))\le 2^{4a} \mu(B(y', \frac 14 D^{k'}))\]
from the doubling property \eqref{doublingx} and
\eqref{squeezedyadic} gives
\begin{equation}\label{sumcompare}
    K\sum_{y'': (y'',k-K|y,k)}
    \mu(I_3(y'',k-K))
\end{equation}
\begin{equation}\label{sumcompare1}
    \le 2^{4a} \sum_{k-K<k'\le k}
   \left[ \sum_{y': (y',k'|y,k)}
\mu(B(y', \frac 14 D^{k'}))\right]
\end{equation}
Each ball $B(y', \frac 14 D^{k'})$ occurring in
\eqref{sumcompare1} is contained in $I_3(y',k')$
by \eqref{squeezedyadic} and in turn contained in
$I_3(y,k)$ by \eqref{4.31}. Assume for the moment all these balls are pairwise disjoint. Then
by additivity of the measure,
\begin{equation}
    K\sum_{y'': (y'',k-K|y,k)}
    \mu(I_3(y'',k-K))
    \le 2^{4a}
\mu(I_3(y,k))\,
\end{equation}
which by $K=2^{4a+1}$ implies \eqref{new-small-boundary}.

It thus remains to prove that the balls
occurring in
\eqref{sumcompare1} are pairwise disjoint.
Let $(u,l)$ and $(u',l')$ be two parameter pairs occurring
in the sum of \eqref{sumcompare1} and let
$ B(u, \frac 14 D^l)$ and $B({u'}, \frac 14 D^{l'})$
be the corresponding balls. If
$l=l'$, then the balls are equal or disjoint by
\eqref{squeezedyadic} and \eqref{disji} of \Cref{basic-grid-structure}. Assume then without loss of generality that $l'<l$. Towards a contradiction, assume that
\begin{equation}\label{bulbul}
    B(u, \frac 14 D^l)\cap B({u'}, \frac 14 D^{l'})\neq \emptyset
\end{equation}
As $(u',l'|y,k)$, there is a point $x$ in
$X\setminus I_3(y,k)$ with $\rho(x,u')<6D^{l'}$.
Using $D>25$, we conclude from the triangle inequality and \eqref{bulbul} that
$x\in B(u,\frac 12D^l)$. However, $B(u,\frac 12 D^l)\subset I_3(u,l)$,
and $I_3(u,l)\subset I_3(y,k)$, a contradiction to
$x\not\in I_3(y,k)$.
This proves the lemma.
\end{proof}

\begin{lemma}[smaller boundary]
\label{smaller-boundary}
\uses{small-boundary}
Let $K = 2^{4a+1}$
and let $n\ge 0$ be an integer. Then
for each $-S+nK\le k\le S$ we have
   \begin{equation}
        \label{very-new-small}
        \sum_{y'\in Y_{k-nK}: (y',k-nK|y,k)}\mu(I_3(y',k-nK)) \le 2^{-n} \mu(I_3(y,k))\,.
    \end{equation}
\end{lemma}
\begin{proof}
    We prove this by induction on $n$. If $n=0$,
    both sides of \eqref{very-new-small} are equal to
    $\mu(I_3(y,k))$ by \eqref{disji}. If $n=1$, this follows from \Cref{small-boundary}.

    Assume $n>1$ and \eqref{very-new-small} has been proven for $n-1$.
We write \eqref{very-new-small}
     \begin{equation}
             \sum_{y''\in Y_{k-nK}: (y'',k-nK|y,k)}\mu(I_3(y'',k-nK))
    \end{equation}
     \begin{equation}
= \sum_{y'\in Y_{k-K}:(y',k-K|y,k)} \left[ \sum_{y''\in Y_{k-nK}: (y'',k-nK|y',k-K)}\mu(I_3(y'',k-nK)) \right]
    \end{equation}
Applying the induction hypothesis, this is bounded by
         \begin{equation}
= \sum_{y'\in Y_{k-K}:(y',k-K|y,k)} 2^{1-n}\mu(I_3(y',k-K))
    \end{equation}
Applying \eqref{new-small-boundary} gives
\eqref{very-new-small}, and proves the lemma.
\end{proof}

\begin{lemma}[boundary measure]
\label{boundary-measure}
\uses{smaller-boundary}
 For each $-S\le k\le S$ and $y\in Y_k$ and $0<t<1$
 with $tD^k\ge D^{-S}$ we have
    \begin{equation}
        \label{old-small-boundary}
        \mu(\{x \in I_3(y,k) \ : \ \rho(x, X \setminus I_3(y,k)) \leq t D^{k}\}) \le D t^\kappa \mu(I_3(y,k))\,.
    \end{equation}
\end{lemma}
\begin{proof}
Let $x\in I_3(y,k)$ with $\rho(x, X \setminus I_3(y,k)) \leq t D^{k}$. Let $K = 2^{4a+1}$ as in \Cref{smaller-boundary}.
Let $n$ be the largest integer such that
$D^{nK} \le \frac{1}{t}$, so that $tD^k \le D^{k-nK}$ and
\begin{equation}
\label{eq-n-size}
    D^{nK} > \frac{1}{tD^K}\,.
\end{equation}
Let $k' = k - nK$, by the assumption $tD^k \ge D^{-S}$, we have $k' \ge -S$. By \eqref{3coverdyadic}, there exists $y' \in Y_{k'}$ with $x \in I_3(y',k')$. By the squeezing property \eqref{squeezedyadic} and the assumption on $x$, we have
$$
    \rho(y', X \setminus I_3(y,k)) \le \rho(x,y') + \rho(x, X \setminus I_3(y,k)) \le 4 D^{k'} + t D^{k}\,.
$$
By the assumption on $n$ and the definition of $k'$, this is
$$
    \le 4D^{k'} + D^{k - nK} < 6D^{k'}\,.
$$
Together with \eqref{3dyadicproperty} thus $(y',k'|y,k)$. We have shown that
$$
    \{x \in I_3(y,k) \ : \ \rho(x, X \setminus I_3(y,k)) \leq t D^{k}\}
$$
$$
    \subset \bigcup_{y'\in Y_{k-nK}: (y',k-nK|y,k)}I_3(y',k-nK)\,.
$$
Using monotonicity and additivity of the measure and \Cref{smaller-boundary}, we obtain
$$
    \mu(\{x \in I_3(y,k) \ : \ \rho(x, X \setminus I_3(y,k)) \leq t D^{k}\}) \le 2^{-n} \mu(I_3(y,k))\,.
$$
By \eqref{eq-n-size} and the definition \eqref{defineD} of $D$, this is bounded by
$$
    t^{1/(100a^2 K)} D \mu(I_3(y,k))\,,
$$
which completes the proof by the definition \eqref{definekappa} of $\kappa$.
\end{proof}

Let $\mathcal{D}$ be the set of all $I_3(y,k)$ with $k\in [-S,S]$ and
$y\in Y_k$. Define
\begin{equation}
s(I_3(y,k)):=k
\end{equation}
\begin{equation}
c(I_3(y,k)):=y\,.
\end{equation}

\begin{proof}[Proof of \Cref{grid-existence}]
\proves{grid-existence}
We show that $(\mathcal{D},c,s)$ constitutes a grid structure. Property \eqref{eq-vol-sp-cube}
follows from \eqref{squeezedyadic}, while \eqref{eq-small-boundary} follows from \Cref{boundary-measure}.

Let $x\in B(o, D^S)$. We show properties
\eqref{coverdyadic},
\eqref{dyadicproperty} and
\eqref{coverball}
for $(\mathcal{D},c,s)$ and $x$.

We first show \eqref{coverdyadic} by contradiction. Then there is an $I$ violating the conclusion of
\eqref{coverdyadic}. Pick such $I=I_3(y,l)$ such that $l$ is minimal.
{By assumption, we have $-S\le k<l$; in particular $-S<l$}.
By definition, $I_3(y, l)$ is contained in $I_1(y, l)\cup I_2(y, l)$, which is contained in the union of $I_3(y',l-1)$ with $y'\in Y_{l-1}$.
By minimality of $l$, each such $I_3(y',l-1)$ is contained in the union of
all $I_3(z,k)$ with $z\in Y_k$. This proves \eqref{coverdyadic}.

We now show \eqref{dyadicproperty}. Assume to get a contradiction that
there are non-disjoint $I, J\in \mathcal{D}$ with $s(I)\le s(J)$
and $I \not \subset J$. We may assume the existence of such $I$ and $J$ with minimal
$s(J)-s(I)$. Let $k=s(I)$. Assume first $s(J)=k$. Let $I=I_3(y_1,k)$ and $J=I_3(y_2,k)$ with $y_1,y_2\in Y_k$.
If $y_1=y_2$, then $I=J$, a contradiction to $I\not \subset J$.
If $y_1\neq y_2$, then $I\cap J=\emptyset$ by \eqref{disji}, a contradiction to the non-disjointedness of $I,J$.
Assume now $s(J)>k$. Choose $y\in I\cap J$. By property \eqref{coverdyadic},
there is $K\in \mathcal{D}$ with $s(K)=s(J)-1$ and $y\in K$. By construction
of $J$, and pairwise disjointedness of all $I_3(w,s(J)-1)$ that we have already seen,
we have $K\subset J$. By minimality of $s(J)$, we have $I\subset K$.
This proves $I\subset J$ and thus \eqref{dyadicproperty}.

We next establish \eqref{coverball}. Let $-S\leq k\leq S$. Using \eqref{unioni} for $j=3$, we get
\begin{equation}
x\in B(o, D^S)\subset B(o, 4D^S-2D^k)\subset \bigcup_{y\in Y_k} I_3(y,k)\, .
\end{equation}
Thus, there exists a dyadic cube $I=I_3(y, k)$ with $s(I)=k$ and $x\in I$.
This proves \eqref{coverball}.
\end{proof}

\section{Proof of Tile Structure Lemma}
\label{subsectiles}
Choose a grid structure $(\mathcal{D}, c, s)$ with \Cref{grid-existence}
Let $I \in \mathcal{D}$. Suppose that
\begin{equation}
    \label{eq-tile-Z}
    \mathcal{Z} \subset \bigcup_{\mfa \in \tQ(X)} B_{I^\circ}(\mfa, 1)
\end{equation}
is such that for any $\mfa, \mfb \in \mathcal{Z}$ with $\mfa\ne \mfb$ we have
\begin{equation}
    \label{eq-tile-disjoint-Z}
    B_{I^\circ}(\mfa, 0.3) \cap B_{I^\circ}(\mfb, 0.3) = \emptyset\,.
\end{equation}
By \Cref{ball-metric-entropy} applied to each of the balls $B_{I^\circ}(\mfa, 1)$, $\mfa \in \tQ(X)$, we have
$$
    |\mathcal{Z}| \le 2^{2a} |\tQ(X)|\,.
$$
In particular, there exists a set $\mathcal{Z}$ satisfying both \eqref{eq-tile-Z} and \eqref{eq-tile-disjoint-Z} of maximal cardinality among all such sets. We pick for each $I \in \mathcal{D}$ such a set $\mathcal{Z}(I)$.

\begin{lemma}[frequency ball cover]
\label{frequency-ball-cover}
\leanok
\lean{frequency_ball_cover}
    For each $I \in \mathcal{D}$, we have
    \begin{equation}
        \label{eq-tile-cover}
        \tQ(X) \subset \bigcup_{\mfa \in \tQ(X)} B_{I^\circ}(\mfa, 1) \subset \bigcup_{z \in \mathcal{Z}(I)} B_{I^\circ}(z, 0.7)\,.
    \end{equation}
\end{lemma}

\begin{proof}
% \leanok % the lemma is proven, but let's wait until \mathcal{Z} is defined to actually mark it.
    To show \eqref{eq-tile-cover} note that the first inclusion is obvious. For the second inclusion let $\mfb \in \bigcup_{\mfa \in \tQ(X)} B_{I^\circ}(\mfa, 1)$. By maximality of $\mathcal{Z}(I)$, there must be a point $z \in \mathcal{Z}(I)$ such that $B_{I^\circ}(z, 0.3) \cap B_{I^\circ}(\mfb, 0.3) \ne \emptyset$. Else, $\mathcal{Z}(I) \cup \{\mfb\}$ would be a set of larger cardinality than $\mathcal{Z}(I)$ satisfying \eqref{eq-tile-Z} and \eqref{eq-tile-disjoint-Z}. Fix such $z$, and fix a point $z_1 \in B_{I^\circ}(z, 0.3) \cap B_{I^\circ}(\mfb, 0.3)$. By the triangle inequality, we deduce that
    $$
        d_{I^\circ}(z,\mfb) \le d_{I^\circ}(z,z_1) + d_{I^\circ}(\mfb, z_1) < 0.3 + 0.3 = 0.6\,,
    $$
    and hence $\mfb \in B_{I^\circ}(z, 0.7)$.
\end{proof}

We define
$$
    \fP = \{(I, z) \ : \ I \in \mathcal{D}, z \in \mathcal{Z}(I)\}\,,
$$
$$\scI((I, z)) = I\qquad \text{and} \qquad \fcc((I, z)) = z.$$ We further set $$\ps(\fp) = s(\scI(\fp)),\qquad \qquad \pc(\fp) = c(\scI(\fp)).$$ Then \eqref{tilecenter}, \eqref{tilescale} hold by definition.

It remains to construct the map $\Omega$, and verify properties \eqref{eq-dis-freq-cover}, \eqref{eq-freq-dyadic} and
\eqref{eq-freq-comp-ball}. We first construct an auxiliary map $\Omega_1$. For each $I \in \mathcal{D}$, we pick an enumeration of the finite set $\mathcal{Z}(I)$
$$
    \mathcal{Z}(I) = \{z_1, \dotsc, z_M\}\,.
$$
We define {$\Omega_1:\fP \mapsto \mathcal{P}(\Mf) $ as below}. Set
$$
    \Omega_1((I, z_1)) = B_{I^\circ}(z_1, 0.7) \setminus \bigcup_{z \in \mathcal{Z}(I)\setminus \{z_1\}} B_{I^\circ}(z, 0.3)
$$
and then define iteratively
\begin{equation}
    \label{eq-def-omega1}
    \Omega_1((I, z_k)) = B_{I^\circ}(z_k, 0.7) \setminus \bigcup_{z \in \mathcal{Z}(I) \setminus \{z_k\}} B_{I^\circ}(z, 0.3) \setminus \bigcup_{i=1}^{k-1} \Omega_1((I, z_i))\,.
\end{equation}
\begin{lemma}[disjoint frequency cubes]
    \label{disjoint-frequency-cubes}
    \leanok
    \lean{Construction.disjoint_frequency_cubes}

    For each $I \in \mathcal{D}$, and $\fp_1, \fp_2\in \fP(I)$, if $$\Omega_1(\fp_1)\cap \Omega_1(\fp_2)\neq \emptyset,$$ then $\fp_1=\fp_2$.
\end{lemma}

\begin{proof}
    By the definition of the map $\scI$, we have
    $$
        \fP(I) = \{(I, z) \, : \, z \in \mathcal{Z}(I)\}\,.
    $$
    By \eqref{eq-def-omega1}, the set $\Omega_1((I, z_k))$ is disjoint from each $\Omega_1((I, z_i))$ with $i < k$. Thus the sets $\Omega_1(\fp)$, $\fp \in \fP(I)$ are pairwise disjoint.
\end{proof}

\begin{lemma}[frequency cube cover]
\label{frequency-cube-cover}
\leanok
\lean{Construction.iUnion_ball_subset_iUnion_Î©â‚, Construction.ball_subset_Î©â‚, Construction.Î©â‚_subset_ball}
    For each $I \in \mathcal{D}$, it holds that
    \begin{equation}
    \label{eq-omega1-cover}
         \bigcup_{z \in \mathcal{Z}(I)} B_{I^\circ}(z, 0.7)\subset \bigcup_{\fp \in \fP(I)} \Omega_1(\fp)\,.
    \end{equation}
    For every $\fp \in \fP$, it holds that
    \begin{equation}
        \label{eq-omega1-incl}
        B_{\fp}(\fcc(\fp), 0.3) \subset \Omega_1(\fp) \subset B_{\fp}(\fcc(\fp), 0.7)\,.
    \end{equation}
\end{lemma}

\begin{proof}
    For \eqref{eq-omega1-incl} let $\fp = (I, z)$.
    The second inclusion in \eqref{eq-omega1-incl} then follows from \eqref{eq-def-omega1} and the equality $B_{\fp}(\fcc(\fp), 0.7) = B_{I^\circ}(z, 0.7)$, which is true by definition.
    For the first inclusion in \eqref{eq-omega1-incl} let $\mfa \in B_{\fp}(\fcc(\fp),0.3)$. Let $k$ be such that $z = z_k$ in the enumeration we chose above. It follows immediately from \eqref{eq-def-omega1} and \eqref{eq-tile-disjoint-Z} that
    $\mfa \notin \Omega_1((I, z_i))$ for all $i < k$. Thus, again from \eqref{eq-def-omega1}, we have
    $\mfa \in \Omega_1((I,z_k))$.

    To show \eqref{eq-omega1-cover} let $\mfa \in \bigcup_{z \in \mathcal{Z}(I)} B_{I^\circ}(z,0.7)$.
    If there exists $z \in \mathcal{Z}(I)$ with $\mfa \in B_{I^\circ}(z,0.3)$, then
    $$
        z \in \Omega_1((I, z)) \subset \bigcup_{\fp \in \fP(I)} \Omega_1(\fp)
    $$
    by the first inclusion in \eqref{eq-omega1-incl}.

    Now suppose that there exists no $z \in \mathcal{Z}(I)$ with $\mfa \in B_{I^\circ}(z, 0.3)$. Let $k$ be minimal such that $\mfa \in B_{I^\circ}(z_k, 0.7)$. Since $\Omega_1((I, z_i)) \subset B_{I^\circ}(z_i, 0.7)$ for each $i$ by \eqref{eq-def-omega1}, we have that $\mfa \notin \Omega_1((I, z_i))$ for all $i < k$. Hence $\mfa \in \Omega_1((I, z_k))$, again by \eqref{eq-def-omega1}.
\end{proof}

Now we are ready to define the function $\Omega$. For all cubes $I \in \mathcal{D}$ such that there exists no $J \in \mathcal{D}$ with $I \subset J$ and $I \ne J$, we define for all $\fp \in \fP(I)$
\begin{equation}
    \label{eq-max-omega}
    \fc(\fp) = \Omega_1(\fp)\,.
\end{equation}
For cubes $I \in \mathcal{D}$ for which there exists $J \in \mathcal{D}$ with $I \subset J$ and $I \ne J$, we define $\Omega$ by recursion. We can pick an inclusion minimal $J \in \mathcal{D}$ among the finitely many cubes such that $I \subset J$ and $I \ne J$. This $J$ is unique: Suppose that $J'$ is another inclusion minimal cube with $I \subset J'$ and $I \ne J'$. Without loss of generality, we have that $s(J) \le s(J')$. By \eqref{dyadicproperty}, it follows that $J \subset J'$. Since $J'$ is minimal with respect to inclusion, it follows that $J = J'$. Then we define
\begin{equation}
    \label{eq-it-omega}
    \fc(\fp) = \bigcup_{z \in \mathcal{Z}(J) \cap \Omega_1(\fp)} \Omega((J, z)) \cup B_{\fp}(\fcc(\fp),0.2)\,.
\end{equation}

We now verify that $(\fP,\scI,\fc,\fcc,\pc,\ps)$ forms a tile structure.
\begin{proof}[Proof of \Cref{tile-structure}]
    \proves{tile-structure}
    First, we prove \eqref{eq-freq-comp-ball}. If $I \in \mathcal{D}$ is maximal in $\mathcal{D}$ with respect to set inclusion, then \eqref{eq-freq-comp-ball} holds for all $\fp \in \fP(I)$ by \eqref{eq-max-omega} and \eqref{eq-omega1-incl}. Now suppose that $I$ is not maximal in $\mathcal{D}$ with respect to set inclusion. Then we may assume by induction that for all $J \in \mathcal{D}$ with $I \subset J$ and all $\fp' \in \fP(J)$, \eqref{eq-freq-comp-ball} holds. Let $J$ be the unique minimal cube in $\mathcal{D}$ with $I \subsetneq J$.

    Suppose that $\mfa \in \Omega(\fp)$. If $\mfa\in B_{\fp}(\mathcal{Q}(\fp), 0.2)$, then since
    \begin{equation*}
        B_{\fp}(\mathcal{Q}(\fp), 0.2)\subset B_{\fp}(\mathcal{Q}(\fp), 1)\, ,
    \end{equation*}
    we conclude that $\mfa\in B_{\fp}(\mathcal{Q}(\fp), 0.7)$. If not, by \eqref{eq-it-omega}, there exists $z \in \mathcal{Z}(J) \cap \Omega_1(\fp)$ with $\mfa \in \Omega(J,z)$. Using the triangle inequality and \eqref{eq-omega1-incl}, we obtain
    $$
        d_{I^\circ}(\fcc(\fp),\mfa) \le d_{I^\circ}(\fcc(\fp), z) + d_{I^\circ}(z, \mfa) \le 0.7 + d_{I^\circ}(z, \mfa)\,.
    $$
    By \Cref{monotone-cube-metrics} and the induction hypothesis, this is estimated by
    $$
        \le 0.7 + 2^{-95a} d_{J^\circ}(z,\mfa) \le 0.7 + 2^{-95a}\cdot 1 < 1\,.
    $$
    This shows the second inclusion in \eqref{eq-freq-comp-ball}. The first inclusion is immediate from \eqref{eq-it-omega}.

    Next, we show \eqref{eq-dis-freq-cover}. Let $I \in \mathcal{D}$.

    If $I$ is maximal with respect to inclusion, then disjointedness of the sets $\fc(\fp)$ for $\fp \in \fP(I)$ follows from the definition \eqref{eq-max-omega} and \Cref{disjoint-frequency-cubes}. To obtain the inclusion in \eqref{eq-dis-freq-cover} one combines the inclusions \eqref{eq-tile-cover} and \eqref{eq-omega1-cover}
    of \Cref{frequency-cube-cover} with \eqref{eq-max-omega}.

    Now we turn to the case where there exists $J \in \mathcal{D}$ with $I \subset J$ and $I\ne J$. In this case we use induction: It suffices to show \eqref{eq-dis-freq-cover} under the assumption that it holds for all cubes $J \in \mathcal{D}$ with $I \subset J$. As shown before definition \eqref{eq-it-omega}, we may choose the unique inclusion minimal such $J$. To show disjointedness of the sets $\fc(\fp), \fp \in \fP(I)$ we pick two tiles $\fp, \fp' \in \fP(I)$ and $\mfa \in \fc(\fp) \cap \fc(\fp')$.
    Then we are by \eqref{eq-it-omega} in one of the following four cases.

    1. There exist $z \in \mathcal{Z}(J) \cap \Omega_1(\fp)$ such that $\mfa \in \Omega(J, z)$, and there exists $z' \in \mathcal{Z}(J) \cap \Omega_1(\fp')$ such that $\mfa \in \Omega(J, z')$. By the induction hypothesis, that \eqref{eq-dis-freq-cover} holds for $J$, we must have $z = z'$. By \Cref{disjoint-frequency-cubes}, we must then have $\fp = \fp'$.

    2. There exists $z \in \mathcal{Z}(J) \cap \Omega_1(\fp)$ such that $\mfa \in \Omega(J,z)$, and $\mfa \in B_{\fp'}(\fcc(\fp'), 0.2)$. Using the triangle inequality, \Cref{monotone-cube-metrics} and \eqref{eq-freq-comp-ball}, we obtain
    $$
        d_{\fp'}(\fcc(\fp'),z) \le d_{\fp'}(\fcc(\fp'), \mfa) + d_{\fp'}(z, \mfa) \le 0.2 + 2^{-95a} \cdot 1 < 0.3\,.
    $$
    Thus $z \in \Omega_1(\fp')$ by \eqref{eq-omega1-incl}. By \Cref{disjoint-frequency-cubes}, it follows that $\fp = \fp'$.

    3. There exists $z' \in \mathcal{Z}(J) \cap \Omega_1(\fp')$ such that $\mfa \in \Omega(J,z')$, and $\mfa \in B_{\fp}(\fcc(\fp), 0.2)$. This case is the same as case 2., after swapping $\fp$ and $\fp'$.

    4. We have $\mfa \in B_{\fp}(\fcc(\fp), 0.2) \cap B_{\fp'}(\fcc(\fp'), 0.2)$. In this case it follows that $\fp = \fp'$ since the sets $B_{\fp}(\fcc(\fp), 0.2)$ are pairwise disjoint by the inclusion \eqref{eq-omega1-incl} and \Cref{disjoint-frequency-cubes}.

    To show the inclusion in \eqref{eq-dis-freq-cover}, let $\mfa \in \tQ(X)$. By the induction hypothesis, there exists $\fp \in \fP(J)$ such that $\mfa \in \Omega(\fp)$. By definition of the set $\fP$, we have $\fp = (J, z)$ for some $z \in \mathcal{Z}(J)$. By \eqref{eq-tile-Z}, there exists $x \in X$ with $d_{J^\circ}(\tQ(x), z) \le 1$. By \Cref{monotone-cube-metrics}, it follows that $d_{I^\circ}(\tQ(x), z) \le 1$.
    Thus, by \eqref{eq-tile-cover}, there exists $z' \in \mathcal{Z}(I)$ with $z \in B_{I^\circ}(z', 0.7)$. Then by Lemma \eqref{frequency-cube-cover} there exists $\fp' \in \fP(I)$ with $z \in \mathcal{Z}(J) \cap \Omega_1(\fp')$. Consequently, by \eqref{eq-it-omega}, $\mfa \in \fc(\fp')$. This completes the proof of \eqref{eq-dis-freq-cover}.

    Finally, we show \eqref{eq-freq-dyadic}. Let $\fp, \fq \in \fP$ with $\scI(\fp) \subset \scI(\fp)$ and $\fc(\fp) \cap \fc(\fq) \ne \emptyset$. If we have $\ps(\fp) \ge \ps(\fq)$, then it follows from \eqref{dyadicproperty} that $I = J$, thus $\fp, \fq \in \fP(I)$. By \eqref{eq-dis-freq-cover} we have then either $\fc(\fp) \cap \fc(\fq) = \emptyset$ or $\fc(\fp) = \fc(\fq)$. By the assumption in \eqref{eq-freq-dyadic} we have $\fc(\fp) \cap \fc(\fq) \ne \emptyset$, so we must have $\fc(\fp) = \fc(\fq)$ and in particular $\fc(\fq) \subset \fc(\fp)$.

    So it remains to show \eqref{eq-freq-dyadic} under the additional assumption that $\ps(\fq) > \ps(\fp)$. In this case, we argue by induction on $\ps(\fq)-\ps(\fp)$. By \eqref{coverdyadic}, there exists a cube $J \in \mathcal{D}$ with $s(J) = \ps(\fq) - 1$ and $J \cap\scI(\fp) \ne \emptyset$. We pick one such $J$. By \eqref{dyadicproperty}, we have $\scI(\fp) \subset J \subset \scI(\fq)$.

    By \eqref{eq-tile-Z}, there exists $x \in X$ with $d_{\fq}(\tQ(x), \fcc(\fq)) \le 1$. By \Cref{monotone-cube-metrics}, it follows that $d_{J^\circ}(\tQ(x), \fcc(\fq)) \le 1$.
    Thus, by \eqref{eq-tile-cover}, there exists $z' \in \mathcal{Z}(J)$ with $\fcc(\fq) \in B_{J^\circ}(z', 0.7)$. Then by \Cref{frequency-cube-cover} there exists $\fq' \in \fP(J)$ with $\fcc(\fq) \in\Omega_1(\fq')$.
    By \eqref{eq-it-omega}, it follows that $\Omega(\fq) \subset \Omega(\fq')$. Note that then $\scI(\fp) \subset \scI(\fq')$ and $\fc(\fp) \cap \fc(\fq') \ne \emptyset$ and $\ps(\fq') - \ps(\fp) = \ps(\fq) - \ps(\fp) - 1$. Thus, we have by the induction hypothesis that $\Omega(\fq') \subset \Omega(\fp)$. This completes the proof.
\end{proof}

\chapter{Proof of discrete Carleson}
\label{proptopropprop}



Let a grid structure $(\mathcal{D}, c, s)$ and a tile structure $(\fP, \scI, \fc, \fcc)$ for this grid structure be given. In \Cref{subsectilesorg}, we decompose the set $\fP$ of tiles into subsets. Each subset will be controlled by one of three methods. The guiding principle of the decomposition is to be able to apply the forest estimate of \Cref{forest-operator} to the final subsets defined in \eqref{defc5}. This application is done in \Cref{subsecforest}. The miscellaneous subsets along the construction of the forests will either be thrown into exceptional sets, which are defined and controlled in \Cref{subsetexcset}, or will be controlled by the antichain estimate of \Cref{antichain-operator}, which is done in \Cref{subsecantichain}. \Cref{subsec-lessim-aux} contains some auxiliary lemmas needed for the proofs in Subsections \ref{subsecforest}-\ref{subsecantichain}.

\section{Organisation of the tiles}\label{subsectilesorg}

In the following definitions, $k, n$, and
$j$ will be nonnegative integers.
Define
$\mathcal{C}(G,k)$ to be the set of $I\in \mathcal{D}$
such that there exists a $J\in \mathcal{D}$ with $I\subset J$
and
\begin{equation}\label{muhj1}
   {\mu(G \cap J)} > 2^{-k-1}{\mu(J)}\, ,
\end{equation}
but there does not exist a $J\in \mathcal{D}$ with $I\subset J$ and
\begin{equation}\label{muhj2}
   {\mu(G \cap J)} > 2^{-k}{\mu(J)}\,.
\end{equation}
Let
\begin{equation}
    \label{eq-defPk}
    \fP(k)=\{\fp\in \fP \ : \ \scI(\fp)\in \mathcal{C}(G,k)\}
\end{equation}
Define $ {\mathfrak{M}}(k,n)$ to be the set of $\fp \in \fP(k)$ such that
 \begin{equation}\label{ebardense}
    \mu({E_1}(\fp)) > 2^{-n} \mu(\scI(\fp))
 \end{equation}
and there does not exist $\fp'\in \fP(k)$ with
$\fp'\neq \fp$ and $\fp\le \fp'$ such that
 \begin{equation}\label{mnkmax}
    \mu({E_1}(\fp')) > 2^{-n} \mu(\scI(\fp')).
 \end{equation}
Define for a collection $\fP'\subset \fP(k)$
\begin{equation}
    \label{eq-densdef}
   \dens_k' (\fP'):= \sup_{\fp'\in \fP'}\sup_{\lambda \geq 2} \lambda^{-a} \sup_{\fp \in \fP(k): \lambda \fp' \lesssim \lambda \fp}
    \frac{\mu({E}_2(\lambda, \fp))}{\mu(\scI(\fp))}\,.
\end{equation}
Sorting by density, we define
\begin{equation}
    \label{def-cnk}
    \fC(k,n):=\{\fp\in \fP(k) \ : \
    2^{4a}2^{-n}< \dens_k'(\{\fp\}) \le
    2^{4a}2^{-n+1}\}\,.
\end{equation}
Following Fefferman \cite{fefferman}, we
define for $\fp \in \fC(k,n)$
\begin{equation}\label{defbfp}
     \mathfrak{B}(\fp) := \{ \mathfrak{m} \in \mathfrak{M}(k,n) \ : \ 100 \fp \lesssim \mathfrak{m}\}
\end{equation}
and
\begin{equation}\label{defcnkj}
       \fC_1(k,n,j) := \{\fp \in \fC(k,n) \ : \ 2^{j} \leq |\mathfrak{B}(\fp)| < 2^{j+1}\}\,.
\end{equation}
and
\begin{equation}\label{defl0nk}
       \fL_0(k,n) := \{\fp \in \fC(k,n) \ : \ |\mathfrak{B}(\fp)| <1\}\,.
\end{equation}
Together with the following removal of minimal layers, the splitting into $\fC_1(k,n,j)$ will lead to a separation of trees.
Define recursively for $0\le l\le Z(n+1)$
\begin{equation}
    \label{eq-L1-def}
    \fL_1(k,n,j,l)
\end{equation}
to be the set of minimal elements with respect to $\le$ in
\begin{equation}
    \fC_1(k,n,j)\setminus \bigcup_{0\le l'<l}
\fL_1(k,n,j,l')\, .
\end{equation}
Define
\begin{equation}
    \label{eq-C2-def}
    \fC_2(k,n,j):= \fC_1(k,n,j)\setminus \bigcup_{0\le l'\le Z(n+1)}
\fL_1(k,n,j,l')\, .
\end{equation}

The remaining tile organization will be relative to
prospective tree tops, which we define now.
Define
\begin{equation}\label{defunkj}
     \fU_1(k,n,j)
\end{equation}
to be the set of all
$\fu \in \fC_1(k,n,j)$ such that
for all $\fp \in \fC_1(k,n,j)$
with $\scI(\fu)$ strictly contained in
$\scI(\fp)$ we have $B_{\fu}(\fcc(\fu), 100) \cap B_{\fp}(\fcc(\fp),100) = \emptyset$.

We first remove the pairs that are outside the immediate reach of any of the prospective tree tops.
Define
\begin{equation}
\label{eq-L2-def}
\fL_2(k,n,j)
\end{equation}
to be the set of all $\fp\in \fC_2(k,n,j)$ such that there
does not exist
$\fu\in \fU_1(k,n,j)$
with $\scI(\fp)\neq \scI(\fu)$ and $2\fp\lesssim \fu$.
Define
\begin{equation}
\label{eq-C3-def}
\fC_3(k,n,j):=\fC_2(k,n,j)
  \setminus \fL_2(k,n,j)\, .
\end{equation}


We next remove the maximal layers.
Define recursively for $0 \le l \le Z(n+1)$
\begin{equation}
    \label{eq-L3-def}
    \fL_3(k,n,j,l)
\end{equation}
to be the set of all maximal elements with respect to $\le$ in
\begin{equation}
    \fC_3(k,n,j) \setminus \bigcup_{0 \le l' < l} \fL_3(k,n,j,l')\,.
\end{equation}
Define
\begin{equation}
\label{eq-C4-def}
\fC_4(k,n,j):=\fC_3(k,n,j)
  \setminus \bigcup_{0 \le l \le Z(n+1)} \fL_3(k,n,j,l)\,.
\end{equation}

Finally, we remove the boundary pairs relative to the prospective tree tops. Define
\begin{equation}
    \label{eq-L-def}
    \mathcal{L}(\fu)
\end{equation}
to be the set of all $I \in \mathcal{D}$ with $I \subset \scI(\fu)$ and $s(I) = \ps(\fu) - Z(n+1) - 1$ and
\begin{equation}
    B(c(I), 8 D^{s(I)})\not \subset \scI(\fu)\, .
\end{equation}
Define
\begin{equation}
    \label{eq-L4-def}
    \fL_4(k,n,j)
\end{equation}
to be the set of all $\fp\in \fC_4(k,n,j)$ such that there exists
$\fu\in \fU_1(k,n,j)$
with $\scI(\fp) \subset \bigcup \mathcal{L}(\fu)$, and define
\begin{equation}\label{defc5}
\fC_5(k,n,j):=\fC_4(k,n,j)
  \setminus \fL_4(k,n,j)\, .
\end{equation}


We define three exceptional sets.
The first exceptional set $G_1$ takes into account the ratio of the measures of $F$ and $G$.
Define $\fP_{F,G}$ to be the set of all $\fp\in \fP$
with
\begin{equation}
    \dens_2(\{\fp\})\ge 2^{2a+5}\frac{\mu(F)}{\mu(G)}\,.
\end{equation}
Define
\begin{equation}\label{definegone}
    G_1:=\bigcup_{\fp\in \fP_{F,G} }\scI(\fp)\, .
\end{equation}
For an integer $\lambda\ge 0$, define $A(\lambda,k,n)$ to be the set
of all $x\in X$ such that
\begin{equation}
    \label{eq-Aoverlap-def}
    % remark(Georges Gonthier): removed 1+
    \sum_{\fp \in \mathfrak{M}(k,n)}\mathbf{1}_{\scI(\fp)}(x)>\lambda 2^{n+1}
\end{equation}
and define
\begin{equation}\label{definegone2}
    G_2:=
\bigcup_{k\ge 0}\bigcup_{k< n}
A(2n+6,k,n)\, .
\end{equation}
Define
    \begin{equation}\label{defineg3}
        G_3 :=
        \bigcup_{k\ge 0}\, \bigcup_{n \geq k}\,
        \bigcup_{0\le j\le 2n+3}
        \bigcup_{\fp \in \fL_4 (k,n,j)}
        \scI(\fp)\, .
     \end{equation}
Define $G'=G_1\cup G_2 \cup G_3$
The following bound of the measure of $G'$ will be proven in
\Cref{subsetexcset}.
\begin{lemma}[exceptional set]
\label{exceptional-set}
\uses{first-exception,second-exception, third-exception}
We have
\begin{equation}
    \mu(G')\le 2^{-2}\mu(G)\, .
\end{equation}
\end{lemma}

In \Cref{subsecforest}, we identify each set $\fC_5(k,n,j)$ outside $G'$ as forest and use Proposition
\ref{forest-operator} to prove the following lemma.

\begin{lemma}[forest union]
\label{forest-union}
\uses{forest-operator,C-dens1,C6-forest, forest-geometry, forest-convex,forest-separation, forest-inner,forest-stacking}
  Let
  \begin{equation}
      \fP_1 =\bigcup_{k\ge 0}\bigcup_{n\ge k}
      \bigcup_{0\le j\le 2n+3}\fC_5(k,n,j)
  \end{equation}
  For all $f:X\to \C$ with $|f|\le \mathbf{1}_F$ we have
\begin{equation}
    \label{disclesssim1}
    \int_{G \setminus G'} \left|\sum_{\fp \in \fP_1} T_{\fp} f \right|\, \mathrm{d}\mu \le \frac{2^{435a^3}}{(q-1)^3} \mu(G)^{1 - \frac{1}{q}} \mu(F)^{\frac{1}{q}}\,.
    % Note(Georges Gonthier): denominator should be changed to (q-1)^4.
\end{equation}
\end{lemma}

In \Cref{subsecantichain}, we decompose
the complement of the set of tiles in Lemma
\ref{forest-union} and apply the antichain estimate of
\Cref{antichain-operator} to prove the following lemma.

\begin{lemma}[forest complement]
\label{forest-complement}
\uses{antichain-operator,antichain-decomposition,L0-antichain,L2-antichain,L1-L3-antichain,C-dens1}
  Let
  \begin{equation}
      \fP_2 =\fP\setminus \fP_1\,.
  \end{equation}
 For all $f:X\to \C$ with $|f|\le \mathbf{1}_F$ we have
\begin{equation}
    \label{disclesssim2}
    \int_{G \setminus G'} \left|\sum_{\fp \in \fP_2} T_{\fp} f\right| \, \mathrm{d}\mu \le \frac{2^{210a^3}}{(q-1)^4} \mu(G)^{1 - \frac{1}{q}} \mu(F)^{\frac{1}{q}}\,.
\end{equation}
\end{lemma}
\Cref{discrete-Carleson} follows by applying
triangle inequality to \eqref{disclesssim}
according to the splitting in \Cref{forest-union}
and \Cref{forest-complement} and using both Lemmas as well
as the bound on the set $G'$ given by \Cref{exceptional-set}.


\section{Proof of the Exceptional Sets Lemma}
\label{subsetexcset}


We prove separate bounds for $G_1$, $G_2$, and $G_3$
in Lemmas \ref{first-exception},
\ref{second-exception}, and \ref{third-exception}. Adding up these bounds proves \Cref{exceptional-set}.

The bound for $G_1$ is follows from the Vitali covering lemma, \Cref{Hardy-Littlewood}.

\begin{lemma}
[first exception]\label{first-exception}
\uses{Hardy-Littlewood}
We have
\begin{equation}
    \mu(G_1)\le 2^{-4}\mu(G)\, .
\end{equation}
\end{lemma}
\begin{proof}
Let
$$
    K = 2^{2a+5}\frac{\mu(F)}{\mu(G)}\,.
$$
For each $\fp\in \fP_{F,G}$ pick a
$r(\fp)>4D^{\ps(\fp)}$ with
$$
  {\mu(F\cap B(\pc(\fp),r(\fp)))}\ge K{\mu(B(\pc(\fp),r(\fp)))}\, .
$$
This ball exists by definition of $\fP_{F,G}$
and $\dens_2$. By applying \Cref{Hardy-Littlewood}to the collection of balls
$$
    \mathcal{B} = \{B(\pc(\fp),r(\fp)) \ : \ \fp \in \fP_{F,G}\}
$$
and the function $u = \mathbf{1}_F$, we obtain
$$
    \mu(\bigcup \mathcal{B}) \le 2^{2a+1} K^{-1} \mu(F)\,.
$$
We conclude with \eqref{eq-vol-sp-cube} and $r(\fp)>4D^{\ps(\fp)}$
$$
    \mu(G_1)= \mu(\bigcup_{\fp\in \fP_{F,G}} \scI(\fp))
    \le \mu(\bigcup \mathcal{B})\le 2^{2a+1} K^{-1} \mu (F) = 2^{-4}\mu(G)\,.
$$
\end{proof}


We turn to the bound of $G_2$, which relies on the Dyadic Covering \Cref{dense-cover} and the
John-Nirenberg \Cref{John-Nirenberg} below.

\begin{lemma}[dense cover]
\label{dense-cover}

For each $k\ge 0$, the union of all dyadic cubes
in $\mathcal{C}(G,k)$ has measure at most $2^{k+1} \mu(G)$ .
\end{lemma}
\begin{proof}
The union of dyadic cubes in $\mathcal{C}(G,k)$
is contained the union of elements of the set $\mathcal{M}(k)$
of all dyadic cubes $J$ with
${\mu(G \cap J)} > 2^{-k-1}{\mu(J)}$.
The union of elements in the set $\mathcal{M}(k)$ is contained in the union of elements in
the set $\mathcal{M}^*(k)$ of maximal elements in
$\mathcal{M}(k)$ with respect to set inclusion. Hence
\begin{equation}\label{cbymstar}
\mu (\bigcup \mathcal{C}(G,k))\le \mu (\bigcup \mathcal{M}^*(k))\le
\sum_{J\in \mathcal{M}^*(k)}\mu(J)
\end{equation}
Using the definition of $\mathcal{M}(k)$ and then
the pairwise disjointedness of elements in
$\mathcal{M}^*(k)$,
we estimate \eqref{cbymstar} by
\begin{equation}
\le
2^{k+1}\sum_{J\in \mathcal{M}^*(k)}\mu(J\cap G)
\le 2^{k+1}\mu(G).
\end{equation}
This proves the lemma.
\end{proof}




\begin{lemma}[pairwise disjoint]
\label{pairwise-disjoint}

     If $\fp, \fp' \in {\mathfrak{M}}(k,n)$ and
     \begin{equation}\label{eintersect}
     {E_1}(\fp)\cap {E_1}(\fp')\neq \emptyset,
     \end{equation}
     then $\fp=\fp'$.
\end{lemma}
\begin{proof}
Let $\fp,\fp'$ be as in the lemma. By definition of $E_1$,
we have
$E_1(\fp)\subset \scI(\fp)$ and analogously for $\fp'$, we conclude from \eqref{eintersect} that $\scI(\fp)\cap \scI(\fp')\neq \emptyset$. Let without loss of generality $\scI(\fp)$ be maximal in
$\{\scI(\fp),\scI(\fp')\}$, then $\scI(\fp')\subset \scI(\fp)$.
By \eqref{eintersect}, we conclude by definition of $E_1$ that $\fc(\fp)\cap \fc(\fp')\neq \emptyset$. By
\eqref{eq-freq-dyadic} we conclude $\fc(\fp)\subset \fc(\fp')$. It follows that $\fp'\le \fp$. By maximality
\eqref{mnkmax}
of $\fp'$, we have $\fp'=\fp$. This proves the lemma.
\end{proof}


\begin{lemma}[dyadic union]
\label{dyadic-union}

For each $x\in A(\lambda,k,n)$,
there is a dyadic cube $I$
that contains $x$ and is
a subset of
$A(\lambda,k,n)$.
\end{lemma}

\begin{proof}
Fix $k,n,\lambda,x$ as in the lemma such that $x\in A(\lambda,k,n)$.
Let $\mathcal{M}$ be the set of dyadic cubes $\scI(\fp)$ with $\fp$ in $\mathfrak{M}(k,n)$ and $x\in \scI(\fp)$.
By definition of $A(\lambda,k,n)$, the cardinality of $\mathcal{M}$ is at least $1+\lambda 2^{n+1}$.
Let $I$ be a cube of smallest scale in $\mathcal{M}$.
Then $I$ is contained in all cubes of $\mathcal{M}$.
It follows that $I\subset A(\lambda,k,n)$.
\end{proof}

\begin{lemma}[John Nirenberg]
\label{John-Nirenberg}
\uses{dense-cover, pairwise-disjoint,dyadic-union}
    For all integers $k,n,\lambda\ge 0$, we have
    \begin{equation}\label{alambdameasure}
        \mu(A(\lambda,k,n)) \le 2^{k+1-\lambda}\mu(G)\, .
    \end{equation}


\end{lemma}
\begin{proof}
Fix $k,n$ as in the lemma
and suppress notation to write
$A(\lambda)$ for $A(\lambda,k,n)$.
We prove the lemma by induction on $\lambda$.
For $\lambda=0$, we use that $A(\lambda)$ by definition of $\mathfrak{M}(k,n)$ is contained in the union of elements in $ \mathcal{C}(G,k)$. \Cref{dense-cover} then completes the base of the induction.

Now assume that the statement of \Cref{John-Nirenberg}
is proven for some integer $\lambda\ge 0$.
The set $A(\lambda+1)$ is contained in the set $A(\lambda)$.
Let $\mathcal{M}$ be the set of dyadic cubes which are a subset of $A(\lambda)$. By \Cref{dyadic-union}, the union of $\mathcal{M}$ is $A(\lambda)$.
Let $\mathcal{M}^*$ be the set of maximal dyadic cubes in $\mathcal{M}$.

Let $L\in \mathcal{M}^*$. For each $x\in L$, we have
\begin{equation}\label{suminout}
 \sum_{\fp \in {\mathfrak{M}}(k,n)} \mathbf{1}_{\scI(\fp)}(x)=
   \sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \subset L} \mathbf{1}_{\scI(\fp)}(x)+
  \sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \not \subset L} \mathbf{1}_{\scI(\fp)}(x)\, .
\end{equation}
If the second sum on the right-hand-side is not zero, there is
an element of $\mathcal{D}$ strictly containing $L$.
Let $\hat{L}$ be such a dyadic cube with minimal $s(L)$. Then $\hat{L}$ is contained in $\scI(\fp)$ for all $\fp$
contributing to the second sum in
\eqref{suminout}.
Hence the second sum in \eqref{suminout} is constant on
$\hat{L}$.
By maximality of $L$, the second sum is less than $1+\lambda 2^{n+1}$ somewhere on $\hat{L}$, thus on all of $\hat{L}$ and consequently also
at $x$.
If $x$ is in addition in $A(\lambda+1)$, then
the left-hand-side of \eqref{suminout} is at least
$1+(\lambda+1) 2^{n+1}$, so we have by the triangle inequality for the first sum on the right-hand side
\begin{equation}\label{mnkonl}
\sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \subset L} \mathbf{1}_{\scI(\fp)}(x)\ge 2^{n+1}\, .\end{equation}
By \Cref{pairwise-disjoint}, we have
\begin{equation}
\sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \subset L} \mu({E_1}(\fp)) \leq \mu(L)\, .
\end{equation}
Multiplying by $2^n$ and applying \eqref{ebardense}, we obtain
\begin{equation}\label{mnkintl}
    \sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \subset L} \mu(\scI(\fp)) \leq 2^n \mu(L)\, .
\end{equation}
We then have with \eqref{mnkonl} and \eqref{mnkintl}
\begin{equation}
2^{n+1}\mu(A(\lambda+1)\cap L) =
 \int_{A(\lambda+1)\cap L} 2^{n+1} d\mu
\end{equation}
\begin{equation}
\le
    \int \sum_{\fp \in {\mathfrak{M}}(k,n):\scI(\fp) \subset L} \mathbf{1}_{\scI(\fp)} d\mu
\le 2^n \mu(L)\, .
\end{equation}
Hence
\begin{equation}
    2\mu(A(\lambda+1))=2\sum_{L\in \mathcal{M}^*}
\mu(A(\lambda+1)\cap L)\le
\sum_{L\in \mathcal{M}^*}\mu( L)= \mu(A(\lambda))\, .
\end{equation}
Using the induction hypothesis, this proves
\eqref{alambdameasure} for $\lambda+1$ and completes the proof of the lemma.
\end{proof}

\begin{lemma}[second exception]
\label{second-exception}
\uses{John-Nirenberg}
We have
\begin{equation}
    \mu(G_2)\le 2^{-4} \mu(G)\, .
\end{equation}
\end{lemma}
\begin{proof}

We use \Cref{John-Nirenberg} and sum twice a geometric series
to obtain
\begin{equation}
    \sum_{0\le k}\sum_{k< n}
\mu(A(2n+6,k,n))\le \sum_{0\le k}\sum_{k< n} 2^{k-5-2n}\mu(G)
\end{equation}
\begin{equation}
   \le \sum_{0\le k} 2^{-k-5}\mu(G)\le 2^{-4}\mu(G)\, .
\end{equation}
This proves the lemma.
\end{proof}


We turn to the set $G_3$.

\begin{lemma}[top tiles]
\label{top-tiles}
 \uses{John-Nirenberg}
    We have
    \begin{equation}\label{eq-musum}
        % Note(Georges Gonthier): suggested new factor
        \sum_{\mathfrak{m} \in \mathfrak{M}(k,n)} \mu(\scI(\mathfrak{m}))\le 2^{n+k+3}\mu(G).
    \end{equation}
\end{lemma}
\begin{proof}
% Note(Georges Gonthier): sum should start at 0, not 1
We write the left-hand side of \eqref{eq-musum}
\begin{equation}
    \int \sum_{\mathfrak{m} \in \mathfrak{M}(k,n)} \mathbf{0}_{\scI(\mathfrak{m})}(x) \, d\mu(x) \le
2^{n+1} \sum_{\lambda=0}^{|\mathfrak{M}|}\mu(A(\lambda, k,n))\,.
\end{equation}
Using \Cref{John-Nirenberg}
and then summing a geometric series, we estimate this by
\begin{equation}
    \le
2^{n+1}\sum_{\lambda=0}^{|\mathfrak{M}|}
2^{k+1-\lambda}\mu(G)
\le
2^{n+1}2^{k+2}\mu(G)\, .
\end{equation}
This proves the lemma.
\end{proof}


\begin{lemma}[tree count]
\label{tree-count}

Let $k,n,j\ge 0$. We have for every $x\in X$
\begin{equation}
    \sum_{\fu\in \fU_1(k,n,j)} \mathbf{1}_{\scI(\fu)}(x)
    \le 2^{-j}
    2^{9a} \sum_{\mathfrak{m}\in \mathfrak{M}(k,n)}
     \mathbf{1}_{\scI(\mathfrak{m})}(x)
\end{equation}
\end{lemma}

\begin{proof}
Let $x\in X$. For each
$\fu\in \fU_1(k,n,j)$ with $x\in \scI(\fu)$, as $\fu \in \fC_1(k,n,j)$,
there are at least $2^{j}$ elements $\mathfrak{m}\in \mathfrak{M}(k,n)$
with $100\fu \lesssim \mathfrak{m}$ and in particular
$x\in \scI(\mathfrak{m})$. Hence
\begin{equation}\label{ubymsum}
     \mathbf{1}_{\scI(\fu)}(x)
    \le 2^{-j}\sum_{\mathfrak{m} \in \mathfrak{M}(k,n): 100\fu\lesssim \mathfrak{m}} \mathbf{1}_{\scI(\mathfrak{m})}(x)\, .
\end{equation}
Conversely, for each $\mathfrak{m}\in \mathfrak{M}(k,n)$
with $x\in \scI(\mathfrak{m})$,
let $\fU(\mathfrak{m})$ be the set of
$\fu\in \fU_1(k,n,j)$ with $x\in \scI(\fu)$
and $100\fu \lesssim \mathfrak{m}$.
Summing \eqref{ubymsum} over $\fu$ and counting the pairs
$(\fu,\mathfrak{m})$ with $100\fu \lesssim \mathfrak{m}$
differently gives
\begin{equation}\label{usumbymsum}
     \sum_{\fu\in \fU_1(k,n,j)} \mathbf{1}_{\scI(\fu)}(x)
    \le 2^{-j}\sum_{\mathfrak{m} \in \mathfrak{M}(k,n)}
    \sum_{\fu \in \fU(\mathfrak{m})} \mathbf{1}_{\scI(\mathfrak{m})}(x)\, .
\end{equation}
We estimate the number of elements in $\fU(\mathfrak{m})$.
Let $\fu \in \fU(\mathfrak{m})$.
Then by definition of
$\fU(\mathfrak{m})$
\begin{equation}\label{dby2}
     d_{\fu}(\fcc(\fu),\fcc(\mathfrak{m}))\le 100\, .
\end{equation}
If $\fu'$ is a further element in $\fU(\mathfrak{m})$ with $\fu\neq \fu'$, then
\begin{equation}
    \fcc(\mathfrak{m})
    \in B_{\fu}(\fcc(\fu),100)\cap B_{\fu'}(\fcc(\fu'),100)\ .
\end{equation}
By the last display and definition of $\fU_1(k,n,j)$, none of $\scI(\fu)$, $\scI(\fu')$ is strictly contained in the other. As both contain $x$, we have $\scI(\fu)=\scI(\fu')$.
We then have $d_{\fu}=d_{\fu'}$.

By \eqref{eq-freq-comp-ball}, the balls
$B_{\fu}(\fcc(\fu),0.2)$ and
$B_{\fu}(\fcc(\fu'),0.2)$ are
contained respectively in $\fc(\fu)$
and $\fc(\fu')$ and thus are disjoint by \eqref{eq-dis-freq-cover}.
By \eqref{dby2} and the triangle inequality, both balls are contained in $B_{\fu}(\fcc(\mathfrak{m}), 100.2)$.

By \eqref{thirddb} applied nine times, there is a collection of at most
$2^{9a}$ balls of radius $0.2$ with respect to the metric $d_{\fu}$ which cover the ball $B_{\fu}(\fcc(\mathfrak{m}),100.2)$.
Let $B'$ be a ball in this cover.
As the center of $B'$ can be in at most one of the disjoint balls
$B_{\fu}(\fcc(\fu),0.2)$ and
$B_{\fu}(\fcc(\fu'),0.2)$,
the ball $B'$ can contain at most
one of the points $\fu$, $\fu'$.

Hence the set $\fU(\mathfrak{m})$ has at most
$2^{9a}$ many elements.
Inserting this into \eqref{usumbymsum} proves the lemma.
\end{proof}

\begin{lemma}[boundary exception]
\label{boundary-exception}

Let $\mathcal{L}(\fu)$ be as defined in \eqref{eq-L-def}. We have for each $\fu\in \fU_1(k,n,l)$,
\begin{equation}
\mu(\bigcup_{I\in \mathcal{L}(\fu)} I)
\le D^{1-\kappa Z(n+1)}
        \mu(\scI(\mathfrak{u})).
\end{equation}

\end{lemma}


\begin{proof}
  Let $\fu\in \fU_1(k,n,l)$.
Let $I \in \mathcal{L}(\fu)$. Then we have $s(I) = \ps(\fu) - Z(n+1) - 1$ and $I \subset \scI(\fu)$ and $B(c(I), 8D^{s(I)}) \not \subset \scI(\fu)$.
By \eqref{eq-vol-sp-cube}, the set $I$
is contained in $B(c(I), 4D^{s(I)})$.
By the triangle inequality, the set $I$
is contained in
\begin{equation}
    X(\fu):=\{x \in \scI(\fu) \, : \, \rho(x, X \setminus \scI(\fu)) \leq 12 D^{\ps(\fu) - Z(n+1)-1}\}\,.
\end{equation}
 By the small boundary property \eqref{eq-small-boundary}, noting that
 \begin{equation*}
     12D^{\ps(\fu) - Z(n+1) - 1} = 12D^{s(I)} > D^{-S}\ ,
 \end{equation*} we have
   $$
        \mu(X(\fu)) \le
        D\cdot(12 D^{-Z(n+1)-1})^\kappa
        \mu(\scI(\mathfrak{u})).
    $$
Using $\kappa<1$ and $D \ge 12$, this proves the lemma.
\end{proof}














    \begin{lemma}[third exception]
    \label{third-exception}
\uses{tree-count,boundary-exception, top-tiles}
       We have
\begin{equation}
    \mu(G_3)\le 2^{-4} \mu(G)\, .
\end{equation}
    \end{lemma}



    \begin{proof}
As each $\fp\in \fL_4(k,n,j)$
is contained in $\cup\mathcal{L}(\fu)$ for some
$\fu\in \fU_1(k,n,l)$, we have
\begin{equation}
\mu(\bigcup_{\fp \in \fL_4 (k,n,j)}\scI(\fp))
\le \sum_{\fu\in \fU_1(k,n,j)}
\mu(\bigcup_{I \in \mathcal{L} (\fu)}I).
\end{equation}
Using \Cref{boundary-exception} and then \Cref{tree-count}, we estimate this further
 by
\begin{equation}
    \le \sum_{\fu\in \fU_1(k,n,j)}
    D^{1-\kappa Z(n+1)}
        \mu(\scI(\mathfrak{u}))
\end{equation}
\begin{equation}
    \le 2^{100a^2+9a+1-j} \sum_{\mathfrak{m}\in \mathfrak{M}(k,n)}
     D^{-\kappa Z(n+1)}
    \mu(\scI(\mathfrak{m}))\,.
\end{equation}
Using \Cref{top-tiles}, we estimate this by
  \begin{equation}
     \le
2^{100a^2 + 9a + 1-j} D^{-\kappa Z(n+1)}
     2^{n+k+3}\mu(G)\, .
\end{equation}
Now we estimate $G_3$ defined in \eqref{defineg3} by
\begin{equation}
    \mu(G_3)\le \sum_{k\ge 0}\, \sum_{n \geq k}\,
    \sum_{0\le j\le 2n+3}
    \mu(\bigcup_{\fp \in \fL_4 (k,n,j)}
    \scI(\fp))
\end{equation}
\begin{equation}
    \le \sum_{k\ge 0}\, \sum_{n \geq k}\,
    \sum_{0\le j\le 2n+3}
    2^{100a^2 + 9a + 4 + n + k -j} D^{-\kappa Z(n+1)}\mu(G)
\end{equation}
Summing geometric series, using that $D^{\kappa Z}\ge 8$ by \eqref{defineD}, \eqref{definekappa} and \eqref{defineZ}, we estimate this by
\begin{equation}
    \le \sum_{k\ge 0}\, \sum_{n \geq k}\,
    2^{100a^2 + 9a + 5 + n + k} D^{-\kappa Z(n+1)}\mu(G)
\end{equation}
\begin{equation}
    = \sum_{k\ge 0} 2^{100a^2 + 9a + 5 + 2k} D^{-\kappa Z(k+1)} \sum_{n \geq k}\,
    2^{n - k} D^{-\kappa Z(n-k)}\mu(G)
\end{equation}
\begin{equation}
    \le \sum_{k\ge 0} 2^{100a^2 + 9a + 6 + 2k} D^{-\kappa Z(k+1)}\mu(G)
\end{equation}
\begin{equation}
   \le 2^{100a^2 + 9a + 7} D^{-\kappa Z}\mu(G)
\end{equation}
Using $D = 2^{100a^2}$ and $a \ge 4$ and $\kappa Z \ge 2$ by \eqref{defineD} and \eqref{definekappa} proves the lemma.
\end{proof}

\section{Auxiliary lemmas}
\label{subsec-lessim-aux}
Before proving \Cref{forest-union} and \Cref{forest-complement}, we collect some useful properties of $\lesssim$.

\begin{lemma}[wiggle order 1]
    \label{wiggle-order-1}

    If $n\fp \lesssim m\fp'$ and
    $n' \ge n$ and $m \ge m'$ then $n'\fp \lesssim m'\fp'$.
\end{lemma}

\begin{proof}
    This follows immediately from the definition \eqref{wiggleorder} of $\lesssim$ and the two inclusions $B_{\fp}(\fcc(\fp), n) \subset B_{\fp}(\fcc(\fp), n')$ and $B_{\fp'}(\fcc(\fp'), m') \subset B_{\fp'}(\fcc(\fp'), m)$.
\end{proof}

\begin{lemma}[wiggle order 2]
    \label{wiggle-order-2}
    \uses{monotone-cube-metrics}

    Let $n, m \ge 1$.
    If $\fp, \fp' \in \fP$ with $\scI(\fp) \ne \scI(\fp')$ and
    \begin{equation}
        \label{eq-wiggle1}
        n \fp \lesssim \fp'
    \end{equation}
    then
    \begin{equation}
        \label{eq-wiggle2}
        (n + 2^{-95 a} m) \fp \lesssim m\fp'\,.
    \end{equation}
\end{lemma}

\begin{proof}
    The assumption \eqref{eq-wiggle1} together with the definition \eqref{wiggleorder} of $\lesssim$ implies that $\scI(\fp) \subsetneq \scI(\fp')$. Let $\mfa \in B_{\fp'}(\fcc(\fp'), m)$. Then we have by the triangle inequality
    $$
        d_{\fp}(\fcc(\fp), \mfa) \le d_{\fp}(\fcc(\fp), \fcc(\fp')) + d_{\fp}(\fcc(\fp'), \mfa)
    $$
    Using \eqref{eq-wiggle1} and \eqref{wiggleorder} for the first summand, and \Cref{monotone-cube-metrics} for the second summand, this is estimated by
    $$
        n + 2^{-95a} d_{\fp'}(\fcc(\fp'), \mfa) < n + 2^{-95a} m\,.
    $$
    Thus $B_{\fp'}(\fcc(\fp'),m) \subset B_{\fp}(\fcc(\fp),n + 2^{-95a}m)$. Combined with $\scI(\fp) \subset \scI(\fp')$, this yields \eqref{eq-wiggle2}.
\end{proof}

\begin{lemma}[wiggle order 3]
\label{wiggle-order-3}
\uses{wiggle-order-1, wiggle-order-2}
    The following implications hold for all $\fq, \fq' \in \fP$:
    % Note: some fixes were suggested by Georges Gonthier
    \begin{equation}
        \label{eq-sc1}
        \fq \le \fq' \ \text{and} \ \lambda \ge 2 \implies \lambda \fq \lesssim \lambda \fq'\,,
    \end{equation}
    \begin{equation}
        \label{eq-sc2}
        10\fq \lesssim \fq' \ \text{and} \ \scI(\fq) \ne \scI(\fq') \implies 100 \fq \lesssim 100 \fq'\,,
    \end{equation}
    \begin{equation}
        \label{eq-sc3}
        2\fq \lesssim \fq' \ \text{and} \ \scI(\fq) \ne \scI(\fq') \implies 4 \fq \lesssim 500 \fq'\,.
    \end{equation}
\end{lemma}

\begin{proof}
    All three implications are easy consequences of \Cref{wiggle-order-1}, \Cref{wiggle-order-2} and the fact that $a \ge 4$.
\end{proof}



We call a collection $\mathfrak{A}$ of tiles convex if
\begin{equation}
    \label{eq-convexity}
    \fp \le \fp' \le \fp'' \ \text{and} \ \fp, \fp'' \in \mathfrak{A} \implies \fp' \in \mathfrak{A}\,.
\end{equation}

\begin{lemma}[P convex]
    \label{P-convex}

    For each $k$, the collection $\fP(k)$ is convex.
\end{lemma}

\begin{proof}
    Suppose that $\fp \le \fp' \le \fp''$ and $\fp, \fp'' \in \fP(k)$. By \eqref{eq-defPk} we have $\scI(\fp), \scI(\fp'') \in \mathcal{C}(G,k)$, so there exists by \eqref{muhj1} some $J \in \mathcal{D}$ with
    $$
        \scI(\fp') \subset \scI(\fp'') \subset J
    $$
    and $\mu(G \cap J) > 2^{-k-1} \mu(J)$. Thus \eqref{muhj1} holds for $\scI(\fp')$. On the other hand, by \eqref{muhj2}, there exists no $J \in \mathcal{D}$ with $\scI(\fp) \subset J$ and $\mu(G \cap J) > 2^{-k} \mu(J)$. Since $\scI(\fp) \subset \scI(\fp')$, this implies that \eqref{muhj2} holds for $\scI(\fp')$. Hence $\scI(\fp') \in \mathcal{C}(G,k)$, and therefore by \eqref{eq-defPk} $\fp' \in \fP(k)$.
\end{proof}

\begin{lemma}[C convex]
    \label{C-convex}
    \uses{P-convex}
    For each $k,n$, the collection $\fC(k,n)$ is convex.
\end{lemma}

\begin{proof}
    Let $\fp \le \fp' \le \fp''$ with $\fp, \fp'' \in \fC(k,n)$. Then, in particular, $\fp, \fp'' \in \fP(k)$, so, by \Cref{P-convex}, $\fp' \in \fP(k)$. Next, we show that if $\fq \le \fq' \in \fP(k)$ then $\dens'_k(\{\fq\}) \ge \dens_k'(\{\fq'\})$. If $\fp \in \fP(k)$ and $\lambda \ge 2$ with $\lambda \fq' \lesssim \lambda \fp$, then it follows from $\fq \le \fq'$, \eqref{eq-sc1} of \Cref{wiggle-order-3} and transitivity of $\lesssim$ that $\lambda \fq \lesssim \lambda \fp$. Thus the supremum in the definition \eqref{eq-densdef} of $\dens_k'(\{\fq\})$ is over a superset of the set the supremum in the definition of $\dens_k'(\{\fq'\})$ is taken over, which shows $\dens'_k(\{\fq\}) \ge \dens_k'(\{\fq'\})$. From $\fp' \le \fp''$, $\fp'' \in \fC(k,n)$ and \eqref{def-cnk} it then follows that
    $$
        2^{4a}2^{-n} < \dens_k'(\{\fp''\}) \le \dens_k'(\{\fp'\})\,.
    $$
    Similarly, it follows from $\fp \le \fp'$, $\fp \in \fC(k,n)$ and \eqref{def-cnk} that
    $$
        \dens_k'(\{\fp'\}) \le \dens_k'(\{\fp\}) \le 2^{4a}2^{-n+1}\,.
    $$
    Thus $\fp' \in \fC(k,n)$.
\end{proof}

\begin{lemma}[C1 convex]
    \label{C1-convex}
    \uses{C-convex}
    For each $k,n,j$, the collection $\fC_1(k,n,j)$ is convex.
\end{lemma}

\begin{proof}
    Let $\fp\le\fp'\le\fp''$ with $\fp, \fp'' \in \fC_1(k,n,j)$. By \Cref{C-convex} and the inclusion $\fC_1(k,n,j) \subset \fC(k,n)$, which holds by definition \eqref{defcnkj}, we have $\fp' \in \fC(k,n)$. By \eqref{eq-sc1} and transitivity of $\lesssim$ we have that $\fq \le \fq'$ and $100 \fq' \lesssim \mathfrak{m}$ imply $100 \fq \lesssim \mathfrak{m}$. So, by \eqref{defbfp}, $\mathfrak{B}(\fp'') \subset \mathfrak{B}(\fp') \subset \mathfrak{B}(\fp)$. Consequently, by \eqref{defcnkj}
    $$
        2^j \le |\mathfrak{B}(\fp'')|\le |\mathfrak{B}(\fp')| \le |\mathfrak{B}(\fp)| < 2^{j+1}\,,
    $$
    thus $\fp' \in \fC_1(k,n,j)$.
\end{proof}

\begin{lemma}[C2 convex]
    \label{C2-convex}
    \uses{C1-convex}
    For each $k,n,j$, the collection $\fC_2(k,n,j)$ is convex.
\end{lemma}

\begin{proof}
     Let $\fp \le \fp' \le \fp''$ with $\fp, \fp'' \in \fC_2(k,n,j)$. By \eqref{eq-C2-def}, we have
     \begin{equation*}
         \fC_2(k,n,j) \subset \fC_1(k,n,j)\ .
     \end{equation*} Combined with \Cref{C1-convex}, it follows that $\fp' \in \fC_1(k,n,j)$. Suppose that $\fp' \notin \fC_2(k,n,j)$. By \eqref{eq-C2-def}, this implies that there exists $0 \le l' \le Z(n+1)$ with $\fp' \in \fL_1(k,n,j,l')$. By the definition \eqref{eq-L1-def} of $\fL_1(k,n,j,l')$, this implies that $\fp$ is minimal with respect to $\le$ in $\fC_1(k,n,j) \setminus \bigcup_{l < l'} \fL_1(k,n,j,l)$. Since $\fp \in \fC_2(k,n,j)$ we must have $\fp \ne \fp'$. Thus $\fp \le \fp'$ and $\fp \ne \fp'$. By minimality of $\fp'$ it follows that $\fp \notin \fC_1(k,n,j) \setminus \bigcup_{l < l'} \fL_1(k,n,j,l)$. But by \eqref{eq-C2-def} this implies $\fp \notin \fC_2(k,n,j)$, a contradiction.
\end{proof}

\begin{lemma}[C3 convex]
    \label{C3-convex}
    \uses{C2-convex}
    For each $k,n,j$, the collection $\fC_3(k,n,j)$ is convex.
\end{lemma}

\begin{proof}
    Let $\fp \le \fp' \le \fp''$ with $\fp, \fp'' \in \fC_3(k,n,j)$. By \eqref{eq-C3-def} and \Cref{C2-convex} it follows that $\fp' \in \fC_2(k,n,j)$. Suppose that $\fp' \notin \fC_3(k,n,j)$. Then, by \eqref{eq-C3-def} and \eqref{eq-L2-def}, there exists $\fu \in \fU_1(k,n,j)$ with $2\fp' \lesssim \fu$ and $\scI(\fp') \ne \scI(\fu)$. Together this gives $\scI(\fp') \subsetneq \scI(\fu)$. From $\fp' \le \fp$, \eqref{eq-sc1} and transitivity of $\lesssim$ we then have $2\fp \lesssim \fu$. Also, $\scI(\fp) \subset \scI(\fp') \subsetneq \scI(\fu)$, so $\scI(\fp) \ne \scI(\fu)$. But then $\fp \in \fL_2(k,n,j)$, contradicting by \eqref{eq-C3-def} the assumption $\fp \in \fC_3(k,n,j)$.
\end{proof}

\begin{lemma}[C4 convex]
    \label{C4-convex}
    \uses{C3-convex}
    For each $k,n,j$, the collection $\fC_4(k,n,j)$ is convex.
\end{lemma}

\begin{proof}
    Let $\fp \le \fp' \le\fp''$ with $\fp, \fp'' \in \fC_4(k,n,j)$. As before we obtain from the inclusion $\fC_4(k,n,j) \subset \fC_3(k,n,j)$ and \Cref{C3-convex} that $\fp' \in \fC_3(k,n,j)$. Thus, if $\fp' \notin \fC_4(k,n,j)$ then by \eqref{eq-L3-def} there exists $l$ such that $\fp' \in \fL_3(k,n,j,l)$. Thus $\fp'$ is maximal with respect to $\le$ in $\fC_3(k,n,j) \setminus \bigcup_{0 \le l' < l} \fL_3(k,n,j,l')$. Since $\fp'' \in \fC_4(k,n,j)$ we must have $\fp' \ne \fp''$. Thus $\fp' \le \fp''$ and $\fp'\ne \fp''$. By minimality of $\fp'$ it follows that $\fp'' \notin \fC_3(k,n,j) \setminus \bigcup_{l < l'} \fL_3(k,n,j,l)$. But by \eqref{eq-C4-def} this implies $\fp'' \notin \fC_4(k,n,j)$, a contradiction.
\end{proof}

\begin{lemma}[C5 convex]
    \label{C5-convex}
    \uses{C4-convex}
    For each $k,n,j$, the collection $\fC_5(k,n,j)$ is convex.
\end{lemma}

\begin{proof}
    Let $\fp \le \fp' \le\fp''$ with $\fp, \fp'' \in \fC_5(k,n,j)$. Then $\fp, \fp'' \in \fC_4(k,n,j)$ by \eqref{defc5}, and thus by \Cref{C4-convex} also $\fp' \in \fC_4(k,n,j)$. Suppose that $\fp' \notin \fC_5(k,n,j)$. By \eqref{defc5}, it follows that $\fp' \in \fL_4(k,n,j)$.
    By \eqref{eq-L4-def}, there exists $\fu \in \fU_1(k,n,j)$ with $\scI(\fp') \subset \bigcup \mathcal{L}(\fu)$. Then also $\scI(\fp) \subset \bigcup \mathcal{L}(\fu)$, a contradiction.
\end{proof}

\begin{lemma}[dens compare]
    \label{dens-compare}

    We have for every $k\ge 0$ and $\fP'\subset \fP(k)$
\begin{equation}
    \dens_1(\fP')\le \dens_k'(\fP')\, .
\end{equation}
\end{lemma}
\begin{proof}
It suffices to show that for all $\fp'\in \fP'$
and $\lambda\ge 2$ and $\fp\in \fP(\fP')$ with $\lambda \fp' \lesssim \lambda \fp$ we have
\begin{equation}
    \frac{\mu({E}_2(\lambda, \fp))}{\mu(\scI(\fp))}
    \le \sup_{\fp'' \in \fP(k): \lambda \fp' \lesssim \lambda \fp''}
    \frac{\mu({E}_2(\lambda, \fp''))}{\mu(\scI(\fp''))}.
\end{equation}
    Let such $\fp'$, $\lambda$, $\fp$ be given.
    It suffices to show that $\fp\in \fP(k)$,
    that is, it satisfies \eqref{muhj1}
    and \eqref{muhj2}.

We show \eqref{muhj1}.
 As $\fp\in \fP(\fP')$, there exists
$\fp''\in \fP'$ with $\scI(\fp')\subset \scI(\fp'')$. By assumption on $\fP'$, we have $\fp''\in \fP(k)$ and there exists
$J\in \mathcal{D}$ with
   $\scI(\fp'')\subset J$ and
   \begin{equation}
       \mu(G\cap J)>2^{-k-1} \mu(J).
   \end{equation}
Then also $\scI(\fp')\subset J$, which proves
\eqref{muhj1} for $\fp$.

We show \eqref{muhj2}. Assume to get a contradiction that
there exists $J\in \mathcal{D}$ with
   $\scI(\fp)\subset J$ and
   \begin{equation}\label{mugj}
       \mu(G\cap J)>2^{-k} \mu(J).
   \end{equation}
   As $\lambda\fp'\lesssim \lambda\fp$, we have $\scI(\fp')\subset \scI(\fp)$, and therefore
    $\scI(\fp')\subset J$. This contradicts
   $\fp'\in \fP'\subset \fP(k)$. This proves
\eqref{muhj2} for $\fp$.
\end{proof}

\begin{lemma}[C dens1]
    \label{C-dens1}
    \uses{dens-compare}
    For each set $\mathfrak{A} \subset \mathfrak{C}(k,n)$, we have
    $$
        \dens_1(\mathfrak{A}) \le 2^{4a}2^{-n+1}\,.
    $$
\end{lemma}

\begin{proof}
    We have by \Cref{dens-compare} that
    $\dens_1(\mathfrak{A}) \le \dens_k'(\mathfrak{A})$. Since $\mathfrak{A} \subset \fC(k,n)$, it follows from monotonicity of suprema and the definition \eqref{eq-densdef} that
    $
        \dens_k'(\mathfrak{A}) \le \dens_k'(\fC(k,n))\,.
    $
    By \eqref{eq-densdef} and \eqref{def-cnk}, we have
    $$
        \dens_k'(\fC(k,n)) = \sup_{\fp \in \fC(k,n)} \dens_k'(\{\fp\}) \le 2^{4a}2^{-n+1}\,.
    $$
\end{proof}

\section{Proof of the Forest Union Lemma}
\label{subsecforest}

Fix $k,n,j\ge 0$.
Define
$$
    \fC_6(k,n,j)
$$
to be the set of all tiles $\fp \in \fC_5(k,n,j)$ such that $\scI(\fp) \not\subset G'$. The following chain of lemmas
establishes that the set $\fC_6(k,n,j)$ can be written as a union of a small number of $n$-forests.

For $\fu\in \fU_1(k,n,j)$, define
\begin{equation}
    \label{eq-T1-def}
    \mathfrak{T}_1(\fu):= \{\fp \in \fC_1(k,n,j) \ : \scI(\fp)\neq \scI(\fu), \ 2\fp \lesssim \fu\}\,.
\end{equation}
Define
\begin{equation}
    \label{eq-U2-def}
    \fU_2(k,n,j) := \{ \fu \in \fU_1(k,n,j) \, : \, \mathfrak{T}_1(\fu) \cap \fC_6(k,n,j) \ne \emptyset\}\,.
\end{equation}

Define a relation $\sim$ on $\fU_2(k,n,j)$
by setting $\fu\sim \fu'$
for $\fu,\fu'\in \fU_2(k,n,j)$
if $\fu=\fu'$ or there exists $\fp$ in $\mathfrak{T}_1(\fu)$
with $10 \fp\lesssim \fu'$.

\begin{lemma}[relation geometry]
    \label{relation-geometry}
    \uses{wiggle-order-3}
    If $\fu \sim \fu'$, then $\scI(u) = \scI(u')$ and
    \begin{equation*}
        B_{\fu}(\fcc(\fu), 100) \cap B_{\fu'}(\fcc(\fu'), 100) \neq \emptyset\ .
    \end{equation*}
\end{lemma}

\begin{proof}
    Let $\fu, \fu' \in \fU_2(k,n,j)$ with $\fu \sim \fu'$. If $\fu = \fu'$ then the conclusion of the Lemma clearly holds. Else, there exists $\fp \in \fC_1(k,n,j)$ such that $\scI(\fp) \ne \scI(\fu)$ and $2 \fp \lesssim \fu$ and $10 \fp \lesssim \fu'$.
    Using \Cref{wiggle-order-1} and \eqref{eq-sc2} of \Cref{wiggle-order-3}, we deduce that
    \begin{equation}
        \label{eq-Fefferman-trick0}
        100 \fp\lesssim 100 \fu\,, \qquad 100 \fp \lesssim 100\fu'\,.
    \end{equation}
    Now suppose that $B_{\fu}(\fcc(\fu), 100) \cap B_{\fu'}(\fcc(\fu'), 100) = \emptyset$. Then we have $\mathfrak{B}(\fu) \cap \mathfrak{B}(\fu') = \emptyset$, by the definition \eqref{defbfp} of $\mathfrak{B}$ and the definition \eqref{wiggleorder} of $\lesssim$, but also $\mathfrak{B}(\fu) \subset \mathfrak{B}(\fp)$ and $\mathfrak{B}(\fu') \subset \mathfrak{B}(\fp)$, by \eqref{defbfp}, \eqref{wiggleorder} and \eqref{eq-Fefferman-trick0}
    Hence,
    $$
        |\mathfrak{B}(\fp)| \geq |\mathfrak{B}(\fu)| + |\mathfrak{B}(\fu')| \geq 2^{j} + 2^j = 2^{j+1}\,,
    $$
    which contradicts $\fp \in \fC_1(k,n,j)$. Therefore we must have
    \begin{equation*}
        B_{\fu}(\fcc(\fu), 100) \cap B_{\fu'}(\fcc(\fu'), 100) \ne \emptyset\, .
    \end{equation*}

    It follows from $2\fp \lesssim \fu$ and $10\fp \lesssim \fu'$ that $\scI(\fp) \subset \scI(\fu)$ and $\scI(\fp) \subset \scI(\fu')$. By \eqref{dyadicproperty}, it follows that $\scI(\fu)$ and $\scI(\fu')$ are nested.
    Combining this with the conclusion of the last paragraph and definition \eqref{defunkj} of $\fU_1(k,n,j)$, we obtain that $\scI(\fu) = \scI(\fu')$.
\end{proof}


\begin{lemma}[equivalence relation]
\label{equivalence-relation}
\uses{relation-geometry}
For each $k,n,j$, the relation $\sim$ on
$\fU_2(k,n,j)$ is an equivalence relation.
\end{lemma}

\begin{proof}
    Reflexivity holds by definition.
    For transitivity, suppose that
    \begin{equation*}
        \fu, \fu', \fu'' \in \fU_1(k,n,j)
    \end{equation*}
    and $\fu \sim \fu'$, $\fu' \sim \fu''$.
    By \Cref{relation-geometry}, it follows that $\scI(\fu) =\scI(\fu') = \scI(\fu'')$, that there exists
    \begin{equation*}
        \mfa \in B_{\fu}(\fcc(\fu), 100) \cap B_{\fu'}(\fcc(\fu'), 100)
    \end{equation*}
    and that there exists
    \begin{equation*}
        \mfb \in B_{\fu'}(\fcc(\fu'), 100) \cap B_{\fu''}(\fcc(\fu''), 100)\, .
    \end{equation*}
    If $\fu = \fu'$, then $\fu \sim \fu''$ holds by assumption. Else, there exists by the definition of $\sim$ some $\fp \in \mathfrak{T}_1(\fu)$ with $10\fp\lesssim \fu'$.
    Then we have $2\fp \lesssim \fu$ and $\fp \ne \fu$ by definition of $\mathfrak{T}_1(\fu)$, so $4 \fp \lesssim 500 \fu$ by \eqref{eq-sc3}. For $q \in B_{\fu''}(\fcc(\fu''), 1)$ it follows by the triangle inequality that
    \begin{align*}
        d_{\fu}(\fcc(\fu), q) &\le d_{\fu}(\fcc(\fu), \mfa) + d_{\fu}(\mfa, \fcc(\fu'))\\
        &\quad+ d_{\fu}(\fcc(\fu'), \mfb) + d_{\fu}(\mfb, \fcc(\fu'')) +
        d_{\fu}(\fcc(\fu''), q)\,.
    \end{align*}
    Using \eqref{defdp} and the fact that $\scI(\fu) = \scI(\fu') = \scI(\fu'')$ this equals
    \begin{align*}
        &\quad d_{\fu}(\fcc(\fu), \mfa) + d_{\fu'}(\mfa, \fcc(\fu'))\\
        &\quad+ d_{\fu'}(\fcc(\fu'), \mfb) + d_{\fu''}(\mfb, \fcc(\fu'')) +
        d_{\fu''}(\fcc(\fu''), q)\\
        &< 100 + 100 + 100 + 100 + 1 < 500\,.
    \end{align*}
    Since $4\fp \lesssim 500 \fu$, it follows that $d_{\fp}(\fcc(\fp), q) < 4 < 10$. We have shown that $B_{\fu''}(\fcc(\fu''), 1) \subset B_{\fp}(\fcc(\fp), 10)$, combining this with $\scI(\fu'') = \scI(\fu)$ gives $\fu \sim \fu''$.

    For symmetry suppose that $\fu \sim \fu'$. By Lemma \eqref{relation-geometry}, it follows that $\scI(\fu) = \scI(\fu')$ and that there exists $\mfa \in B_{\fu}(\fcc(\fu), 100) \cap B_{\fu'}(\fcc(\fu'), 100)$. Again, for $\fu = \fu'$ symmetry is obvious. If $\fu \ne \fu'$, then there exists $\fp \in \mathfrak{T}_1(\fu')$ with $10\fp\lesssim \fu$. By definition of $\mathfrak{T}_1(\fu')$, \Cref{wiggle-order-1} and \eqref{eq-sc3}, it follows that
    \begin{equation}
        \label{eq-rel1}
        10\fp \lesssim 4\fp \lesssim 500 \fu'\,.
    \end{equation}
    If $q \in B_{\fu}(\fcc(\fu),1)$ then we have from the triangle inequality and the fact that $\scI(\fu) = \scI(\fu')$:
    \begin{align*}
        d_{\fu'}(\fcc(\fu'), q) &\le d_{\fu'}(\fcc(\fu'), \mfa) + d_{\fu'}(\mfa, \fcc(\fu)) + d_{\fu'}(\fcc(\fu), q)\\
        &= d_{\fu'}(\fcc(\fu'), \mfa) + d_{\fu}(\mfa, \fcc(\fu)) + d_{\fu}(\fcc(\fu), q)\\
        &< 100 + 100 + 1 < 500\,.
    \end{align*}
    Combining this with \eqref{eq-rel1} and \eqref{wiggleorder}, we get
    \begin{equation*}
     B_{\fu}(\fcc(\fu), 1) \subset B_{\fp}(\fcc(\fp), 10)\, .
    \end{equation*}
    Since $2\fp \lesssim \fu'$, we have $\scI(\fp) \subset \scI(\fu') = \scI(\fu)$. Thus, $10\fp \lesssim \fu$ which completes the proof of $\fu' \sim \fu$.
\end{proof}

Choose a set $\fU_3(k,n,j)$ of representatives for the equivalence
classes of $\sim$ in $\fU_2(k,n,j)$.
Define for each $\fu\in \fU_3(k,n,j)$
\begin{equation}\label{definesv}
\fT_2(\fu):=
   \bigcup_{\fu\sim \fu'}\mathfrak{T}_1(\fu')\cap \fC_6(k,n,j)\, .
\end{equation}

\begin{lemma}[C6 forest]
\label{C6-forest}
\uses{equivalence-relation}
We have
\begin{equation}
    \fC_6(k,n,j)=\bigcup_{\fu\in \fU_3(k,n,j)}\mathfrak{T}_2(\fu)\, .
\end{equation}
\end{lemma}
\begin{proof}
    Let $\fp \in \fC_6(k,n,j)$.
    By \eqref{eq-C4-def} and \eqref{defc5}, we have $\fp \in \fC_3(k,n,j)$. By \eqref{eq-L2-def} and \eqref{eq-C3-def}, there exists $\fu \in \fU_1(k,n,j)$ with $2\fp \lesssim \fu$ and $\scI(\fp) \ne \scI(\fu)$, that is, with $\fp \in \mathfrak{T}_1(\fu)$. Then $\mathfrak{T}_1(\fu)$ is clearly nonempty, so $\fu \in \fU_2(k,n,j)$. By the definition of $\fU_3(k,n,j)$, there exists $\fu' \in \fU_3(k,n,j)$ with $\fu \sim \fu'$. By \eqref{definesv}, we have $\fp \in \mathfrak{T}_2(\fu')$.
\end{proof}

\begin{lemma}[C6 convex]
    \label{C6-convex}
    \uses{C5-convex}
    Let $\fu \in \fU_3(k,n,j)$. If $\fp \le \fp' \le \fp''$ and $\fp, \fp'' \in \mathfrak{T}_2(\fu)$, then $\fp' \in \mathfrak{T}_2(\fu)$.
\end{lemma}

\begin{proof}
    Suppose that $\fp, \fp'' \in \mathfrak{T}_2(\fu)$. Then by \Cref{C5-convex}, we have
$\fp' \in \fC_5(k,n,j)$. Since $\fp \in \fC_6(k,n,j)$ we have $\scI(\fp) \not\subset G'$, hence $\scI(\fp') \not \subset G'$. This implies $\fp' \in \fC_6(k,n,j)$. Since $\fp'' \in \mathfrak{T}_2(\fu)$, we have $2\fp'' \lesssim \fu'$ and $\scI(\fp'')\ne\scI(\fu')$ for some $\fu' \sim \fp''$. By \eqref{eq-sc1}, we have $2\fp' \lesssim 2\fp''$, so by transitivity of $\lesssim$ we have $2\fp' \lesssim \fu'$. Finally, $\scI(\fp') \subset \scI(\fp'')$ implies $\scI(\fp') \ne \scI(\fu')$, thus $\fp' \in \mathfrak{T}_1(\fu') \subset \mathfrak{T}_2(\fu)$.
\end{proof}


\begin{lemma}[forest geometry]
    \label{forest-geometry}
    \uses{relation-geometry}
    For each $\fu\in \fU_3(k,n,j)$,
    the set $\mathfrak{T}_2(\fu)$
    satisfies \eqref{forest1}.
\end{lemma}
\begin{proof}
    Let $\fp \in \mathfrak{T}_2(\fu)$. By \eqref{definesv}, there exists $\fu' \sim \fu$ with $\fp \in \mathfrak{T}_1(\fu')$. Then we have $2\fp \lesssim \fu'$ and $\scI(\fp) \ne \scI(\fu')$, so by \eqref{eq-sc3} $4\fp \lesssim 500\fu'$.
    Further, by \Cref{relation-geometry}, we have that $\scI(\fu') = \scI(\fu)$ and there exists $\mfa \in B_{\fu'}(\fcc(\fu'),100) \cap B_{\fu}(\fcc(\fu),100)$.
    Let $\mfb \in B_{\fu}(\fcc(\fu), 1)$.
    Using the triangle inequality and the fact that $\scI(\fu') =\scI(\fu)$, we obtain
    \begin{align*}
        d_{\fu'}(\fcc(\fu'), \mfb) &\le d_{\fu'}(\fcc(\fu'), \mfa) + d_{\fu'}(\fcc(\fu), \mfa) + d_{\fu'}(\fcc(\fu), \mfb)\\
        &= d_{\fu'}(\fcc(\fu'), \mfa) + d_{\fu}(\fcc(\fu), \mfa) + d_{\fu}(\fcc(\fu), \mfb)\\
        &< 100 + 100 + 1 < 500\,.
    \end{align*}
    Combining this with $4\fp \lesssim 500\fu'$, we obtain
    $$
        B_{\fu}(\fcc(\fu), 1) \subset B_{\fu'}(\fcc(\fu'), 500) \subset B_{\fp}(\fcc(\fp), 4)\,.
    $$
    Together with $\scI(\fp) \subset \scI(\fu') = \scI(\fu)$, this gives $4\fp \lesssim 1\fu$, which is \eqref{forest1}.
\end{proof}

\begin{lemma}[forest convex]
    \label{forest-convex}
    \uses{C6-convex}
    For each $\fu\in \fU_3(k,n,j)$,
    the set $\mathfrak{T}_2(\fu)$
    satisfies the convexity condition \eqref{forest2}.
\end{lemma}

\begin{proof}
    Let $\fp, \fp'' \in \mathfrak{T}_2(\fu)$ and $\fp' \in \fP$ with $\fp \le \fp' \le \fp''$. By \eqref{definesv} we have $\fp, \fp'' \in \fC_6(k,n,j) \subset \fC_5(k,n,j)$. By \Cref{C5-convex}, we have $\fp' \in \fC_5(k,n,j)$. Since $\fp \in \fC_6(k,n,j)$ we have $\scI(\fp) \not \subset G'$, so $\scI(\fp') \not \subset G'$ and therefore also $\fp' \in \fC_6(k,n,j)$.

    By \eqref{definesv} there exists $\fu' \in \fU_2(k,n,j)$ with $\fp'' \in \mathfrak{T}_1(\fu')$ and hence $2\fp'' \lesssim \fu'$ and $\scI(\fp'') \ne \scI(\fu')$. Together this implies $\scI(\fp'') \subsetneq \scI(\fu')$. With the inclusion $\scI(\fp') \subset \scI(\fp'')$ from $\fp' \le \fp''$, it follows that $\scI(\fp') \subsetneq \scI(\fu')$ and hence $\scI(\fp') \ne \scI(\fu')$.
    By \eqref{eq-sc1} and transitivity of $\lesssim$ we further have $2\fp' \lesssim \fu'$, so $\fp' \in \mathfrak{T}_1(\fu')$.
    It follows that $\fp' \in \mathfrak{T}_2(\fu)$, which shows \eqref{forest2}.
\end{proof}

\begin{lemma}[forest separation]
    \label{forest-separation}
    \uses{monotone-cube-metrics}
    For each $\fu,\fu'\in \fU_3(k,n,j)$ with $\fu\neq \fu'$ and each $\fp \in \fT_2(\fu)$
    with $\scI(\fp)\subset \scI(\fu')$ we have
    \begin{equation}
    d_{\fp}(\fcc(\fp), \fcc(\fu')) > 2^{Z(n+1)}\,.
    \end{equation}
\end{lemma}

\begin{proof}
    By the definition \eqref{eq-C2-def} of $\fC_2(k,n,j)$, there exists a tile $\fp' \in \fC_1(k,n,j)$ with $\fp' \le \fp$ and $\ps(\fp') = \ps(\fp)- Z(n+1)$.
    By \Cref{monotone-cube-metrics} we have
    $$
        d_{\fp}(\fcc(\fp), \fcc(\fu')) \ge 2^{95a Z(n+1)} d_{\fp'}(\fcc(\fp), \fcc(\fu'))\,.
    $$
    By \eqref{eq-sc1} we have $2\fp' \lesssim 2\fp$, so by transitivity of $\lesssim$ there exists $\mathfrak{v} \sim \fu$ with $2\fp' \lesssim \mathfrak{v}$ and $\scI(\fp') \ne \scI(\mathfrak{v})$. Since $\fu, \fu'$ are not equivalent under $\sim$, we have $\mathfrak{v} \not \sim \fu'$, thus $10\fp' \not\lesssim \fu'$. This implies that there exists $q \in B_{\fu'}(\fcc(\fu'), 1) \setminus B_{\fp'}(\fcc(\fp'), 10)$.

    From $\fp' \le \fp$, $\scI(\fp') \subset \scI(\fp) \subset \scI(\fu')$ and \Cref{monotone-cube-metrics} it then follows that
    \begin{align*}
        &\quad d_{\fp'}(\fcc(\fp), \fcc(\fu'))\\
        &\ge -d_{\fp'}(\fcc(\fp), \fcc(\fp')) + d_{\fp'}(\fcc(\fp'), q) - d_{\fp'}(q, \fcc(\fu'))\\
        &\ge -d_{\fp'}(\fcc(\fp), \fcc(\fp')) + d_{\fp'}(\fcc(\fp'), q) - d_{\fu'}(q, \fcc(\fu'))\\
        &> -1 + 10 - 1 = 8\,.
    \end{align*}
    The lemma follows by combining the two displays with the fact that $95 a \ge 1$.
\end{proof}

\begin{lemma}[forest inner]
    \label{forest-inner}
    \uses{relation-geometry}
    For each $\fu\in \fU_3(k,n,j)$
    and each $\fp \in \mathfrak{T}_2(\fu)$
    we have
    \begin{equation}
        B(\pc(\fp), 8 D^{\ps(\fp)}) \subset \scI(\fu).
    \end{equation}
\end{lemma}

\begin{proof}
    Let $\fp \in \mathfrak{T}_2(\fu)$. Let
    \begin{equation}
        \label{eq-c3-tree}
        \fq \in \bigcup_{\fu \sim \fu'} \mathfrak{T}_1(\fu') \cap \fC_3(k,n,j)
    \end{equation}
    be a maximal element of this set with respect to $\le$ such that $\fp \le \fq$.
    We show that there is no $\fq' \in \fC_3(k,n,j)$ with $\fq \le \fq'$ and $\fq \ne \fq'$. Indeed, suppose $\fq'$ was such a tile.
    By \eqref{eq-C3-def} there exists $\fu'' \in \fU_1(k,n,j)$ with $2\fq' \lesssim \fu''$. Then we have in particular by \Cref{wiggle-order-1} that $10 \fp \lesssim \fu''$. Let $\fu' \sim \fu$ be such that $\fp \in \mathfrak{T}_1(\fu')$. By definition of $\sim$, we have $\fu' \sim \fu''$, hence $\fu \sim \fu''$. This implies that $\fq'$ is in the set in \eqref{eq-c3-tree}, contradicting maximality of $\fq$.

    Let $\fu' \sim \fu$ with $\fq \in \mathfrak{T}_1(\fu')$. By the definition \eqref{eq-T1-def} of $\mathfrak{T}_1$, we have $\ps(\fp) < \ps(\fu')$. By \Cref{relation-geometry}, we have $\ps(\fu) = \ps(\fu')$, hence $\ps(\fq) < \ps(\fu)$. By definition of $\fC_4(k,n,j)$, $\fp$ is not in any of the maximal $Z(n+1)$ layers of tiles in $\fC_3(k,n,j)$, and hence $\ps(\fp) \le \ps(\fq) - Z(n+1) \le \ps(\fu) - Z(n+1) - 1$.

    Thus, there exists some cube $I \in \mathcal{D}$ with $s(I) = \ps(\fu) - Z(n+1) - 1$ and $I \subset \scI(\fu)$ and $\scI(\fp) \subset I$. Since $\fp \in \fC_5(k,n,j)$, we have that $I \notin \mathcal{L}(\fu)$, so $B(c(I), 8D^{s(I)}) \subset \scI(\fu)$. By the triangle inequality, \eqref{defineD} and $a \ge 4$, the same then holds for the subcube $\scI(\fp) \subset I$.
\end{proof}


\begin{lemma}[forest stacking]
    \label{forest-stacking}
    It holds that
    \begin{equation}
        \sum_{\fu \in \fU_3(k,n,j)} \mathbf{1}_{\scI(\fu)} \le 1 + (4n+12)2^{n}\,.
    \end{equation}
    % Note(Georges Gonthier): Because we removed the `1 +` from \eqref{eq-Aoverlap-def} we can also remove the 1+ here.
\end{lemma}

\begin{proof}
    Suppose that a point $x$ is contained in more than $1 + (4n + 12)2^n$ cubes $\scI(\fu)$ with $\fu \in \fU_3(k,n,j)$. Since $\fU_3(k,n,j) \subset \fC_1(k,n,j)$ for each such $\fu$, there exists $\mathfrak{m} \in \mathfrak{M}(k,n)$ such that $100\fu \lesssim \mathfrak{m}$. We fix such an $\mathfrak{m}(\fu) := \mathfrak{m}$ for each $\fu$, and claim that the map $\fu \mapsto\mathfrak{m}(\fu)$ is injective. Indeed, assume for $\fu\neq \fu'$ there is $\mathfrak{m} \in \mathfrak{M}(k,n)$ such that $100\fu \lesssim \mathfrak{m}$ and $100\fu' \lesssim \mathfrak{m}$. By \eqref{dyadicproperty}, either $\scI(\fu) \subset \scI(\fu')$ or $\scI(\fu') \subset \scI(\fu)$. By \eqref{defunkj}, $B_{\fu}(\fcc(\fu),100) \cap B_{\fu'}(\fcc(\fu'), 100) = \emptyset$. This contradicts $\Omega(\mathfrak{m})$ being contained in both sets by \eqref{eq-freq-comp-ball}. Thus $x$ is contained in more than $1 + (4n + 12)2^n$ cubes $\scI(\mathfrak{m})$, $\mathfrak{m} \in \mathfrak{M}(k,n)$. Consequently, we have by \eqref{eq-Aoverlap-def} that $x \in A(2n + 6, k,n) \subset G_2$. Let $\scI(\fu)$ be an inclusion minimal cube among the $\scI(\fu'), \fu' \in \fU_3(k,n,j)$ with $x \in \scI(\fu)$. By the dyadic property \eqref{dyadicproperty}, we have $\scI(\fu) \subset \scI(\fu')$ for all cubes $\scI(\fu')$ containing $x$. Thus
    $$
        \scI(\fu) \subset \{y \ : \ \sum_{\fu \in \fU_3(k,n,j)} \mathbf{1}_{\scI(\fu)}(y) > 1 + (4n+12)2^{n}\} \subset G_2\,.
    $$
    Thus $\mathfrak{T}_1(\fu) \cap \fC_6(k,n,j) = \emptyset$.
    This contradicts $\fu \in \fU_2(k,n,j)$.
\end{proof}
We now turn to the proof of \Cref{forest-union}.
\begin{proof}[Proof of \Cref{forest-union}]
    \proves{forest-union}

    We first fix $k,n, j$.
    By \eqref{definetp} and \eqref{defineep}, we have that
    $\mathbf{1}_{\scI(\fp)} T_{\fp}f(x) = T_{\fp}f(x)$ and hence $\mathbf{1}_{G \setminus G'} T_{\fp}f(x)= 0$ for all $\fp \in \fC_5(k,n,j) \setminus \fC_6(k,n,j)$.
    Thus it suffices to estimate the contribution of the sets $\fC_6(k,n,j)$. By \Cref{forest-stacking}, we can decompose $\fU_3(k,n,j)$ as a disjoint union of at most $4n + 13$ collections $\fU_4(k,n,j,l)$, $1 \le l \le 4n+13$, each satisfying
    $$
        \sum_{\fu \in \fU_4(k,n,j,l)} \mathbf{1}_{\scI(\fu)} \le 2^n\,.
    $$
    By Lemmas \ref{forest-geometry}, \ref{forest-convex}, \ref{forest-separation}, \ref{forest-inner} and \ref{C-dens1}, the pairs
    $$
        (\fU_4(k,n,j,l), \mathfrak{T}_2|_{\fU_4(k,n,j,l)})
    $$
    are $n$-forests for each $k,n,j,l$, and by \Cref{C6-forest}, we have
    $$
        \fC_6(k,n,j) = \bigcup_{l = 1}^{4n + 13} \bigcup_{\fu \in \fU_4(k,n,j,l)} \mathfrak{T}_2(\fu)\,.
    $$
    Since $\scI(\fp) \not\subset G_1$ for all $\fp \in \fC_6(k,n,j)$, we have $\fC_6(k,n,j) \cap \fP_{F,G} = \emptyset$ and hence
    $$
        \dens_2(\bigcup_{\fu \in \fU_4(k,n,j,l)} \mathfrak{T}_2(\fu)) \le 2^{2a + 5} \frac{\mu(F)}{\mu(G)}\,.
    $$
    Using the triangle inequality according to the splitting by $k,n,j$ and $l$ in \eqref{disclesssim1} and applying \Cref{forest-operator} to each term, we obtain the estimate
    $$
        \sum_{k \ge 0}\sum_{n \ge k} (2n+3)(4n+13) 2^{432a^3}2^{-(1-\frac{1}{q})n}(2^{2a+5} \frac{\mu(F)}{\mu(G)})^{\frac{1}{q} - \frac{1}{2}} \|f\|_2 \|\mathbf{1}_{G\setminus G'}\|_2
    $$
    for the left hand side of \eqref{disclesssim1}. Since $|f| \le \mathbf{1}_F$, we have $\|f\|_2 \le \mu(F)^{1/2}$, and we have $\|\mathbf{1}_{G\setminus G'}\|_2 \le \mu(G)^{1/2}$. Combining this with $a \ge 4$, we estimate by
    $$
        2^{433a^3} \mu(F)^{\frac{1}{q}} \mu(G)^{1
        -\frac{1}{q}} \sum_{k \ge 0}\sum_{n \ge k}n^2 2^{-(1-\frac{1}{q})n}\,.
    $$ % n^2 -> (n+1)^2
    Interchanging the order of summation, the sum equals
    $$
        \sum_{n \ge 0} n^2(n+1) 2^{-\frac{q-1}{q}n} \le \frac{2^{2a^3}}{(q-1)^3}\,,
    $$
    which completes the proof of the lemma.
\end{proof}

\section{Proof of the Forest Complement Lemma}
\label{subsecantichain}

Define $\fP_{X \setminus G'}$ to be the set of all $\fp \in \fP$ such that $\scI(\fp) \not \subset G'$.
\begin{lemma}[antichain decomposition]
\label{antichain-decomposition}
    We have that
    \begin{align}
        \label{eq-fp'-decomposition}
        &\quad \fP_2 \cap \fP_{X \setminus G'}\\
        &= \bigcup_{k \ge 0} \bigcup_{n \ge k} \fL_0(k,n) \cap \fP_{X \setminus G'} \\
        &\quad\cup \bigcup_{k \ge 0} \bigcup_{n \ge k}\bigcup_{0 \le j \le 2n+3} \fL_2(k,n,j) \cap \fP_{X \setminus G'}\\
        &\quad\cup \bigcup_{k \ge 0} \bigcup_{n \ge k}\bigcup_{0 \le j \le 2n+3} \bigcup_{0 \le l \le Z(n+1)} \fL_1(k,n,j,l) \cap \fP_{X \setminus G'}\\
        &\quad\cup \bigcup_{k \ge 0} \bigcup_{n \ge k}\bigcup_{0 \le j \le 2n+3} \bigcup_{0 \le l \le Z(n+1)} \fL_3(k,n,j,l)\cap \fP_{X \setminus G'}\,.
    \end{align}
\end{lemma}
% Note(Georges Gonthier): the second sentence of this proof is not technically true
% Can we restrict ourselves to a grid with only 1 top cube?
% Or alternatively, redefine \MfP_{X \ G'} to be the p s.t. I(p) \cap (G \ G') has nonzero measure.

\begin{proof}
    Let $\fp \in \fP_2 \cap \fP_{X \setminus G'}$. Clearly, for every cube $J \in \mathcal{D}$ there exists some $k \ge 0$ such that \eqref{muhj1} holds, and for no cube $J \in \mathcal{D}$ and no $k < 0$ does \eqref{muhj2} hold. Thus $\fp \in \fP(k)$ for some $k \ge 0$.

    Next, since $E_2(\lambda, \fp') \subset \scI(\fp')\cap G$ for every $\lambda \ge 2$ and every tile $\fp' \in \fP(k)$ with $\lambda\fp \lesssim \lambda \fp'$, it follows from \eqref{muhj2} that $\mu(E_2(\lambda, \fp')) \le 2^{-k} \mu(\scI(\fp'))$ for every such $\fp'$, so $\dens_k'(\{\fp\}) \le 2^{-k}$. Combining this with $a \ge 0$, it follows from \eqref{def-cnk} that there exists $n\ge k$ with $\fp \in \fC(k,n)$.

    Since $\fp \in \fP_{X \setminus G'}$, we have in particular $\scI(\fp) \not \subset A(2n + 6, k, n)$, so there exist at most $1 + (4n + 12)2^n < 2^{2n+4}$ tiles $\mathfrak{m} \in \mathfrak{M}(k,n)$ with $\fp \le \mathfrak{m}$. It follows that $\fp \in \fL_0(k,n)$ or $\fp \in \fC_1(k,n,j)$ for some $1 \le j \le 2n + 3$. In the former case we are done, in the latter case the inclusion to be shown follows immediately from the definitions of the collections $\fC_i$ and $\fL_i$.
\end{proof}

\begin{lemma}[L0 antichain]
\label{L0-antichain}
\uses{monotone-cube-metrics}
    We have that
    $$
        \fL_0(k,n) = \dot{\bigcup_{1 \le l \le n}} \fL_0(k,n,l)\,,
    $$
    where each $\fL_0(k,n,l)$ is an antichain.
\end{lemma}

\begin{proof}
    It suffices to show that $\fL_0(k,n)$ contains no chain of length $n + 1$. Suppose that we had such a chain $\fp_0 \le \fp_1 \le \dotsb \le \fp_{n}$ with $\fp_i \ne \fp_{i+1}$ for $i =0, \dotsc, n-1$. By \eqref{def-cnk}, we have that $\dens_k'(\{\fp_n\}) > 2^{-n}$. Thus, by \eqref{eq-densdef}, there exists $\fp' \in \fP(k)$ and $\lambda \ge 2$ with $\lambda \fp_n \le \lambda \fp'$ and
    \begin{equation}
        \label{eq-p'}
        \frac{\mu(E_2(\lambda, \fp'))}{\mu(\scI(\fp'))} > \lambda^{a} 2^{4a} 2^{-n}\,.
    \end{equation}
    Let $\mathfrak{O}$ be the set of all $\fp'' \in \fP(k)$ such that we have $ \scI(\fp'') = \scI(\fp')$ and $B_{\fp'}(\fcc(\fp'), \lambda) \cap \Omega(\fp'') \neq \emptyset$.
    We now show that
    \begin{equation}
        \label{eq-O-bound}
        |\mathfrak{O}| \le 2^{4a}\lambda^a\,.
    \end{equation}
    The balls $B_{\fp'}(\fcc(\fp''), 0.2)$, $\fp'' \in \mathfrak{O}$ are disjoint by \eqref{eq-freq-comp-ball},
    and by the triangle inequality contained in $B_{\fp'}(\fcc(\fp'), \lambda+1)$.
    % Note(Georges Gonthier): \lambda+1 should be \lambda+1.2
    By assumption \eqref{thirddb} on $\Theta$, this ball can be covered with
    $$
        2^{a(\lceil \log_2(\lambda+1)\rceil + 2)} \le 2^{a(\log_2(\lambda) + 4)} = 2^{4a}\lambda^a
    $$  % Note(Georges Gonthier): this approximation still barely holds
    many $d_{\fp'}$-balls of radius $1/4$.
    % Note(Georges Gonthier): 1/4 should be 1/5 (or something in between)
    By the triangle inequality, each such ball contains at most one $\fcc(\fp'')$, and each $\fcc(\fp'')$ is contained in one of the balls. Thus we get \eqref{eq-O-bound}.

    By \eqref{definee1} and \eqref{definee2} we have $E_2(\lambda, \fp') \subset \bigcup_{\fp'' \in \mathfrak{O}} E_1(\fp'')$, thus
    $$
        2^{4a}\lambda^a 2^{-n} < \sum_{\fp'' \in \mathfrak{O}} \frac{\mu(E_1(\fp''))}{\mu(\scI(\fp''))}\,.
    $$
    Hence there exists a tile $\fp'' \in \mathfrak{O}$ with
    \begin{equation*}
        \mu(E_1(\fp'')) \ge 2^{-n} \mu(\scI(\fp'))\,.
    \end{equation*}
    By the definition \eqref{mnkmax} of $\mathfrak{M}(k,n)$, there exists a tile $\mathfrak{m} \in \mathfrak{M}(k,n)$ with $\fp' \leq \mathfrak{m}$. From \eqref{eq-p'}, the inclusion $E_2(\lambda, \fp') \subset \scI(\fp')$ and $a\ge 1$ we obtain
    $$
        2^n \geq 2^{4a} \lambda^{a} \geq \lambda\,.
    $$
    From the triangle inequality, \Cref{monotone-cube-metrics} and $a \ge 1$, we now obtain for all $\mfa \in B_{\mathfrak{m}}(\fcc(\mathfrak{m}), 1)$ that
    \begin{align*}
        &\quad d_{\fp_0}(\fcc(\fp_0), \mfa)\\
        &\leq d_{\fp_0}(\fcc(\fp_0), \fcc(\fp_{n})) + d_{\fp_0}(\fcc(\fp_{n}), \fcc(\fp')) + d_{\fp_0}(\fcc(\fp'), \fcc(\fp''))\\
        &\quad+ d_{\fp_0}(\fcc(\fp''), \fcc(\mathfrak{m})) +
        d_{\fp_0}(\fcc(\mathfrak{m}), \mfa)\\
        &\leq 1 + 2^{-95an} (d_{\fp_{n}}(\fcc(\fp_n), \fcc(\fp')) + d_{\fp'}(\fcc(\fp'), \fcc(\fp''))\\
        &\quad+ d_{\fp''}(\fcc(\fp''), \fcc(\mathfrak{m})) +
        d_{\mathfrak{m}}(\fcc(\mathfrak{m}), \mfa))\\
        &\leq 1 + 2^{-95an}(\lambda + (\lambda + 1) + 1 + 1) \leq 100\,.
    \end{align*}
    Thus, by \eqref{straightorder}, $100\fp_0 \lesssim \mathfrak{m}$, a contradiction to $\fp_0 \notin \fC(k,n)$.
\end{proof}

\begin{lemma}[L2 antichain]
\label{L2-antichain}
\uses{monotone-cube-metrics}
    Each of the sets $\fL_2(k,n,j)$ is an antichain.
\end{lemma}

\begin{proof}
    Suppose that there are $\fp_0, \fp_1 \in \fL_2(k,n,j)$ with $\fp_0 \ne \fp_1$ and $\fp_0 \le \fp_1$. By \Cref{wiggle-order-1} and \Cref{wiggle-order-2}, it follows that $2\fp_0 \lesssim 200\fp_1$. Since $\fL_2(k,n,j)$ is finite, there exists a maximal $l \ge 1$ such that there exists a chain $2\fp_0 \lesssim 200 \fp_1 \lesssim \dotsb \lesssim 200 \fp_l$ with $\fp_i \ne \fp_{i+1}$ for $i = 0, \dotsc, l-1$.
    If we have $\fp_l \in \fU_1(k,n,j)$, then it follows from $2\fp_0 \lesssim 200 \fp_l \lesssim \fp_l$ and \eqref{eq-L2-def} that $\fp_0 \not\in \fL_2(k,n,j)$, a contradiction. Thus, by the definition \eqref{defunkj} of $\fU_1(k,n,j)$, there exists $\fp_{l+1} \in \fC_1(k,n,j)$ with $\scI(\fp_l) \subsetneq \scI(\fp_{l+1}) $ and $\mfa \in B_{\fp_l}(\fcc(\fp_l), 100) \cap B_{\fp_{l+1}}(\fcc(\fp_{l+1}), 100)$. Using the triangle inequality and \Cref{monotone-cube-metrics}, one deduces that $200 \fp_l \lesssim 200\fp_{l+1}$. This contradicts maximality of $l$.
\end{proof}

\begin{lemma}[L1 L3 antichain]
\label{L1-L3-antichain}
    Each of the sets $\fL_1(k,n,j,l)$ and $\fL_3(k,n,j,l)$ is an antichain.
\end{lemma}

\begin{proof}
    By its definition \eqref{eq-L1-def}, each set $\fL_1(k,n,j,l)$ is a set of minimal elements in some set of tiles with respect to $\le$. If there were distinct $\fp, \fq \in \fL_1(k,n,j,l)$ with $\fp \le \fq$, then $\fq$ would not be minimal. Hence such $\fp, \fq$ do not exist. Similarly, by \eqref{eq-L3-def}, each set $\fL_3(k,n,j,l)$ is a set of maximal elements in some set of tiles with respect to $\le$. If there were distinct $\fp, \fq \in \fL_3(k,n,j,l)$ with $\fp \le \fq$, then $\fp$ would not be maximal.
\end{proof}

We now turn to the proof of \Cref{forest-complement}.
\begin{proof}[Proof of \Cref{forest-complement}]
    \proves{forest-complement}
    If $\fp \not\in \fP_{X \setminus G'}$, then $\scI(\fp) \subset G'$. By \eqref{definetp} and \eqref{definee1}, it follows that
    $\mathbf{1}_{G \setminus G'} T_{\fp}f(x) = 0$. We thus have
    $$
        \mathbf{1}_{G\setminus G'} \sum_{\fp \in \fP_2} T_{\fp}f(x) = \mathbf{1}_{G\setminus G'} \sum_{\fp \in \fP_2 \cap \fP_{X \setminus G'}} T_{\fp}f(x)\,.
    $$
    Let $\fL(k,n)$ denote any of the terms $\fL_i(k,n,j,l) \cap \fP_{X \setminus \fP_2}$ on the right hand side of \eqref{eq-fp'-decomposition}, where the indices $j, l$ may be void. Then $\fL(k,n)$ is an antichain, by Lemmas \ref{L0-antichain},\ref{L2-antichain}, \ref{L1-L3-antichain}. Further, we have
    \begin{equation*}
    \dens_1(\fL(k,n)) \le 2^{4a+1 - n}
    \end{equation*}
    by \Cref{C-dens1}, and we have
    \begin{equation*}
     \dens_2(\fL(k,n)) \le 2^{2a+5} \frac{\mu(F)}{\mu(G)},
     \end{equation*}
     since
     \begin{equation*}
     \fL(k,n) \cap \fP_{F,G} \subset \fP_{X \setminus \fP_2} \cap \fP_{F, G} = \emptyset.
     \end{equation*}

    Applying now the triangle inequality according to the decomposition in \Cref{antichain-decomposition}, and then applying \Cref{antichain-operator} to each term, we obtain the estimate
    \begin{multline*}
        \le \sum_{k \ge 0} \sum_{n \ge k} (n + (2n+4) + 2(2n+4) Z(n+1)) \\
        \times 2^{201a^3}(q-1)^{-1} (2^{4a+1-n})^{\frac{q-1}{8a^4}} (2^{2a+5} \frac{\mu(F)}{\mu(G)})^{\frac{1}{q} - \frac{1}{2}} \|f\|_2\|\mathbf{1}_{G\setminus G'}\|_2\,.
    \end{multline*}
    Because $|f| \le \mathbf{1}_F$, we have $\|f\|_2 \le \mu(F)^{1/2}$, and we have $\|\mathbf{1}_{G\setminus G'}\|_2 \le \mu(G)^{1/2}$. Using this and \eqref{defineZ}, we bound
    $$
        \le 2^{202a^3} (q - 1)^{-1} \mu(F)^{\frac{1}{q}} \mu(G)^{\frac{1}{q'}} \sum_{k \ge 0} \sum_{n \ge k} n^2 2^{-n\frac{q-1}{8a^4}}\,.
    $$
    The last sum equals, by changing the order of summation,
    $$
        \sum_{n \ge 0} n^2(n+1) 2^{-n\frac{q-1}{8a^4}} \le \frac{2^{8a^3}}{(q-1)^3}\,.
    $$
    This completes the proof.
\end{proof}

\chapter{Proof of the Antichain Operator Proposition}

\label{antichainboundary}

Let an antichain $\mathfrak{A}$
and functions $f$, $g$ as in \Cref{antichain-operator} be given.
We prove \eqref{eq-antiprop}
in \Cref{sec-TT*-T*T}
as the geometric mean of two inequalities,
each involving one of the two densities.
One of these two inequalities will need a careful estimate formulated in
\Cref{tile-correlation} of
the $TT^*$ correlation between two tile operators.
\Cref{tile-correlation} will be proven in
\Cref{sec-tile-operator}.

The summation of the contributions of these individual correlations will require a
geometric \Cref{antichain-tile-count} counting the relevant tile pairs.
\Cref{antichain-tile-count} will be proven in Subsection
\ref{subsec-geolem}.






\section{The density arguments}\label{sec-TT*-T*T}

We begin with the following crucial disjointedness property of the sets $E(\fp)$ with $\fp \in \mathfrak{A}$.
\begin{lemma}[tile disjointness]
\label{tile-disjointness}
\lean{E_disjoint}
\leanok
Let $\fp,\fp'\in \mathfrak{A}$.
If there exists an $x\in X$ with $x\in E(\fp)\cap E(\fp')$,
then $\fp= \fp'$.
\end{lemma}
\begin{proof}\leanok
Let $\fp,\fp'$ and $x$ be given.
Assume without loss of generality that $\ps(\fp)\le \ps(\fp')$.
As we have $x\in E(\fp)\subset \scI(\fp)$ and $x\in E(\fp')\subset \scI(\fp')$ by Definition \eqref{defineep}, we conclude
for $i=1,2$ that
$\tQ(x)\in\fc(\fp)$ and $\tQ(x)\in\fc(\fp')$. By \eqref{eq-freq-dyadic} we have $\fc(\fp')\subset \fc(\fp)$. By Definition
\eqref{straightorder}, we conclude $\fp\le \fp'$. As $\mathfrak{A}$ is an antichain, we conclude $\fp=\fp'$.
This proves the lemma.
\end{proof}



Let $\mathcal{B}$ be the collection of balls
\begin{equation}
    B(\pc(\fp), 8D^{\ps(\fp)})
\end{equation}
with $\fp\in \mathfrak{A}$ and recall the definition of
$M_{\mathcal{B}}$ from Definition \ref{def-hlm}.

\begin{lemma}[maximal bound antichain]
    \label{maximal-bound-antichain}
    \uses{tile-disjointness}
    \lean{MaximalBoundAntichain}
    \leanok
    Let $x\in X$.
    Then
    \begin{equation}\label{hlmbound}
    | \sum_{\fp \in \mathfrak{A}}T_{\fp} f(x)|\le 2^{107 a^3} M_{\mathcal{B}} f (x) \, .
    \end{equation}
\end{lemma}

\begin{proof}
Fix $x\in X$. By \Cref{tile-disjointness}, there is at most one $\fp \in \mathfrak{A}$
such that
 $T_{\fp} f(x)$ is not zero.
 If there is no such $\fp$, the estimate \eqref{hlmbound} follows.

 Assume there is such a $\fp$.
 By definition of $T_{\fp}$ we have $x\in E(\fp)\subset \scI(\fp)$ and by the squeezing property \eqref{eq-vol-sp-cube}
\begin{equation}\label{eqtttt0}
    \rho(x, \pc(\fp))\le 4D^{\ps(\fp)}\, .
\end{equation}

Let $y\in X$ with $K_{\ps(\fp)}(x,y)\neq 0$. By Definition \eqref{defks} of $K_{\ps(\fp)}$
we have
\begin{equation}\label{supp-Ks1}
   \frac{1}{4} D^{\ps(\fp)-1}
   \leq \rho(x,y) \leq \frac{1}{2} D^{\ps(\fp)}\, .
\end{equation}
The triangle inequality with \eqref{eqtttt0} and \eqref{supp-Ks1} implies
\begin{equation}
    \rho(\pc(\fp),y)\le 8D^{\ps(\fp)}\, .
\end{equation}
Using the kernel bound \eqref{eqkernel-size} and the lower bound in \eqref{supp-Ks}
we obtain
\begin{equation}
|K_{\ps(\fp)}(x,y)|\le \frac{2^{a^3}}{\mu(B(x,\frac 14 D^{{\ps(\fp)}-1}))}\, .
\end{equation}
Using $D=2^{100a^2}$
and the doubling property \eqref{doublingx} $5 +100a^2$ times estimates
the last display by
\begin{equation}
\le \frac{2^{5a+101a^3}}{\mu(B(x, 8D^{\ps(\fp)}))}\, .
\end{equation}
 Using that {$|e(\mfa)|$} is bounded by $1$
for every $\mfa\in \Mf$, we estimate with the triangle inequality and the above information
 \begin{equation}
  | T_{\fp} f(x)|
    \le \frac{2^{5a+101 a^3}}{\mu(B(x, 8D^{\ps(\fp)}))} \int _{\mu(B(x, 8D^{\ps(\fp)}))} |f(y)|\, dy
  \end{equation}
This together with $a\ge 1$ proves the Lemma.
\end{proof}

Set
\begin{equation}
    \tilde{q}=\frac {2q}{1+q}\,.
\end{equation}
Since $1< q\le 2$, we have $1<\tilde{q}<q\le 2$.
\begin{lemma}[dens2 antichain]
\label{dens2-antichain}
\uses{Hardy-Littlewood,maximal-bound-antichain}
\lean{Dens2Antichain}
\leanok
We have that
\begin{equation}\label{eqttt9}
  \left|\int \overline{g(x)} \sum_{\fp \in \mathfrak{A}} T_{\fp} f(x)\, d\mu(x)\right|\le
  2^{111a^2}({q}-1)^{-1} \dens_2(\mathfrak{A})^{\frac 1{\tilde{q}}-\frac 12} \|f\|_2\|g\|_2\, .
\end{equation}
\end{lemma}
\begin{proof}
We have $f=\mathbf{1}_Ff$. Using H\"older's inequality, we obtain for
each $x\in B'$ and each $B'\in \mathcal{B}$ using $1<\tilde{q}\le 2$
\begin{equation}
    \frac 1{\mu(B')}\int_{B'} |f(y)|\, d\mu(y)
\end{equation}
\begin{equation}
    \le
    \left(\frac 1{\mu(B')}\int_{B'} |f(y)|^{\frac {2{\tilde{q}}}{3\tilde{q}-2}}\, d\mu(y)\right)^{\frac 32-\frac 1{\tilde{q}}}
    \left(\frac 1{\mu(B')}\int_{B'} \mathbf{1}_F(y)\, d\mu(y)\right)^{\frac 1{\tilde{q}}-\frac 12}
\end{equation}
\begin{equation}
    \le \left(M_{\mathcal{B}} (|f|^{\frac {2{\tilde{q}}}{3{\tilde{q}}-2}})(x)\right)^{\frac 32-\frac 1{\tilde{q}}}
\dens_2(\mathfrak{A})^{\frac 1{\tilde{q}}-\frac 12}\, .
\end{equation}
Taking the maximum over all $B'$ containing $x$, we obtain
\begin{equation} \label{eqttt1}
    M_{\mathcal{B}}|f|\le
    M_{\mathcal{B},\frac {2{\tilde{q}}}{3{\tilde{q}}-2} } |f|
    \dens_2(\mathfrak{A})^{\frac 1{\tilde{q}}-\frac 12}\, .
\end{equation}
We have with \Cref{Hardy-Littlewood}
\begin{equation}
\left\|M_{\mathcal{B}, \frac {2q}{3q-2}} f\right\|_2\le 2^{2a}(3\tilde{q}-2)(2\tilde{q}-2)^{-1}\|f\|_2\, .
\end{equation}
Using $1<\tilde{q}\le 2$ estimates the last display by
\begin{equation}\label{eqttt2}
 2^{2a+2} (\tilde{q}-1)^{-1} \|f\|_2\, .
\end{equation}
We obtain with Cauchy-Schwarz
and then \Cref{maximal-bound-antichain}
 \begin{equation}
     |\int \overline{g(x)} \sum_{\fp \in \mathfrak{A}} T_{\fp} f(x)\, d\mu(x)|
\end{equation}
 \begin{equation}
     \le \|g\|_2 \Big\| \sum_{\fp \in \mathfrak{A}} T_{\fp} f \Big\|_2
\end{equation}
 \begin{equation}
     \le 2^{107a^2}\|g\|_2 \| M_{\mathcal{B}}f \|_2
\end{equation}
With \eqref{eqttt1} and
\eqref{eqttt2} we can estimate the last display by
\begin{equation}
    \le 2^{107a^2+2a+2}(\tilde{q}-1)^{-1} \|g\|_2 \|f\|_2\dens_2(\mathfrak{A})^{\frac 1{\tilde{q}}-\frac 12}
\end{equation}
Using $a\ge 4$ and
$(\tilde q - 1)^{-1} = (q+1)/(q-1) \le 3(q-1)^{-1}$
proves the lemma.
\end{proof}


\begin{lemma}[dens1 antichain]\label{dens1-antichain}
\uses{Hardy-Littlewood, tile-correlation,antichain-tile-count}
Set $p:=4a^4$. We have
    \begin{equation}\label{eqttt3}
  \left|\int \overline{g(x)} \sum_{\fp \in \mathfrak{A}} T_{\fp} f(x)\, d\mu(x)\right|\le
   2^{150a^3}\dens_1(\mathfrak{A})^{\frac 1{2p}} \|f\|_2\|g\|_2\,.
\end{equation}
\end{lemma}



\begin{proof}

 We write for the expression inside the absolute values on the left-hand side of \eqref{eqttt3}
\begin{equation}
  \sum_{\fp \in \mathfrak{A}}\iint \overline{g(x)} \mathbf{1}_{E(\fp)}(x)
  {K_{\ps(\fp)}(x,y)}e(\tQ(x)(y) -
   \tQ(x)(x))
   f(y)\, d\mu(y)\,d\mu(x)
\end{equation}
\begin{equation}
  =\int \sum_{\fp \in \mathfrak{A}} \overline{T_{\fp} ^*g(y)} f(y)\, d\mu(y)
\end{equation}
with the adjoint operator
\begin{equation}\label{eq-tstarwritten}
    T_{\fp}^*g(y)=\int_{E(\fp)} \overline{K_{\ps(\fp)}(x,y)}e(-\tQ(x)(y)+
    \tQ(x)(x))g(x)\, d\mu(x)\, .
\end{equation}





 We have by expanding the square
\begin{equation}
    \int \Big|\sum_{\fp\in \mathfrak{A}}T^*_{\fp}g(y)\Big|^2\, d\mu(y)=
    \int \left(\sum_{\fp\in \mathfrak{A}} T^*_{\fp}g(y)\right)
    \left(\sum_{\fp'\in \mathfrak{A}}\overline{T^*_{\fp'}g(y)}\right)\, d\mu(y)
\end{equation}
\begin{equation}\label{eqtts1}
    \le \sum_{\fp\in \mathfrak{A}} \sum_{\fp'\in \mathfrak{A}}
    \Big|\int T^*_{\fp}g(y)\overline{T^*_{\fp'}g(y)}\, d\mu(y)\Big|\,.
\end{equation}
We split the sum into the terms with $\ps(\fp')\le \ps(\fp)$
and $\ps(\fp)< \ps(\fp')$. Using the symmetry of each summand,
we may switch $\fp$ and $\fp'$ in the second sum. Using further positivity
of each summand to replace the condition $\ps(\fp')< \ps(\fp)$
by $\ps(\fp')\le \ps(\fp)$ in the second sum, we estimate \eqref{eqtts1} by
\begin{equation}\label{eqtts2}
    \le2 \sum_{\fp\in \mathfrak{A}} \sum_{\fp'\in \mathfrak{A}: \ps(\fp')\le \ps(\fp)}
    \Big|\int T^*_{\fp}g(y)\overline{T^*_{\fp'}g(y)}\, d\mu(y)\Big|\,.
\end{equation}
The following basic $TT^*$ estimate will be proved in \Cref{sec-tile-operator}.
\begin{lemma}[tile correlation]
    \label{tile-correlation}
    \uses{Holder-van-der-Corput,correlation-kernel-bound,tile-uncertainty,tile-range-support}
    Let $\fp, \fp'\in \fP$ with
    $\ps({\fp'})\leq \ps({\fp})$.
    Then
    \begin{equation}
        \label{eq-basic-TT*-est}
        \left|\int T^*_{\fp'}g\overline{T^*_{\fp}g}\right|
    \end{equation}
    \begin{equation}
        \le 2^{255a^3}\frac{(1+d_{\fp'}(\fcc(\fp'), \fcc(\fp))^{-1/(2a^2+a^3)}}{\mu(\scI(\fp))}\int_{E(\fp')}|g|\int_{E(\fp)}|g|\,.
    \end{equation}
    Moreover, the term \eqref{eq-basic-TT*-est} vanishes unless
    \begin{equation}
        \scI(\fp') \subset B(\pc(\fp), 15D^{\ps(\fp)})\, .
    \end{equation}
\end{lemma}
Define for $\fp\in \fP$
\begin{equation}
    B(\fp):=B(\pc(\fp), 15D^{\ps(\fp)})
\end{equation}
and define
\begin{equation}
    \label{eq-Dp-definition}
    \mathfrak{A}(\fp):=\{\fp'\in\mathfrak{A}: \ps(\fp')\leq \ps(\fp) \land \scI(\fp') \subset B(\fp)\}.
\end{equation}
Note that by the squeezing property \eqref{eq-vol-sp-cube}
and the doubling property \eqref{doublingx} applied
$6$ times we have
\begin{equation}\label{eqttt4}
    \mu(B(\fp))\le 2^{6a} \mu(\scI(\fp))\, .
\end{equation}
Using \Cref{tile-correlation} and \eqref{eqttt4}, we estimate \eqref{eqtts2} by
\begin{equation}\label{eqtts3}
     \le 2^{255a^3+6a+1} \sum_{\fp\in \mathfrak{A}}
    \int_{E(\fp)}|g|(y) h(\fp)\, d\mu(y)
\end{equation}
with $h(\fp)$ defined as
\begin{equation}\label{def-hp}
    \frac 1{\mu(B(\fp))}\int \sum_{\fp'\in \mathfrak{A}(\fp)}
    {(1+d_{\fp'}(\fcc(\fp'), \fcc(\fp))^{-1/(2a^2+a^3)}}(\mathbf{1}_{E(\fp')}|g|)(y')\, d\mu(y')\,.
\end{equation}
The following lemma will be proved in \Cref{subsec-geolem}.
\begin{lemma}[antichain tile count]
    \label{antichain-tile-count}
    \uses{global-antichain-density}
    Set $p:=4a^4$ and let $p'$ be the dual exponent of $p$, that is $1/p+1/p'=1$.
    For every $\mfa\in\Mf$ and every subset $\mathfrak{A}'$ of $\mathfrak{A}$ we have
    \begin{equation}
        \label{eq-antichain-Lp}
        \Big\|\sum_{\fp\in\mathfrak{A}'}(1+d_{\fp}(\fcc(\fp), \mfa))^{-1/(2a^2+a^3)}\mathbf{1}_{E(\fp)}\mathbf{1}_G\Big\|_{p}
    \end{equation}
    \begin{equation}
        \le
        2^{104a}\dens_1(\mathfrak{A})^{\frac 1p}\mu\left(\cup_{\fp\in\mathfrak{A}'}I_{\fp}\right)^{\frac 1p}\, .
    \end{equation}
\end{lemma}

Note that $p\geq 4$ since $a>4$.
We estimate $h(\fp)$ as defined in \eqref{def-hp} with H\"older using $|g|\le \mathbf{1}_G$ and $E(\fp')\subset B(\fp)$ by

\begin{equation}
    \frac{\|g\mathbf{1}_{B(\fp)}\|_{p'}}{\mu(B(\fp))}
    \Big\|\sum_{\fp\in\mathfrak{A}(\fp)}(1+d_{\fp}(\fcc(\fp), \fc(\fp'))^{-1/(2a^2+a^3)}\mathbf{1}_{E(\fp)}\mathbf{1}_G\Big\|_{p}\, .
\end{equation}
Then we apply \Cref{antichain-tile-count} to estimate this by
\begin{equation}\label{eqttt5}
    \le 2^{104a}
    \frac{\|g\mathbf{1}_{B(\fp)}\|_{p'}}{\mu(B(\fp))}
    \dens_1(\mathfrak{A})^{\frac 1p}\mu(B(\fp))^{\frac 1p}\,.
\end{equation}
Let $\mathcal{B}'$ be the collection of all balls
$B(\fp)$ with $\fp\in \mathfrak{A}$. Then
for each $\fp\in \mathfrak{A}$ and $x\in B(\fp)$ we have by
definition \eqref{def-hlm} of $M_{\mathcal{B}',p'}$
\begin{equation}
    \|g\mathbf{1}_{B(\fp)}\|_{p'}\le
    \mu(B(\fp))^{\frac 1{p'}} M_{\mathcal{B}',p'}g(x) \, .
\end{equation}
Hence we can estimate \eqref{eqttt5} by
\begin{equation}
\label{eqttt5b}
    \le
    2^{104a}
    (M_{\mathcal{B}', p'}g(x))
   \dens_1(\mathfrak{A})^{\frac 1p}\, .
\end{equation}
With this estimate of $h(\fp)$,
using $E(\fp)\subset B(\fp)$ by construction of $B(\fp)$, we estimate
\eqref{eqtts3} by
 \begin{equation}\label{eqtts4}
 \le 2^{255a^3+110a + 1} { \dens_1(\mathfrak{A})^{\frac 1p}}\sum_{\fp\in \mathfrak{A}}
 \int_{E(\fp)}|g|(y)M_{\mathcal{B}', p'}g(y) \, dy\,.
         \end{equation}
Using \Cref{tile-disjointness},
the last display is observed to be
\begin{equation}\label{eqtts4a}
= 2^{255a^3+110a + 1}
 {\dens_1(\mathfrak{A})^{\frac 1p}} \int |g|(y)(M_{\mathcal{B}', p'}g)(y) \, dy\,.
         \end{equation}
Applying Cauchy-Schwarz and using \Cref{Hardy-Littlewood}estimates the last display by
\begin{equation}
    2^{255a^3+110a + 1} \dens_1(\mathfrak{A})^{\frac 1p}
    \|g\|_2 \|M_{\mathcal{B}', p'} g\|_2
\end{equation}
\begin{equation}
    \le 2^{255a^3+110a + 3}\frac{2}{2-p'}
    \dens_1(\mathfrak{A})^{\frac 1p}\|g\|_2 ^2\,.
\end{equation}
Using $p>4$ and thus $1<p'<\frac 43$, we estimate the last display by
\begin{equation}
    \le 2^{255a^3+110a + 5} \dens_1(\mathfrak{A})^{\frac 1p}
    \|g\|_2^2\,.
\end{equation}
Now \Cref{dens1-antichain} follows by applying Cauchy-Schwarz on the left-hand side and using
$a\ge 4$.
\end{proof}
We have
\begin{equation}
    \left (\frac 1{\tilde{q}} -\frac 12\right) (2-q)= \frac 1q -\frac 12\,.
\end{equation}
Multiplying the $(2-q)$-th power of \eqref{eqttt9} and the $(q-1)$-th power of \eqref{eqttt3}
and estimating gives after simplification of some factors
\begin{equation}\label{eqttt8}
    \Big|\int \overline{g(x)} \sum_{\fp \in \mathfrak{A}} T_{\fp} f(x)\, d\mu(x)\Big|
\end{equation}
 \begin{equation}
    \le 2^{150a^3}({q}-1)^{-1} \dens_1(\mathfrak{A})^{\frac {q-1}{2p}}\dens_2(\mathfrak{A})^{\frac 1{q}-\frac 12} \|f\|_2\|g\|_2\, .
\end{equation}
With the definition of $p$, this implies
\Cref{antichain-operator}.


\section{Proof of the Tile Correlation Lemma}\label{sec-tile-operator}

The next lemma prepares an application of
\Cref{Holder-van-der-Corput}.
\begin{lemma}[correlation kernel bound]\label{correlation-kernel-bound}
Let $-S\le s_1\le s_2\le S$ and let $x_1,x_2\in X$.
Define \begin{equation}
 \varphi(y) := \overline{K_{s_1}(x_1, y)}
 K_{s_2}(x_2, y) \, .
\end{equation}
If $\varphi(y)\neq 0$, then
\begin{equation}\label{eqt10}
    y\in B(x_1, D^{s_1})\, .
\end{equation}
Moreover, we have with $\tau = 1/a$
\begin{equation}\label{eqt11}
  \|\varphi\|_{C^\tau(B(x_1, D^{s_1}))}\le
\frac{2^{254 a^3}}{\mu(B(x_1, D^{s_1}))\mu(B(x_2, D^{s_2}))}
      \, .
\end{equation}

\end{lemma}
\begin{proof}

If $\varphi(y)$ is not zero, then $K_{s_1}(x_1, y)$ is not zero and thus
\eqref{supp-Ks} gives \eqref{eqt10}.

We next have for $y$ with \eqref{eq-Ks-size}
\begin{equation}\label{suppart}
    |\varphi(y)|\le
    \frac{2^{204 a^3}}{\mu(B(x_1, D^{s_1}))\mu(B(x_2, D^{s_2}))}
\end{equation}
and for $y'\neq y$ additionally with \eqref{eq-Ks-smooth}
\begin{equation}
    |\varphi(y)-\varphi(y')|
 \end{equation}
 \begin{equation}
 \le
 |K_{s_1}(x_1,y)-K_{s_1}(x_1,y'))||
 K_{s_2}(x_2, y)|
\end{equation}
 \begin{equation}+|K_{s_1}(x_1, y')|
 |K_{s_2}(x_2, y) - K_{s_2}(x_2, y'))|
\end{equation}
\begin{equation}
      \le \frac{2^{252 a^3}}{\mu(B(x_1, D^{s_1}))\mu(B(x_2, D^{s_2}))}
       \left(\left(\frac{ \rho(y,y')}{D^{s_1}}\right)^{1/a}+
       \left(\frac{ \rho(y,y')}{D^{s_2}}\right)^{1/a}\right)
\end{equation}
\begin{equation}\label{holderpart}
      \le \frac{2^{253 a^3}}{\mu(B(x_1, D^{s_1}))\mu(B(x_2, D^{s_2}))}
       \left(\frac{ \rho(y,y')}{D^{s_1}}\right)^{1/a}\,.
\end{equation}
Adding the estimates \eqref{suppart} and \eqref{holderpart} gives \eqref{eqt11}.
This proves the lemma.
\end{proof}
The next lemma is a geometric estimate for two tiles.
\begin{lemma}\label{tile-uncertainty}
\uses{monotone-cube-metrics}
    Let $\fp_1, \fp_2\in \fP$ with
$\ps({\fp_1})\leq \ps({\fp_2})$. For each $x_1\in E(\fp_1)$ and
$x_2\in E(\fp_2)$ we have
\begin{equation}\label{tgeo}
  1+d_{\fp_1}(\fcc(\fp_1), \fcc(\fp_2))\le
    2^{3a}(1 + d_{B(x_1, D^{\ps(\fp_1)})}(\tQ(x_1),\tQ(x_2)))\, .
\end{equation}
\end{lemma}
\begin{proof}
Let $i\in \{1,2\}$.
By Definition \eqref{defineep} of $E$,
we have $\tQ(x_i)\in \fc(\fp_i)$
With \eqref{eq-freq-comp-ball} we then conclude
\begin{equation}\label{dponetwo}
    d_{\fp_i}(\tQ(x_i),\fcc(\fp_i))\le 1\, .
\end{equation}
We have $\scI(\fp_1)\subset \scI(\fp_2)$ by \eqref{dyadicproperty}. Using \Cref{monotone-cube-metrics} it follows that
\begin{equation}\label{tgeo0.5}
    d_{\fp_1}(\tQ(x_2), \fcc(\fp_2)) \le 1\,.
\end{equation}
By the triangle inequality, we obtain from \eqref{dponetwo} and
\eqref{tgeo0.5}
\begin{equation}\label{tgeo1}
     1+d_{\fp_1}(\fcc(\fp_1), \fcc(\fp_2))\le 3 +d_{\fp_1}(\tQ(x_1), \tQ(x_2))\, .
\end{equation}
As $x_1\in \scI(\fp_1)$ by Definition \eqref{defineep} of $E$, we have by the squeezing property \eqref{eq-vol-sp-cube}
\begin{equation}
    d(x_1,\pc(\fp_1))\le 4D^{\ps(\fp_1)}
\end{equation}
and thus by \eqref{eq-vol-sp-cube} again and the triangle inequality
\begin{equation}
    \scI(\fp_1)\subset B(x_1,8D^{\ps(\fp_1)})\, .
\end{equation}
We thus estimate the right-hand side of \eqref{tgeo1} with monotonicity \eqref{monotonedb} of the metrics $d_B$ by
\begin{equation}\label{tgeo1.5}
    \le 3+d_{B(x_1,8D^{\ps(\fp_1)})}(\tQ(x_1), \tQ(x_2))\, .
\end{equation}
This is further estimated by applying the doubling property \eqref{firstdb} three times by
\begin{equation}\label{tgeo2}
    \le 3+2^{3a}d_{B_1(x_1, D^{\ps(\fp_1)})}(\tQ(x_1), \tQ(x_2))\, .
\end{equation}
Now \eqref{tgeo} follows with $a\ge 1$.
\end{proof}




\begin{lemma}[tile range support]\label{tile-range-support}
    For each $\fp\in \fP$, and each $y\in X$, we have that
\begin{equation}\label{tstargnot0}
     T_{\fp}^* g(y)\neq 0
\end{equation}
   implies
\begin{equation}\label{ynotfar}
    y\in B(\pc(\fp),5D^{\ps(\fp)})\, .
\end{equation}
\end{lemma}
\begin{proof}
Fix $\fp$ and $y$ with \eqref{tstargnot0}.
Then there exists $x\in E(\fp)$ with
\begin{equation}
   \overline{K_{\ps(\fp)}(x,y)}e(-\tQ(x)(y)
    +\tQ(x)(x))g(x) \neq 0\, .
\end{equation}
As $E(\fp)\subset \scI(\fp)$ and by the squeezing property
\eqref{eq-vol-sp-cube}, we have
\begin{equation}
    \rho(x,\pc(\fp))\le 4D^{\ps(\fp)}\, .
\end{equation}
As $K_{\ps(\fp)}(x,y)\neq 0$, we have by \eqref{supp-Ks}
that
\begin{equation}
\rho(x,y)\le \frac 12 D^{\ps(\fp)}\, .
\end{equation}
Now \eqref{ynotfar} follows by the triangle inequality.
\end{proof}


We now prove \Cref{tile-correlation}. We begin with \eqref{eq-basic-TT*-est}.

We expand the left-hand side of \eqref{eq-basic-TT*-est} as
\begin{equation}\label{tstartstar}
\left|\int \int_{E(\fp_1)} \overline{K_{\ps(\fp_1)}(x_1,y)}e(-\tQ(x_1)(y)+
    \tQ(x_1)(x_1))g(x_1)\, d\mu(x_1) \right.
\end{equation}
\begin{equation}
 \times \left.\int_{E(\fp_2)} {K_{\ps(\fp_2)}(x_2,y)}e(\tQ(x_2)(y)
    -\tQ(x_2)(x_2))\overline{g(x_2)}\, d\mu(x_2)\, d\mu(y)\right|\, .
\end{equation}
By Fubini and the triangle inequality and
the fact $|e(\tQ(x_i)(x_i))|=1$ for $i=1,2$, we can estimate
\eqref{tstartstar} from above by
\begin{equation}\label{eqa1}
    \int_{E(\fp_1)} \int_{E(\fp_2)} {\bf I}(x_1, x_2)\, d\mu(x_1)d\mu(x_2)\,.
\end{equation}
with
\begin{equation}
    {\bf I}(x_1, x_2):=
    \left|\int
    e(-\tQ(x_1)(y)+\tQ(x_2)(y))\varphi_{x_1,x_2}(y)
    d\mu(y) \, g(x_1)g(x_2)\right|
\end{equation}


We estimate for fixed $x_1\in E(\fp_1)$ and
$x_2\in E(\fp_2)$ the inner integral of \eqref{eqa1} with
\Cref{Holder-van-der-Corput}. The function
$\varphi:=\varphi_{x_1,x_2}$ satisfies the assumptions of
\Cref{Holder-van-der-Corput} with $z = x_1$ and $R = D^{s_1}$ by \Cref{correlation-kernel-bound}.
We obtain with $B':= B(x_1, D^{\ps(\fp_1)})$,
\begin{equation*}
 {\bf I}(x_1, x_2) \le 2^{8a} \mu(B') \|{\varphi}\|_{C^\tau(B')}
       (1 + d_{B'}(\tQ(x_1),\tQ(x_2)))^{-1/(2a^2+a^3)}
\end{equation*}
\begin{equation}
\label{eqa1.5}
 \le \frac{2^{254a^3+8a}}
 {\mu(B(x_2, D^{\ps(\fp_2)}))}
       (1 + d_{B'}(\tQ(x_1),\tQ(x_2)))^{-1/(2a^2+a^3)}\,.
\end{equation}
Using \Cref{tile-uncertainty} and $a\ge 1$ estimates \eqref{eqa1.5} by
\begin{equation}\label{eqa2}
 \le \frac{2^{254a^3 + 8a + 1}}
 {\mu(B(x_2, D^{\ps(\fp_2)}))}
       (1+d_{\fp_1}(\fcc(\fp_1), \fcc(\fp_2)))^{-1/(2a^2+a^3)}\,.
\end{equation}
As $x_2\in \scI(\fp_2)$ by Definition \eqref{defineep} of $E$, we have by \eqref{eq-vol-sp-cube}
\begin{equation}
    \rho(x_2,\pc(\fp_2))\le 4D^{\ps(\fp_2)}
\end{equation}
and thus by \eqref{eq-vol-sp-cube} again and the triangle inequality
\begin{equation}
    \scI(\fp_2)\subset B(x_2,8D^{\ps(\fp_2)})\, .
\end{equation}
Using three iterations of the doubling property \eqref{doublingx} give
\begin{equation}
    \mu(\scI(\fp_2))\le 2^{3a}\mu(B(x_2,D^{\ps(\fp_2)}))\, .
\end{equation}
With $a\ge 1$ and \eqref{eqa2} we conclude \eqref{eq-basic-TT*-est}.


Now assume the left-hand side of \eqref{eq-basic-TT*-est} is not zero.
There is a $y\in X$ with
\begin{equation}
    T^*_{\fp}g(y)\overline{T^*_{\fp'}g(y)}\neq 0
\end{equation}
By the triangle inequality and \Cref{tile-range-support}, we conclude
\begin{equation}
   \rho(\pc(\fp),\pc(\fp'))\le \rho(\pc(\fp),y) +\rho(\pc(\fp'),y)
   \le 5D^{\ps(\fp)}+5D^{\ps(\fp')}\le 10 D^{\ps(\fp)}\, .
\end{equation}
By the squeezing property \eqref{eq-vol-sp-cube} and the triangle inequality,
we conclude
\begin{equation}
    \scI(\fp') \subset B(\pc(\fp), 15D^{\ps(\fp)})\, .
\end{equation}
   This completes the proof of Lemma \ref{tile-correlation}.





\section{Proof of the Antichain Tile Count Lemma}
\label{subsec-geolem}


\begin{lemma}[tile reach]\label{tile-reach}
\uses{monotone-cube-metrics}
Let $\mfa\in \Mf$ and $N\ge0$ be an integer.
Let $\fp, \fp'\in \fP$ with
\begin{equation}\label{eqassumedismfa}
    d_{\fp}(\fcc(\fp), \mfa))\le 2^N\,
\end{equation}
\begin{equation}\label{eqassumedismfap}
    d_{\fp'}(\fcc(\fp'), \mfa))\le 2^N\, .
\end{equation}
Assume $\scI(\fp)\subset \scI(\fp')$ and $\ps(\fp)<\ps(\fp')$.
Then
\begin{equation}\label{lp'lp''}2^{N+2}\fp\lesssim 2^{N+2} \fp'\, .
\end{equation}
\end{lemma}

\begin{proof}
By \Cref{monotone-cube-metrics}, we have
\begin{equation}
     d_{\fp}(\fcc(\fp'),\mfa)
     \le d_{\fp'}(\fcc(\fp'),\mfa)
     \le 2^{N} \, .
\end{equation}
Together with \eqref{eqassumedismfa} and the triangle inequality, we obtain
\begin{equation}\label{eqdistqpqp}
    d_{\fp'}(\fcc(\fp'),\fcc(\fp))\le 2^{N+1} \, .
\end{equation}
Now assume
\begin{equation}
    \mfa'\in B_{\fp'}(\fcc(\fp'),2^{N+2}).
\end{equation}
By the doubling property \eqref{firstdb}, applied five times, we have
\begin{equation}\label{ageo1} d_{B(\pc(\fp'),8D^{\ps(\fp')})}(\fcc(\fp'),\mfa') < 2^{5a+N+2}\, .
\end{equation}
We have by the squeezing property \eqref{eq-vol-sp-cube}
\begin{equation}
 \pc(\fp)\in
B(\pc(\fp'),4D^{\ps(\fp')})\, .
\end{equation}
Hence by the triangle inequality
\begin{equation}
 B(\pc(\fp), 4D^{\ps(\fp')})
 \subset
B(\pc(\fp'),8D^{\ps(\fp')})\, .
\end{equation}
Together with \eqref{ageo1} and monotonicity \eqref{monotonedb} of $d$
\begin{equation}
    d_{B(\pc(\fp),4D^{\ps(\fp')})}(\fcc(\fp'),\mfa') < 2^{5a+N+2}\, .
\end{equation}
Using the doubling property \eqref{seconddb} $5a+2$ times gives
\begin{equation}
    d_{B(\pc(\fp),2^{2-5a^2-2a}D^{\ps(\fp')})}(\fcc(\fp'),\mfa') < 2^{N}\, .
\end{equation}
Using $\ps(\fp)<\ps(\fp')$ and $D=2^{100a^2}$ and $a\ge 4$ gives
\begin{equation}
    d_{\fp}(\fcc(\fp'),\mfa') < 2^{N}\, .
\end{equation}
With the triangle inequality and \eqref{eqdistqpqp},
\begin{equation}
    d_{\fp}(\fcc(\fp),\mfa') < 2^{N+2}\, .
\end{equation}
This shows
\begin{equation}
B_{\fp'}(\fcc(\fp'),2^{N+2})\subset B_{\fp}(\fcc(\fp),2^{N+2})\, .
\end{equation}
This implies \eqref{lp'lp''} and completes the proof of the lemma.
\end{proof}

For $\mfa \in \Mf$ and $N\ge 0$ define
\begin{equation}\label{eqantidefap}
    \mathfrak{A}_{\mfa,N}:=\{\fp\in\mathfrak{A}: 2^{N}\le 1+d_{\fp}(\fcc(\fp), \mfa)\le 2^{N+1}\} \, .
\end{equation}


\begin{lemma}[stack density]
\label{stack-density}
Let $\mfa \in \Mf$, $N\ge 0$ and
$L\in \mathcal{D}$. Then
\begin{equation}\label{eqanti-1}
    \sum_{\fp\in\mathfrak{A}_{\mfa,N}:\scI(\fp)=L}\mu(E(\fp)\cap G)\le 2^{a(N+5)}\dens_1(\mathfrak{A})\mu(L)\, .
\end{equation}
\end{lemma}
\begin{proof}
Let $\mfa,N,L$ be given and set
\begin{equation}
\mathfrak{A}':=\{\fp\in\mathfrak{A}_{\mfa,N}:\scI(\fp)=L\}\, .
\end{equation}
Let
$\fp\in\mathfrak{A}'$.
We have
by Definition \eqref{definedens1}
using $\lambda=2$ and the squeezing property \eqref{eq-freq-comp-ball}
\begin{equation}\label{eqanti-3}
\mu(E(\fp)\cap G)\le \mu(E_2(2, \fp))\le 2^{a}\dens_1(\mathfrak{A}')\mu(L)\, .
\end{equation}
By the covering property \eqref{thirddb}, applied $N+4$ times, there is a collection $\Mf'$ of at most $2^{a(N+4)}$
elements such that
\begin{equation}\label{eqanti-4}
    B_{\fp}(\mfa, 2^{N+1})\subset \bigcup_{\mfa'\in \Mf'}
    B_{\fp}(\mfa', 0.2)\, .
\end{equation}
As each $\fcc(\fp)$ with $\fp\in \mathfrak{A}_{\mfa,N}$
is contained in the left-hand-side
of \eqref{eqanti-4}
by definition, it is in at least one $B_{\fp}(\mfa', 0.2)$
with $\mfa'\in \Mf'$.


For two different $\fp,\fp'\in \mathfrak{A}'$, we have by
\eqref{eq-dis-freq-cover} that
$\fc(\fp)$ and $\fc(\fp')$ are disjoint and thus by the squeezing property \eqref{eq-freq-comp-ball} we have for every $\mfa'\in \Mf'$
\begin{equation}
    \mfa'\not\in B_{\fp}(\fcc(\fp), 0.2)\cap
B_{\fp}(\fcc(\fp'), 0.2)\, .
\end{equation}
Hence at most one of $\fcc(\fp)$
and $\fcc(\fp)$ is in
$B_{\fp}(\mfa', 0.2)$.
It follows that there are at most $2^{a(N+4)}$ elements in
$\mathfrak{A}'$. Adding \eqref{eqanti-3} over $\mathfrak{A}'$ proves
\eqref{eqanti-1}.


\end{proof}


\begin{lemma}[local antichain density]\label{local-antichain-density}
\uses{tile-disjointness,tile-reach}
Let $\mfa\in\Mf$ and {$N$} be
an integer. Let $\fp_{\mfa}$ be a tile with $\mfa\in \fc(\fp_{\mfa})$.
Then we have
\begin{equation}\label{eqanti-0.5}
    \sum_{\fp\in\mathfrak{A}_{\mfa,N}: \ps(\fp_{\mfa})<\ps(\fp)}\mu(E(\fp)\cap G \cap \scI(\fp_{\mfa}))
    \le \mu (E_2(2^{N+3},\fp_{\mfa}))
 \, .
\end{equation}



\end{lemma}

\begin{proof}


Let $\fp$ be any tile in $\mathfrak{A}_{\mfa,N}$ with $\ps(\fp_{\mfa})<\ps(\fp)$. By definition of
$E$, the tile contributes zero to the sum on the left-hand side of \eqref{eqanti-0.5} unless
 $\scI(\fp)\cap \scI(\fp_{\mfa}) \neq \emptyset$, which we may assume. With $\ps(\fp_{\mfa})<\ps(\fp)$
and the dyadic property
\eqref{dyadicproperty} we conclude $\scI(\fp_{\mfa})\subset \scI(\fp)$.
By the squeezing property
\eqref{eq-freq-comp-ball},
we conclude from
$\mfa\in \fc(\fp_{\mfa})$
that
\begin{equation}
    \mfa\in B(\fcc(\fp_{\mfa}), 1)\, .
\end{equation}
We conclude from $\fp \in \mathfrak{A}_{\mfa,N}$ that
\begin{equation}
    \mfa \in B(\fcc(\fp), 2^{N+1})\, .
\end{equation}
With \Cref{tile-reach}, we conclude
\begin{equation}
    2^{N+3}\fp_{\mfa} \lesssim 2^{N+3}\fp \, .
\end{equation}
By Definition \eqref{definee2} of $E_2$, we conclude
\begin{equation}
    E(\fp)\cap G \subset E_2(2^{N+3},\fp_{\mfa})\, .
\end{equation}
Using disjointedness of the various $E(\fp)$ with $\fp\in \mathfrak{A}$ by \Cref{tile-disjointness}, we obtain \eqref{eqanti-0.5}.
This proves the lemma.
\end{proof}
\begin{lemma}[global antichain density]
\label{global-antichain-density}
\uses{stack-density,local-antichain-density}
Let $\mfa\in\Mf$ and let $N\ge 0$ be
an integer. Then we have
\begin{equation}\label{eqanti00}
    \sum_{\fp\in\mathfrak{A}_{\mfa,N}}\mu(E(\fp)\cap G)
    \le
 2^{101a^3+Na}\dens_1(\mathfrak{A})\mu\left(\cup_{\fp\in\mathfrak{A}}I_{\fp}\right)\, .
\end{equation}
\end{lemma}



\begin{proof}
{Fix $\mfa$ and $N$. Let
$\mathfrak{A}'$ be the set of $\fp\in\mathfrak{A}_{\mfa,N}$ such that $\scI(\fp)\cap G$ is not empty.}


   Let $\mathcal{L}$ be the collection of dyadic cubes $I\in\mathcal{D}$ such that $I\subset \scI(\fp)$ for some $\fp\in\mathfrak{A}'$ and if $\scI(\fp)\subset I$ for some $\fp\in\mathfrak{A}'$, then $\ps(\fp)=-S$. By \eqref{coverdyadic}, for each $\fp \in \mathfrak{A}'$
   and each $x\in \scI(\fp)\cap G$, there is $I\in \mathcal{D}$ with $s(I)=-S$ and $x\in I$. By \eqref{dyadicproperty},
   we have $I\subset \scI(\fp)$. Hence
   \begin{equation}
       \scI(\fp)\subset \bigcup\{I\in \mathcal{D}: s(I)=-S, I\subset \scI(\fp)\}\subset \bigcup \mathcal{L}\, .
   \end{equation}
As each $I\in \mathcal{L}$ satisfies $I\subset \scI(\fp)$ for some $\fp$ in $\mathfrak{A'}$, we conclude
     \begin{equation}
\bigcup\mathcal{L}=\bigcup_{\fp \in \mathfrak{A}'}\scI(\fp)\, .
   \end{equation}
Let $\mathcal{L}^*$ be the set of maximal elements in $\mathcal{L}$ with respect to set inclusion.
By \eqref{dyadicproperty}, the elements in $\mathcal{L}^*$ are pairwise disjoint and we have
 \begin{equation}\label{eqdecAprime}
\bigcup\mathcal{L}^*=\bigcup_{\fp \in \mathfrak{A}'}\scI(\fp)\, .
   \end{equation}
Using the partition \eqref{eqdecAprime} into elements of $\mathcal{L}$ in \eqref{eqanti0}, it suffices to show for each $L\in \mathcal{L}^*$
\begin{equation}\label{eqanti0}
    \sum_{\fp\in\mathfrak{A}'}\mu(E(\fp)\cap G \cap L)
    \le
    2^{101a^3+aN}
    \dens_1(\mathfrak{A})\mu(L)\,.
\end{equation}
Fix $L\in \mathcal{L}^*$.
By definition of $L$, there exists an element $\fp'\in \mathfrak{A}'$ such that $L\subset \scI(\fp')$. Pick such an element $\fp
'$
in $\mathfrak{A}$ with minimal $\ps(\fp')$. As $\scI(\fp')\not \subset L$ or $s(L) = -S$ by definition of $L$, we have
with \eqref{dyadicproperty} that $s(L)< \ps(\fp')$ or $s(L) = -S$. In particular $s(L)<S$.

If there exists no cube $J \in \mathcal{D}$ with $L \subsetneq J$, then by the definition of $\mathcal{L}$ we must have $s(L) = -S$. By \eqref{dyadicproperty}, this implies that each tile $\fp$ with $E(\fp) \cap L \ne \emptyset$ must satisfy $\scI(\fp) = L$. Thus the left hand side of \eqref{eqanti0} equals
\begin{equation}
    \sum_{\fp\in\mathfrak{A}':\scI(\fp)=L}\mu(E(\fp)\cap G\cap L)\,.
\end{equation}
Thus in this case \eqref{eqanti0} is a direct consequence of \Cref{stack-density} and $a \ge 4$.

We now assume that there exists a cube $J \in \mathcal{D}$ with $L \subsetneq J$.
By \eqref{coverdyadic}, there is an
$L'\in \mathcal{D}$ with $s(L')=s(L)+1$ and $c(L)\in L'$. By \eqref{dyadicproperty}, we have
$L\subset L'$.

We split the left-hand side of \eqref{eqanti0} as
\begin{equation}\label{eqanti1}
    \sum_{\fp\in\mathfrak{A}':\scI(\fp)=L'}\mu(E(\fp)\cap G\cap L)
\end{equation}
\begin{equation}\label{eqanti2}
    +
     \sum_{\fp\in\mathfrak{A}':\scI(\fp)\neq L'}\mu(E(\fp)\cap G\cap L)\, ,
\end{equation}

We first estimate \eqref{eqanti1}
with \Cref{stack-density} by
\begin{equation}\label{equanti1.5}
    \le \sum_{\fp\in\mathfrak{A}':\scI(\fp)=L'}\mu(E(\fp)\cap G\cap L')\le 2^{a(N+5)}\dens_1(\mathfrak{A})\mu(L')\, .
\end{equation}



We turn to \eqref{eqanti2}.
Consider the element $\fp'\in \mathfrak{A}'$ as above
with $L\subset \scI(\fp')$ and $s(L)<\ps(\fp')$.
As $L\subset L'$ and $s(L')=s(L)+1$, we conclude with the dyadic property that $L'\subset \scI(\fp')$.
By maximality of $L$, we have
$L'\not\in \mathcal{L}$.
This together with the existence of the given $\fp'\in \mathfrak{A}$
with $L'\subset \scI(\fp')$
shows by definition of $\mathcal{L}$ that there exists $\fp''\in \mathfrak{A}'$ with
$\scI(\fp'')\subset L'$.




By the covering property \eqref{eq-dis-freq-cover}, there exists a unique $\fp_{\mfa}$ with
\begin{equation*}
    \scI(\fp_{\mfa})=L'
\end{equation*}
such that $\mfa\in \fc(\fp_{\mfa})$.
Note that
\begin{equation}
    \mfa\in B(\fcc(\fp_{\mfa}), 1)
\end{equation}
and as $\fp'' \in \mathfrak{A}_{\mfa,N}$ that
\begin{equation}
    \mfa \in B(\fcc(\fp''), 2^{N+1})\, .
\end{equation}
By \Cref{tile-reach}, we conclude
\begin{equation}
    2^{N+3}\fp'' \lesssim 2^{N+3}\fp_{\mfa} \, .
\end{equation}
As $\fp''\in \mathfrak{A}'$, we have by Definition
\eqref{definedens1} of $\dens_1$ that
\begin{equation}\label{pmfadens}
   \mu(E_2(2^{N+3}, \fp_{\mfa}))\le 2^{Na+3a}\dens_1(\mathfrak{A}) {\mu(L')}\, .
\end{equation}
Now let $\fp$ be any tile in the summation set in \eqref{eqanti2}, that is, $\fp\in \mathfrak{A}'$ and $\scI(\fp)\neq L'$.
Then $\scI(\fp)\cap L\neq \emptyset$. It follows by the dyadic property \eqref{dyadicproperty}
and the definition of $L$ that
$L\subset \scI(\fp)$ and $L\neq \scI(\fp)$. By the dyadic property \eqref{dyadicproperty}, we have
$s(L)<\ps(\fp)$ and thus $s(L')\le \ps(\fp)$. By the dyadic property
   \eqref{dyadicproperty} again, we have $L'\subset \scI(\fp)$.
As $L'\neq \scI(\fp)$, we conclude $s(L)<\ps(\fp)$.
By \Cref{local-antichain-density}, we can thus estimate \eqref{eqanti2} by
\begin{equation}\label{eqanti0.5}
    \sum_{\fp\in\mathfrak{A}':\scI(\fp)\neq L'}\mu(E(\fp)\cap G\cap L')
    \le \mu (E_2(2^{N+3},\fp_{\mfa}))\, .
\end{equation}
Using the decomposition
into \eqref{eqanti1} and
\eqref{eqanti2} and the estimates
\eqref{equanti1.5},
\eqref{eqanti-0.5},
\eqref{pmfadens} we obtain the estimate
\begin{equation}\label{eqanti3.14}
\sum_{\fp\in\mathfrak{A}'}\mu(E(\fp)\cap G \cap L)
    \le (2^{a(N+5)}+2^{Na+3a})\dens_1(\mathfrak{A})\mu(L')\,.
\end{equation}

Using $s(L')=s(L)+1$ and $D=2^{100a^2}$ and the
squeezing property \eqref{eq-vol-sp-cube}
and the doubling property \eqref{doublingx} $100a^2+4$ times , we obtain
\begin{equation}
    \mu(L')\le 2^{100a^3+4a}\mu(L)\, .
\end{equation}
Inserting in \eqref{eqanti3.14} and using $a\ge 4$ gives \eqref{eqanti0}.
This completes the proof of the lemma.
\end{proof}



We turn to the proof of \Cref{antichain-tile-count}.




\begin{proof}


Using that $\mathfrak{A}$ is the union of the
$\mathfrak{A}_{\mfa,N}$ with $N\ge 0$,
we estimate the left-hand side \eqref{eq-antichain-Lp}
with the triangle inequality by
\begin{equation}\label{eqanti23}
\le \sum_{N\ge 0} \left\|\sum_{\fp\in \mathfrak{A}_{\mfa,N}} 2^{-N/(2a^2+a^3)}\mathbf{1}_{E(\fp)} \mathbf{1}_G\right\|_{p}
\end{equation}
We consider each individual term in this sum and estimate it's $p$-th power.
   Using that for each $x\in X$ by \Cref{global-antichain-density} there is at most one $\fp\in \mathfrak{A}$ with $x\in E(\fp)$,
 we have
 \begin{equation}
     \left\|\sum_{\fp\in \mathfrak{A}_{\mfa,N}} 2^{-N/(2a^2+a^3)}\mathbf{1}_{E(\fp)} \mathbf{1}_G\right\|_{p}^p
 \end{equation}
\begin{equation}
    =\int_G\Big(\sum_{\fp\in \mathfrak{A}_{\mfa,N}}2^{-N/(2a^2+a^3)}\mathbf{1}_{E(\fp)}(x)\Big)^p\, d\mu(x)
\end{equation}
\begin{equation}
  = \int _G\sum_{\fp\in\mathfrak{A}_{\mfa,N}}2^{-pN/(2a^2+a^3)}\mathbf{1}_{E(\fp)}(x)\, d\mu(x)
\end{equation}
\begin{equation}
  = 2^{-pN/(2a^2+a^3)} \sum_{\fp\in\mathfrak{A}_{\mfa,N}}\mu(E(\fp)\cap G)
\end{equation}

Using \Cref{global-antichain-density}, we estimate the last display by
\begin{equation}\label{eqanti21}
    \le 2^{-pN/(2a^2+a^3)+101a^3+Na}\dens_1(\mathfrak{A})\mu\left(\cup_{\fp\in\mathfrak{A}}\scI(\fp)\right)
\end{equation}
Using that with $a\ge 4$ and since $p = 4a^4$, we have
\begin{equation}
    pN/(2a^2+a^3)\ge
    4a^4N/(3a^3) \ge Na+N\, .
\end{equation}
Hence we have for \eqref{eqanti21} the upper bound
\begin{equation}\label{eqanti22}
\le 2^{101a^3-N}\dens_1(\mathfrak{A})\mu\left(\cup_{\fp\in\mathfrak{A}}\scI(\fp)\right)\, .
\end{equation}
Taking th $p$-th root and summing over $N\ge 0$ gives for \eqref{eqanti23} the upper bound

\begin{equation}
\le \left(\sum_{N\ge 0} 2^{-N/p}\right)2^{101a^3/p}\dens_1(\mathfrak{A})^{{\frac{1}{p}}}\mu\left(\cup_{\fp\in\mathfrak{A}}\scI(\fp)\right)^{{\frac{1}{p}}}
\end{equation}
\begin{equation}
\le \left(1-2^{-1/p}\right)^{-1}
2^{101a^3/p}
\dens_1(\mathfrak{A})^{\frac 1p}\mu\left(\cup_{\fp\in\mathfrak{A}}\scI(\fp)\right)^{\frac 1p}\, .
\end{equation}
Using that $p = 4a^4$ and $a \ge 4$, this proves the lemma.
\end{proof}







\chapter{Proof of the Forest Operator Proposition}

\label{treesection}

\section{The pointwise tree estimate}
Fix a forest $(\fU, \fT)$. The main result of this subsection is \Cref{pointwise-tree-estimate}, we begin this section with some definitions necessary to state the lemma.

For $\fu \in \fU$ and $x\in X$, we define
$$
    \sigma (\fu, x):=\{\ps(\fp):\fp\in \fT(\fu), x\in E(\fp)\}\,.
$$
This is a subset of $\mathbb{Z} \cap [-S, S]$, so has a minimum and a maximum. We set
$$
    \overline{\sigma} (\fu, x) := \max \sigma(\fT(\fu), x)
$$
$$
    \underline{\sigma} (\fu, x) := \min\sigma(\fT(\fu), x)\,.
$$
\begin{lemma}[convex scales]
\label{convex-scales}
    For each $\fu \in \fU$, we have
    $$
        \sigma(\fu, x) = \mathbb{Z} \cap [\underline{\sigma} (\fu, x), \overline{\sigma} (\fu, x)]\,.
    $$
\end{lemma}

\begin{proof}
    Let $s \in \mathbb{Z}$ with $\underline{\sigma} (\fu, x) \le s \le \overline{\sigma} (\fu, x)$. By definition of $\sigma$, there exists $\fp \in \fT(\fu)$ with $\ps(\fp) = \underline{\sigma} (\fu, x)$ and $x \in E(\fp)$, and there exists $\fp'' \in \fT(\fu)$ with $\ps(\fp'') = \overline{\sigma} (\fu, x)$ and $x \in E(\fp'') \subset \scI(\fp'')$. By property \eqref{coverdyadic} of the dyadic grid, there exists a cube $I \in \mathcal{D}$ of scale $s$ with $x \in I$. By property \eqref{eq-dis-freq-cover}, there exists a tile $\fp' \in \fP(I)$ with $\tQ(x) \in \fc(\fp')$. By the dyadic property \eqref{dyadicproperty} we have $\scI(\fp) \subset \scI(\fp') \subset \scI(\fp'')$, and by \eqref{eq-freq-dyadic}, we have $\fc(\fp'') \subset \fc(\fp') \subset \fc(\fp)$. Thus $\fp \le \fp' \le\fp''$, which gives with the convexity property \eqref{forest2} of $\fT(\fu)$ that $\fp' \in \fT(\fu)$, so $s \in \sigma(\fu, x)$.
\end{proof}

For a nonempty collection of tiles $\mathfrak{S} \subset \fP$ we define
$$
    \mathcal{J}_0(\mathfrak{S})
$$
to be the collection of all dyadic cubes $J \in \mathcal{D}$ such that $s(J) = -S$ or
$$
    \scI(\fp) \not\subset B(c(J), 100D^{s(J) + 1})
$$
for all $\fp \in \mathfrak{S}$. We define $\mathcal{J}(\mathfrak{S})$ to be the collection of inclusion maximal cubes in $\mathcal{J}_0(\mathfrak{S})$.

We further define
$$
    \mathcal{L}_0(\mathfrak{S})
$$
to be the collection of dyadic cubes $L \in \mathcal{D}$ such that $s(L) = -S$, or there exists $\fp \in \mathfrak{S}$ with $L \subset \scI(\fp)$ and there exists no $\fp \in \mathfrak{S}$ with $\scI(\fp) \subset L$. We define $\mathcal{L}(\mathfrak{S})$ to be the collection of inclusion maximal cubes in $\mathcal{L}_0(\mathfrak{S})$.

\begin{lemma}[dyadic partitions]
    \label{dyadic-partitions}
    For each $\mathfrak{S} \subset \fP$, we have
    \begin{equation}
        \label{eq-J-partition}
        \bigcup_{I \in \mathcal{D}} I = \dot{\bigcup_{J \in \mathcal{J}(\mathfrak{S})}} J
    \end{equation}
    and
    \begin{equation}
        \label{eq-L-partition}
        \bigcup_{\fp\in \mathfrak{S}} \scI(\fp) = \dot{\bigcup_{L \in \mathcal{L}(\mathfrak{S})}} L\,.
    \end{equation}
\end{lemma}

\begin{proof}
    Since $\mathcal{J}(\mathfrak{S})$ is the set of inclusion maximal cubes in $\mathcal{J}_0(\mathfrak{S})$, cubes in $\mathcal{J}(\mathfrak{S})$ are pairwise disjoint by \eqref{dyadicproperty}. The same applies to $\mathcal{L}(\mathfrak{S})$.

    If $x \in \bigcup_{I \in \mathcal{D}} I$, then there exists by \eqref{coverdyadic} a cube $I \in \mathcal{D}$ with $x \in I$ and $s(I) = -S$. Then $I \in \mathcal{J}_0(\mathfrak{S})$. There exists an inclusion maximal cube in $\mathcal{J}_0(\mathfrak{S})$ containing $I$. This cube contains $x$ and is contained in $\mathcal{J}(\mathfrak{S})$. This shows one inclusion in \eqref{eq-J-partition}, the other one follows from $\mathcal{J}(\mathfrak{S}) \subset \mathcal{D}$.

    The proof of the two inclusions in \eqref{eq-L-partition} is similar.
\end{proof}

For a finite collection of pairwise disjoint cubes $\mathcal{C}$, define the projection operator
$$
    P_{\mathcal{C}}f(x) :=\sum_{J\in\mathcal{C}}\mathbf{1}_J(x) \frac{1}{\mu(J)}\int_J f(y) \, \mathrm{d}\mu(y)\,.
$$
Given a scale $-S \le s\le S$ and a point $x \in \bigcup_{I\in \mathcal{D}, s(I) = s} I$, there exists a unique cube in $\mathcal{D}$ of scale $s$ containing $x$ by \eqref{coverdyadic}. We denote it by $I_s(x)$. Define the nontangential maximal operator
\begin{equation}
    \label{eq-TN-def}
    T_{\mathcal{N}} f(x) := \sup_{-S \le s_1 < s_2 \le S} \sup_{x' \in I_{s_1}(x)} \left| \sum_{s = s_1}^{s_2} \int K_s(x',y) f(y) \, \mathrm{d}\mu(y) \right|\,.
\end{equation}
Define for each $\fu \in \fU$ the auxiliary operator
$$
    S_{1,\fu}f(x)
$$
\begin{equation}
    \label{eq-def-S-op}
    :=\sum_{I\in\mathcal{D}} \mathbf{1}_{I}(x) \sum_{\substack{J\in \mathcal{J}(\fT(\fu))\\
    J\subset B(c(I), 16 D^{s(I)})}} \frac{D^{(s(J) - s(I))/a}}{\mu(B(c(I), 16D^{s(I)}))}\int_J |f(y)| \, \mathrm{d}\mu(y)\,.
\end{equation}
Define also the collection of balls
$$
    \mathcal{B} = \{B(c(I), D^{s + s(I)}) \ : \ I \in \mathcal{D}\,, 0 \le s \le S + 5\}\,.
$$

The following pointwise estimate for operators associated to sets $\fT(\fu)$ is the main result of this subsection.

\begin{lemma}[pointwise tree estimate]
    \label{pointwise-tree-estimate}
    \uses{first-tree-pointwise,second-tree-pointwise,third-tree-pointwise}
    Let $\fu \in \fU$ and $L \in \mathcal{L}(\fT(\fu))$. Let $x, x' \in L$.
    Then for all bounded functions $f$ with bounded support
    $$
        \left|\sum_{\fp \in \fT(\fu)} T_{\fp}[ e(\fcc(\fu))f](x)\right|
    $$
    \begin{equation}
        \label{eq-LJ-ptwise}
        \leq 2^{151a^3}(M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(x')+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(x')|,
    \end{equation}
\end{lemma}


\begin{proof}
    By \eqref{definetp}, if $T_{\fp}[ e(-\fcc(\fu))f](x) \ne 0$, then $x \in E(\fp)$. Combining this with $|e(\fcc(\fu)(x)-\tQ(x)(x))| = 1$, we obtain
    $$
        |\sum_{\fp \in \fT(\fu)} T_{\fp}[ e(\fcc(\fu))f](x)|
    $$
    \begin{multline*}
        = \Bigg| \sum_{s \in \sigma(\fu, x)} \int e(-\fcc(\fu)(y) + \tQ(x)(y) + \fcc(\fu)(x) -\tQ(x)(x))\times\\
        K_s(x,y)f(y) \, \mathrm{d}\mu(y) \Bigg|\,.
    \end{multline*}
    Using the triangle inequality, we bound this by the sum of three terms:
    \begin{multline}
        \label{eq-term-A}
        \le \Bigg| \sum_{s \in \sigma(\fu, x)} \int (e(-\fcc(\fu)(y) + \tQ(x)(y) + \fcc(\fu)(x) -\tQ(x)(x))-1)\times\\
        K_s(x,y)f(y) \, \mathrm{d}\mu(y) \Bigg|
    \end{multline}
    \begin{equation}
        \label{eq-term-B}
        + \Bigg| \sum_{s \in \sigma(\fu, x)} \int K_s(x,y) P_{\mathcal{J}(\fT(\fu))} f(y) \, \mathrm{d}\mu(y) \Bigg|
    \end{equation}
    \begin{equation}
        \label{eq-term-C}
        + \Bigg| \sum_{s \in \sigma(\fu, x)} \int K_s(x,y) (f(y) - P_{\mathcal{J}(\fT(\fu))} f(y)) \, \mathrm{d}\mu(y) \Bigg|\,.
    \end{equation}
    The proof is completed using the bounds for these three terms proven in \Cref{first-tree-pointwise}, \Cref{second-tree-pointwise} and \Cref{third-tree-pointwise}.
\end{proof}

\begin{lemma}[first tree pointwise]
    \label{first-tree-pointwise}
    \uses{convex-scales}
    For all $\fu \in \fU$, all $L \in \mathcal{L}(\fT(\fu))$, all $x, x' \in L$ and all bounded $f$ with bounded support, we have
    $$
        \eqref{eq-term-A} \le 10 \cdot 2^{105a^3} M_{\mathcal{B}, 1}P_{\mathcal{J}(\fT(\fu))}|f|(x')\,.
    $$
\end{lemma}

\begin{proof}
    Let $s \in \sigma(\fu,x)$.
    If $x, y \in X$ are such that $K_s(x,y)\neq 0$, then, by \eqref{supp-Ks}, we have $\rho(x,y)\leq 1/2 D^s$. By $1$-Lipschitz continuity of the function $t \mapsto \exp(it) = e(t)$ and the property \eqref{osccontrol} of the metrics $d_B$, it follows that
    \begin{multline*}
        |e(-\fcc(\fu)(y)+\tQ(x)(y)+\fcc(\fu)(x)-\tQ(x)(x))-1|\\
        \leq d_{B(x, 1/2 D^{s})}(\fcc(\fu), \tQ(x))\,.
    \end{multline*}
    Let $\fp_s \in \fT(\fu)$ be a tile with $\ps(\fp_s) = s$ and $x \in E(\fp_s)$, and let $\fp'$ be a tile with $\ps(\fp') = \overline{\sigma}(\fu, x)$ and $x \in E(\fp')$.
    Using the doubling property \eqref{firstdb}, the definition of $d_{\fp}$ and \Cref{monotone-cube-metrics}, we can bound the previous display by
    $$
        2^a d_{\fp_s}(\fcc(\fu), \tQ(x)) \le 2^{a} 2^{s - \overline{\sigma}(\fu, x)} d_{\fp'}(\fcc(\fu), \tQ(x))\,.
    $$
    Since $\fcc(\fu) \in B_{\fp'}(\fcc(\fp'), 4)$ by \eqref{forest1} and $\tQ(x) \in \Omega(\fp') \subset B_{\fp'}(\fcc(\fp'), 1)$ by \eqref{eq-freq-comp-ball}, this is estimated by
    $$
        \le 5 \cdot 2^{a} 2^{s - \overline{\sigma}(\fu, x)} \,.
    $$
    Using \eqref{eq-Ks-size}, it follows that
    $$
        \eqref{eq-term-A} \le 5\cdot 2^{103a^3} \sum_{s\in\sigma(x)}2^{s - \overline{\sigma}(\fu, x)} \frac{1}{\mu(B(x,D^s))}\int_{B(x,0.5D^{s})}|f(y)|\,\mathrm{d}\mu(y)\,.
    $$
    By \eqref{eq-J-partition}, the collection $\mathcal{J}$ is a partition of $X$, so this is estimated by
    $$
         5\cdot 2^{103a^3} \sum_{s\in\sigma(x)}2^{s - \overline{\sigma}(\fu, x)} \frac{1}{\mu(B(x,D^s))}\sum_{\substack{J \in \mathcal{J}(\fT(\fu))\\J \cap B(x, 0.5D^s) \ne \emptyset} }\int_{J}|f(y)|\,\mathrm{d}\mu(y)\,.
    $$
    This expression does not change if we replace $|f|$ by $P_{\mathcal{J}(\fT(\fu))}|f|$.

    Let $J \in \mathcal{J}(\fT(\fu))$ with $B(x, 0.5 D^s) \cap J \ne \emptyset$. By the triangle inequality and since $x \in E(\fp_s) \subset B(\pc(\fp_s), 4D^{s})$, it follows that $B(\pc(\fp_s), 4.5D^s) \cap J \ne \emptyset$. If $s(J) \ge s$ and $s(J) > -S$, then it follows from the triangle inequality, \eqref{eq-vol-sp-cube} and \eqref{defineD} that $\scI(\fp_s) \subset B(c(J), 100 D^{s(J)+1})$, contradicting $J \in \mathcal{J}(\mathfrak{T}(\fu))$. Thus $s(J) \le s - 1$ or $s(J) = -S$. If $s(J) = -S$ and $s(J) > s - 1$, then $s = -S$. Thus we always have $s(J) \le s$. It then follows from the triangle inequality and \eqref{eq-vol-sp-cube} that $J \subset B(\pc(\fp_s), 16 D^s)$.

    Thus we can continue our chain of estimates with
    $$
        5\cdot 2^{103a^3} \sum_{s\in\sigma(x)}2^{s - \overline{\sigma}(\fu, x)} \frac{1}{\mu(B(x,D^s))}\int_{B(\pc(\fp_s),16 D^s)}P_{\mathcal{J}(\fT(\fu))}|f(y)|\,\mathrm{d}\mu(y)\,.
    $$
    We have $B(\pc(\fp_s), 16D^s)) \subset B(x, 32D^s)$, by \eqref{eq-vol-sp-cube} and the triangle inequality, since $x \in \scI(\fp)$. Combining this with the doubling property \eqref{doublingx}, we obtain
    $$
        \mu(B(\pc(\fp_s), 16D^s)) \le 2^{5a} \mu(B(x, D^s))\,.
    $$
    Since $a \ge 4$, it follows that \eqref{eq-term-A} is bounded by
    $$
        2^{104a^3} \sum_{s\in\sigma(x)}2^{s - \overline{\sigma}(\fu, x)} \frac{1}{\mu(B(\pc(\fp_s),16D^s))}\int_{B(\pc(\fp_s),16D^s)}P_{\mathcal{J}(\fT(\fu))}|f(y)|\,\mathrm{d}\mu(y)\,.
    $$
    Since $L \in \mathcal{L}(\fT(\fu))$, we have $s(L) \le \ps(\fp)$ for all $\fp \in \fT(\fu)$. Since $x\in L \cap \scI(\fp_s)$, it follows by \eqref{dyadicproperty} that $L \subset \scI(\fp_s)$, in particular $x' \in \scI(\fp_s) \subset B(\pc(\fp_s), 16D^s)$. Thus
    $$
        \le 2^{104a^3} \sum_{s\in\sigma(x)}2^{s - \overline{\sigma}(\fu, x)} M_{\mathcal{B}, 1}P_{\mathcal{J}(\fT(\fu))}|f|(x')
    $$
    $$
        \le 2^{105a^3} M_{\mathcal{B}, 1}P_{\mathcal{J}(\fT(\fu))}|f|(x')\,.
    $$
    This completes the estimate for term \eqref{eq-term-A}.
\end{proof}

\begin{lemma}[second tree pointwise]
    \label{second-tree-pointwise}
    For all $\fu \in \fU$, all $L \in \mathcal{L}(\fT(\fu))$, all $x, x' \in L$ and all bounded $f$ with bounded support, we have
    $$
         \Bigg| \sum_{s \in \sigma(\fu, x)} \int K_s(x,y) P_{\mathcal{J}(\fT(\fu))} f(y) \, \mathrm{d}\mu(y) \Bigg| \le T_{\mathcal{N}} P_{\mathcal{J}(\fT(\fu))} f(x')\,.
    $$
\end{lemma}

\begin{proof}
    Let $s = \underline{\sigma}(\fu, x)$. By definition, there exists a tile $\fp \in \fT(\fu)$ with $\ps(\fp) = s$ and $x \in E(\fp)$. Then $x \in \scI(\fp) \cap L$. By \eqref{dyadicproperty} and the definition of $\mathcal{L}(\fT(\fu))$, it follows that $L \subset \scI(\fp)$, in particular $x' \in \scI(\fp)$, so $x \in I_s(x')$.
    The lemma now follows from the definition of $T_{\mathcal{N}}$.
\end{proof}

\begin{lemma}[third tree pointwise]
    \label{third-tree-pointwise}
    For all $\fu \in \fU$, all $L \in \mathcal{L}(\fT(\fu))$, all $x, x' \in L$ and all bounded $f$ with bounded support, we have
    \begin{equation*}
        \Bigg| \sum_{s \in \sigma(\fu, x)} \int K_s(x,y) (f(y) - P_{\mathcal{J}(\fT(\fu))} f(y)) \, \mathrm{d}\mu(y) \Bigg|
    \end{equation*}
    \begin{equation*}
          \le 2^{151a^3} S_{1,\fu} P_{\mathcal{J}(\fT(\fu))}|f|(x')\,.
    \end{equation*}
\end{lemma}

\begin{proof}
    We have for $J \in \mathcal{J}(\fT(\fu))$:
    $$
        \int_J K_{s}(x,y)(1 - P_{\mathcal{J}(\fT(\fu))})f(y) \, \mathrm{d}\mu(y)
    $$
    \begin{equation}
    \label{eq-canc-comp}
        = \int_J \frac{1}{\mu(J)} \int_J K_s(x,y) - K_s(x,z) \, \mathrm{d}\mu(z) \,f(y) \, \mathrm{d}\mu(y)\,.
    \end{equation}
    By \eqref{eq-Ks-smooth} and \eqref{eq-vol-sp-cube}, we have for $y, z \in J$
    $$
        |K_s(x,y) - K_s(x,z)| \le \frac{2^{150a^3}}{\mu(B(x, D^s))} \left(\frac{8 D^{s(J)}}{D^s}\right)^{1/a}\,.
    $$
    Suppose that $s \in \sigma(\fu, x)$.
    If $K_s(x,y) \ne 0$ for some $y \in J \in \mathcal{J}(\fT(\fu))$ then, by \eqref{supp-Ks}, $y \in B(x, 0.5 D^s) \cap J \ne \emptyset$. Let $\fp \in \fT(\fu)$ with $\ps(\fp) = s$ and $x \in E(\fp)$. Then $B(\pc(\fp_s), 4.5D^s) \cap J \ne \emptyset$ by the triangle inequality. If $s(J) \ge s$ and $s(J) > -S$, then it follows from the triangle inequality, \eqref{eq-vol-sp-cube} and \eqref{defineD} that $\scI(\fp) \subset B(c(J), 100 D^{s(J)+1})$, contradicting $J \in \mathcal{J}(\mathfrak{T}(\fu))$. Thus $s(J) \le s - 1$ or $s(J) = -S$. If $s(J) = -S$ and $s(J) > s - 1$, then $s = -S$. So in both cases, $s(J) \le s$. It then follows from the triangle inequality and \eqref{eq-vol-sp-cube} that $J \subset B(x, 16 D^s)$.

    Thus, we can estimate \eqref{eq-term-C} by
    $$
        2^{150a^3 + 3/a}\sum_{\fp\in \mathfrak{T}}\frac{\mathbf{1}_{E(\fp)}(x)}{\mu(B(x,D^{\ps(\fp)}))}\sum_{\substack{J\in \mathcal{J}(\fT(\fu))\\J\subset B(x, 16D^{\ps(\fp)})}} D^{(s(J) - \ps(\fp))/a} \int_J |f|\,.
    $$
    $$
        = 2^{150a^3 + 3/a}\sum_{I \in \mathcal{D}} \sum_{\substack{\fp\in \mathfrak{T}\\ \scI(\fp) = I}}\frac{\mathbf{1}_{E(\fp)}(x)}{\mu(B(x, D^{s(I)}))}\sum_{\substack{J\in \mathcal{J}(\fT(\fu))\\J\subset B(x, 16 D^{\ps(\fp)})}} D^{(s(J) - s(I))/a} \int_J |f|\,.
    $$
    By \eqref{eq-dis-freq-cover} and \eqref{defineep}, the sets $E(\fp)$ for tiles $\fp$ with $\scI(\fp) = I$ are pairwise disjoint.
    If $x \in E(\fp)$ then in particular $x \in \scI(\fp)$, so by \eqref{eq-vol-sp-cube} $B(c(I),16D^{s(I)}) \subset B(x, 32D^{s(I)})$. By the doubling property \eqref{doublingx}
    $$
        \mu(B(c(I), 16D^{s(I)})) \le 2^{5a} \mu(B(x, D^{s(I)}))\,.
    $$
    Since $a \ge 4$ we can continue our estimate with
    $$
        \le 2^{151a^3}\sum_{I \in \mathcal{D}} \frac{\mathbf{1}_{I}(x)}{\mu(B(c(I), 16D^{s(I)}))}\sum_{\substack{J\in \mathcal{J}(\fT(\fu))\\J\subset B(x, 16 D^{\ps(\fp)})}} D^{(s(J) - \ps(\fp))/a} \int_J |f|\,.
    $$
    Finally, it follows from the definition of $\mathcal{L}(\fT(\fu))$ that $x \in \scI(\fp)$ if and only if $x' \in \scI(\fp)$, thus this equals
    $$
         2^{151a^3} S_{1,\fu} P_{\mathcal{J}(\fT(\fu))}|f|(x')\,.
    $$
    This completes the proof.
\end{proof}

\section{An auxiliary \texorpdfstring{$L^2$}{L2} tree estimate}

In this subsection we prove the following estimate on $L^2$ for operators associated to trees.

\begin{lemma}[tree projection estimate]
    \label{tree-projection-estimate}
    \uses{dyadic-partitions,pointwise-tree-estimate,nontangential-operator-bound,boundary-operator-bound}
    Let $\fu \in \fU$.
    Then we have for all $f, g$ bounded with bounded support
    $$
        \Bigg|\int_X \sum_{\fp \in \fT(\fu)} \bar g(y) T_{\fp}f(y) \, \mathrm{d}\mu(y) \Bigg|
    $$
    \begin{equation}
        \label{eq-tree-est}
         \le 2^{104a^3}\|P_{\mathcal{J}(\fT(\fu))}|f|\|_{2}\|P_{\mathcal{L}(\fT(\fu))}|g|\|_{2}.
    \end{equation}
\end{lemma}

Below, we deduce \Cref{tree-projection-estimate} from \Cref{pointwise-tree-estimate} and the following estimates for the operators in \Cref{pointwise-tree-estimate}.

\begin{lemma}[nontangential operator bound]
    \label{nontangential-operator-bound}
  \uses{Hardy-Littlewood}
    For all bounded $f$ with bounded support
    $$
        \|T_{\mathcal{N}} f\|_2 \le 2^{103a^3} \|f\|_2\,.
    $$
\end{lemma}

\begin{lemma}[boundary operator bound]
    \label{boundary-operator-bound}
    \uses{Hardy-Littlewood,boundary-overlap}
    For all $\fu \in \fU$ and all bounded functions $f$ with bounded support
    \begin{equation}
        \label{eq-S-bound}
        \|S_{1,\fu}f\|_2 \le 2^{12a} \|f\|_2\,.
    \end{equation}
\end{lemma}

\begin{proof}[Proof of \Cref{tree-projection-estimate}]
    \proves{tree-projection-estimate}
    For each $L \in \mathcal{L}(\fT(\fu))$, choose a point $x'(L) \in L$ such that for all $y \in L$
    $$
        (M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(x')+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(x')|
    $$
    \begin{equation}
        \label{eq-x'L-almost-inf}
        \le 2 ((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(y)+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)|)\,.
    \end{equation}
    This point exists since \eqref{eq-x'L-almost-inf} is non-negative for each $y$.
    Then we have by \Cref{pointwise-tree-estimate} for each $L \in \mathcal{L}(\fT(\fu))$
    $$
        \int_L |g(y)| \Bigg| \sum_{\fp \in \fT(\fu)} T_{\fp} f(y) \Bigg| \, \mathrm{d}\mu(y)
    $$
    $$
        \le 2^{151a^3} \int_L |g(y)| ((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(x')+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(x')| ) \, \mathrm{d}\mu(y)
    $$
    \begin{multline*}
        \le 2^{151a^3} \int_L |g(y)| \, \mathrm{d}\mu(y)\times\\
         \int_L 2((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(y)+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)| ) \, \mathrm{d}\mu(y)
    \end{multline*}
    \begin{multline*}
        = 2^{151a^3 + 1} \int_L P_{\mathcal{L}(\fT(\fu))}|g|(y)\times \\((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(y)+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)| ) \, \mathrm{d}\mu(y)\,.
    \end{multline*}
    By \eqref{definetp}, we have $T_{\fp} f = \mathbf{1}_{\scI(\fp)} T_{\fp} f$ for all $\fp \in \fP$, so
    $$
        \Bigg| \int \bar g(y) \sum_{\fp \in \fT(\fu)} T_{\fp} f(y) \, \mathrm{d}\mu(y) \Bigg| = \Bigg| \int_{\bigcup_{\fp \in \fT(\fu)} \scI(\fp)} \bar g(y) \sum_{\fp \in \fT(\fu)} T_{\fp} f(y) \, \mathrm{d}\mu(y) \Bigg|\,.
    $$
    Since $\mathcal{L}(\fT(\fu))$ partitions $\bigcup_{\fp \in \fT(\fu)} \scI(\fp)$ by \Cref{dyadic-partitions},
    we get from the triangle inequality
    $$
        \le \sum_{L \in \mathcal{L}(\fT(\fu))} \int_L |g(y)| \Bigg| \sum_{\fp \in \fT(\fu)} T_{\fp} f(y) \Bigg| \, \mathrm{d}\mu(y)
    $$
    which by the above computation is bounded by
    \begin{multline*}
        2^{151a^3 + 1} \sum_{L \in \mathcal{L}(\fT(\fu))} \int_L P_{\mathcal{L}(\fT(\fu))}|g|(y) \times \\((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(y)+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)| ) \, \mathrm{d}\mu(y)
    \end{multline*}
    \begin{multline*}
        = 2^{151a^3 + 1} \int_X P_{\mathcal{L}(\fT(\fu))}|g|(y)\times \\((M_{\mathcal{B},1}+S_{1,\fu})P_{\mathcal{J}(\fT(\fu))}|f|(y)+|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)| ) \, \mathrm{d}\mu(y)\,.
    \end{multline*}
    Applying Cauchy-Schwarz and Minkowski's inequality, this is bounded by
    \begin{multline*}
        2^{151a^3 + 1} \|P_{\mathcal{L}(\fT(\fu))}|g|\|_2 \times \\(\|M_{\mathcal{B},1}P_{\mathcal{J}(\fT(\fu))}|f|\|_2 + \|S_{1,\fu}P_{\mathcal{J}(\fT(\fu))}|f|\|_2 + \|T_{\mathcal{N}}P_{\mathcal{J}(\fT(\fu))}f(y)|\|_2)\,.
    \end{multline*}
    By \Cref{Hardy-Littlewood}, \Cref{nontangential-operator-bound} and \Cref{boundary-operator-bound}, the second factor is at most
    $$
        (2^{2a+1} + 2^{12a})\|P_{\mathcal{J}(\fT(\fu))}|f|\|_2 + 2^{103a^3} \|P_{\mathcal{J}(\fT(\fu))}f\|_2\,.
    $$
    By the triangle inequality we have for all $x \in X$ that $|P_{\mathcal{J}(\fT(\fu))}f|(x) \le P_{\mathcal{J}(\fT(\fu))}|f|(x)$, thus we can further estimate the above by
    $$
        (2^{2a+1} + 2^{12a} + 2^{103a^3}) \|P_{\mathcal{J}(\fT(\fu))}|f|\|_2\,.
    $$
    This completes the proof since $a \ge 4$.
\end{proof}

Now we prove the two auxiliary lemmas. We begin with the nontangential maximal operator $T_{\mathcal{N}}$.

\begin{proof}[Proof of \Cref{nontangential-operator-bound}]
    \proves{nontangential-operator-bound}
    Fix $s_1, s_2$. By \eqref{eq-psisum} we have for all $x \in (0, \infty)$
    $$
        \sum_{s = s_1}^{s_2} \psi(D^{-s}x) = 1 - \sum_{s < s_1} \psi(D^{-s}x) - \sum_{s > s_1} \psi(D^{-s}x)\,.
    $$
    Since $\psi$ is supported in $[\frac{1}{4D}, \frac{1}{2}]$, the two sums on the right hand side are zero for all $x \in [\frac{1}{2}D^{s_1-1}, \frac{1}{4} D^{s_2 - 1}]$, hence
    $$
        x \in [\frac{1}{2}D^{s_1-1}, \frac{1}{4} D^{s_2}] \implies \sum_{s = s_1}^{s_2} \psi(D^{-s}x) = 1\,.
    $$
    Since $\psi$ is supported in $[\frac{1}{4D}, \frac{1}{2}]$, we further have
    $$
        x \notin [\frac{1}{4}D^{s_1 - 1}, \frac{1}{2}D^{s_2}] \implies \sum_{s = s_1}^{s_2} \psi(D^{-s}x) = 0\,.
    $$
    Finally, since $\psi \ge 0$ and $\sum_{s \in \mathbb{Z}} \psi(D^{-s}x) = 1$, we have for all $x$
    $$
        0 \le \sum_{s = s_1}^{s_2} \psi(D^{-s}x) \le 1\,.
    $$
    Let $x' \in I_{s_1}(x)$. By the triangle inequality and \eqref{eq-vol-sp-cube}, it holds that $\rho(x,x') \le 8D^{s_1}$. We have
    $$
        \Bigg|\sum_{s = s_1}^{s_2} \int K_s(x',y) f(y) \, \mathrm{d}\mu(y)\Bigg|
    $$
    $$
        = \Bigg|\int \sum_{s = s_1}^{s_2} \psi(D^{-s}\rho(x',y)) K(x',y) f(y) \, \mathrm{d}\mu(y)\Bigg|
    $$
    \begin{equation}
        \label{eq-sharp-trunc-term}
        \le \Bigg| \int_{8D^{s_1} \le \rho(x',y) \le \frac{1}{4}D^{s_2}} K(x',y) f(y) \, \mathrm{d}\mu(y) \Bigg|
    \end{equation}
    \begin{equation}
        \label{eq-lower-bound-term}
        + \int_{\frac{1}{4}D^{s_1-1} \le \rho(x',y) \le 8D^{s_1}} |K(x', y)| |f(y)| \, \mathrm{d}\mu(y)
    \end{equation}
    \begin{equation}
        \label{eq-upper-bound-term}
        + \int_{\frac{1}{4}D^{s_2} \le \rho(x',y) \le \frac{1}{2}D^{s_2}} |K(x', y)| |f(y)| \, \mathrm{d}\mu(y)\,.
    \end{equation}
    The first term \eqref{eq-sharp-trunc-term} is at most $T_* f(x)$.

    The other two terms will be estimated by the finitary maximal function from \Cref{Hardy-Littlewood}.
    For the second term \eqref{eq-lower-bound-term} we use \eqref{eqkernel-size} which implies that for all $y$ with $\rho(x', y) \ge \frac{1}{4}D^{s_1 - 1}$, we have
    $$
        |K(x', y)| \le \frac{2^{a^3}}{\mu(B(x', \frac{1}{4}D^{s_1 - 1}))}\,.
    $$
    Using $D=2^{100a^2}$
    and the doubling property \eqref{doublingx} $6 +100a^2$ times estimates
    the last display by
    \begin{equation}
    \label{pf-nontangential-operator-bound-imeq}
        \le \frac{2^{6a+101a^3}}{\mu(B(x', 16D^{s_1}))}\, .
    \end{equation}
    By the triangle inequality and \eqref{eq-vol-sp-cube}, we have
    $$
        B(x', 8D^{s_1}) \subset B(c(I_{s_1}(x)), 16D^{s(I_{s_1}(x))})\,.
    $$
    Combining this with \eqref{pf-nontangential-operator-bound-imeq}, we conclude that \eqref{eq-lower-bound-term} is at most
    $$
        2^{6a + 101a^3} M_{\mathcal{B},1} f(x)\,.
    $$

    For \eqref{eq-upper-bound-term} we argue similarly. We have for all $y$ with $\rho(x', y) \ge \frac{1}{4}D^{s_2}$
    $$
        |K(x', y)| \le \frac{2^{a^3}}{\mu(B(x', \frac{1}{4}D^{s_2}))}\,.
    $$
    Using the doubling property \eqref{doublingx} $6$ times estimates
    the last display by
    \begin{equation}
        \le \frac{2^{6a + a^3}}{\mu(B(x', 16 D^{s_2}))}\, .
    \end{equation}
    Note that by \eqref{dyadicproperty} we have $I_{s_1}(x) \subset I_{s_2}(x)$, in particular $x' \in I_{s_2}(x)$.
    By the triangle inequality and \eqref{eq-vol-sp-cube}, we have
    $$
        B(x', 8D^{s_2}) \subset B(c(I_{s_2}(x)), 16D^{s(I_{s_2}(x))})\,.
    $$
    Combining this, \eqref{eq-upper-bound-term} is at most
    $$
        2^{6a+a^3} M_{\mathcal{B},1} f(x)\,.
    $$

    Using $a \ge 4$, taking a supremum over all $x' \in I_{s_1}(x)$ and then a supremum over all $-S \le s_1 < s_2 \le S$, we obtain
    $$
        T_{\mathcal{N}} f(x) \le T_*f(x) + 2^{102a^3} M_{\mathcal{B},1} f(x)\,.
    $$
    The lemma now follows from assumption \eqref{nontanbound}, \Cref{Hardy-Littlewood}and $a \ge 4$.
\end{proof}

We need the following lemma to prepare the $L^2$-estimate for the auxiliary operators $S_{1, \fu}$.

\begin{lemma}[boundary overlap]
    \label{boundary-overlap}
    For every cube $I \in \mathcal{D}$, there exist at most $2^{8a}$ cubes $J \in \mathcal{D}$ with $s(J) = s(I)$ and $B(c(I), 16D^{s(I)}) \cap B(c(J), 16 D^{s(J)}) \ne \emptyset$.
\end{lemma}

\begin{proof}
    Suppose that $B(c(I), 16 D^{s(I)}) \cap B(c(J), 16 D^{s(J)}) \ne \emptyset$ and $s(I) = s(J)$. Then $B(c(I), 32 D^{s(I)}) \subset B(c(J), 64 D^{s(J)})$. Hence by the doubling property \eqref{doublingx}
    $$
        2^{8a}\mu(B(c(J), \frac{1}{4}D^{s(J)})) \ge \mu(B(c(I), 32 D^{s(I)}))\,,
    $$
    and by the triangle inequality, the ball $B(c(J), \frac{1}{4}D^{s(J)})$ is contained in $B(c(I), 32 D^{s(I)})$.

    If $\mathcal{C}$ is any finite collection of cubes $J \in \mathcal{D}$ satisfying $s(J) = s(I)$ and
    \begin{equation*}
        B(c(I), 16 D^{s(I)}) \cap B(c(J), 16 D^{s(J)}) \ne\emptyset\ ,
    \end{equation*} then it follows from \eqref{eq-vol-sp-cube} and pairwise disjointedness of cubes of the same scale \eqref{dyadicproperty} that the balls $B(c(J), \frac{1}{4} D^{s(J)})$ are pairwise disjoint. Hence
    \begin{align*}
        \mu(B(c(I), 32 D^{s(I)})) &\ge \sum_{J \in \mathcal{C}} \mu(B(c(J), \frac{1}{4}D^{s(J)}))\\
        &\ge |\mathcal{C}| 2^{-8a} \mu(B(c(I), 32 D^{s(I)}))\,.
    \end{align*}
    Since $\mu$ is doubling and $\mu \ne 0$, we have $\mu(B(c(I), 32D^{s(I)})) > 0$. The lemma follows after dividing by $2^{-8a}\mu(B(c(I), 32D^{s(I)}))$.
\end{proof}

Now we can bound the operators $S_{1, \fu}$.

\begin{proof}[Proof of \Cref{boundary-operator-bound}]
    \proves{boundary-operator-bound}
    Note that by definition, $S_{1,\fu}f$ is a finite sum of indicator functions of cubes $I \in \mathcal{D}$ for each locally integrable $f$, and hence is bounded, has bounded support and is integrable. Let $g$ be another function with the same three properties. Then $\bar g S_{1,\fu}f$ is integrable, and we have
    $$
        \Bigg|\int \bar g(y) S_{1,\fu}f(y) \, \mathrm{d}\mu(y)\Bigg|
    $$
    \begin{multline*}
        = \Bigg|\sum_{I\in\mathcal{D}} \frac{1}{\mu(B(c(I), 16 D^{s(I)}))} \int_I \bar g(y) \, \mathrm{d}\mu(y)\\
        \times \sum_{J\in \mathcal{J}\,:\,J\subseteq B(c(I), 16 D^{s(I)})} D^{(s(J)-s(I))/a}\int_J |f(y)| \,\mathrm{d}\mu(y)\Bigg|
    \end{multline*}
    \begin{multline*}
        \le \sum_{I\in\mathcal{D}} \frac{1}{\mu(B(c(I), 16D^{s(I)}))} \int_{B(c(I), 16D^{s(I)})} | g(y)| \, \mathrm{d}\mu(y)\\ \times \sum_{J\in \mathcal{J}\,:\,J\subseteq B(c(I), 16 D^{s(I)})} D^{(s(J)-s(I))/a}\int_J |f(y)| \,\mathrm{d}\mu(y)\,.
    \end{multline*}
    Changing the order of summation and using $J \subset B(c(I), 16 D^{s(I)})$ to bound the first average integral by $M_{\mathcal{B},1}|g|(y)$ for any $y \in J$, we obtain
    \begin{align}
    \label{eq-boundary-operator-bound-1}
        \le \sum_{J\in\mathcal{J}}\int_J|f(y)| M_{\mathcal{B},1}|g|(y) \, \mathrm{d}\mu(y) \sum_{I \in \mathcal{D} \, : \, J\subset B(c(I),16 D^{s(I)})} D^{(s(J)-s(I))/a}.
    \end{align}
    By \eqref{eq-vol-sp-cube} and \eqref{defineD} the condition $J \subset B(c(I), 16 D^{s(I)})$ implies $s(I) \ge s(J)$. By \Cref{boundary-overlap}, there are at most $2^{8a}$ cubes $I$ at each scale with $J \subset B(c(I), D^{s(I)})$.
    By convexity of $t \mapsto D^t$ and since $D \ge 2$, we have for all $-1 \le t \le 0$
    $$
        D^t \le 1 + t\left(1 - \frac{1}{D}\right) \le 1 + \frac{1}{2}t\,,
    $$
    so $(1 - D^{-1/a})^{-1} \le 2a \le 2^a$.
    Using this estimate for the sum of the geometric series,
    we conclude that \eqref{eq-boundary-operator-bound-1} is at most
    $$
        2^{9a} \sum_{J\in\mathcal{J}}\int_J|f(y)| M_{\mathcal{B},1}|g|(y) \, \mathrm{d}\mu(y)\,.
    $$
    The collection $\mathcal{J}$ is a partition of $X$, so this equals
    $$
        2^{9a} \int_X|f(y)| M_{\mathcal{B},1}|g|(y) \, \mathrm{d}\mu(y)\,.
    $$
    Using Cauchy-Schwarz and \Cref{Hardy-Littlewood}we conclude
    $$
        \left|\int \bar g S_{1,\fu}f \, \mathrm{d}\mu \right| \le 2^{11a+1} \|g\|_2\|f\|_2\,.
    $$
    The lemma now follows by choosing $g = S_{1,\fu}f$ and dividing on both sides by the finite $\|S_{1,\fu}f\|_2$.
\end{proof}

\section{The quantitative \texorpdfstring{$L^2$}{L2} tree estimate}

The main result of this subsection is the following quantitative bound for operators associated to trees, with decay in the densities $\dens_1$ and $\dens_2$.

\begin{lemma}[densities tree bound]
    \label{densities-tree-bound}
    \uses{tree-projection-estimate,local-dens1-tree-bound,local-dens2-tree-bound}
    Let $\fu \in \fU$. Then for all $f,g$ bounded with bounded support
    \begin{equation}
        \label{eq-cor-tree-est}
        \left|\int_X \bar g \sum_{\fp \in \fT(\fu)} T_{\fp }f \, \mathrm{d}\mu \right| \le 2^{155a^3} \dens_1(\fT(\fu))^{1/2} \|f\|_2\|g\|_2\,.
    \end{equation}
    If $|f| \le \mathbf{1}_F$, then we have
    \begin{equation}
        \label{eq-cor-tree-est-F}
        \left| \int_X \bar g \sum_{\fp \in \fT(\fu)} T_{\fp }f\, \mathrm{d}\mu \right| \le 2^{256a^3} \dens_1(\fT(\fu))^{1/2} \dens_2(\fT(\fu))^{1/2} \|f\|_2\|g\|_2\,.
    \end{equation}
\end{lemma}

Below, we deduce this lemma from \Cref{tree-projection-estimate} and the following two estimates controlling the size of support of the operator and its adjoint.

\begin{lemma}[local dens1 tree bound]
    \label{local-dens1-tree-bound}
    \uses{monotone-cube-metrics}
    Let $\fu \in \fU$ and $L \in \mathcal{L}(\fT(\fu))$. Then
    \begin{equation}
    \label{eq-1density-estimate-tree}
        \mu(L \cap \bigcup_{\fp \in \fT(\fu)} E(\fp)) \le 2^{101a^3} \dens_1(\fT(\fu)) \mu(L)\,.
    \end{equation}
\end{lemma}

\begin{lemma}[local dens2 tree bound]
    \label{local-dens2-tree-bound}
    Let $J \in \mathcal{J}(\fT(\fu))$ be such that there exist $\fq \in \fT(\fu)$ with $J \cap \scI(\fq) \ne \emptyset$. Then
    $$
        \mu(F \cap J) \le 2^{200a^3 + 19} \dens_2(\fT(\fu))\,.
    $$
\end{lemma}

\begin{proof}[Proof of \Cref{densities-tree-bound}]
    \proves{densities-tree-bound}
    Denote
    $$
        \mathcal{E}(\fu) = \bigcup_{\fp \in \fT(\fu)} E(\fp)\,.
    $$
    Then we have
    $$
        \left| \int_X \bar g \sum_{\fp \in \fT(\fu)} T_{\fp} f \, \mathrm{d}\mu \right| = \left| \int_X \overline{ g\mathbf{1}_{\mathcal{E}(\fu)}} \sum_{\fp \in \fT(\fu)} T_{\fp} f \, \mathrm{d}\mu \right|\,.
    $$
    By \Cref{tree-projection-estimate}, this is bounded by
    \begin{equation}
        \label{eq-both-factors-tree}
        \le 2^{104a^3}\|P_{\mathcal{J}(\fT(\fu))}|f|\|_2 \|P_{\mathcal{L}(\fT(\fu))} |\mathbf{1}_{\mathcal{E}(\fu)}g|\|_2\,.
    \end{equation}
    We bound the two factors separately.
    We have
    $$
        \|P_{\mathcal{L}(\fT(\fu))} |\mathbf{1}_{\mathcal{E}(\fu)}g|\|_2 = \left( \sum_{L \in \mathcal{L}(\fT(\fu))} \frac{1}{\mu(L)} \left(\int_{L \cap \mathcal{E}(\fu)} |g(y)| \, \mathrm{d}\mu(y)\right)^2 \right)^{1/2}\,.
    $$
    By Cauchy-Schwarz and \Cref{local-dens1-tree-bound} this is at most
    $$
        \le \left( \sum_{L \in \mathcal{L}(\fT(\fu))} 2^{101a^3} \dens_1(\fT(\fu)) \int_{L \cap \mathcal{E}(\fu)} |g(y)|^2 \, \mathrm{d}\mu(y) \right)^{1/2}\,.
    $$
    Since cubes $L \in \mathcal{L}(\fT(\fu))$ are pairwise disjoint by \Cref{dyadic-partitions}, this is
    \begin{equation}
        \label{eq-factor-L-tree}
         \le 2^{51 a^3} \dens_1(\fT(\fu))^{1/2} \|g\|_2\,.
    \end{equation}
    Similarly, we have
    \begin{equation}
        \label{eq-cor-tree-proof}
        \|P_{\mathcal{J}(\fT(\fu))}|f|\|_2 = \left( \sum_{J \in \mathcal{J}(\fT(\fu))} \frac{1}{\mu(J)} \left(\int_J |f(y)| \, \mathrm{d}\mu(y)\right)^2 \right)^{1/2}\,.
    \end{equation}
    By Cauchy-Schwarz, this is
    $$
        \le \left( \sum_{J \in \mathcal{J}(\fT(\fu))} \int_J |f(y)|^2 \, \mathrm{d}\mu(y) \right)^{1/2}\,.
    $$
    Since cubes in $\mathcal{J}(\fT(\fu))$ are pairwise disjoint by \Cref{dyadic-partitions}, this at most
    \begin{equation}
        \label{eq-factor-J-tree}
        \|f\|_2\,.
    \end{equation}
    Combining \eqref{eq-both-factors-tree}, \eqref{eq-factor-L-tree} and \eqref{eq-factor-J-tree} and using $a \ge 4$ gives \eqref{eq-cor-tree-est}.

    If $f \le \mathbf{1}_F$ then $f = f\mathbf{1}_F$, so
    $$
        \left( \sum_{J \in \mathcal{J}(\fT(\fu))} \int_J |f(y)|^2 \, \mathrm{d}\mu(y) \right)^{1/2} = \left( \sum_{J \in \mathcal{J}(\fT(\fu))} \int_{J \cap F} |f(y)|^2 \, \mathrm{d}\mu(y) \right)^{1/2}\,.
    $$
    We estimate as before, using now \Cref{local-dens2-tree-bound} and Cauchy-Schwarz, and obtain that this is
    $$
        \le 2^{100a^3 + 10} \dens_2(\fT(\fu))^{1/2} \|f\|_2\,.
    $$
    Combining this with \eqref{eq-both-factors-tree}, \eqref{eq-factor-L-tree} and $a \ge 4$ gives \eqref{eq-cor-tree-est-F}.
\end{proof}

Now we prove the two auxiliary estimates.

\begin{proof}[Proof of \Cref{local-dens1-tree-bound}]
    \proves{local-dens1-tree-bound}
    If the set on the right hand side is empty, then \eqref{eq-1density-estimate-tree} holds. If not, then there exists $\fp \in \fT(\fu)$ with $L \cap \scI(\fp) \ne \emptyset$.

    Suppose first that there exists such $\fp$ with $\ps(\fp) \le s(L)$. Then by \eqref{dyadicproperty} $\scI(\fp) \subset L$, which gives by the definition of $\mathcal{L}(\fT(\fu))$ that $s(L) = -S$ and hence $L = \scI(\fp)$. Let $\fq \in \fT(\fu)$ with $E(\fq) \cap L \ne \emptyset$. Since $s(L) = -S \le \ps(\fq)$ it follows from \eqref{dyadicproperty} that $\scI(\fp) = L \subset \scI(\fq)$. We have then by \Cref{monotone-cube-metrics}
    \begin{align*}
        d_{\fp}(\fcc(\fp), \fcc(\fq)) &\le d_{\fp}(\fcc(\fp), \fcc(\fu)) + d_{\fp}(\fcc(\fq), \fcc(\fu))\\
        &\le d_{\fp}(\fcc(\fp), \fcc(\fu)) + d_{\fq}(\fcc(\fq), \fcc(\fu))\,.
    \end{align*}
    Using that $\fp, \fq \in \fT(\fu)$ and \eqref{forest1}, this is at most $8$. Using again the triangle inequality and \Cref{monotone-cube-metrics}, we obtain that for each $q \in B_{\fq}(\fcc(\fq), 1)$
    $$
        d_{\fp}(\fcc(\fp), q) \le d_{\fp}(\fcc(\fp), \fcc(\fq)) + d_{\fq}(\fcc(\fq), q) \le 9\,.
    $$
    Thus $L \cap E(\fq) \subset E_2(9, \fp)$. We obtain
    $$
        \mu(L \cap \bigcup_{\fq \in \fT(\fu)} E(\fq)) \le \mu(E_2(9, \fp))\,.
    $$
    By the definition of $\dens_1$, this is bounded by
    $$
        9^a \dens_1(\fT(\fu)) \mu(\scI(\fp)) =9^a \dens_1(\fT(\fu)) \mu(L)\,.
    $$
    Since $a \ge 4$, \eqref{eq-1density-estimate-tree} follows in this case.

    Now suppose that for each $\fp \in \fT(\fu)$ with $L \cap E(\fp) \ne \emptyset$, we have $\ps(\fp) > s(L)$. Since there exists at least one such $\fp$, there exists in particular at least one cube $L'' \in \mathcal{D}$ with $L \subset L''$ and $s(L'') > s(L)$. By \eqref{coverdyadic}, there exists $L' \in \mathcal{D}$ with $L \subset L'$ and $s(L') = s(L) + 1$. By the definition of $\mathcal{L}(\fT(\fu))$ there exists a tile $\fp'' \in \fT(\fu)$ with $\scI(\fp'') \subset L'$. Let $\fp'$ be the unique tile such that $\scI(\fp') = L'$ and such that $\Omega(\fu) \cap \Omega(\fp') \ne \emptyset$. Since by \eqref{forest1} $\ps(\fp') = s(L') \le \ps(\fp) < \ps(\fu)$, we have by \eqref{dyadicproperty} and \eqref{eq-freq-dyadic} that $\Omega(\fu) \subset \Omega(\fp')$. Let $\fq \in \fT(\fu)$ with $L \cap E(\fq) \ne \emptyset$. As shown above, this implies $\ps(\fq) \ge s(L')$, so by \eqref{dyadicproperty} $L' \subset \scI(\fq)$. If $q \in B_{\fq}(\fcc(\fq), 1)$, then by a similar calculation as above, using the triangle inequality, \Cref{monotone-cube-metrics} and \eqref{forest1}, we obtain
    $$
        d_{\fp'}(\fcc(\fp'), q) \le d_{\fp'}(\fcc(\fp'), \fcc(\fq)) + d_{\fq}(\fcc(\fq), q) \le 6\,.
    $$
    Thus $L \cap E(\fq) \subset E_2(6, \fp')$. Since $\scI(\fp'') \subset \scI(\fp') \subset \scI(\fp)$ and $\fp'', \fp \in \fT(\fu)$, we have $\fp' \in \fP(\fT(\fu))$. We deduce using the definition \eqref{definedens1} of $\dens_1$
    $$
        \mu(L \cap \bigcup_{\fq \in \fT(\fu)} E(\fq)) \le \mu(E_2(6, \fq')) \le 6^a \dens_1(\fT(\fu)) \mu(L')\,.
    $$
    Using the doubling property \eqref{doublingx}, \eqref{eq-vol-sp-cube}, and $a \ge 4$ this is estimated by
    $$
        6^a 2^{100a^3 + 5}\dens_1(\fT(\fu)) \mu(L) \le 2^{101 a^3} \dens_1(\fT(\fu))\mu(L)\,.
    $$
    This completes the proof.
\end{proof}

\begin{proof}[Proof of \Cref{local-dens2-tree-bound}]
    \proves{local-dens2-tree-bound}
    Suppose first that there exists a tile $\fp \in \fT(\fu)$ with $\scI(\fp) \subset B(c(J), 100 D^{s(J) + 1})$. By the definition of $\mathcal{J}(\fT(\fu))$, this implies that $s(J) = -S$, and in particular $\ps(\fp) \ge s(J)$. Using the triangle inequality and \eqref{eq-vol-sp-cube} it follows that $J \subset B(\pc(\fp), 200 D^{\ps(\fp) + 1})$. From the doubling property \eqref{doublingx}, $D=2^{100a^2}$ and \eqref{eq-vol-sp-cube}, we obtain
    $$
        \mu(\scI(\fp)) \le 2^{100a^3 + 9} \mu(J)
    $$
    and hence
    $$
        \mu( B(\pc(\fp), 200 D^{\ps(\fp) + 1})) \le 2^{200a^3 +19} \mu(J)\,.
    $$
    With the definition \eqref{definedens2} of $\dens_2$ it follows that
    $$
        \mu(J \cap F) \le \mu( B(\pc(\fp), 200 D^{\ps(\fp) + 1}) \cap F)
    $$
    $$
        \le \dens_2(\fT(\fu)) \mu( B(\pc(\fp), 200 D^{\ps(\fp) + 1})) \le 2^{200a^3 +19} \dens_2(\fT(\fu))\mu(J)\,,
    $$
    completing the proof in this case.

    Now suppose that there does not exist a tile $\fp \in \fT(\fu)$ with $\scI(\fp) \subset B(c(J), 100 D^{s(J) + 1})$. If we had $\ps(\fq) \le s(J)$, then by \eqref{dyadicproperty} and \eqref{eq-vol-sp-cube} $\scI(\fq) \subset J \subset B(c(J), 100 D^{s(J) + 1})$, contradicting our assumption. Thus $\ps(\fq) > s(J)$. Then, by \eqref{coverdyadic} and \eqref{dyadicproperty}, there exists some cube $J' \in \mathcal{D}$ with $s(J') = s(J) + 1$ and $J \subset J'$. By definition of $\mathcal{J}(\fT(\fu))$ there exists some $\fp \in \fT(\fu)$ such that $\scI(\fp) \subset B(c(J'), 100 D^{s(J') + 1})$. From the doubling property \eqref{doublingx}, $D=2^{100a^2}$ and \eqref{eq-vol-sp-cube}, we obtain
    \begin{equation}
        \label{eq-measure-comparison-1}
        \mu(B(\pc(\fp), 4D^{\ps(\fp)})) \le 2^{4a} \mu(\scI(\fp)) \le 2^{200a^3 + 14} \mu(J)\,.
    \end{equation}
    If $J \subset B(\pc(\fp), 4 D^{\ps(\fp)})$, then we bound
    $$
        \mu(J \cap F) \le \mu(B(\pc(\fp), 4D^{\ps(\fp)}) \cap F)
    $$
    and use the definition \eqref{definedens2}
    $$
        \le \dens_2(\fT(\fu)) \mu(B(\pc(\fp), 4D^{\ps(\fp)})) \le 2^{200a^3 + 14} \mu(J)\,.
    $$
    From now on we assume $J \not \subset B(\pc(\fp), 4 D^{\ps(\fp)})$.
    Since
    \begin{equation*}
        \pc(\fp) \in \scI(\fp) \subset B(c(J'), 100 D^{s(J') + 1})\, ,
    \end{equation*}
    we have by \eqref{eq-vol-sp-cube} and the triangle inequality
    $$
        J \subset J' \subset B(c(J'), 4D^{s(J')}) \subset B(\pc(\fp), 104 D^{s(J') + 1})\,.
    $$
    In particular this implies $104 D^{s(J') + 1} > 4D^{\ps(\fp)}$. By the triangle inequality we also have
    $$
        B(\pc(\fp), 104 D^{s(J') + 1}) \subset B(c(J), 204 D^{s(J') + 1})\,,
    $$
    so from the doubling property \eqref{doublingx}
    $$
        \mu( B(\pc(\fp), 104 D^{s(J') + 1})) \le 2^{200a^3 + 10} \mu(J)\,.
    $$
    From here one completes the proof as in the other cases.
\end{proof}

\section{Almost orthogonality of separated trees}

The main result of this subsection is the almost orthogonality estimate for operators associated to distinct trees in a forest in \Cref{correlation-separated-trees} below. We will deduce it from Lemmas \ref{correlation-distant-tree-parts} and \ref{correlation-near-tree-parts}, which are proven in Subsections \ref{subsec-big-tiles} and \ref{subsec-rest-tiles}, respectively. Before stating it, we introduce some relevant notation.

The adjoint of the operator $T_{\fp}$ defined in \eqref{definetp} is given by
\begin{equation}
    \label{definetp*}
    T_{\fp}^* g(x) = \int_{E(\fp)} \overline{K_{\ps(\fp)}(y,x)} e(-\tQ(y)(x)+ \tQ(y)(y)) g(y) \, \mathrm{d}\mu(y)\,.
\end{equation}

\begin{lemma}[adjoint tile support]
    \label{adjoint-tile-support}
    For each $\fp \in \fP$, we have
    $$
        T_{\fp}^* g = \mathbf{1}_{B(\pc(\fp), 5D^{\ps(\fp)})} T_{\fp}^* \mathbf{1}_{\scI(\fp)} g\,.
    $$
    For each $\fu \in \fU$ and each $\fp \in \fT(\fu)$, we have
    $$
        T_{\fp}^* g = \mathbf{1}_{\scI(\fu)} T_{\fp}^* \mathbf{1}_{\scI(\fu)} g\,.
    $$
\end{lemma}

\begin{proof}
    By \eqref{forest1}, $E(\fp) \subset \scI(\fp) \subset \scI(\fu)$. Thus by \eqref{definetp*}
    $$
         T_{\fp}^* g(x) = T_{\fp}^* (\mathbf{1}_{\scI(\fp)} g)(x)
    $$
    $$
        = \int_{E(\fp)} \overline{K_{\ps(\fp)}(y,x)} e(-\tQ(y)(x) + \tQ(y)(y)) \mathbf{1}_{\scI(\fp)}(y) g(y) \, \mathrm{d}\mu(y)\,.
    $$
    If this integral is not $0$, then there exists $y \in \scI(\fp)$ such that $K_{\ps(\fp)}(y,x) \ne 0$. By \eqref{supp-Ks}, \eqref{eq-vol-sp-cube} and the triangle inequality, it follows that
    \begin{equation*}
        x \in B(\pc(\fp), 5 D^{\ps(\fp)})\, .
    \end{equation*}
    Thus
    $$
        T_{\fp}^* g(x) = \mathbf{1}_{B(\pc(\fp), 5D^{\ps(\fp)})}(x) T_{\fp}^* (\mathbf{1}_{\scI(\fp)} g)(x)\,.
    $$
    The second claimed equation follows now since $\scI(\fp) \subset \scI(\fu)$ and by \eqref{forest6} $B(\pc(\fp), 5D^{\ps(\fp)}) \subset \scI(\fu)$.
\end{proof}

\begin{lemma}[adjoint tree estimate]
    \label{adjoint-tree-estimate}
    \uses{densities-tree-bound}
    For all bounded $g$ with bounded support, we have that
    $$
        \left\| \sum_{\fp \in \fT(\fu)} T_{\fp}^* g\right\|_2 \le 2^{155a^3} \dens_1(\fT(\fu))^{1/2} \|g\|_2\,.
    $$
\end{lemma}

\begin{proof}
    By Cauchy-Schwarz and \Cref{densities-tree-bound}, we have for all bounded $f,g$ with bounded support that
    $$
        \left| \int_X \overline{\sum_{\fp\in \fT(\fu)} T_{\fp}^* g} f \,\mathrm{d}\mu \right| = \left| \int_X g \sum_{\fp \in \fT(\fu)} T_{\fp} f \,\mathrm{d}\mu \right|
    $$
    \begin{equation}
        \label{eq-adjoint-bound}
        \le 2^{155a^3} \dens_1(\fT(\fu))^{1/2} \|g\|_2 \|f\|_2\,.
    \end{equation}
    Let $f = \sum_{\fp \in \fT(\fu)} T_{\fp}^* g$. If $g$ is bounded and has bounded support, then the same is true for $f$. In particular $\|f\|_2 < \infty$. Dividing \eqref{eq-adjoint-bound} by $\|f\|_2$ completes the proof.
\end{proof}

We define
$$
    S_{2,\fu}g := \left|\sum_{\fp \in \fT(\fu)} T_{\fp}^*g \right| + M_{\mathcal{B},1}g + |g|\,.
$$
\begin{lemma}[adjoint tree control]
    \label{adjoint-tree-control}
    \uses{adjoint-tree-estimate}
    We have for all bounded $g$ with bounded support
    $$
        \|S_{2, \fu} g\|_2 \le 2^{156a^3} \|g\|_2\,.
    $$
\end{lemma}

\begin{proof}
    This follows immediately from Minkowski's inequality, \Cref{Hardy-Littlewood}and \Cref{adjoint-tree-estimate}, using that $a \ge 4$.
\end{proof}


Now we are ready to state the main result of this subsection.

\begin{lemma}[correlation separated trees]
    \label{correlation-separated-trees}
    \uses{correlation-distant-tree-parts,correlation-near-tree-parts}
    For any $\fu_1 \ne \fu_2 \in \fU$ and all bounded $g_1, g_2$ with bounded support, we have
    \begin{equation}
        \label{eq-lhs-sep-tree}
        \left| \int_X \sum_{\fp_1 \in \fT(\fu_1)} \sum_{\fp_2 \in \fT(\fu_2)} T^*_{\fp_1}g_1 \overline{T^*_{\fp_2}g_2 }\,\mathrm{d}\mu \right|
    \end{equation}
    \begin{equation}
        \label{eq-rhs-sep-tree}
        \le 2^{550a^3-3n} \prod_{j =1}^2 \| S_{2, \fu_j} g_j\|_{L^2(\scI(\fu_1) \cap \scI(\fu_2))}\,.
    \end{equation}
\end{lemma}

\begin{proof}[Proof of \Cref{correlation-separated-trees}]
    \proves{correlation-separated-trees}
    By \Cref{adjoint-tile-support} and \eqref{dyadicproperty}, the left hand side \eqref{eq-lhs-sep-tree} is $0$ unless $\scI(\fu_1) \subset \scI(\fu_2)$ or $\scI(\fu_2) \subset \scI(\fu_1)$. Without loss of generality we assume that $\scI(\fu_1) \subset \scI(\fu_2)$.

    Define
    \begin{equation}
        \label{def-Tree-S-set}
         \mathfrak{S} := \{\fp \in \fT(\fu_1) \cup \fT(\fu_2) \ : \ d_{\fp}(\fcc(\fu_1), \fcc(\fu_2)) \ge 2^{Zn/2}\,\}.
    \end{equation}
    \Cref{correlation-separated-trees} follows by combining the definition \eqref{defineZ} of $Z$ with the following two lemmas.
    \begin{lemma}[correlation distant tree parts]
        \label{correlation-distant-tree-parts}
        \uses{Holder-van-der-Corput,Lipschitz-partition-unity,Holder-correlation-tree,lower-oscillation-bound}
        We have for all $\fu_1 \ne \fu_2 \in \fU$ with $\scI(\fu_1) \subset \scI(\fu_2)$ and all bounded $g_1, g_2$ with bounded support
        \begin{equation}
            \label{eq-lhs-big-sep-tree}
            \left| \int_X \sum_{\fp_1 \in \fT(\fu_1)} \sum_{\fp_2 \in \fT(\fu_2) \cap \mathfrak{S}} T^*_{\fp_1}g_1 \overline{T^*_{\fp_2}g_2 }\,\mathrm{d}\mu \right|
        \end{equation}
        \begin{equation}
            \label{eq-rhs-big-sep-tree}
            \le 2^{541a^3} 2^{-Zn/(4a^2 + 2a^3)} \prod_{j =1}^2 \| S_{2, \fu_j} g_j\|_{L^2(\scI(\fu_1))}\,.
        \end{equation}
    \end{lemma}
    \begin{lemma}[correlation near tree parts]
        \label{correlation-near-tree-parts}
        \uses{tree-projection-estimate,dyadic-partition-2,bound-for-tree-projection}
        We have for all $\fu_1 \ne \fu_2 \in \fU$ with $\scI(\fu_1) \subset \scI(\fu_2)$ and all bounded $g_1, g_2$ with bounded support
        \begin{equation}
            \label{eq-lhs-small-sep-tree}
            \left| \int_X \sum_{\fp_1 \in \fT(\fu_1)} \sum_{\fp_2 \in \fT(\fu_2) \setminus \mathfrak{S}} T^*_{\fp_1}g_1 \overline{T^*_{\fp_2}g_2 }\,\mathrm{d}\mu \right|
        \end{equation}
        \begin{equation}
            \label{eq-rhs-small-sep-tree}
            \le 2^{222a^3} 2^{-Zn 2^{-10a}} \prod_{j =1}^2 \| S_{2, \fu_j} g_j\|_{L^2(\scI(\fu_1)}\,.
        \end{equation}
    \end{lemma}
\end{proof}

In the proofs of both lemmas, we will need the following observation.

\begin{lemma}[overlap implies distance]
    \label{overlap-implies-distance}
    Let $\fu_1 \ne \fu_2 \in \fU$ with $\scI(\fu_1) \subset \scI(\fu_2)$. If $\fp \in \fT(\fu_1) \cup \fT(\fu_2)$ with $\scI(\fp) \cap \scI(\fu_1) \ne \emptyset$, then $\fp \in \mathfrak{S}$. In particular, we have $\fT(\fu_1) \subset \mathfrak{S}$.
\end{lemma}

\begin{proof}
    Suppose first that $\fp \in \fT(\fu_1)$. Then $\scI(\fp) \subset \scI(\fu_1) \subset \scI(\fu_2)$, by \eqref{forest1}. Thus we have by the separation condition \eqref{forest5}, \eqref{eq-freq-comp-ball}, \eqref{forest1} and the triangle inequality
    \begin{align*}
        d_{\fp}(\fcc(\fu_1), \fcc(\fu_2)) &\ge d_{\fp}(\fcc(\fp), \fcc(\fu_2)) - d_{\fp}(\fcc(\fp), \fcc(\fu_1))\\
        &\ge 2^{Z(n+1)} - 4\\
        &\ge 2^{Zn}\,,
    \end{align*}
    using that $Z= 2^{12a}\ge 4$. Hence $\fp \in \mathfrak{S}$.

    Suppose now that $\fp \in \fT(\fu_2)$. If $\scI(\fp) \subset \scI(\fu_1)$, then the same argument as above with $\fu_1$ and $\fu_2$ swapped shows $\fp \in \mathfrak{S}$. If $\scI(\fp) \not \subset \scI(\fu_1)$ then, by \eqref{dyadicproperty}, $\scI(\fu_1) \subset \scI(\fp)$. Pick $\fp' \in \fT(\fu_1)$, we have $\scI(\fp') \subset \scI(\fu_1) \subset \scI(\fp)$. Hence, by \Cref{monotone-cube-metrics} and the first paragraph
    $$
        d_{\fp}(\fcc(\fu_1), \fcc(\fu_2)) \ge d_{\fp'}(\fcc(\fu_1), \fcc(\fu_2)) \ge 2^{Zn}\,,
    $$
    so $\fp \in \mathfrak{S}$.
\end{proof}

To simplify the notation, we will write at various places throughout the proof of Lemmas \ref{correlation-distant-tree-parts} and \ref{correlation-near-tree-parts} for a subset $\fC \subset \fP$
$$
    T_{\fC} f := \sum_{\fp \in \fC} T_{\fp} f\,, \quad\quad T_{\fC}^* g := \sum_{\fp\in\fC} T_{\fp}^* g\,.
$$

\section{Proof of the Tiles with large separation Lemma}
    \label{subsec-big-tiles}

\Cref{correlation-distant-tree-parts} follows from the van der Corput estimate in \Cref{Holder-van-der-Corput}. We apply this proposition in \Cref{subsubsec-van-der-corput}. To prepare this application, we first, in \Cref{subsubsec-pao}, construct a suitable partition of unity, and show then, in \Cref{subsubsec-holder-estimates} the H\"older estimates needed to apply \Cref{Holder-van-der-Corput}.

\subsection{A partition of unity}
\label{subsubsec-pao}
    Define
    $$
        \mathcal{J}' = \{J \in \mathcal{J}(\mathfrak{S}) \ : \ J \subset \scI(\fu_1)\}\,.
    $$

    \begin{lemma}[dyadic partition 1]
        \label{dyadic-partition-1}
        \uses{dyadic-partitions}
        We have that
        $$
            \scI(\fu_1) = \dot{\bigcup_{J \in \mathcal{J}'}} J\,.
        $$
    \end{lemma}

    \begin{proof}
        By \Cref{dyadic-partitions}, it remains only to show that each $J \in \mathcal{J}(\mathfrak{S})$ with $J \cap \scI(\fu_1) \ne \emptyset$ is in $\mathcal{J}'$. But if $J \notin \mathcal{J}'$, then by \eqref{dyadicproperty} $\scI(\fu_1) \subsetneq J$. Pick $\fp \in \fT(\fu_1) \subset \mathfrak{S}$. Then $\scI(\fp) \subsetneq J$. This contradicts the definition of $\mathcal{J}(\mathfrak{S})$.
    \end{proof}

    For cubes $J \in \mathcal{D}$, denote
    \begin{equation}
        \label{def-BJ}
        B(J) := B(c(J), 8D^{s(J)}).
    \end{equation}
    The main result of this subsubsection is the following.

    \begin{lemma}[Lipschitz partition unity]
        \label{Lipschitz-partition-unity}
           \uses{dyadic-partition-1,moderate-scale-change}
        There exists a family of functions $\chi_J$, $J \in \mathcal{J}'$ such that \begin{equation}
            \label{eq-pao-1}
            \mathbf{1}_{\scI(\fu_1)} = \sum_{J \in \mathcal{J}'} \chi_J\,,
        \end{equation}
        and for all $J \in \mathcal{J}'$ and all $y,y' \in \scI(\fu_1)$
        \begin{equation}
            \label{eq-pao-2}
            0 \leq \chi_J(y) \leq \mathbf{1}_{B(J)}(y)\,,
        \end{equation}
        \begin{equation}
            \label{eq-pao-3}
            |\chi_J(y) - \chi_J(y')| \le 2^{226a^3} \frac{\rho(y,y')}{D^{s(J)}}\,.
        \end{equation}
    \end{lemma}

    In the proof, we will use the following auxiliary lemma.

    \begin{lemma}[moderate scale change]
        \label{moderate-scale-change}

        If $J, J' \in \mathcal{J'}$ with
        $$
            B(J) \cap B(J') \ne \emptyset\,,
        $$
        then $|s(J) - s(J')| \le 1$.
    \end{lemma}

    \begin{proof}[Proof of \Cref{Lipschitz-partition-unity}]
        \proves{Lipschitz-partition-unity}
        For each cube $J \in \mathcal{J}$ let
        $$
            \tilde\chi_J(y) = \max\{0, 8 - D^{-s(J)} \rho(y, c(J))\}\,,
        $$
        and set
        $$
            a(y) = \sum_{J \in \mathcal{J}'} \tilde \chi_J(y)\,.
        $$
        We define
        \[
            \chi_J(y) := \frac{\tilde \chi_J(y)}{a(y)}\,.
        \]
        Then, due to \eqref{forest6} and \eqref{def-BJ}, the properties \eqref{eq-pao-1} and \eqref{eq-pao-2} are clearly true. Estimate \eqref{eq-pao-3} follows from \eqref{eq-pao-2} if $y, y' \notin B(J)$. Thus we can assume that $y \in B(J)$. We have by the triangle inequality
        $$
            |\chi_J(y) - \chi_J(y')| \le \frac{|\tilde \chi_J(y) - \tilde \chi_J(y')|}{a(y)} + \frac{\tilde \chi_J(y')|a(y) - a(y')|}{a(y)a(y')}
        $$
        Since $\tilde \chi_J(z) \ge 4$ for all $z \in B(c(J), 4) \supset J$ and by \Cref{dyadic-partition-1}, we have that $a(z) \ge 4$ for all $z \in \scI(\fu_1)$. So we can estimate the above further by
        $$
            \le 2^{-2}(|\tilde \chi_J(y) - \tilde \chi_J(y')| + \tilde \chi_J(y')|a(y) - a(y')|)\,.
        $$
        If $y' \notin B(\pc(\fp), 8D^{\ps(\fp)})$ then the second summand vanishes. Else, we can estimate the above, using also that $|\tilde \chi_J(y')| \le 8$, by
        $$
            \le 2^{-2} |\tilde \chi_J(y) - \tilde \chi_J(y')| + 2 \sum_{\substack{J' \in \mathcal{J}'\\ B(c(J'), 8D^{s(J')}) \cap B(c(J), 8D^{s(J)}) \ne \emptyset}}|\tilde \chi_{J'}(y) - \tilde \chi_{J'} (y')|\,.
        $$
        By the triangle inequality, we have for all dyadic cubes $I \in \mathcal{J}'$
        $$
            |\tilde \chi_I(y) - \tilde \chi_I(y')| \le \rho(y, y') D^{-s(I)}\,.
        $$
        Using this above, we obtain
        $$
            |\chi_J(y) - \chi_J(y')| \le \rho(y,y') \Big( \frac{1}{4} D^{-s(J)} + 2 \sum_{\substack{J' \in \mathcal{J}'\\ B(J') \cap B(J) \ne \emptyset}} D^{-s(J')}\Big)\,.
        $$
        By \Cref{moderate-scale-change}, this is at most
        $$
             \frac{\rho(y,y')}{D^{s(J)}} \left( \frac{1}{4} + 2D |\{J' \in \mathcal{J}' \ : \ B(J') \cap B(J) \ne \emptyset\}|\right)\,.
        $$
        By \eqref{eq-vol-sp-cube} and \Cref{dyadic-partition-1}, the balls $B(c(J'), \frac{1}{4} D^{s(J')})$ are pairwise disjoint, so by \Cref{moderate-scale-change} the balls $B(c(J'), \frac{1}{4} D^{s(J) - 1})$ are also disjoint. By the triangle inequality and \Cref{moderate-scale-change}, each such ball for $J'$ in the set of the last display is contained in
        $$
            B(c(J), 9 D^{s(J) + 1})\,.
        $$
        By the doubling property \eqref{doublingx}, we further have
        $$
            \mu\Big(B(c(J'), \frac{1}{4}D^{s(J')})\Big) \ge 2^{-200a^3 - 6} \mu(B(c(J), 9 D^{s(J) + 1}))
        $$
        for each such ball.
        Thus
        $$
            |\{J' \in \mathcal{J}' \ : \ B(J') \cap B(J) \ne \emptyset\}| \le 2^{200a^3 + 6}\,.
        $$
        Recalling that $D=2^{100a^2}$, we obtain
        $$\frac{1}{4} + 2D |\{J' \in \mathcal{J}' \ : \ B(J') \cap B(J) \ne \emptyset\}|\leq 2^{200a^3 + 100a^2+ 8}.$$
        Since $a\ge 4$, \eqref{eq-pao-3} follows.
    \end{proof}

    \begin{proof}[Proof of \Cref{moderate-scale-change}]
        \proves{moderate-scale-change}
        Suppose that $s(J') < s(J) - 1$. Then $s(J) > -S$. Thus, by the definition of $\mathcal{J}'$ there exists no $\fp \in \mathfrak{S}$ with
        \begin{equation}
            \label{eq-tile-incl-1}
            \scI(\fp) \subset B(c(J), 100D^{s(J) + 1})\,.
        \end{equation}
        Since $s(J') < s(J)$ and $J', J \subset \scI(\fu_1)$, we have $J' \subsetneq \scI(\fu_1)$.
        By \eqref{coverdyadic}, \eqref{dyadicproperty} there exists a cube $J'' \in \mathcal{D}$ with $J \subset J''$ and $s(J'') = s(J') + 1$. By the definition of $\mathcal{J}'$, there exists a tile $\fp \in \mathfrak{S}$ with
        \begin{equation}
            \label{tile-incl-2}
            \scI(\fp) \subset B(c(J''), 100 D^{s(J')+2})\,.
        \end{equation}
        But by the triangle inequality and \eqref{defineD}, we have
        $$
            B(c(J''), 100 D^{s(J')+2}) \subset B(c(J), 100D^{s(J) + 1})\,,
        $$
        which contradicts \eqref{eq-tile-incl-1} and \eqref{tile-incl-2}.
    \end{proof}


\subsection{H\"older estimates for adjoint tree operators}
\label{subsubsec-holder-estimates}
    Let $g_1, g_2:X \to \mathbb{C}$ be bounded with bounded support.
    Define for $J \in \mathcal{J}'$
    \begin{equation}
        \label{def-hj}
        h_J(y) := \chi_J(y)\cdot(e(\fcc(\fu_1)(y)) T_{\fT(\fu_1)}^* g_1(y)) \cdot \overline{(e(\fcc(\fu_2)(y)) T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2(y))}\,.
    \end{equation}
    The main result of this subsubsection is the following $\tau$-H\"older estimate for $h_J$, where $\tau = 1/a$.

    \begin{lemma}[Holder correlation tree]
        \label{Holder-correlation-tree}
        \uses{global-tree-control-2}
        We have for all $J \in \mathcal{J}'$ that
        \begin{equation}
            \label{hHolder}
            \|h_J\|_{C^{\tau}(B(c(J), 8D^{s(J)}))} \le 2^{535a^3} \prod_{j = 1,2} (\inf_{B(c(J), \frac{1}{8}D^{s(J)})} |T_{\fT(\fu_j)}^* g_j| + \inf_J M_{\mathcal{B}, 1} |g_j|)\,.
        \end{equation}
    \end{lemma}

    We will prove this lemma at the end of this section, after establishing several auxiliary results.

    We begin with the following H\"older continuity estimate for adjoints of operators associated to tiles.
    \begin{lemma}[Holder correlation tile]
        \label{Holder-correlation-tile}
        \uses{adjoint-tile-support}
        Let $\fu \in \fU$ and $\fp \in \fT(\fu)$. Then for all $y, y' \in X$ and all bounded $g$ with bounded support, we have
        $$
            |e(\fcc(\fu)(y)) T_{\fp}^* g(y) - e(\fcc(\fu)(y')) T_{\fp}^* g(y')|
        $$
        \begin{equation}
            \label{T*Holder2}
            \le \frac{2^{151a^3}}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \left(\frac{\rho(y, y')}{D^{\ps(\fp)}}\right)^{1/a} \int_{E(\fp)} |g(x)| \, \mathrm{d}\mu(x)\,.
        \end{equation}
    \end{lemma}

    \begin{proof}
        By \eqref{definetp*}, we have
        $$
            |e(\fcc(\fu)(y)) T_{\fp}^* g(y) - e(\fcc(\fu)(y')) T_{\fp}^* g(y')|
        $$
        \begin{multline*}
            =\bigg| \int_{E(\fp)} e(\tQ(x)(x) - \tQ(x)(y) + \fcc(\fu)(y)) \overline{K_{\ps(\fp)}(x, y)} g(x) \\
            - e(\tQ(x)(x) - \tQ(x)(y') + \fcc(\fu)(y')) \overline{K_{\ps(\fp)}(x, y')} g(x) \, \mathrm{d}\mu(x)\bigg|
        \end{multline*}
        \begin{multline*}
            \leq\int_{E(\fp)} |g(x)| |e(\tQ(x)(y) - \tQ(x)(y') - \fcc(\fu)(y) + \fcc(\fu)(y'))\overline{K_{\ps(\fp)}(x, y)}\\
            - \overline{K_{\ps(\fp)}(x, y')}| \, \mathrm{d}\mu(x)
        \end{multline*}
        \begin{multline}
            \leq\int_{E(\fp)} |g(x)| |e(-\tQ(x)(y) + \tQ(x)(y') + \fcc(\fu)(y) - \fcc(\fu)(y')) - 1| \\
            \times |\overline{K_{\ps(\fp)}(x, y)}|\, \mathrm{d}\mu(x) \label{T*Holder1b}
        \end{multline}
        \begin{equation}
            + \int_{E(\fp)} |g(x)| |\overline{K_{\ps(\fp)}(x, y)} - \overline{K_{\ps(\fp)}(x, y')} |\, \mathrm{d}\mu(x)\,.\label{T*Holder1}
        \end{equation}
        By the oscillation estimate \eqref{osccontrol}, we have
        $$
            |-\tQ(x)(y) + \tQ(x)(y') + \fcc(\fu)(y) - \fcc(\fu)(y')|
        $$
        \begin{equation}
            \label{eq-lem-tile-Holder-comp}
            \le d_{B(y, \rho(y,y'))}(\tQ(x), \fcc(\fu))\,.
        \end{equation}
        Suppose that $y, y' \in B(\pc(\fp), 5D^{\ps(\fp)})$, so that $\rho(y,y') \le 10D^{\ps(\fp)}$. Let $k \in \mathbb{Z}$ be such that $2^{ak}\rho(y,y') \le 10D^{\ps(\fp)}$ but $2^{a(k+1)} \rho(y,y') > 10D^{\ps(\fp)}$. In particular, $k \ge 0$. Then, using \eqref{firstdb}, we can bound \eqref{eq-lem-tile-Holder-comp} from above by
        $$
            2^{-k} d_{B(\pc(\fp), 10 D^{\ps(\fp)})}(\tQ(x), \fcc(\fu)) \le 2^{6a - k} d_{\fp}(\tQ(x), \fcc(\fu))\,.
        $$
        Since $x \in E(\fp)$ we have $\tQ(x) \in \Omega(\fp) \subset B_{\fp}(\fcc(\fp), 1)$, and since $\fp \in \fT(\fu)$ we have $\fcc(\fu) \in B_{\fp}(\fcc(\fp), 4)$, so this is estimated by
        $$
            \le 5 \cdot 2^{6a - k}\,.
        $$
        By definition of $k$, we have
        $$
            k \le \frac{1}{a} \log_2\left(\frac{10 D^{\ps(\fp)}}{\rho(y,y')}\right)\,,
        $$
        which gives
        \begin{equation}
            \label{eq-lem-Tile-holder-im1}
             |-\tQ(x)(y) + \tQ(x)(y') + \fcc(\fu)(y) - \fcc(\fu)(y')| \le 5 \cdot 2^{6a} \left(\frac{\rho(y,y')}{10 D^{\ps(\fp)}}\right)^{1/a}\,.
        \end{equation}
        For all $x \in \scI(\fp)$, we have by \eqref{doublingx} that
        $$
            \mu(B(x, D^{\ps(\fp)})) \ge 2^{-3a} \mu(B(\pc(\fp), 4D^{\ps(\fp)}))\,.
        $$
        Combining the above with \eqref{eq-Ks-size}, \eqref{eq-Ks-smooth} and \eqref{eq-lem-Tile-holder-im1},
        we obtain
        $$
            \eqref{T*Holder1b}+\eqref{T*Holder1} \le \frac{2^{3a}}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \int_{E(\fp)}|g(x)| \, \mathrm{d}\mu(x) \times
        $$
        $$
            (2^{102a^3} \cdot 5 \cdot 2^{6a} \left(\frac{\rho(y,y')}{ D^{\ps(\fp)}}\right)^{1/a} + 2^{150a^3} \left(\frac{\rho(y,y')}{D^{\ps(\fp)}}\right)^{1/a})
        $$
        Since $\rho(y,y') \le 10 D^{\ps(\fp)}$, we conclude
        $$
            \eqref{T*Holder1b}+\eqref{T*Holder1} \le \frac{2^{151a^3}}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \left(\frac{\rho(y,y')}{D^{\ps(\fp)}}\right)^{1/a} \int_{E(\fp)}|g(x)| \, \mathrm{d}\mu(x)\,.
        $$

        Next, if $y,y' \notin B(\pc(\fp), 5D^{\ps(\fp)})$, then $T_{\fp}^*g(y) = T_{\fp}^*g(y') = 0$, by \Cref{adjoint-tile-support}. Then \eqref{T*Holder2} holds.

        Finally, if $y \in B(\pc(\fp), 5D^{\ps(\fp)})$ and $y' \notin B(\pc(\fp), 5D^{\ps(\fp)})$, then
        $$
            |e(\fcc(\fu)(y)) T_{\fp}^* g(y) - e(\fcc(\fu)(y')) T_{\fp}^* g(y')| = |T_{\fp}^* g(y)|
        $$
        $$
            \le \int_{E(\fp)} |K_{\ps(\fp)}(x,y)| |g(x)| \, \mathrm{d}\mu(x)\,.
        $$
        By the same argument used to prove \eqref{eq-Ks-aux}, this is bounded by
        \begin{equation}
            \label{eq-lem-Tile-holder-im2}
            \le 2^{102a^3} \int_{E(\fp)} \frac{1}{\mu(B(x, D^s))} \psi(D^{-s} \rho(x,y)) |g(x)| \, \mathrm{d}\mu(x)\,.
        \end{equation}
        It follows from the definition of $\psi$ that
        $$
            \psi(x) \le \max\{0, (2 - 4x)^{1/a}\}\,.
        $$
        Now for all $x\in E(\fp)$, it follows by the triangle inequality and \eqref{eq-vol-sp-cube} that
        \begin{multline*}
        2 - 4D^{-\ps(\fp)}\rho(x,y)\leq 2 - 4D^{-\ps(\fp)}\rho(y, \pc(\fp)) + 4 D^{-\ps(\fp)}\rho(x, \pc(\fp))\\\leq 18 - 4 D^{-\ps(\fp)} \rho(y, \pc(\fp)) \leq 4 D^{-\ps(\fp)}\rho(y,y') - 2 .
        \end{multline*}
        Combining the above with the previous estimate on $\psi$, we get
        $$
            \psi(D^{-\ps(\fp)}\rho(x,y)) \le 4 (D^{-\ps(\fp)}\rho(y,y'))^{1/a}.
        $$
        Further, we obtain from the doubling property \eqref{doublingx} and \eqref{eq-vol-sp-cube} that
        $$
            \mu(B(x, D^s)) \ge 2^{-2a} \mu(\pc(\fp), 4D^s)\,.
        $$
        Plugging this into \eqref{eq-lem-Tile-holder-im2} and using $a \ge 4$, we get
        $$
            |T_{\fp}^* g(y)| \le \frac{2^{103a^3}}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \left(\frac{\rho(y,y')}{D^{\ps(\fp)}}\right)^{1/a} \int_{E(\fp)} |g(x)| \, \mathrm{d}\mu(y)\,,
        $$
        which completes the proof of the lemma.
    \end{proof}

    Recall that
    \begin{equation*}
        B(J) := B(c(J), 8D^{s(J)}).
    \end{equation*}
    We also denote
    \begin{equation*}
     B^\circ{}(J) := B(c(J), \frac{1}{8}D^{s(J)})\, .
    \end{equation*}


    \begin{lemma}[limited scale impact]
        \label{limited-scale-impact}
        \uses{overlap-implies-distance}
        Let $\fp \in \fT_2 \setminus \mathfrak{S}$, $J \in \mathcal{J}'$ and suppose that
        $$
           B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset\,.
        $$
        Then
        $$
            s(J) \le \ps(\fp) \le s(J) + 10a^2 + 2\,.
        $$
    \end{lemma}

    \begin{proof}
        For the first estimate, assume that $\ps(\fp) < s(J)$, then in particular $\ps(\fp) \le \ps(\fu_1)$. Since $\fp \notin \mathfrak{S}$, we have by \Cref{overlap-implies-distance} that $\scI(\fp) \cap \scI(\fu_1) = \emptyset$.
        Since $B\Big(c(J), \frac{1}{4} D^{s(J)}\Big) \subset \scI(J) \subset \scI(\fu_1)$, this implies
        $$
            \rho(c(J), \pc(\fp)) \ge \frac{1}{4}D^{s(J)}\,.
        $$
        On the other hand
        $$
            \rho(c(J), \pc(\fp)) \le \frac{1}{8} D^{s(J)} + 8 D^{\ps(\fp)}\,,
        $$
        by our assumption. Thus $D^{\ps(\fp)} \ge 64 D^{s(J)}$, which contradicts \eqref{defineD} and $a \ge 4$.

        For the second estimate, assume that $\ps(\fp) > s(J) +10a^2 + 2$. Since $J \in \mathcal{J}'$, we have $J \subsetneq \scI(\fu_1)$. Thus there exists $J' \in \mathcal{D}$ with $J \subset J'$ and $s(J') = s(J) + 1$, by \eqref{coverdyadic} and \eqref{dyadicproperty}. By definition of $\mathcal{J}'$, there exists some $\fp' \in \mathfrak{S}$ such that $\scI(\fp') \subset B(c(J'), 100 D^{s(J) + 2})$. On the other hand, since $B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset$, by the triangle inequality it holds that
        $$
            B(c(J'), 100 D^{s(J) + 10a^2 + 2}) \subset B(\pc(\fp), 10 D^{\ps(\fp)})\,.
        $$
        Using the definition of $\mathfrak{S}$, we have
        $$
            2^{Zn/2} \le d_{\fp'}(\fcc(\fu_1), \fcc(\fu_2)) \le d_{B(c(J'), 100 D^{s(J) + 2})}(\fcc(\fu_1), \fcc(\fu_2))\,.
        $$
        By \eqref{seconddb}, this is
        $$
            \le 2^{-10a} d_{B(c(J'), 100 D^{s(J) + 10a^2 + 2})}(\fcc(\fu_1), \fcc(\fu_2))
        $$
        $$
            \le 2^{-10a} d_{B(\pc(\fp), 10 D^{\ps(\fp)})}(\fcc(\fu_1), \fcc(\fu_2))\,,
        $$
        and by \eqref{firstdb} and the definition of $\mathfrak{S}$
        $$
            \le 2^{-4a} d_{\fp}(\fcc(\fu_1), \fcc(\fu_2)) \le 2^{-4a} 2^{Zn/2}\,.
        $$
        This is a contradiction, the second estimate follows.
    \end{proof}


    \begin{lemma}[local tree control]
        \label{local-tree-control}
        \uses{limited-scale-impact}
        For all $J \in \mathcal{J}'$ and all bounded $g$ with bounded support
        $$
            \sup_{B^\circ{}(J)} |T_{\mathfrak{T}(\mathfrak{u}_2)\setminus\mathfrak{S}}^* g| \le 2^{104a^3} \inf_J M_{\mathcal{B},1}|g|
        $$
    \end{lemma}

    \begin{proof}
        By the triangle inequality and since $T_{\fp}^* g = \mathbf{1}_{B(\pc(\fp), 5D^{\ps(\fp)})} T_{\fp}^* g$, we have
        $$
            \sup_{B^\circ{}(J)} |T_{\fT(\fu_2) \setminus\mathfrak{S}}^* g|
            \leq \sup_{B^\circ{}(J)} \sum_{\substack{\fp \in \fT(\fu_2) \setminus \mathfrak{S}\\ B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset}} |T_{\fp}^*g|\,.
        $$
        By \Cref{limited-scale-impact}, this is at most
        \begin{equation}
            \label{eq-sep-tree-aux-3}
            \sum_{s = s(J)}^{s(J) + 10a^2 + 2} \sum_{\substack{\fp \in \fP, \ps(\fp) = s\\ B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset}} \sup_{B^\circ{}(J)} |T_{\fp}^* g|\,.
        \end{equation}
        If $x \in E(\fp)$ and $B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset$, then
        $$
            B(c(J), 16D^{\ps(\fp)}) \subset B(x, 32 D^{\ps(\fp)})\,,
        $$
        by \eqref{eq-vol-sp-cube} and the triangle inequality. Using the doubling property \eqref{doublingx}, it follows that
        $$
            \mu(B(x, D^{\ps(\fp)})) \ge 2^{-5a} \mu(B(c(J), 16D^{\ps(\fp)}))\,.
        $$
        Using \eqref{definetp*}, \eqref{eq-Ks-size} and that $a \ge 4$, we bound \eqref{eq-sep-tree-aux-3} by
        $$
            2^{103a^3}\sum_{s = s(J)}^{s(J) + 10a^2 + 2} \sum_{\substack{\fp \in \fP, \ps(\fp) = s\\B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset}} \frac{1}{\mu(B(c(J), 16 D^s)} \int_{E(\fp)} |g| \, \mathrm{d}\mu\,.
        $$
        For each $I \in \mathcal{D}$, the sets $E(\fp)$ for $\fp \in \fP$ with $\scI(\fp) = I$ are pairwise disjoint by \eqref{defineep} and \eqref{eq-dis-freq-cover}. Further, if $B(\scI(\fp)) \cap B^\circ(J) \ne \emptyset$ and $\ps(\fp) \ge s(J)$, then $E(\fp) \subset B(c(J), 32 D^{\ps(\fp)})$. Thus the last display is bounded by
        $$
            2^{103a^3}\sum_{s = s(J)}^{s(J) + 10a^2 + 2} \frac{1}{\mu(B(c(J), 32 D^s))} \int_{B(c(J), 16 D^s)} |g| \, \mathrm{d}\mu\,.
        $$
        $$
            \le \inf_{x' \in J} 2^{103a^3}(10a^2 + 3) M_{\mathcal{B}, 1} |g|\,.
        $$
        The lemma follows since for $a \ge 4$ it holds that $10a^2 + 3 \le 2^{a^3}$.
    \end{proof}

    \begin{lemma}[scales impacting interval]
        \label{scales-impacting-interval}
        \uses{overlap-implies-distance}
        Let $\fC = \fT(\fu_1)$ or $\fC = \fT(\fu_2) \cap \mathfrak{S}$. Then for each $J \in \mathcal{J}'$ and $\fp \in \fC$ with $B(\scI(\fp)) \cap B(J) \neq \emptyset$, we have $\ps(\fp) \ge s(J)$.
    \end{lemma}

    \begin{proof}
        By \Cref{overlap-implies-distance}, we have that in both cases, $\fC \subset \mathfrak{S}$. If $\fp \in \fC$ with $B(\scI(\fp)) \cap B(J) \neq \emptyset$ and $\ps(\fp) < s(J)$, then $\scI(\fp) \subset B(c(J), 100 D^{s(J) + 1})$. Since $\fp \in \mathfrak{S}$, it follows from the definition of $\mathcal{J}'$ that $s(J) = -S$, which contradicts $\ps(\fp) < s(J)$.
    \end{proof}

    \begin{lemma}[global tree control 1]
        \label{global-tree-control-1}
        \uses{Holder-correlation-tile,scales-impacting-interval}
        Let $\fC = \fT(\fu_1)$ or $\fC = \fT(\fu_2) \cap \mathfrak{S}$. Then for each $J \in \mathcal{J}'$ and all bounded $g$ with bounded support, we have
        \begin{align}
            \label{TreeUB}
            \sup_{B(J)} |T_{\fC}^*g| \leq \inf_{B^\circ{}(J)} |T^*_{\fC} g| + 2^{154a^3} \inf_{J} M_{\mathcal{B}, 1} |g|
        \end{align}
        and for all $y,y' \in B(J)$
        $$
            |e(\fcc(\fu)(y)) T_{\fC}^* g(y) - e(\fcc(\fu)(y')) T_{\fC}^* g(y')|
        $$
        \begin{equation}
            \label{TreeHolder}
             \le 2^{153a^3} \left(\frac{\rho(y,y')}{D^{s(J)}}\right)^{1/a} \inf_J M_{\mathcal{B},1} |g|\,.
        \end{equation}
    \end{lemma}

    \begin{proof}
        Note that \eqref{TreeUB} follows from \eqref{TreeHolder}, since for $y'\in B^\circ{}(J)$, by the triangle inequality,
        $$\left(\frac{\rho(y,y')}{D^{s(J)}}\right)^{1/a}\le \Big(8 + \frac{1}8\Big)^{1/a}\le 2^{a^3}.$$

        By the triangle inequality, \Cref{adjoint-tile-support} and \Cref{Holder-correlation-tile}, we have for all $y, y' \in B(J)$
        \begin{equation}
            \label{eq-C-Lip}
            |e(\fcc(\fu)(y)) T_{\fC}^* g(y) - e(\fcc(\fu)(y')) T_{\fC}^* g(y')|
        \end{equation}
        $$
            \leq \sum_{\substack{\fp \in \fC\\ B(\scI(\fp)) \cap B(J) \neq \emptyset}} |e(\fcc(\fu)(y)) T_{\fp}^* g(y) - e(\fcc(\fu)(y')) T_{\fp}^* g(y')|
        $$
        $$
            \le 2^{151a^3}\rho(y,y')^{1/a} \sum_{\substack{\fp \in \fC\\ B(\scI(\fp)) \cap B(J) \neq \emptyset}} \frac{D^{- \ps(\fp)/a}}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \int_{E(\fp)} |g| \, \mathrm{d}\mu\,.
        $$
        By \Cref{scales-impacting-interval}, we have $\ps(\fp) \ge s(J)$ for all $\fp$ occurring in the sum. Further, for each $s \ge s(J)$, the sets $E(\fp)$ for $\fp \in \fP$ with $\ps(\fp) = s$ are pairwise disjoint by \eqref{defineep} and \eqref{eq-dis-freq-cover}, and contained in $B(c(J), 32D^{s})$ by \eqref{eq-vol-sp-cube} and the triangle inequality. Using also the doubling estimate \eqref{doublingx}, we obtain that the expression in the last display can be estimated by
        $$
            2^{151a^3}\rho(y,y')^{1/a} \sum_{S \ge s \ge s(J)} D^{-s/a} \frac{2^{3a}}{\mu(B(c(J), 32D^{s}))} \int_{B(c(J), 32D^{s})} |g| \, \mathrm{d}\mu
        $$
        $$
            \le 2^{152a^3} \left(\frac{\rho(y,y')}{D^s}\right)^{1/a} \sum_{S \ge s \ge s(J)} D^{(s(J) - s)/a} \inf_J M_{\mathcal{B},1} |g|\,.
        $$
        By convexity of $t \mapsto D^t$ and since $D \ge 2$, we have for all $-1 \le t \le 0$
        $$
            D^t \le 1 + t(1 - \frac{1}{D}) \le 1 + \frac{1}{2}t\,.
        $$
        Since $-1 \le -1/a <0$, it follows that
        $$
            \sum_{S \ge s \ge s(J)} D^{(s(J) - s)/a} \le \frac{1}{1 - D^{-1/a}} \le 2a \le 2^a\,.
        $$
        Estimate \eqref{TreeHolder}, and therefore the lemma, follow.
    \end{proof}

    \begin{lemma}[global tree control 2]
        \label{global-tree-control-2}
        \uses{global-tree-control-1}
        We have for all $J \in \mathcal{J}'$ and all bounded $g$ with bounded support
        $$
            \sup_{B(J)} |T^*_{\mathfrak{T}_2 \cap \mathfrak{S}} g| \le \inf_{B^\circ{}(J)} |T^*_{\mathfrak{T}_2} g| + 2^{155a^3} \inf_{J} M_{\mathcal{B},1}|g|\,.
        $$
    \end{lemma}

    \begin{proof}
        By \Cref{global-tree-control-1}
        $$
            \sup_{B(J)} |T^*_{\fT(\fu_2) \cap \mathfrak{S}} g| \le \inf_{B^\circ{}(J)} |T_{\fT(\fu_2) \cap \mathfrak{S}}^* g| + 2^{154a^3} \inf_{J} M_{\mathcal{B}, 1} |g|
        $$
        $$
            \le \inf_{B^\circ{}(J)} |T_{\fT(\fu_2)}^* g| + \sup_{B^\circ{}(J)} |T_{\fT(\fu_2) \setminus \mathfrak{S}}^* g| + 2^{154a^3} \inf_{J} M_{\mathcal{B}, 1} |g|\,,
        $$
        and by \Cref{local-tree-control}
        $$
            \le \inf_{B^\circ{}(J)} |T_{\fT(\fu_2)}^* g| + (2^{104a^3} + 2^{154a^3}) \inf_{J} M_{\mathcal{B}, 1} |g|\,.
        $$
        This completes the proof.
    \end{proof}



    \begin{proof}[Proof of \Cref{Holder-correlation-tree}]
        \proves{Holder-correlation-tree}
        Let $P$ be the product on the right hand side of \eqref{hHolder}, and $h_J$ as defined in \eqref{def-hj}.

        By \eqref{eq-pao-2} and \Cref{adjoint-tile-support}, the function $h_J$ is supported in $B(J) \cap \scI(\fu_1)$.
        By \eqref{eq-pao-2} and \Cref{global-tree-control-1}, we have for all $y \in B(J)$:
        $$
            |h_J(y)| \le 2^{308a^3} P\,.
        $$
        We have by the triangle inequality
        \begin{align}
            &|h_J(y) - h_J(y')|\nonumber\\
            \label{eq-h-Lip-1}
            &\le |\chi_J(y) - \chi_J(y')| |T_{\fT(\fu_1)}^* g_1(y)| |T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2(y)|\\
            \label{eq-h-Lip-2}
            & + |\chi_J(y')| |T_{\fT(\fu_1)}^* g_1(y) - T_{\fT(\fu_1)}^* g_1(y')| |T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2(y)|\\
            \label{eq-h-Lip-3}
            & + |\chi_J(y')| |T_{\fT(\fu_1)}^* g_1(y')| |T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2(y) - T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2(y')|\,.
        \end{align}

        As $h_J$ is supported in $\scI(\fu_1)$, we can assume without loss of generality that $y' \in \scI(\fu_1)$.
        If $y \notin \scI(\fu_1)$, then \eqref{eq-h-Lip-1} vanishes. If $y \in \scI(\fu_1)$ then we have by \eqref{eq-pao-3}, \Cref{global-tree-control-1} and \Cref{global-tree-control-2}
        $$
            \eqref{eq-h-Lip-1} \le 2^{534a^3} \frac{\rho(y,y')}{D^{s(J)}} P\,,
        $$
        where $P$ denotes the product on the right hand side of \eqref{hHolder}.

        By \eqref{eq-pao-2}, \Cref{global-tree-control-1} and \Cref{global-tree-control-2}, we have
        $$
            \eqref{eq-h-Lip-2} \le 2^{310a^3} P\,.
         $$

        By \eqref{eq-pao-2}, and twice \Cref{global-tree-control-1}, we have
        $$
            \eqref{eq-h-Lip-3} \le 2^{308a^3} P\,.
        $$
        Using that $\rho(y,y') \le 16D^{s(J)}$ and $a \ge 4$, the lemma follows.
    \end{proof}

\subsection{The van der Corput estimate}
\label{subsubsec-van-der-corput}
    \begin{lemma}[lower oscillation bound]
        \label{lower-oscillation-bound}
        \uses{overlap-implies-distance}
        For all $J \in \mathcal{J}'$, we have that
        $$
            d_{B(J)}(\fcc(\fu_1), \fcc(\fu_2)) \ge 2^{-201a^3} 2^{Zn/2}\,.
        $$
    \end{lemma}

    \begin{proof}
    Since $\emptyset \ne \fT(\fu_1) \subset \mathfrak{S}$ by \Cref{overlap-implies-distance}, there exists at least one tile $\fp \in \mathcal{S}$ with $\scI(\fp) \subsetneq \scI(\fu_1)$. Thus $\scI(\fu_1) \notin \mathcal{J}'$, so $J \subsetneq \scI(\fu_1)$. Thus there exists a cube $J' \in \mathcal{D}$ with $J \subset J'$ and $s(J') = s(J) + 1$, by \eqref{coverdyadic} and \eqref{dyadicproperty}. By definition of $\mathcal{J'}$ and the triangle inequality, there exists $\fp \in \mathfrak{S}$ such that
    $$
        \scI(\fp) \subset B(c(J'), 100 D^{s(J') + 1}) \subset B(c(J), 128 D^{s(J)+2})\,.
    $$
    Thus, by definition of $\mathfrak{S}$:
    \begin{align*}
        2^{Zn/2} \le d_{\fp}(\fcc(\fu_1), \fcc(\fu_2)) \le d_{B(c(J), 128 D^{s(J)+2})}(\fcc(\fu_1), \fcc(\fu_2))\,.
    \end{align*}
    By the doubling property \eqref{firstdb}, this is
    $$
        \le 2^{200a^3 + 4a} d_{B(J)}(\fcc(\fu_1), \fcc(\fu_2))\,,
    $$
    which gives the lemma using $a \ge 4$.
    \end{proof}

    Now we are ready to prove \Cref{correlation-distant-tree-parts}.
    \begin{proof}[Proof of \Cref{correlation-distant-tree-parts}]
    \proves{correlation-distant-tree-parts}
    We have
    $$
        \eqref{eq-lhs-big-sep-tree} = \left| \int_{X} T_{\fT(\fu_1)}^* g_1 \overline{T_{\fT(\fu_2) \cap \mathfrak{S}}^* g_2 }\right|\,.
    $$
    By \Cref{adjoint-tile-support}, the right hand side is supported in $\scI(\fu_1)$. Using \eqref{eq-pao-1} of \Cref{Lipschitz-partition-unity} and the definition \eqref{def-hj} of $h_J$, we thus have
    $$
        \le \sum_{J \in \mathcal{J}'} \left|\int_{B(J)} e(\fcc(\fu_2)(y) - \fcc(\fu_1)(y)) h_J(y) \, \mathrm{d}\mu(y) \right|\,.
    $$
    Using \Cref{Holder-van-der-Corput} with the ball $B(J)$, we bound this by
    $$
        \le 2^{8a} \sum_{J \in \mathcal{J}'} \mu(B(J)) \|h_J\|_{C^{\tau}(B(J))} (1 + d_{B(J)}(\fcc(\fu_1), \fcc(\fu_1)))^{-1/(2a^2+a^3)}\,.
    $$
    Using \Cref{Holder-correlation-tree}, \Cref{lower-oscillation-bound} and $a \ge 4$, we have that the above is bounded from above by
    \begin{multline}
        \label{eq-big-sep-1}
        \le 2^{540a^3} 2^{-Zn/(4a^2 + 2a^3)} \sum_{J \in \mathcal{J}'} \mu(B(J)) \\
        \times \prod_{j=1}^2 (\inf_{B^\circ{}(J)} |T_{\fT(\fu_j)}^* g_j| + \inf_J M_{\mathcal{B},1} g_j)\,.
    \end{multline}
    By the doubling property \eqref{doublingx}
    $$
        \mu(B(J)) \le 2^{6a} \mu(B^\circ{}(J))\,,
    $$
    thus
    $$
        \mu(B(J)) \prod_{j=1}^2 (\inf_{B^\circ{}(J)} |T_{\fT(\fu_j)}^* g_j| + \inf_J M_{\mathcal{B},1} g_j)
    $$
    $$
        \le 2^{6a} \int_{B^\circ{}(J)} \prod_{j=1}^2 ( |T_{\fT(\fu_j)}^* g_j|(x) + M_{\mathcal{B},1} g_j(x)) \, \mathrm{d}\mu(x)
    $$
    $$
        \le 2^{6a} \int_J \prod_{j=1}^2 ( |T_{\fT(\fu_j)}^* g_j|(x) + M_{\mathcal{B},1} g_j(x)) \, \mathrm{d}\mu(x)\,.
    $$
    Summing over $J \in \mathcal{J}'$, we obtain
    $$
        \eqref{eq-big-sep-1} \le 2^{541a^3} 2^{-Zn/(4a^2 + 2a^3)} \int_X \prod_{j=1}^2 ( |T_{\fT(\fu_j)}^* g_j|(x) + M_{\mathcal{B},1} g_j(x)) \, \mathrm{d}\mu(x)\,.
    $$
    Applying the Cauchy-Schwarz inequality, \Cref{correlation-distant-tree-parts} follows.
    \end{proof}

\section{Proof of The Remaining Tiles Lemma}
    \label{subsec-rest-tiles}
    We define
    $$
        \mathcal{J}' = \{J \in \mathcal{J}(\fT(\fu_1)) \, : \, J \subset \scI(\fu_1)\}\,,
    $$
    note that this is different from the $\mathcal{J}'$ defined in the previous subsection.
    \begin{lemma}[dyadic partition 2]
        \label{dyadic-partition-2}
        \uses{dyadic-partitions}
        We have
        $$
            \scI(\fu_1) = \dot{\bigcup_{J \in \mathcal{J}'}} J\,.
        $$
    \end{lemma}

    \begin{proof}
        By \Cref{dyadic-partitions}, it remains only to show that each $J \in \mathcal{J}(\fT(\fu_1))$ with $J \cap \scI(\fu_1) \ne \emptyset$ is in $\mathcal{J}'$. But if $J \notin \mathcal{J}'$, then by \eqref{dyadicproperty} $\scI(\fu_1) \subsetneq J$. Pick $\fp \in \fT(\fu_1)$. Then $\scI(\fp) \subsetneq J$. This contradicts the definition of $\mathcal{J}(\fT(\fu_1))$.
    \end{proof}

    \Cref{correlation-near-tree-parts} follows from the following key estimate.

    \begin{lemma}[bound for tree projection]
        \label{bound-for-tree-projection}
        \uses{adjoint-tile-support,overlap-implies-distance,dyadic-partition-2,thin-scale-impact,square-function-count}
        We have
        $$
            \|P_{\mathcal{J}'}|T_{\mathfrak{T}_2 \setminus \mathfrak{S}}^* g_2|\|_2
            \le 2^{118a^3} 2^{-\frac{100}{202a}Zn\kappa} \|\mathbf{1}_{\scI(\fu_1)} M_{\mathcal{B},1} |g_2|\|_2
        $$
    \end{lemma}

    We prove this lemma below. First, we deduce \Cref{correlation-near-tree-parts}.

    \begin{proof}[Proof of \Cref{correlation-near-tree-parts}]
        \proves{correlation-near-tree-parts}
        By \Cref{tree-projection-estimate} and \Cref{adjoint-tile-support}, we have
        \begin{align*}
            \eqref{eq-lhs-small-sep-tree} \le 2^{104a^3} \|P_{\mathcal{L}(\fT(\fu_1))} |g_1\mathbf{1}_{\scI(\fu_1)}| \|_2 \|\mathbf{1}_{\scI(\fu_1)} P_{\mathcal{J}(\fT(\fu_1) )}|T_{\fT(\fu_2) \setminus \mathfrak{S}}^* g_2|\|_2\,.
        \end{align*}
        It follows from the definition of the projection operator $P$ and Jensen's inequality that
        $$
            \|P_{\mathcal{L}(\fT(\fu_1))} |g_1\mathbf{1}_{\scI(\fu_1)}| \|_2 \le \|g_1 \mathbf{1}_{\scI(\fu_1)}\|_2\,.
        $$
        Since cubes in $\mathcal{J}'$ are pairwise disjoint and by \Cref{dyadic-partition-2}, a cube $J \in \mathcal{J}'$ intersect $\scI(\fu_1)$ if and only if $J \in \mathcal{J}'$. Thus
        $$
            \mathbf{1}_{\scI(\fu_1)} P_{\mathcal{J}(\fT(\fu_1) )}|T_{\fT(\fu_2) \setminus \mathfrak{S}}^* g_2| = P_{\mathcal{J}'}|T_{\fT(\fu_2) \setminus \mathfrak{S}}^* g_2|\,.
        $$
        Combining this with \Cref{bound-for-tree-projection}, the definition \eqref{definekappa} and $a \ge 4$ proves the lemma.
    \end{proof}

    We need two more auxiliary lemmas before we prove \Cref{bound-for-tree-projection}.

    \begin{lemma}[thin scale impact]
        \label{thin-scale-impact}
        If $\fp \in \fT_2 \setminus \mathfrak{S}$ and $J \in \mathcal{J'}$ with $B(\scI(\fp)) \cap B(J) \ne \emptyset$, then
        $$
            \ps(\fp) \le s(J) + 2 - \frac{Zn}{202a^3}\,.
        $$
    \end{lemma}

    \begin{proof}
        Suppose that $\ps(\fp) > s(J) + 2 -\frac{Zn}{202a^3} =: s(J) - s_1$. Then, we have
        $$
            \rho(\pc(\fp), c(J)) \le 8D^{s(J)}+8D^{\ps(\fp)} \le 16 D^{\ps(\fp) + s_1}\,.
        $$
        There exists a tile $\fq \in \fT(\fu_1)$. By \eqref{forest1}, it satisfies $\scI(\fq) \subsetneq \scI(\fu_1)$. Thus $\scI(\fu_1) \notin \mathcal{J}'$. It follows that $J \subsetneq \scI(\fu_1)$. By \eqref{coverdyadic} and \eqref{dyadicproperty}, there exists a cube $J' \in \mathcal{D}$ with $J \subset J'$ and $s(J') = s(J) + 1$. By definition of $\mathcal{J}'$, there exists a tile $\fp' \in \fT(\fu_1)$ with
        $$
            \scI(\fp') \subset B(c(J'), 100 D^{s(J') + 1})\,.
        $$
        By the triangle inequality, the definition \eqref{defineD} and $a \ge 4$, we have
        $$
            B(c(J'), 100 D^{s(J')+1}) \subset B(\pc(\fp), 128 D^{\ps(\fp) + s_1 + 1})\,.
        $$
        Since $\fp' \in \fT(\fu_1)$ and $\scI(\fu_1) \subset \scI(\fu_2)$, we have by \eqref{forest5}
        $$
            d_{\fp'}(\fcc(\fp'), \fcc(\fu_2)) > 2^{Z(n+1)}\,.
        $$
        Hence, by \eqref{forest1}, the triangle inequality and using that by \eqref{defineZ} $Z \ge 2$
        $$
            d_{\fp'}(\fcc(\fu_1), \fcc(\fu_2)) > 2^{Z(n+1)} - 4 \ge 2^{Zn}\,.
        $$
        It follows that
        $$
            2^{Zn} \le d_{\fp'}(\fcc(\fu_1), \fcc(\fu_2)) \le d_{B(\pc(\fp), 128 D^{\ps(\fp) + s_1+ 1})}(\fcc(\fu_1), \fcc(\fu_2))\,.
        $$
        Using \eqref{firstdb}, we obtain
        $$
            \le 2^{9a + 100a^3 (s_1+1)} d_{\fp}(\fcc(\fu_1), \fcc(\fu_2))\,.
        $$
        Since $\fp' \notin \mathfrak{S}$ this is bounded by
        $$
            \le 2^{9a + 100a^3 (s_1+1)} 2^{Zn/2}\,.
        $$
        Thus
        $$
            Z n/2 \le 9a + 100a^3(s_1 + 1)\,,
        $$
        contradicting the definition of $s_1$.
    \end{proof}

    \begin{lemma}[square function count]
        \label{square-function-count}
        For each $J \in \mathcal{J}'$, we have
        $$
            \frac{1}{\mu(J)} \int_J \Bigg(\sum_{\substack{I \in \mathcal{D}, s(I) = s(J) - s\\ I \cap \scI(\fu_1) = \emptyset\\
        J \cap B(I) \ne \emptyset}} \mathbf{1}_{B(I)}\bigg)^2 \, \mathrm{d}\mu \le 2^{104a^2} (8 D^{-s})^\kappa\,.
        $$
    \end{lemma}

    \begin{proof}[Proof of \Cref{square-function-count}]
        \proves{square-function-count}
        Since $J \in \mathcal{J}'$ we have $J \subset \scI(\fu_1)$. Thus, if $B(I) \cap J \ne \emptyset$ then
    \begin{equation}
        \label{eq-sep-small-incl}
        B(I) \cap J \subset \{x \in J \ : \ \rho(x, X \setminus J) \le 8D^{s(I)}\}\,.
    \end{equation}
    Furthermore, for each $s$ the balls $B(I)$ with $s(I) = s$ have bounded overlap: Consider the collection $\mathcal{D}_{s,x}$ of all $I \in \mathcal{D}$ with $x \in B(I)$ and $s(I) = s$. By \eqref{eq-vol-sp-cube} and \eqref{dyadicproperty}, the balls $B(c(I), \frac{1}{4} D^{s(I)})$, $I \in \mathcal{D}_{s,x}$ are disjoint, and by the triangle inequality, they are contained in $B(x, 9 D^{s})$. By the doubling property \eqref{doublingx}, we have
    $$
        \mu(B(x, 9D^{s})) \le 2^{8a} \mu(B(c(I), \frac{1}{4} D^{s(I)}))
    $$
    for each $I \in \mathcal{D}_{s,x}$.
    Thus
    $$
        \mu(B(x, 9D^{s})) \ge \sum_{I \in \mathcal{D}_{s,x}} \mu(B(c(I), \frac{1}{4} D^{s(I)})) \ge 2^{-8a} |\mathcal{D}_{s,x}| \mu(B(x, 9D^{s}))\,.
    $$
    Dividing by the positive $\mu(B(x, 9D^{s}))$, we obtain that for each $x$
    \begin{equation}
        \label{eq-sep-small-bound}
        \Bigg(\sum_{\substack{I \in \mathcal{D}, s(I) = s(J) - s\\ I \cap \scI(\fu_1) = \emptyset\\
        J \cap B(I) \ne \emptyset}} \mathbf{1}_{B(I)}(x) \bigg)^2 = |\mathcal{D}_{s(J) - s,x}|^2 \le 2^{16a} \,.
    \end{equation}
    Combining \eqref{eq-sep-small-incl}, \eqref{eq-sep-small-bound} and the small boundary property \eqref{eq-small-boundary}, noting that $8D^{s(I)}=8D^{-s}D^{s(J)}$, the lemma follows.
\end{proof}


\begin{proof}[Proof of \Cref{bound-for-tree-projection}]
    \proves{bound-for-tree-projection}
    Expanding the definition of $P_{\mathcal{J}'}$, we have
    $$
        \|P_{\mathcal{J}'}|T_{\mathfrak{T}_2 \setminus \mathfrak{S}}^* g_2|\|_2
    $$
    $$
        = \left(\sum_{J \in \mathcal{J}'} \frac{1}{\mu(J)} \left|\int_J \sum_{\fp \in \fT(\fu_2) \setminus \mathfrak{S}} T_{\fp}^* g_2 \, \mathrm{d}\mu(y) \right|^2 \right)^{1/2}\,.
    $$
    We split the innermost sum according to the scale of the tile $\fp$, and then apply the triangle inequality and Minkowski's inequality:
    $$
        \le \sum_{s = -S}^S \left( \sum_{J \in \mathcal{J}'} \frac{1}{\mu(J)} \left|\int_J \sum_{\substack{\fp \in \fT(\fu_2) \setminus \mathfrak{S}\\ \ps(\fp) = s}} T_{\fp}^* g_2 \, \mathrm{d}\mu(y) \right|^2\right)^{1/2}\,.
    $$
    By \Cref{adjoint-tile-support}, the integral in the last display is $0$ if $J \cap B(\scI(\fp)) = \emptyset$. By \Cref{thin-scale-impact}, it follows with $s_1 := \frac{Zn}{202a^3} - 2$:
    \begin{equation}
    \label{eq-sep-tree-small-1}
        = \sum_{s = s_1}^{s_1 + 2S} \Bigg( \sum_{J \in \mathcal{J}'} \frac{1}{\mu(J)} \Bigg|\int_J \sum_{\substack{\fp \in \fT(\fu_2) \setminus \mathfrak{S}\\ \ps(\fp) = s(J) - s\\
        J \cap B(\scI(\fp)) \ne \emptyset}} T_{\fp}^* g_2 \, \mathrm{d}\mu(y) \Bigg|^2\Bigg)^{1/2}\,.
    \end{equation}
    We have by \Cref{adjoint-tile-support} and \eqref{eq-Ks-size}
    $$
        \int |T_{\fp}^* g_2|(y) \, \mathrm{d}\mu(y)
    $$
    $$
        \le 2^{102a^3} \int_{B(\scI(\fp))} \int \frac{1}{\mu(B(x, D^{\ps(\fp)}))} \mathbf{1}_{E(\fp)}(x) |g_2|(x) \, \mathrm{d}\mu(x) \, \mathrm{d}\mu(y)\,.
    $$
    If $x \in E(\fp) \subset \scI(\fp)$, then we have by \eqref{eq-vol-sp-cube} that
    $$
        B(\pc(\fp), 4D^{\ps(\fp)}) \subset B(\scI(\fp))\,.
    $$
    Using the doubling property \eqref{doublingx}, it follows that
    $$
        \mu(B(\pc(\fp), 4D^{\ps(\fp)})) \le 2^{3a} \mu(B(x, D^s))\,.
    $$
    Thus, using also $a \ge 4$
    $$
        \int |T_{\fp}^* g_2|(y) \, \mathrm{d}\mu(y)
    $$
    $$
        \le 2^{103 a^3} \int_{B(\scI(\fp))} \int \frac{1}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \mathbf{1}_{E(\fp)}(x) |g_2|(x) \, \mathrm{d}\mu(x) \, \mathrm{d}\mu(y)\,.
    $$
    Since for each $I \in \mathcal{D}$ the sets $E(\fp), \fp \in \fP(I)$ are disjoint, it follows that
    $$
        \bigg| \int_J \sum_{\substack{\fp \in \fT(\fu_2) \setminus \mathfrak{S}\\ \scI(\fp) = I\\
        J \cap B(\scI(\fp)) \ne \emptyset}} T_{\fp}^* g_2 \, \mathrm{d}\mu \bigg|
    $$
    $$
        \le 2^{103a^3} \int_J \mathbf{1}_{B(I)} \frac{1}{\mu(B(\pc(\fp), 4D^{\ps(\fp)}))} \int_{B(\pc(\fp), 4D^{\ps(\fp)})} |g_2|(x) \, \mathrm{d}\mu(x)
    $$
    $$
        \le 2^{103a^3} \int_J M_{\mathcal{B},1} |g_2|(y) \mathbf{1}_{B(I)}(y) \, \mathrm{d}\mu(y)\,.
    $$
    By \Cref{overlap-implies-distance}, we have $\scI(\fp) \cap \scI(\fu_1) = \emptyset$ for all $\fp \in \fT(\fu_2) \setminus \mathfrak{S}$.
    Thus we can estimate \eqref{eq-sep-tree-small-1} by
    $$
        2^{103a^3} \sum_{s = s_1}^{s_1 + 2S} \Bigg( \sum_{J \in \mathcal{J}'} \frac{1}{\mu(J)} \Bigg|\int_J \sum_{\substack{I \in \mathcal{D}, s(I) = s(J) - s\\ I \cap \scI(\fu_1) = \emptyset\\
        J \cap B(I) \ne \emptyset}} M_{\mathcal{B},1} |g_2| \mathbf{1}_{B(I)} \, \mathrm{d}\mu \Bigg|^2\Bigg)^{\frac 1 2}\,,
    $$
    which is by Cauchy-Schwarz at most
    \begin{equation}
    \label{eq-sep-tree-small-2}
        2^{103a^3} \sum_{s = s_1}^{s_1 + 2S} \Bigg( \sum_{J \in \mathcal{J}'} \int_J ( M_{\mathcal{B},1} |g_2|)^2 \frac{1}{\mu(J)} \int_J \Bigg(\sum_{\substack{I \in \mathcal{D}, s(I) = s(J) - s\\ I \cap \scI(\fu_1) = \emptyset\\
        J \cap B(I) \ne \emptyset}} \mathbf{1}_{B(I)}\bigg)^2 \, \mathrm{d}\mu \Bigg)^{\frac 12}\,.
    \end{equation}
    Using \Cref{square-function-count}, we bound \eqref{eq-sep-tree-small-2} by
    $$
        2^{103a^3} \sum_{s = s_1}^{s_1 + 2S} \left(\sum_{J \in \mathcal{J}'} \int_J (M_{\mathcal{B},1} |g_2|)^2 2^{104a^2} (8 D^{-s})^\kappa\right)^{\frac 1 2}\,,
    $$
    and, since dyadic cubes in $\mathcal{J}'$ form a partition of $\scI(\fu_1)$ by \Cref{dyadic-partition-2}, $\kappa \le 1$ by \eqref{definekappa}, and $a \ge 4$
    $$
        \le 2^{116a^3} \sum_{s = s_1}^{s_1 + 2S} D^{-s\kappa/2} \|\mathbf{1}_{\scI(\fu_1)} M_{\mathcal{B},1} |g_2|\|_2
    $$
    $$
        \le 2^{116a^3} D^{-s_1 \kappa /2} \frac{1}{1 - D^{-\kappa/2}} \|\mathbf{1}_{\scI(\fu_1)} M_{\mathcal{B},1} |g_2|\|_2\,.
    $$
    By convexity of $t \mapsto D^t$ and since $D \ge 2$, we have for all $-1 \le t \le 0$
    $$
        D^t \le 1 + t(1 - \frac{1}{D}) \le 1 + \frac{1}{2}t\,.
    $$
    Using this for $t = -\kappa/2$ and using that $s_1 = \frac{Zn}{202a^3} - 2$ and the definitions \eqref{defineD} and \eqref{definekappa} of $\kappa$ and $D$
    $$
        \le 2^{116a^3} 2^{-100a^2(\frac{Zn}{202a^3} - 2) \frac{\kappa}{2}} \frac{2}{\kappa} \|\mathbf{1}_{\scI(\fu_1)} M_{\mathcal{B},1} |g_2|\|_2
    $$
    $$
        \le \frac{2^{117a^3 + 1}}{\kappa} 2^{-\frac{100}{202a}Zn\kappa} \|\mathbf{1}_{\scI(\fu_1)} M_{\mathcal{B},1} |g_2|\|_2\,.
    $$
    Using the definition \eqref{definekappa} of $\kappa$ and $a \ge 4$, the lemma follows.
\end{proof}



\section{Forests}
In this subsection, we complete the proof of \Cref{forest-operator} from the results of the previous subsections.

Define an $n$-row to be an $n$-forest $(\fU, \fT)$, i.e. satisfying conditions \eqref{forest1} - \eqref{forest6}, such that in addition the sets $\scI(\fu), \fu \in \fU$ are pairwise disjoint.

\begin{lemma}[forest row decomposition]
    \label{forest-row-decomposition}
    Let $(\fU, \fT)$ be an $n$-forest. Then there exists a decomposition
    $$
        \fU = \dot{\bigcup_{1 \le j \le 2^n}} \fU_j
    $$
    such that for all $j = 1, \dotsc, 2^n$ the pair $(\fU_j, \fT|_{\fU_j})$ is an $n$-row.
\end{lemma}

\begin{proof}
    Define recursively $\fU_j$ to be a maximal disjoint set of tiles $\fu$ in
    $$
        \fU \setminus \bigcup_{j' < j} \fU_{j'}
    $$
    with inclusion maximal $\scI(\fu)$. Properties \eqref{forest1}, -\eqref{forest6} for $(\fU_j, \fT|_{\fU_k})$ follow immediately from the corresponding properties for $(\fU, \fT)$, and the cubes $\scI(\fu), \fu \in \fU_j$ are disjoint by definition. The collections $\fU_j$ are also disjoint by definition.

    Now we show by induction on $j$ that each point is contained in at most $2^n - j$ cubes $\scI(\fu)$ with $\fu \in \fU \setminus \bigcup_{j' \le j} \fU_{j'}$. This implies that $\bigcup_{j = 1}^{2^n} \fU_j = \fU$, which completes the proof of the Lemma. For $j = 0$ each point is contained in at most $2^n$ cubes by \eqref{forest3}. For larger $j$, if $x$ is contained in any cube $\scI(\fu)$ with $\fu \in \fU \setminus \bigcup_{j' < j} \fU_{j'}$, then it is contained in a maximal such cube. Thus it is contained in a cube in $\scI(\fu)$ with $\fu \in \fU_j$. Thus the number $\fu \in \fU \setminus \bigcup_{j' \le j} \fU_{j'}$ with $x\in \scI(\fu)$ is zero, or is less than the number of $\fu \in \fU \setminus \bigcup_{j' \le j-1} \fU_{j'}$ with $x \in \scI(\fu)$ by at least one.
\end{proof}

We pick a decomposition of the forest $(\fU, \fT)$ into $2^n$ $n$-rows
\begin{equation*}
(\fU_j, \fT_j) := (\fU_j, \fT|_{\fU_j})
\end{equation*}
as in \Cref{forest-row-decomposition}.

\begin{lemma}[row bound]
    \label{row-bound}
    \uses{densities-tree-bound,adjoint-tile-support}
    For each $1 \le j \le 2^n$ and each bounded $g$ with bounded support, we have
    \begin{equation}
        \label{eq-row-bound-1}
        \left\| \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} T_{\fp}^* g\right\|_2 \le 2^{156a^3} 2^{-n/2} \|g\|_2
    \end{equation}
    and
    \begin{equation}
        \label{eq-row-bound-2}
        \left\| \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} \mathbf{1}_F T_{\fp}^* g\right\|_2 \le 2^{257a^3} 2^{-n/2} \dens_2(\bigcup_{\fu\in \fU}\fT(\fu))^{1/2} \|g\|_2\,.
    \end{equation}
\end{lemma}

\begin{proof}
    By \Cref{densities-tree-bound} and the density assumption \eqref{forest4}, we have for each $\fu \in \fU$ and all bounded $f$ of bounded support that
    \begin{equation}
        \label{eq-explicit-tree-bound-1}
        \left\|\sum_{\fp \in \fT(\fu)} T_{\fp} f \right\|_{2} \le 2^{155a^3} 2^{(4a+1-n)/2} \|f\|_2\,
    \end{equation}
    and
    \begin{equation}
        \label{eq-explicit-tree-bound-2}
        \left\|\sum_{\fp \in \fT(\fu)} T_{\fp} \mathbf{1}_F f \right\|_{2} \le 2^{256a^3} 2^{(4a + 1-n)/2} \dens_2(\fT(\fu))^{1/2} \|f\|_2\,.
    \end{equation}
    Since for each $j$ the top cubes $\scI(\fu)$, $\fu \in \fU_j$ are disjoint, we further have for all bounded $g$ of bounded support by \Cref{adjoint-tile-support}
    $$
        \left\|\mathbf{1}_F \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} T_{\fp}^* g\right\|_2^2 = \left\|\mathbf{1}_F \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} \mathbf{1}_{\scI(\fu)} T_{\fp}^* \mathbf{1}_{\scI(\fu)} g\right\|_2^2
    $$
    $$
        = \sum_{\fu \in \fU_j} \int_{\scI(\fu)} \left| \mathbf{1}_F \sum_{\fp \in \fT(\fu)} T_{\fp}^* \mathbf{1}_{\scI(\fu)} g\right|^2 \, \mathrm{d}\mu
        \le \sum_{\fu \in \fU_j} \left\|\sum_{\fp \in \fT(\fu)} \mathbf{1}_F T_{\fp}^* \mathbf{1}_{\scI(\fu)} g\right\|_2^2\,.
    $$
    Applying the estimate for the adjoint operator following from equation \eqref{eq-explicit-tree-bound-2}, we obtain
    $$
        \le 2^{256a^3} 2^{(4a+1-n)/2} \max_{\fu \in \fU_j}\dens_2(\fT(\fu))^{1/2} \sum_{\fu \in \fU_j} \left\| \mathbf{1}_{\scI(\fu)} g\right\|_2^2\,.
    $$
    Again by disjointedness of the cubes $\scI(\fu)$, this is estimated by
    $$
        2^{256a^3} 2^{(4a+1-n)/2} \max_{\fu \in \fU_j}\dens_2(\fT(\fu))^{1/2} \|g\|_2^2\,.
    $$
    Thus, \eqref{eq-row-bound-2} follows, since $a \ge 4$.
    The proof of \eqref{eq-row-bound-1} from \eqref{eq-explicit-tree-bound-1} is the same up to replacing $F$ by $X$.
\end{proof}

\begin{lemma}[row correlation]
    \label{row-correlation}
    \uses{adjoint-tree-control,correlation-separated-trees}
    For all $1 \le j < j' \le 2^n$ and for all bounded $g_1, g_2$ with bounded support, it holds that
    $$
        \left| \int \sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \sum_{\fp \in \fT_j(\fu)} \sum_{\fp' \in \fT_{j'}(\fu')} T^*_{\fp} g_1 \overline{T^*_{\fp'} g_2} \, \mathrm{d}\mu \right| \le
        2^{862a^3-3n}\|g_1\|_2 \|g_2\|_2\,.
    $$
\end{lemma}

\begin{proof}
    To save some space we will write for subsets $\fC \subset \fP$
    $$
        T_{\fC}^* = \sum_{\fp \in \fC} T_{\fp}^*\,.
    $$
    We have by \Cref{adjoint-tile-support} and the triangle inequality that
    $$
        \left| \int \sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \sum_{\fp \in \fT_j(\fu)} \sum_{\fp' \in \fT_{j'}(\fu')} T^*_{\fp} g_1 \overline{T^*_{\fp'} g_2} \, \mathrm{d}\mu \right|
    $$
    $$
        \le \sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \left| \int T^*_{\fT_j(\fu)} (\mathbf{1}_{\scI(\fu)} g_1) \overline{T^*_{\fT_{j'}(\fu')} (\mathbf{1}_{\scI(\fu')} g_2)} \, \mathrm{d}\mu \right|\,.
    $$
    By \Cref{correlation-separated-trees}, this is bounded by
    \begin{equation}
        \label{eq-S2uu'}
         2^{550a^3-3n} \sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \|S_{2,\fu} g_1\|_{L^2(\scI(\fu')\cap \scI(\fu)} \|S_{2, \fu'} g_2\|_{L^2(\scI(\fu')\cap\scI(\fu))}\,.
    \end{equation}
    We apply the Cauchy-Schwarz inequality in the form
    \begin{equation*}
        \sum_{i \in M} a_i b_i \le (\sum_{i \in M} a_i^2 )^{1/2}(\sum_{i \in M} b_i^2 )^{1/2}
    \end{equation*} to the outer two sums:
    $$
        \le 2^{550a^3-3n} \left(\sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \|S_{2,\fu} g_1\|_{L^2(\scI(\fu')\cap \scI(\fu))}^2 \right)^{1/2}
    $$
    $$
        \left(\sum_{\fu \in \fU_j} \sum_{\fu' \in \fU_{j'}} \|S_{2,\fu'} g_2\|_{L^2(\scI(\fu')\cap\scI(\fu))}^2 \right)^{1/2}\,.
    $$
    By pairwise disjointedness of the sets $\scI(\fu)$ for $\fu \in \fU_j$ and of the sets $\scI(\fu')$ for $\fu' \in \fU_{j'}$, we have
    $$
        \sum_{\fu \in \fU_j}\sum_{\fu' \in \fU_{j'}} \|S_{2,\fu} g_1\|_{L^2(\scI(\fu')\cap \scI(\fu))}^2
        = \sum_{\fu \in \fU_j}\sum_{\fu' \in \fU_{j'}} \int_{\scI(\fu) \cap \scI(\fu')} |S_{2,\fu} g_1(y)|^2 \, \mathrm{d}\mu(y)
    $$
    $$
        \le \int_X |S_{2,\fu}g_1(y)|^2 \, \mathrm{d}\mu(y) = \|S_{2,\fu} g_1\|_2^2\,.
    $$
    Arguing similar for $g_2$, we can estimate \eqref{eq-S2uu'} to be
    $$
        \le 2^{550a^3-3n} \|S_{2,\fu}g_1\|_2 \|S_{2,\fu'} g_2\|_2\,.
    $$
    The lemma now follows from \Cref{adjoint-tree-control}.
\end{proof}

Define for $1 \le j \le 2^n$
$$
    E_j := \bigcup_{\fu \in \fU_j} \bigcup_{\fp \in \fT(\fu)} E(\fp)\,.
$$

\begin{lemma}[disjoint row support]
    \label{disjoint-row-support}
    The sets $E_j$, $1 \le j \le 2^n$ are pairwise disjoint.
\end{lemma}

\begin{proof}
    Suppose that $\fp \in \fT(\fu)$ and $\fp' \in \fT(\fu')$ with $\fu \ne \fu'$ and $x \in E(\fp) \cap E(\fp')$. Suppose without loss of generality that $\ps(\fp) \le \ps(\fp')$. Then $x \in \scI(\fp) \cap \scI(\fp') \subset \scI(\fu')$. By \eqref{dyadicproperty} it follows that $\scI(\fp) \subset \scI(\fu')$. By \eqref{forest5}, it follows that
    $$
        d_{\fp}(\fcc(\fp), \fcc(\fu')) > 2^{Z(n+1)}\,.
    $$
    By the triangle inequality. \Cref{monotone-cube-metrics} and \eqref{forest1} it follows that
    \begin{align*}
        d_{\fp}(\fcc(\fp), \fcc(\fp')) &\ge d_{\fp}(\fcc(\fp), \fcc(\fu')) - d_{\fp}(\fcc(\fp'), \fcc(\fu'))\\
        &> 2^{Z(n+1)} - d_{\fp'}(\fcc(\fp'), \fcc(\fu'))\\
        &\ge 2^{Z(n+1)} - 4\,.
    \end{align*}
    Since $Z \ge 3$ by \eqref{defineZ}, it follows that $\fcc(\fp') \notin B_{\fp}(\fcc(\fp), 1)$, so $\Omega(\fp') \not\subset \Omega(\fp)$ by \eqref{eq-freq-comp-ball}. Hence, by \eqref{eq-freq-dyadic}, $\Omega(\fp) \cap \Omega(\fp') = \emptyset$. But if $x \in E(\fp) \cap E(\fp')$ then $Q(x) \in \Omega(\fp) \cap \Omega(\fp')$. This is a contradiction, and the lemma follows.
\end{proof}

Now we prove \Cref{forest-operator}.

\begin{proof}[Proof of \Cref{forest-operator}]
    \proves{forest-operator}
    To save some space, we will write
    $$
        T_{\mathfrak{R}_j}^* = \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} T_{\fp}^*\,.
    $$
    By \eqref{definetp*}, we have for each $j$
    $$
        T_{\mathfrak{R}_j}^*g = \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} T_{\fp}^* g = \sum_{\fu \in \fU_j} \sum_{\fp \in \fT(\fu)} T_{\fp}^* \mathbf{1}_{E_j} g = T_{\mathfrak{R}_j}^* \mathbf{1}_{E_j} g\,.
    $$
    Hence, by \Cref{forest-row-decomposition},
    $$
        \left\|\sum_{\fu \in \fU} \sum_{\fp \in \fT(\fu)} T^*_{\fp} g\right\|_2^2 = \left\|\sum_{j = 1}^{2^n} T^*_{\mathfrak{R}_{j}} g\right\|_2^2 = \left\|\sum_{j=1}^{2^n} T^*_{\mathfrak{R}_{j}} \mathbf{1}_{E_j} g\right\|_2^2
    $$
    $$
        = \int_X \left|\sum_{j=1}^{2^n} T^*_{\mathfrak{R}_{j}} \mathbf{1}_{E_j} g\right|^2 \, \mathrm{d}\mu
    $$
    $$
        = \sum_{j=1}^{2^n} \int_X |T_{\mathfrak{R}_j}^* \mathbf{1}_{E_j} g|^2 + \sum_{j =1}^{2^n} \sum_{\substack{j' = 1\\j' \ne j}}^{2^n} \int_X \overline{ T_{\mathfrak{R}_j}^* \mathbf{1}_{E_j} g} T_{\mathfrak{R}_{j'}}^* \mathbf{1}_{E_{j'}} g \, \mathrm{d}\mu\,.
    $$
    We use \Cref{row-bound} to estimate each term in the first sum, and \Cref{row-correlation} to bound each term in the second sum:
    $$
        \le 2^{312a^3-n} \sum_{j = 1}^{2^n} \|\mathbf{1}_{E_j} g\|_2^2 + 2^{862a^3-3 n}\sum_{j=1}^{2^n}\sum_{j' = 1}^{2^n} \|\mathbf{1}_{E_j} g\|_2 \|\mathbf{1}_{E_{j'}}g\|_2\,.
    $$
    By Cauchy-Schwarz in the second two sums, this is at most
    $$
        2^{862a^3} (2^{-n} + 2^{n}2^{-3 n}) \sum_{j = 1}^n \|\mathbf{1}_{E_j} g\|_2^2\,,
    $$
    and by disjointedness of the sets $E_j$, this is at most
    $$
        2^{863a^3 - n} \|g\|_2^2\,.
    $$
    Taking adjoints and square roots, it follows that for all $f$
    \begin{equation}
        \label{eq-forest-bound-1}
        \left\|\sum_{\fu \in \fU} \sum_{\fp \in \fT(\fu)} T_{\fp} f\right\|_2 \le 2^{432a^3-\frac{n}{2}} \|f\|_2\,.
    \end{equation}
    On the other hand, we have by disjointedness of the sets $E_j$
    from \Cref{disjoint-row-support}
    $$
        \left\|\sum_{\fu \in \fU} \sum_{\fp \in \fT(\fu)} T_{\fp} f\right\|_2^2 = \left\|\sum_{j=1}^{2^n} \mathbf{1}_{E_j} T_{\mathfrak{R}_{j}} f\right\|_2^2 = \sum_{j = 1}^{2^n} \|\mathbf{1}_{E_j} T_{\mathfrak{R}_{j}} f\|_2^2\,.
    $$
    If $|f| \le \mathbf{1}_F$ then we obtain from \Cref{row-bound} and taking square roots that
    $$
        \le 2^{257a^3} \dens_2(\bigcup_{\fu\in \fU}\fT(\fu))^{\frac{1}{2}} 2^{-\frac{n}{2}} (\sum_{j = 1}^{2^n} \|f\|_2^2)^{\frac{1}{2}}
    $$
    \begin{equation}
        \label{eq-forest-bound-2}
        = 2^{257a^3} \dens_2(\bigcup_{\fu\in \fU}\fT(\fu))^{\frac{1}{2}} \|f\|_2\,.
    \end{equation}
    \Cref{forest-operator} follows by taking the product of the $(2 - \frac{2}{q})$-th power of \eqref{eq-forest-bound-1} and the $(\frac{2}{q} - 1)$-st power of \eqref{eq-forest-bound-2}.
\end{proof}

\chapter{Proof of the H\"older cancellative condition}
\label{liphoel}

We need the following auxiliary lemma.
Recall that $\tau = 1/a$.

\begin{lemma}[Lipschitz Holder approximation]
    \label{Lipschitz-Holder-approximation}
    Let $z\in X$ and $R>0$. Let $\varphi: X \to \mathbb{C}$ be a function supported in the ball
    $B:=B(z,R)$ with finite norm $\|\varphi\|_{C^\tau(B)}$. Let $0<t \leq 1$. There exists a function $\tilde \varphi : X \to \mathbb{C}$, supported in $B(z,2R)$, such that for every $x\in X$
    \begin{equation}\label{eq-firstt}
        |\varphi(x) - \tilde \varphi(x)| \leq t^{\tau} \|\varphi\|_{C^\tau(B)}
    \end{equation}and
   \begin{equation}\label{eq-secondt}
       \|\tilde \varphi\|_{\Lip(B(z,2R))} \leq 2^{4a}t^{-1-a} \|\varphi\|_{C^{\tau}(B)}\, .
   \end{equation}
\end{lemma}


\begin{proof}
   Define for $x,y\in X$ the Lipschitz and thus measurable function
     \begin{equation}
           L(x,y) := \max\{0, 1 - \frac{\rho(x,y)}{tR}\}\, .
    \end{equation}
We have that $L(x,y)\neq 0$ implies
\begin{equation}\label{eql01}
    y\in B(x, tR)\, .
\end{equation}
We have for $y\in B(x, 2^{-1}tR)$ that
\begin{equation}\label{eql30}
           |L(x,y)|\ge 2^{-1} \ .
    \end{equation}
Hence
\begin{equation}
        \int L(x,y) \, \mathrm{d}\mu(y)\ge 2^{-1}\mu(B(x, 2^{-1}Rt))\, .
    \end{equation}
 Let $n$ be the smallest integer so that
 \begin{equation}\label{2nt1}
     2^nt\ge 1\, .
 \end{equation} Iterating $n+2$ times the doubling condition \eqref{doublingx}, we obtain
      \begin{equation}\label{eql32}
        \int L(x,y) \, \mathrm{d}\mu(y)\ge 2^{-1-a(n+2)}\mu(B(x, 2R))\, .
    \end{equation}

Now define
    $$
        \tilde \varphi(x) := \left(\int L(x,y) \, \mathrm{d}\mu(y)\right)^{-1}\int L(x,y) \varphi(y) \, \mathrm{d}\mu(y)\, .
    $$
Using that $\varphi$ is supported in $B(z,R)$ and
\eqref{eql01}, we have that $\tilde{\varphi}$ is supported in $B(z,2R)$.

We prove \eqref{eq-firstt}.
 For any $x\in X$, using
    that $L$ is nonnegative,
    \begin{equation}\label{eql1}
    \left(\int L(x,y) \, \mathrm{d}\mu(y)\right)
        |\varphi(x) - \tilde \varphi(x)|
    \end{equation}
 \begin{equation}\label{eql2}
 = \left| \int L(x,y)(\varphi(x) - \varphi(y)) \, \mathrm{d}\mu(y)\right|\, .
    \end{equation}
Using \eqref{eql01}, we estimate the last display by
 \begin{equation}\label{eql3}
         \le \int_{B(x, tR)} L(x,y)|\varphi(x) - \varphi(y)| \, \mathrm{d}\mu(y)\, .\end{equation}
  Using the definition of $\|\varphi\|_{C^\tau(B)}$, we estimate the last display further by
        \begin{equation}\label{eql4}
         \le \left(\int_{B(x, tR)} L(x,y)
          \rho(x,y)^\tau \, \mathrm{d}\mu(y) \right)\|\varphi\|_{C^\tau(B)}R^{-\tau}\, .
    \end{equation}
  Using the condition on the domain of integration to estimate $\rho(x,y)$ by $tR$ and then expanding the domain by positivity of the integrand, we estimate this further by

    \begin{equation}\label{eql5}
         \le \left(\int L(x,y) \, \mathrm{d}\mu(y)\right)
         \|\varphi\|_{C^\tau(B)} t^{\tau} \, .
    \end{equation}
 Dividing the string of inequalities from \eqref{eql1} to
\eqref{eql5} by the positive integral of $L$ proves \eqref{eq-firstt}.


We turn to \eqref{eq-secondt}. For every $x\in X$, we have
\begin{equation}
    \left|\int L(x,y) \, \mathrm{d}\mu(y)\right||\tilde{\varphi}(x)|
    =\left|\int L(x,y) {\varphi}(y)\, \mathrm{d}\mu(y)\right|
\end{equation}
 \begin{equation}
    \le \left|\int L(x,y) \, \mathrm{d}\mu(y)\right| \sup_{x'\in X}
    |{\varphi}(x')|\ .
\end{equation}
As $\varphi$ is supported on $B$, dividing by the integral of $L$, we obtain
\begin{equation}\label{eql42}
 |\tilde{\varphi}(x)|\le \sup_{x'\in B}
    |{\varphi}(x')|\le \|\varphi\|_{C^\tau(B)}\ .
\end{equation}
If $\rho(x,x')\ge R$, then we have by the triangle inequality
  \begin{equation}\label{eql52}
 R\frac{|\tilde{\varphi}(x') - \tilde \varphi(x)|}{\rho(x,x')} \le
 2\sup_{x''\in X} |\tilde{\varphi}(x'')|\le 2\|\varphi\|_{C^\tau(B)}\, .
\end{equation}
Now assume $\rho(x,x')< R$. For $y\in X$ we have by the triangle inequality and a two fold case distinction
for the maximum in the definition of $L$,
\begin{equation}\label{eql10}
   |L(x,y) - L(x',y)| \le \frac{\rho(x,x')}{tR}.
\end{equation}
We compute with \eqref{eql10}, first adding and subtracting a term in the integral,
\begin{equation}
    \left(\int L(x,y) \, \mathrm{d}\mu(y)\right)
    |\tilde{\varphi}(x') - \tilde \varphi(x)|=
\end{equation}
\begin{equation}
    \left|\int L(x,y) \tilde{\varphi}(x')
    -L(x,y) \tilde{\varphi}(x)
    +L(x',y) \tilde{\varphi}(x')-
     L(x',y) \tilde{\varphi}(x')
    \, \mathrm{d}\mu(y)\right|\,.
\end{equation}
Grouping the second and third and the first and fourth term, we obtain using the definition of $\tilde \varphi$ and Fubini,
\begin{equation}\label{eql21}
    \le \left| \int (L(x',y)-L(x,y)) \varphi(y) \, \mathrm{d}\mu(y)\right|
\end{equation}
\begin{equation}\label{eql22}
    + \left| \int L(x,y) \, \mathrm{d}\mu(y)-\int L(x',y) \, \mathrm{d}\mu(y)\right||\tilde{\varphi}(x')|
\end{equation}
\begin{equation}\label{eql23}
    \le 2 \int |L(x,y) -L(x',y)| \, \mathrm{d}\mu(y)
    \|\varphi\|_{C^\tau(B)}\, ,
\end{equation}
where in the last inequality we have used \eqref{eql42}.
Using further \eqref{eql10} and the support of $L$, we estimate the last display by
\begin{equation}\label{eql224}\le 2 \frac{\rho(x,x')} {tR}\mu(B(x,tR)\cup B(x',tR))
\|\varphi\|_{C^\tau(B)}\, .
    \end{equation}
  Using $\rho(x,x')<R$ and the triangle inequality, we estimate the last display by
\begin{equation}\label{eql225}\le 2
\frac{\rho(x,x')} {tR}
\mu(B(x,2R))
\|\varphi\|_{C^\tau(B)}\, .
    \end{equation}
Dividing by the integral over $L$ and using \eqref{eql32} and \eqref{2nt1}, we obtain
\begin{equation}\label{eql226}
 \frac {R |\tilde{\varphi}(x') - \tilde \varphi(x)|}{\rho(x,x')}
 \le 2^{2+a(n+2)}t^{-1}\|\varphi\|_{C^\tau(B)} \le
 2^{2+3a} t^{-1-a} \|\varphi\|_{C^\tau(B)}\, .
\end{equation}
Combining \eqref{eql52} and \eqref{eql226} using $a\ge 4$ and $t\le 1$ and
adding \eqref{eql42} proves \eqref{eq-secondt} and completes the proof
of \Cref{Lipschitz-Holder-approximation}.
\end{proof}


We turn to the proof of \Cref{Holder-van-der-Corput}.
Let $z\in X$ and $R>0$ and set $B=B(z,R)$. Let $\varphi$
be given as in \Cref{Holder-van-der-Corput}.
Set
\begin{equation}\label{eql69}
    t:=(1+d_B(\mfa,\mfb))^{-\frac{\tau}{2+a}}
\end{equation}
and define $\tilde{\varphi}$ as in \Cref{Lipschitz-Holder-approximation}. Let $\mfa$ and $\mfb$ be in $\Mf$.
Then
   \begin{equation}\label{eql60}
       \left|\int e(\mfa(x)-{\mfb(x)}) \varphi (x)\, \mathrm{d}\mu(x)\right|
   \end{equation}
      \begin{equation}\label{eql61}
   \le \left|\int e(\mfa(x)-{\mfb(x)}) \tilde{\varphi} (x)\, \mathrm{d}\mu(x)\right|
   \end{equation}
           \begin{equation}\label{eql62}
     + \left|\int e(\mfa(x)-{\mfb(x)}) (\varphi (x)-\tilde{\varphi}(x))\, \mathrm{d}\mu(x)\right|
   \end{equation}
Using the cancellative condition \eqref{eq-vdc-cond} of $\Mf$ on the ball $B(z,2R)$, the term \eqref{eql61} is bounded above by
 \begin{equation}\label{eql63}
       2^a \mu(B(z,2R)) \|\tilde{\varphi}\|_{\Lip(B(z,2R))} (1 + d_{B(z,2R)}(\mfa,\mfb))^{-\tau} \, .
 \end{equation}



Using the doubling condition \eqref{doublingx},
the inequality \eqref{eq-secondt}, and the estimate
$d_B\le d_{B(z,2R)}$ from the definition,
we estimate \eqref{eql63} from above by
\begin{equation}\label{eql64}
       2^{6a}t^{-1-a} \mu(B) \|{\varphi}\|_{C^\tau(B)}
       (1 + d_{B}(\mfa,\mfb))^{-\tau} \, .
 \end{equation}

The term \eqref{eql62} we estimate using
\eqref{eq-firstt} and that
$\mfa$ and $\mfb$ are real and thus $e(\mfa)$ and
$e(\mfb)$ bounded in absolute value by $1$.
We obtain for \eqref{eql62} with \eqref{doublingx}
the upper bound
  \begin{equation}\label{eql65}
      \mu(B(z,2R)) t^{\tau} \|\varphi\|_{C^\tau(B)}
      \le 2^a \mu(B) t^{\tau} \|\varphi\|_{C^\tau(B)}
      \,.
 \end{equation}
Using the definition \eqref{eql69} of $t$ and adding
\eqref{eql64} and \eqref{eql65} estimates
\eqref{eql60} from above by
\begin{equation}
       2^{6a} \mu(B) \|{\varphi}\|_{C^\tau(B)}
       (1 + d_{B}(\mfa,\mfb))^{-\frac{\tau}{2+a}}
       \end{equation}
\begin{equation} +
        2^a \mu(B) \|{\varphi}\|_{C^\tau(B)}
       (1 + d_{B}(\mfa,\mfb))^{-\frac{\tau^2}{2+a}}\, .
 \end{equation}
\begin{equation}\label{eql66}
      \le 2^{1+6a} \mu(B) \|{\varphi}\|_{C^\tau(B)}
       (1 + d_{B}(\mfa,\mfb))^{-\frac{\tau^2}{2+a}} \, ,
 \end{equation}
where we used $\tau\le 1$.
This completes the proof of \Cref{Holder-van-der-Corput}.


\chapter{Proof of Vitali covering and Hardy--Littlewood}
\label{sec-hlm}


We begin with a classical representation of the Lebesgue norm.
\begin{lemma}[layer cake representation]\label{layer-cake-representation}
Let $1\le p< \infty$. Then for any measurable function $u:X\to [0,\infty)$ on the measure space $X$
relative to the measure $\mu$
we have
\begin{equation}\label{eq-layercake}
    \|u\|_p^p=p\int_0^\infty \lambda^{p-1}\mu(\{x: u(x)\ge \lambda\})\, d\lambda\, .
\end{equation}
\end{lemma}
\begin{proof}
    The left-hand side of \eqref{eq-layercake} is by definition
\begin{equation}
    \int_X u(x)^p \, d\mu(x)\, .\end{equation}
    Writing $u(x)$ as an elementary integral in $\lambda$ and then using Fubini, we write for the last display
    \begin{equation}
    =\int_X \int _0^{u(x)}
    p \lambda^{p-1} d\lambda\, d\mu(x)
\end{equation}
\begin{equation}
 =p\int _0^{\infty}
    \lambda^{p-1} \mu(\{x: u(x)\ge \lambda\}) d\lambda\, .
\end{equation}
This proves the lemma.
\end{proof}

We turn to the proof of \Cref{Hardy-Littlewood}.
Let the collection $\mathcal{B}$ be given.
We first show \eqref{eq-besico}.



We recursively choose a finite sequence $B_i\in \mathcal{B}$
for $i\ge 0$ as follows. Assume $B_{i'}$
is already chosen for $0\le i'<i$.
If there exists a ball $B_{i}\in \mathcal{B}$ so that $B_{i}$
is disjoint from all $B_{i'}$
with $0\le i'<i$, then choose
such a ball $B_i=B(x_i,r_i)$ with maximal $r_i$.

If there is no such ball, stop the selection and set
$i'':=i$.

By disjointedness of the chosen balls and since $0 \le u$, we have
\begin{equation}
\sum_{0\le i<i''}\int_{B_i} u(x)\, d\mu(x) \le \int_X u(x)\, d\mu(x)\, .
\end{equation}
By \eqref{eq-ball-assumption}, we conclude
\begin{equation}\label{eqbes1}
\lambda \sum_{0\le i<i''}\mu(B_i)
\le \int_X u(x)\, d\mu(x)\, .
\end{equation}
Let $x\in \bigcup \mathcal{B}$.
Choose a ball $B'=B(x',r')\in \mathcal{B}$
such that $x\in B'$.
If $B'$ is one of the selected balls, then
\begin{equation}\label{3rone}
    x\in \bigcup _{0\le i< i''}B_i\subset \bigcup _{0\le i< i''}B(x_i,3r_i)\, .
\end{equation}
If $B'$ is not one of the selected balls, then as it is not selected at time $i''$, there is a selected ball $B_i$ with
$B'\cap B_i\neq \emptyset$.
Choose such $B_i$ with minimal index $i$. As $B'$ is therefore disjoint from all
balls $B_{i'}$ with $i'<i$ and
as it was not selected in place of $B_i$, we have $r_i\ge r'$.

Using a point $y$ in the intersection of $B_i$ and $B'$,
we conclude by the triangle inequality
\begin{equation}
   \rho(x_i,x')\le \rho(x_i,y)+\rho(x',y)\le r_i+r'\le 2r_i \, .
\end{equation}
By the triangle inequality again, we further conclude
\begin{equation}
   \rho(x_i,x)\le \rho(x_i,x')+\rho(x',x)\le 2r_i+r'\le 3r_i \, .
\end{equation}
It follows that
\begin{equation}\label{3rtwo}
    x\in \bigcup _{0\le i< i''}B(x_i,3r_i)\, .
\end{equation}
With \eqref{3rone} and \eqref{3rtwo}, we conclude
\begin{equation}
\bigcup \mathcal{B}\subset
\bigcup _{0\le i< i''}B(x_i,3r_i)\, .
\end{equation}
With the doubling property
\eqref{doublingx} applied twice, we conclude
\begin{equation}\label{eqbes2}
    \mu(\bigcup{\mathcal{B}})
    \le \sum _{0\le i< i''}\mu (B(x_i,3r_i))
    \le 2^{2a}\sum _{0\le i< i''}\mu (B_i)\, .
\end{equation}
With \eqref{eqbes1} and \eqref{eqbes2} we conclude
\eqref{eq-besico}.


We turn to the proof of \eqref{eq-hlm}. We first consider the case $p_1=1$ and recall $M_{\mathcal{B}}=M_{\mathcal{B},1}$.
We write for the $p_2$-th power of left-hand side of \eqref{eq-hlm}
with \Cref{layer-cake-representation}
and a change of variables
\begin{equation}
    \|M_{\mathcal{B}}u(x)\|_{p_2}^{p_2}
   =p_2\int _0^{\infty}
    \lambda^{p_2-1} \mu(\{x: M_{\mathcal{B}}u(x)\ge \lambda\}) d\lambda\,
\end{equation}
\begin{equation} \label{eqbesi11}
   =2^{p_2} p_2\int _0^{\infty}
    \lambda^{p_2-1} \mu(\{x: M_{\mathcal{B}}u(x)\ge 2\lambda\}) d\lambda\, .
\end{equation}
Fix $\lambda\ge 0$ and let $x\in X$ satisfy $M_{\mathcal{B}}u(x)\ge 2\lambda$. By definition of $M_{\mathcal{B}}$, there is a ball
$B'\in \mathcal{B}$ such that
$x\in B'$ and
\begin{equation}\label{eqbesi10}
\int_{B'} u(y)\, d\mu(y)\ge 2\lambda \mu({B'}) \, .
\end{equation}
Define
$u_\lambda(y):=0$ if $|u(y)|<\lambda$ and $u_\lambda(y):=u(y)$ if $|u(y)|\ge \lambda$.
Then with \eqref{eqbesi10}
\begin{equation}
\int_{B'} u_\lambda (y)\, d\mu(y)
=\int_{B'} u (y)\, d\mu(y)-
\int_{B'} (u-u_\lambda) (y) d\mu(y)\,
\end{equation}
\begin{equation}
\ge 2\lambda \mu({B'})-
\int_{B'} (u-u_\lambda) (y) d\mu(y)\, .
\end{equation}
As $(u-u_\lambda)(y)\le \lambda$
by definition, we can estimate the last display by
\begin{equation}
\ge 2\lambda \mu({B'})-
\int_{B'} \lambda \, d\mu(y)
=\lambda \mu({B'})\, .
\end{equation}
Hence $x$ is contained in
$\bigcup(\mathcal{B}_\lambda)$,
where $\mathcal{B}_\lambda$
is the collection of balls $B''$ in $\mathcal{B}$ such that
\begin{equation}
    \int_{B''} u_\lambda (y)\, d\mu(y)\ge \lambda \mu(B'')\, .
\end{equation}
We have thus seen
\begin{equation}
    \{x: M_{\mathcal{B}}u(x)\ge 2\lambda\}\subset
    \bigcup \mathcal{B}_\lambda
\, .
\end{equation}
Applying \eqref{eq-besico} to the collection $\mathcal{B}_\lambda$
gives
\begin{equation}
    \lambda \mu(\{x: M_{\mathcal{B}}u(x)\ge 2\lambda\})\le
   2^{2a}
    \int u_\lambda (x)\, dx\, .
\end{equation}
With \Cref{layer-cake-representation},
\begin{equation}\label{eqbesi12}
    \lambda \mu(\{x: M_{\mathcal{B}}u(x)\ge 2\lambda\})\le
   2^{2a}
    \int_0^\infty \mu (\{x: |u_\lambda (x)|\ge \lambda'\})\, d\lambda'\, .
\end{equation}
By definition of $h_\lambda$, making a case distinction between $\lambda\ge \lambda'$ and $\lambda <\lambda'$, we see that
\begin{equation}\label{eqbesi13}
   \mu (\{x: |u_\lambda (x)|\ge \lambda'\})
   \le
   \mu (\{x: |u (x)|\ge \max(\lambda,\lambda')\})\, .
\end{equation}
We obtain with \eqref{eqbesi11},
\eqref{eqbesi12}, and \eqref{eqbesi13}
\begin{equation}
    \|M_{\mathcal{B}}u(x)\|_{p_2}^{p_2}
 \end{equation}
 \begin{equation}
   \le 2^{p_2+2a} p_2
   \int_0^\infty \lambda^{p_2-2}
   \int_0^\infty
   \mu (\{x: |u (x)|\ge \max(\lambda,\lambda')\})
   \, d\lambda'd\lambda\, .
\end{equation}
We split the integral into $\lambda\ge \lambda'$ and $\lambda<\lambda'$ and resolve the
maximum correspondingly.
We have for $\lambda\ge \lambda'$
with \Cref{layer-cake-representation}
\begin{equation}
    \int_0^\infty \lambda^{p_2-2}
   \int_0^\lambda
   \mu (\{x: |u (x)|\ge \lambda\})
   \, d\lambda'd\lambda
\end{equation}
\begin{equation}
   =\int_0^\infty \lambda^{p_2-1}
     \mu (\{x: |u (x)|\ge \lambda\})
d\lambda.
\end{equation}
\begin{equation}\label{eqbesi14}
   =p_2^{-1} \|u\|_{p_2}^{p_2}\, .
\end{equation}
We have for $\lambda< \lambda'$
with Fubini and \Cref{layer-cake-representation}
\begin{equation}
    \int_0^\infty \lambda^{p_2-2}
   \int_\lambda^\infty
   \mu (\{x: |u(x)|\ge \lambda'\})
   \, d\lambda'd\lambda.
\end{equation}
\begin{equation}
   =\int_0^\infty \int_0^{\lambda'}\lambda^{p_2-2}
     \mu (\{x: |u (x)|\ge \lambda'\})
d\lambda d\lambda'.
\end{equation}
\begin{equation}
   =(p_2-1)^{-1}\int_0^\infty (\lambda')^{p_2-1}
     \mu (\{x: |u(x)|\ge \lambda'\})
d\lambda'.
\end{equation}
\begin{equation}\label{eqbesi15}
   =(p_2-1)^{-1} p_2^{-1}\|u\|_{p_2}^{p_2}\, .
\end{equation}
Adding the two estimates
\eqref{eqbesi14} and \eqref{eqbesi15} gives
\begin{equation}
    \|M_{\mathcal{B}}u(x)\|_{p_2}^{p_2}
   \le 2^{p_2+2a} (1+(p_2-1)^{-1})\|u\|_{p_2}^{p_2}
   = 2^{p_2+2a} p_2(p_2-1)^{-1}\|u\|_{p_2}^{p_2}
   \, .
   \end{equation}
With $a\ge 1$ and $p_2>1$, taking the $p_2$-th root, we obtain \eqref{eq-hlm}.
We turn to the case of general
$1\le p_1<p_2$.
We have
\begin{equation}
    M_{\mathcal{B},p_1}u=(M_{\mathcal{B}} (|u|^{p_1}))^{\frac 1{p_1}}\, .
\end{equation}
Applying the special case of \eqref{eq-hlm} for $M_{\mathcal{B}}$ gives
\begin{equation}
    \|M_{\mathcal{B},p_1}u\|_{p_2}=
    \|M_{\mathcal{B}} (|u|^{p_1})\|_{p_2/p_1}^{\frac 1{p_1}}
\end{equation}
\begin{equation}
    \le 2^{2a} (p_2/p_1) (p_2/p_1-1)^{-1}
    \|(|u|^{p_1})\|_{p_2/p_1}^{\frac 1{p_1}}
    =2^{2a} p_2(p_2-p_1)^{-1}\|u\|_{p_2}\, .
\end{equation}
This proves \eqref{eq-hlm} in general.

Now we construct the operator $M$ satisfying \eqref{eq-ball-av} and \eqref{eq-hlm-2}.

\begin{lemma}[covering separable space]
    \label{covering-separable-space}
    For each $r > 0$, there exists a countable collection $C(r) \subset X$ of points such that
    $$
        X \subset \bigcup_{c \in C(r)} B(c, r)\,.
    $$
\end{lemma}

\begin{proof}
    It clearly suffices to construct finite collections $C(r,k)$ such that
    $$
        B(o, r2^k) \subset \bigcup_{c \in C(r,k)} B(c,r)\,,
    $$
    since then the collection $C(r) = \bigcup_{k \in \mathbb{N}} C(r,k)$ has the desired property.

    Suppose that $Y \subset B(o, r2^k)$ is a collection of points such that for all $y, y' \in Y$ with $y \ne y'$, we have $\rho(y,y') \ge r$. Then the balls $B(y, r/2)$ are pairwise disjoint and contained in $B(o, r2^{k+1})$. If $y \in B(o, r)$, then $B(o, r2^{k+1}) \subset B(y, r2^{k+2})$. Thus, by the doubling property \eqref{doublingx},
    $$
        \mu(B(y, \frac{r}{2})) \ge 2^{-(k+2)a} \mu(B(o, r2^{k+1}))\,.
    $$
    Thus, we have
    $$
        \mu(B(o, r2^{k+1})) \ge \sum_{y \in Y} \mu(B(y, \frac{r}{2})) \ge |Y| 2^{-(k+2)a} \mu(B(o, r2^{k+1}))\,.
    $$
    We conclude that $|Y| \le 2^{(k+2)a}$. In particular, there exists a set $Y$ of maximal cardinality. Define $C(r,k)$ to be such a set.

    If $x \in B(o, r2^k)$ and $x \notin C(r,k)$, then there must exist $y \in C(r,k)$ with $\rho(x,y) < r$. Thus $C(r,k)$ has the desired property.
\end{proof}

For each $k \in \mathbb{N}$ we choose a countable set $C(2^k)$ as in the lemma.
Define
$$
    \mathcal{B}_\infty = \{B(c, 2^k) \ : \ c \in C(2^k), k \in \mathbb{N}\}\,.
$$
By \Cref{covering-separable-space}, this is a countable collection of balls. We choose an enumeration $\mathcal{B}_\infty = \{B_1, \dotsc\}$ and define
$$
    \mathcal{B}_n = \{B_1, \dotsc, B_n\}\,.
$$
We define
$$
    Mw := 2^{2a}\sup_{n \in \mathbb{N}} M_{\mathcal{B}_n}w\,.
$$
This function is measurable for each measurable $w$, since it is a countable supremum of measurable functions. Estimate \eqref{eq-hlm-2} follows immediately from \eqref{eq-hlm} and the monotone convergence theorem.

It remains to show \eqref{eq-ball-av}. Let $B = B(x, r) \subset X$. Let $k$ be the smallest integer such that $2^k \ge r$, in particular we have $2^k < 2r$. By definition of $C(2^k)$, there exists $c \in C(2^k)$ with $x \in B(c, 2^k)$. By the triangle inequality, we have $B(c, 2^k) \subset B(x, 4r)$, and hence by the doubling property \eqref{doublingx}
$$
    \mu(B(c, 2^k)) \le 2^{2a} \mu(B(x,r))\,.
$$
It follows that for each $z \in B(x,r)$
\begin{align*}
    \frac{1}{\mu(B(x,r))}\int_{B(x,r)} |w(y)| \, \mathrm{d}\mu(y) &\le \frac{2^{2a}}{\mu(B(c,2^k))}\int_{B(c,2^k)} |w(y)| \, \mathrm{d}\mu(y) \\
    &\le Mw(z)\,.
\end{align*}
This completes the proof.


\chapter{Proof of The Classical Carleson Theorem}



The convergence of partial Fourier sums is proved in
\Cref{10classical} in two steps. In the first step,
we establish convergence on a suitable dense subclass of functions. We choose smooth functions as subclass, the convergence is stated in \Cref{convergence-for-smooth} and proved in \Cref{10smooth}.
In the second step, one controls the relevant error of approximating a general function by a function in
the subclass. This is stated in \Cref{control-approximation-effect} and proved
in \Cref{10difference}.
The proof relies on a bound on the real Carleson maximal operator stated in \Cref{real-Carleson} and proved in \Cref{10carleson}.
This latter proof refers to the main Carleson \Cref{metric-space-Carleson}. Two assumptions in \Cref{metric-space-Carleson} require more work. The boundedness of the nontangential maximal operator $T^*$ defined in \eqref{def-tang-unm-op} is established in \Cref{nontangential-Hilbert} using $L^2$ and weak $L^1$ bounds for the Hilbert transform, Lemmas
\ref{Hilbert-strong-2-2} and \ref{Hilbert-weak-1-1}. These lemmas are proved in Subsections \ref{subsec-cotlar},
\ref{10hilbert} and \ref{subsec-CZD}.
The cancellative property is verified by \Cref{van-der-Corput}, which is proved in \Cref{10vandercorput}.
Several further auxiliary lemmas are stated
and proved in Subsection
\ref{10classical}, the proof of one of these auxiliary lemmas, \Cref{spectral-projection-bound}, is done in \Cref{10projection}.

All subsections past \Cref{10classical} are mutually independent.

 Subsections \ref{subsec-cotlar} uses bounds for the Hardy--Littlewood maximal function on the real line. There may be a better path through Lean than we choose here.
 We refer to \Cref{Hardy-Littlewood}, the assumptions of it,
 namely that the real line fits into the setting of \Cref{overviewsection},
 is done in \Cref{10carleson}.



\section{The classical Carleson theorem}
\label{10classical}

Let a uniformly continuous $2\pi$-periodic function $f:\R\to \mathbb{C}$ and $0<\epsilon<1$ be given.
Let
\begin{equation}
    C_{a,q} := \frac{2^{450a^3}}{(q-1)^5}
\end{equation}
denote the constant from \Cref{metric-space-Carleson}.
Define
\begin{equation}
    \epsilon' := \frac \epsilon {4 (C_{4,2} \cdot (8 / (\pi\epsilon))^{\frac 1 2} + \pi)}.
\end{equation}
By uniform continuity of $f$, there is a $0<\delta<\pi$
such that for all $x,x' \in \R$ with $|x-x'|\le \delta$
we have
\begin{equation}\label{uniconbound}
|f(x)-f(x')|\le \epsilon' \, .
\end{equation}
Define
\begin{equation}\label{def-fzero}
f_0:=f \ast \phi_\delta,
\end{equation}
where $\phi_\delta$ is a nonnegative smooth bump function with $\supp (\phi_\delta) \subset (-\delta, \delta)$ and $\int _\R \phi_\delta (x) \, dx = 1$.

\begin{lemma}[smooth approximation]
    \label{smooth-approximation}
    \leanok
    \lean{}
    The function $f_0$ is $2\pi$-periodic.
    The function $f_0$ is smooth (and therefore measurable).
    The function $f_0$ satisfies for all $x\in \R$:
    \begin{equation}\label{eq-ffzero}
    |f(x)-f_0(x)|\le \epsilon' \, ,
    \end{equation}
\end{lemma}

\begin{proof}
    \leanok
    Most of this is part of the Lean library.
\end{proof}

We prove in \Cref{10smooth}:
\begin{lemma}[convergence for smooth]
    \label{convergence-for-smooth}
    \leanok
    \lean{}
    \uses{convergence-for-twice-contdiff}
    There exists some $N_0 \in \N$ such that for all $N>N_0$ and $x\in [0,2\pi]$ we have
    \begin{equation}
        |S_N f_0 (x)- f_0(x)|\le \frac \epsilon 4\, .
    \end{equation}
\end{lemma}

We prove in \Cref{10difference}:
\begin{lemma}[control approximation effect]
    \label{control-approximation-effect}
    \leanok
    \lean{}
    \uses{real-Carleson}
    There is a set $E \subset \R$ with Lebesgue measure
    $|E|\le \epsilon$ such that for all
    \begin{equation}
        x\in [0,2\pi)\setminus E
    \end{equation}
   we have
   \begin{equation}
    \label{eq-max-partial-sum-diff}
    \sup_{N\ge 0} |S_Nf(x)-S_Nf_0(x)| \le \frac \epsilon 4\,.
    \end{equation}
\end{lemma}

We are now ready to prove classical Carleson:
\begin{proof} [Proof of \Cref{classical-Carleson}]
\proves{classical-Carleson}
\leanok
Let $N_0$ be as in \Cref{convergence-for-smooth}.
For every
\begin{equation}
x\in [0, 2\pi) \setminus E\, ,
\end{equation}
and every $N>N_0$ we have by the triangle inequality
\begin{equation*}
    |f(x)-S_Nf(x)|
    \end{equation*}
    \begin{equation}\label{epsilonthird}
    \le |f(x)-f_0(x)|+ |f_0(x)-S_Nf_0(x)|+|S_Nf_0(x)-S_N f(x)|\, .
\end{equation}
Using \Cref{smooth-approximation,convergence-for-smooth,control-approximation-effect}, we estimate \eqref{epsilonthird} by
\begin{equation}
    \le \epsilon' +\frac \epsilon 4 +\frac \epsilon 4\le \epsilon\, .
\end{equation}
This shows \eqref{aeconv} for the given $E$ and $N_0$.
\end{proof}

Let $\kappa:\R\to \R$ be the function defined by
$\kappa(0)=0$ and for $0<|x|<1$
\begin{equation}\label{eq-hilker}
\kappa(x)=\frac { 1-|x|}{1-e^{ix}}\,
\end{equation}
and for $|x|\ge 1$
\begin{equation}\label{eq-hilker1}
\kappa(x)=0\, .
\end{equation}
Note that this function is continuous at every point $x$ with $|x|>0$.

The proof of \Cref{control-approximation-effect} will
use the following \Cref{real-Carleson}, which itself is proven
 in \Cref{10carleson} as an application of
 \Cref{metric-space-Carleson}.
\begin{lemma}[real Carleson]\label{real-Carleson}
\leanok
\lean{}
\uses{metric-space-Carleson,real-line-metric,real-line-measure,real-line-doubling,oscillation-control,frequency-monotone,frequency-ball-doubling,frequency-ball-growth,integer-ball-cover,real-van-der-Corput,nontangential-Hilbert}
    Let $F,G$ be Borel subsets of $\R$ with finite measure. Let $f$ be a bounded measurable function on $\R$ with $|f|\le \mathbf{1}_F$. Then
\begin{equation}
    \left|\int _G Tf(x) \, dx\right| \le C_{4,2} |F|^{\frac 12} |G|^{\frac 12} \, ,
\end{equation}
where
\begin{equation}
    \label{define-T-carleson}
    T f(x)=\sup_{n\in \mathbb{Z}}
    \sup_{r>0}\left|\int_{r<|x-y|<1} f(y)\kappa(x-y) e^{iny}\, dy\right|\, .
\end{equation}
\end{lemma}


One of the main assumption of \Cref{metric-space-Carleson}, concerning the operator $T_*$ defined in \eqref{def-tang-unm-op}, is verified by the following lemma, which is proved in \Cref{subsec-cotlar}.


\begin{lemma}[nontangential Hilbert]\label{nontangential-Hilbert}
\uses{simple-nontangential-Hilbert}
    For every bounded measurable function $g$ with bounded support we have
\begin{equation}\label{concretetstarbound}
    \|T_*g\|_2\le 2^{43}\|g\|_2,
\end{equation}
where
\begin{equation}\label{concretetstar}
    T_* g(x):=\sup_{0<r_1<r_2<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_1<|x'-y|<r_2}
g(y) \kappa(x'-y)\, dy\right|\, .
\end{equation}
\end{lemma}
The proof of \Cref{nontangential-Hilbert} relies on the next two auxiliary Lemmas.

For $r\in (0,1)$, $x\in \mathbb{R}$ and a bounded, measurable function $g$ on $\mathbb{R}$ with bounded support, we define
\begin{equation}
\label{def-H_r}
H_r g(x):= \int_{r<|x-y|<1}
g(y) \kappa(x-y)\, dy.
\end{equation}

The following Lemma is proved in \Cref{10hilbert}


\begin{lemma}[Hilbert strong 2 2]
    \label{Hilbert-strong-2-2}
    \uses{modulated-averaged-projection,integrable-bump-convolution,dirichlet-approximation}
    Let $0<r<1$. Let $f$ be a bounded, measurable function on $\mathbb{R}$ with bounded support. Then
    \begin{equation}
        \label{eq-Hr-L2-bound}
        \|H_rf\|_{2}\leq 2^{13} \|f\|_2.
    \end{equation}
\end{lemma}

The following Lemma is proved in \Cref{subsec-CZD}

\begin{lemma}[Hilbert weak 1 1]
    \label{Hilbert-weak-1-1}
    \uses{Hilbert-strong-2-2,Hilbert-kernel-bound,Hilbert-kernel-regularity,Calderon-Zygmund-decomposition}
    Let $f$ be a bounded measurable function on $\mathbb{R}$ with bounded support. Let $\alpha>0$. Then for all $r\in (0, 1)$, we have
    \begin{equation}
        \label{eq-weak-1-1}
        \mu\left(\{x\in \mathbb{R}: |H_r f(x)|>\alpha\}\right)\leq \frac{2^{19}}{\alpha} \int |f(y)|\, dy.
    \end{equation}
\end{lemma}

The next lemma will be used to verify that the collection $\Mf$ of modulation functions in our application of \Cref{metric-space-Carleson} satisfies the condition \eqref{eq-vdc-cond}.
It is proved in \Cref{10vandercorput}.

\begin{lemma}[van der Corput]
\label{van-der-Corput}
    Let $\alpha<\beta$ be real numbers. Let $g:\R\to \C$ be a measurable function and assume
    \begin{equation}
        \|g\|_{Lip(\alpha,\beta)}:=\sup_{\alpha\le x\le \beta}|g(x)|+|\beta-\alpha|
        \sup_{\alpha\le x<y\le \beta} \frac {|g(y)-g(x)|}{|y-x|}<\infty\, .
    \end{equation}
    Then for any $0\le \alpha<\beta\le 2\pi$ we have
    \begin{equation}
        \int _{\alpha}^{\beta} g(x) e^{-inx}\, dx\le 2\pi |\beta-\alpha|\|g\|_{Lip(\alpha,\beta)}(1+|n||\beta-\alpha|)^{-1}\, .
    \end{equation}

\end{lemma}


We close this section with six lemmas that are used
across the following subsections.

\begin{lemma}[mean zero oscillation]
\label{mean-zero-oscillation}
Let $n\in \mathbb{Z}$ with $n\neq 0$, then
\begin{equation}
\int_0^{2\pi} e^{inx}\, dx=0\,.
\end{equation}
\end{lemma}
\begin{proof}
We have
\begin{equation*}
\int_0^{2\pi} e^{inx}\, dx=\left[ \frac 1{in}e^{inx}\right]_0^{2\pi}=\frac 1{in}(e^{2\pi i n}-e^{2\pi i 0})=\frac 1{in}(1-1)=0\, . \qedhere
\end{equation*}

\end{proof}

\begin{lemma}[Dirichlet kernel]
\label{dirichlet-kernel}
\leanok
\lean{}
We have for every $2\pi$-periodic bounded measurable $f$ and every $N\ge 0$
\begin{equation}
    S_Nf(x)=\frac 1{2\pi}\int_{0}^{2\pi}f(y) K_N(x-y)\, dy
\end{equation}
where $K_N$ is the $2\pi$-periodic continuous function of
$\R$ given by
\begin{equation}\label{eqksumexp}
\sum_{n=-N}^N e^{in x'}\, .
\end{equation}
We have for $e^{ix'}\neq 1$ that
\begin{equation}\label{eqksumhil}
    K_N(x')=\frac{e^{iNx'}}{1-e^{-ix'}}
      +\frac {e^{-iNx'}}{1-e^{ix'}} \, .
\end{equation}


\end{lemma}


\begin{proof}
\leanok
We have by definitions and interchanging sum and integral
   \begin{equation*}
        S_Nf(x)=\sum_{n=-N}^N \widehat{f}_n e^{inx}
    \end{equation*}
       \begin{equation*}
    =\sum_{n=-N}^N \frac 1{2\pi}\int_{0}^{2\pi}
    f(x) e^{in(x-y)}\, dy
    \end{equation*}
 \begin{equation}\label{eq-expsum}
     =\frac 1{2\pi}\int_{0}^{2\pi}
    f(y) \sum_{n=-N}^N e^{in(x-y)}\, dy\, .
 \end{equation}
This proves the first statement of the lemma.
By a telescoping sum, we have for every $x'\in \R$
\begin{equation}
    \left( e^{\frac 12 ix'}-e^{-\frac 12 ix'}\right) \sum_{n=-N}^N e^{inx'}= e^{(N+\frac 12) ix'}-e^{-(N+\frac 12) ix'}\, .
\end{equation}
If $e^{ix'}\neq 1$, the first factor on the left-hand side is not $0$ and we may divide by this factor to obtain
\begin{equation}
      \sum_{n=-N}^N e^{inx'}= \frac{e^{i(N+\frac 1 2)x'}}{e^{\frac 12 ix'}-e^{-\frac 12ix'}}
      -\frac{e^{-i(N+\frac 1 2)x'}}{e^{\frac 12 ix'}-e^{-\frac 12ix'}}
       =\frac{e^{iNx'}}{1-e^{-ix'}}
      +\frac {e^{-iNx'}}{1-e^{ix'}}\, .
\end{equation}
This proves the second part of the lemma.
\end{proof}

\begin{lemma}[lower secant bound]
    \label{lower-secant-bound}
    \leanok
    \lean{lower_secant_bound'}
    Let $\eta>0$ and $-2\pi +\eta \le x\le 2\pi-\eta$ with $|x|\ge \eta$. Then
    \begin{equation}
        |1-e^{ix}|\ge \frac{2}{\pi} \eta
    \end{equation}
\end{lemma}
\begin{proof}
    \leanok
    We have
    $$
        |1 - e^{ix}| = \sqrt{(1 - \cos(x))^2 + \sin^2(x)} \ge |\sin(x)|\,.
    $$
    If $0 \le x \le \frac{\pi}{2}$, then we have from concavity of $\sin$ on $[0, \pi]$ and $\sin(0) = 0$ and $\sin(\frac{\pi}{2}) = 1$
    $$
        |\sin(x)| \ge \frac{2}{\pi} x \ge \frac{2}{\pi} \eta\,.
    $$
    When $x\in \frac{m\pi}{2} + [0, \frac{\pi}{2}]$ for $m \in \{-4, -3, -2, -1, 1, 2, 3\}$ one can argue similarly.
\end{proof}

The following lemma will be proved in \Cref{10projection}.

\begin{lemma}[spectral projection bound]
\label{spectral-projection-bound}
\uses{partial-sum-projection,partial-sum-selfadjoint}
    Let $f$ be a bounded $2\pi$-periodic measurable function. Then, for all $N\ge 0$
   \begin{equation}\label{snbound}
   \|S_Nf\|_{L^2[-\pi, \pi]} \le \|f\|_{L^2[-\pi, \pi]}.
   \end{equation}
\end{lemma}

\begin{lemma}[Hilbert kernel bound]
\label{Hilbert-kernel-bound}
\leanok
\lean{}
\uses{lower-secant-bound}
    For $x,y\in \R$ with $x\neq y$ we have
    \begin{equation}\label{eqcarl30}
        |\kappa(x-y)|\le 2^2(2|x-y|)^{-1}\, .
    \end{equation}
\end{lemma}
\begin{proof}
\leanok
    Fix $x\neq y$. If $\kappa(x-y)$ is zero, then \eqref{eqcarl30} is evident. Assume $\kappa(x-y)$ is not zero, then $0<|x-y|<1$.
    We have
\begin{equation}\label{eqcarl31}
|\kappa(x-y)|=\left|\frac {1-|x-y|}{1-e^{i(x-y)}}\right|\, .
\end{equation}
We estimate
with \Cref{lower-secant-bound}
\begin{equation}\label{eqcarl311}
|\kappa(x-y)|\le \frac {1}{|1-e^{i(x-y)}|}\le \frac 2{|x-y|}\, .
\end{equation}
This proves \eqref{eqcarl30} in the given case and completes the proof of the lemma.
\end{proof}

\begin{lemma}[Hilbert kernel regularity]
\label{Hilbert-kernel-regularity}
\leanok
\lean{}
\uses{lower-secant-bound}
    For $x,y,y'\in \R$ with $x\neq y,y'$ and
    \begin{equation}
        \label{eq-close-hoelder}
        2|y-y'|\le |x-y|\, ,
    \end{equation}
    we have
    \begin{equation}\label{eqcarl301}
        |\kappa(x-y) - \kappa(x-y')|\le 2^{8}\frac{1}{|x-y|} \frac{|y-y'|}{|x-y|}\, .
    \end{equation}
\end{lemma}

\begin{proof}
\leanok
    Upon replacing $y$ by $y-x$ and $y'$ by $y'-x$ on the left-hand side of \eqref{eq-close-hoelder}, we can assume that $x = 0$. Then the assumption \eqref{eq-close-hoelder} implies that $y$ and $y'$ have the same sign. Since $\kappa(y) = \bar \kappa(-y)$ we can assume that they are both positive. Then it follows from \eqref{eq-close-hoelder} that
    $$
        \frac{y}{2} \le y' \,.
    $$
    We distinguish four cases. If $y, y' \le 1$, then we have
    $$
        |\kappa(-y) - \kappa(-y')| = \left| \frac{1 - y}{1- e^{-iy}} - \frac{1 - y'}{1- e^{-iy'}}\right|
    $$
    and by the fundamental theorem of calculus
    $$
        = \left| \int_{y'}^{y} \frac{-1 + e^{-it} + i(1-t)e^{it}}{(1 - e^{-it})^2} \,dt \right|\,.
    $$
    Using $y' \ge \frac{y}{2}$ and \Cref{lower-secant-bound}, we bound this by
    $$
        \le |y - y'| \sup_{\frac{y}{2} \le t \le 1} \frac{3}{|1 - e^{-it}|^2} \le 3 |y-y'| (2 \frac{2}{y})^2 \le 2^{6} \frac{|y-y'|}{|y|^2}\,.
    $$
    If $y \le 1$ and $y' > 1$, then $\kappa(-y') = 0$ and we have from the first case
    $$
        |\kappa(-y) - \kappa(-y')| = |\kappa(-y) - \kappa(-1)| \le 2^{6} \frac{|y-1|}{|y|^2} \le 2^{6} \frac{|y-y'|}{|y|^2}\,.
    $$
    Similarly, if $y > 1$ and $y' \le 1$, then $\kappa(-y) = 0$ and we have from the first case
    $$
        |\kappa(-y) - \kappa(-y')| = |\kappa(-y') - \kappa(-1)| \le 2^{6} \frac{|y'-1|}{|y'|^2} \le 2^{6} \frac{|y-y'|}{|y'|^2}\,.
    $$
    Using again $y' \ge \frac{y}{2}$, we bound this by
    $$
        \le 2^{6} \frac{|y-y'|}{|y / 2|^2} = 2^{8} \frac{|y-y'|}{|y|^2}
    $$
    Finally, if $y, y' > 1$ then
    $$
        |\kappa(-y) - \kappa(-y')| = 0 \le 2^{8} \frac{|y-y'|}{|y|^2}\,.
    $$
\end{proof}






\section{Smooth functions.}
\label{10smooth}
\begin{lemma}
\label{fourier-coeff-derivative}
\leanok
\lean{}
Let $f:\R \to \C$ be $2\pi$-periodic and differentiable, and let $n \in \Z \setminus \{0\}$. Then
\begin{equation}
    \widehat{f}_n = \frac{1}{i n} \widehat{f'}_n.
\end{equation}
\end{lemma}
\begin{proof}
\leanok
This is part of the Lean library.
\end{proof}

\begin{lemma}
\label{convergence-of-coeffs-summable}
\leanok
\lean{}
Let $f:\R \to \C$ such that
\begin{equation}
    \sum_{n\in \Z} |\widehat{f}_n| < \infty.
\end{equation}
Then
\begin{equation}
    \sup_{x\in [0,2\pi]} |f(x) - S_Nf(x)| \rightarrow 0
\end{equation}
as $N \rightarrow \infty$.
\end{lemma}

\begin{proof}
\leanok
    This is part of the Lean library.
\end{proof}

\begin{lemma}
    \label{convergence-for-twice-contdiff}
    \uses{fourier-coeff-derivative,convergence-of-coeffs-summable}
    \leanok
    \lean{}
    Let $f:\R \to \C$ be $2\pi$-periodic and twice continuously differentiable. Then
    \begin{equation}
        \sup_{x\in [0,2\pi]} |f(x) - S_Nf(x)| \rightarrow 0
    \end{equation}
    as $N \rightarrow \infty$.
\end{lemma}
\begin{proof}
\leanok
By \Cref{convergence-of-coeffs-summable}, it suffices to show that the Fourier coefficients $\widehat{f}_n$ are summable.
Applying \Cref{fourier-coeff-derivative} twice and using the fact that $f''$ is continuous and thus bounded on $[0,2\pi]$ , we compute
\begin{equation*}
    \sum_{n\in \Z} |\widehat{f}_n| = |\widehat{f}_0| + \sum_{n\in \Z \setminus \{0\}} \frac {1}{n^2} |\widehat{f''}_n|
    \le |\widehat{f}_0| + \left(\sup_{x\in [0,2\pi]} |f(x)| \right) \cdot \sum_{n\in \Z \setminus \{0\}} \frac {1}{n^2}
    < \infty.
\end{equation*}
\end{proof}

\begin{proof}
\leanok
\proves{convergence-for-smooth}
    \Cref{convergence-for-smooth} now follows directly from the previous \Cref{convergence-for-twice-contdiff}.
\end{proof}

\section{Proof of Cotlar's Inequality}
\label{subsec-cotlar}




\begin{lemma}[estimate x shift]
\label{estimate-x-shift}
\uses{Hilbert-kernel-bound,Hilbert-kernel-regularity}
Let $0<r<1$ and $x\in \mathbb{R}$. Let $g$ be a bounded measurable function with bounded support on $\mathbb{R}$. Let $Mg$ be the Hardy--Littlewood function
defined in Proposition
\ref{Hardy-Littlewood}.
Then for all $x'$ with $|x-x'|<r$.
\begin{equation}\label{xx'difference}
\left|\int_{r<|x-y|<1}
g(y) \kappa(x-y)\, dy
-\int_{r<|x'-y|<1}
g(y) \kappa(x'-y)\, dy
\right|\le 2^{13}Mg(x)\, .
\end{equation}
\end{lemma}
\begin{proof}
\proves{estimate-x-shift}

First note that the
conditions $|x-y|<1$
and $|x'-y|<1$ may be removed as the factor containing $\kappa$
vanishes without these conditions.

We split the first integral in \eqref{xx'difference}
into the domains $r<|x-y|\le 2r$
and $2r<|x-y|$. The integral over the first domain we estimate
by $\eqref{firstxx'}$ below.
For the second domain, we
observe with $|x-x'|<r$ and the triangle inequality that $r<|x'-y|$. We therefore combine on this domain with the
corresponding part of the second integral in \eqref{xx'difference} and estimate that by $\eqref{secondxx'}$
below. The remaining part of the second integral in
\eqref{xx'difference} we estimate by $\eqref{thirdxx'}$.
Overall, we have estimated \eqref{xx'difference}
by


\begin{equation}
\label{firstxx'}
\int_{r<|x-y|\le 2r}
|g(y)| |\kappa(x-y)|\, dy
\end{equation}
\begin{equation}\label{secondxx'}
  + \left|\int_{2r<|x-y|}
g(y) (\kappa(x'-y)-\kappa(x-y))\, dy
\right|
\end{equation}
\begin{equation}
\label{thirdxx'}
  +\left|\int_{r<|x'-y|, r<|x-y|<2r}
|g(y) \kappa(x'-y)|\, dy
\right|
\end{equation}
Using the bound on $\kappa$ in \Cref{Hilbert-kernel-bound}, we estimate
\eqref{firstxx'} by
\begin{equation}
\label{firstxx'b}
 \frac 8 r\int_{|x-y|<2r}
|g(y)|\, dy\, .
\end{equation}
Using the definition of $Mg$, we estimate
\eqref{firstxx'b} by
\begin{equation}
\label{firstxx'c}
 \le 32{Mg(x)}\, .
\end{equation}
Similarly, in the domain of \eqref{thirdxx'}
we note by the triangle inequality
and assumption on $x'$ that $|x'-y|\le 3r$ and thus we estimate
\eqref{thirdxx'}
by
\begin{equation}
\label{thirdxx'b}
 \frac 8{r}\int_{|x'-y|<3r}
|g(y)| \, dy\le 48 Mg(x)
\end{equation}

We turn to the term \eqref{secondxx'}.
Let $\nu$ be the smallest integer
such that $2^\nu> 2/r$.
Using that the kernel vanishes unless $|x-y|<2$, we decompose and estimate
\eqref{secondxx'}
with the triangle inequality by
\begin{equation}\label{secondxx'b}
 \sum_{j=1}^\nu \int_{2^jr<|x-y|\le 2^{j+1}r}
|g(y)| |\kappa(x'-y)-\kappa(x-y)|\, dy\,.
\end{equation}
Using \Cref{Hilbert-kernel-regularity}, we estimate \eqref{secondxx'b}
by
\begin{equation*}
 2^{10}\sum_{j=1}^\nu \int_{2^jr<|x-y|\le 2^{j+1}r}
|g(y)| \frac{|x-x'|}{|x-y|^2}\, dy
\end{equation*}
\begin{equation*}
\le 2^{10}\sum_{j=1}^\nu \frac 1{2^{2j}r}\int_{2^jr<|x-y|\le 2^{j+1}r}
|g(y)| \, dy
\end{equation*}
\begin{equation}\label{secondxx'c}
\le 2^{10}\sum_{j=1}^\nu {2^{1-j}} Mg(x)\,.
\end{equation}
Using a geometric series, we estimate
\eqref{secondxx'c} by
\begin{equation}\label{secondxx'd}
\le 2^{11} Mg(x)\,.
\end{equation}
Summing the estimates
for \eqref{firstxx'},
\eqref{secondxx'}, and
\eqref{thirdxx'}
proves the lemma.
\end{proof}

Recall that
\begin{equation*}
    H_rg(x)=\int_{r<|x-y|<1} g(y) \kappa(x-y)\, dy\, .
\end{equation*}


\begin{lemma}[Cotlar control]
\label{Cotlar-control}
\uses{estimate-x-shift}
Let $0<r<r_1<1$ and $x\in \mathbb{R}$. Let $g$ be a bounded measurable function with bounded support on $\mathbb{R}$. Let $Mg$ be the Hardy--Littlewood function
defined in Proposition
\ref{Hardy-Littlewood}.
Then for all $x'\in \R$ with $|x'-x|<\frac {r_1}4$ we have
\begin{equation}\label{eq-cotlar-control}
\left|H_{r_1} g(x)
\right|\le
|H_{r}(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(x')|+
2^{15}Mg(x)\, .
\end{equation}
\end{lemma}

\begin{proof}
Let $x$ and $x'$ be given with $|x'-x|<\frac {r_1}4$.
By an application of \Cref{estimate-x-shift}, we estimate
the left-hand-side of
\eqref{eq-cotlar-control} by
\begin{equation}\label{eqcotlar0}
|H_{r_1}(g)(x')|+
2^{13}Mg(x)\,.
\end{equation}
We have
\begin{equation}
\label{eqcotlar-1}
H_{r_1}(g)(x')=
\int_{r_1<|x'-y|<1} g(y) \kappa(x'-y)\, dy\, .
\end{equation}
On the domain $r_1<|x'-y|$, we have $\frac {r_1}2<|x-y|$. Hence we may write
for \eqref{eqcotlar-1}
\begin{equation*}
H_{r_1}(g)(x')=\int_{r_1<|x'-y|<1} (g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(y) \kappa(x'-y)\, dy
\end{equation*}
\begin{equation}\label{eqcotlar1}
=H_{r_1}(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(x')\, .
\end{equation}
Combining the estimate \eqref{eqcotlar0} with the identification \eqref{eqcotlar1}, we obtain
\begin{equation}\label{eqcotlar5}
\left|H_{r_1} g(x)
\right|\le
|H_{r_1}(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(x')|+
2^{13}Mg(x)\, .
\end{equation}
We have

\begin{equation*}
(H_{r}-H_{r_1})(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(x')
\end{equation*}
\begin{equation}\label{eqcotlar2}
= \int_{ {r}<|x'-y|<r_1}
(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(y)k(x'-y)\, dy\, .
\end{equation}
Assume first $r\ge \frac {r_1} 4$.
Then we estimate \eqref{eqcotlar2} with
\Cref{Hilbert-kernel-bound} by
\begin{equation*}
\int_{\frac {r_1}4<|x'-y|<r_1}
|g(y)k(x'-y)|\, dy
\end{equation*}
\begin{equation}\label{eqcotlar3}
\le \frac {32}{r_1}\int_{|x'-y|<r_1}
|g(y)|\, dy \le 64 Mg(x')\, .
\end{equation}
Assume now $r\le \frac {r_1} 4$.
As $|x'-y|\le \frac{r_1}4$ implies
$|x-y|\le \frac {r_1} 2$, we see that
\eqref{eqcotlar2} equals
\begin{equation*}
 \int_{ {\frac {r_1} 4}<|x'-y|<r_1}
(g-g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})(y)k(x'-y)\, dy\, ,
\end{equation*}
which we again estimate as above by \eqref{eqcotlar3}.
In both cases, \eqref{eq-cotlar-control} follows by the triangle inequality from \eqref{eqcotlar5} and the estimate for
\eqref{eqcotlar2}.
\end{proof}

\begin{lemma}[Cotlar sets]
\label{Cotlar-sets}
\uses{Hilbert-weak-1-1}
Let $0<r<r_1<1$ and $x\in \mathbb{R}$. Let $g$ be a bounded measurable function with bounded support on $\mathbb{R}$. Let $Mg$ be the Hardy--Littlewood maximal function
defined in Proposition
\ref{Hardy-Littlewood}.
Let $x\in \R$.
Then the measure $|F_1|$ of the set $F_1$ of all $x'\in
[x-\frac{r_1}4,x+\frac{r_1}4]$ such that
\begin{equation}
\label{first-cotlar-exception}
    |H_{r}(g)(x')|>4M(H_{r}g)(x)
\end{equation}
is less than or equal to $r_1/8$.
Moreover, the measure $|F_2|$ of the set $F_2$ of all $x'\in
[x-\frac{r_1}4,x+\frac{r_1}4]$ such that
\begin{equation}
\label{second-cotlar-exception}
    |H_{r}(g\mathbf{1}_{[x-\frac {r_1} 2,x+\frac {r_1}2]})|>2^{22}Mg(x)
\end{equation}
is less than $r_1/8$.
\end{lemma}

\begin{proof}
Let $r$, $r_1$, $x$ and $g$ be given.
If $M(H_{r}g)(x)=0$, then $H_{r}g$ is constant zero
and $F_1$ is empty and the estimate on $F_1$ trivial.
Assume $M(H_{r}g)(x)>0$.
We have with \eqref{first-cotlar-exception}
\begin{equation}
    M(H_{r}g)(x)\ge
    \frac 2{r_1}\int_{|x'-x|<\frac {r_1}4}|H_{r}g(x')|\, dx'
\end{equation}
\begin{equation}
    \ge
    \frac 2{r_1}\int_{F_1} 4 M(H_{r}g)(x)\, dx'
\end{equation}
Dividing by $M(H_{r}g)(x)$ gives
\begin{equation}
    1\ge \frac 8{r_1} |F_1|\, .
\end{equation}
This gives the desired bound for the measure of $F_1$.

We turn to the set $F_2$. Similarly as above we may assume $Mg(x)>0$.
The set $F_2$ is then estimated with \Cref{Hilbert-weak-1-1}
by
\begin{equation}
   \frac {2^{19}}{2^{22}Mg(x)}\int |g\mathbf{1}_{[x-\frac {r_1}2, x+\frac {r_1}2]}|(y)\, dy
\end{equation}
\begin{equation}
   \le \frac {2^{19}}{2^{22}Mg(x)}r_1Mg(x)= \frac {r_1}8\,.
\end{equation}
This gives the desired bound for the measure of $F_2$.
\end{proof}

\begin{lemma}[Cotlar estimate]
\label{Cotlar-estimate}
\uses{Cotlar-control, Cotlar-sets}
Let $0<r<r_1<1$ and $x\in \mathbb{R}$. Let $g$ be a bounded measurable function with bounded support on $\mathbb{R}$. Let $Mg$ and $M(H_r g)$ be the respective Hardy--Littlewood maximal functions
defined in Proposition
\ref{Hardy-Littlewood}.
Then for all $x\in \R$
\begin{equation}\label{eq-cotlar-estimate}
\left|
\int_{r_1<|x-y|<1}
g(y) \kappa(x-y)\, dy
\right|
\end{equation}
\begin{equation}\le
2^{2}M(H_rg)(x)+ 2^{23} Mg(x)
\, .
\end{equation}
\end{lemma}


\begin{proof}
By \Cref{Cotlar-control}, the measure of the set
of all $x'\in
[x-\frac{r_1}4,x+\frac{r_1}4]$
such that at least one of the conditions
\eqref{first-cotlar-exception} and
\eqref{second-cotlar-exception} is satisfied is at most $r_1/4$ and hence not all of
 $x'\in
[x-\frac{r_1}4,x+\frac{r_1}4]$. Pick an
$x'\in
[x-\frac{r_1}4,x+\frac{r_1}4]$ such that both conditions are not satisfied.
Applying \Cref{Cotlar-control}
for this $x'$ and using the triangle inequality
estimates the left-hand side of \eqref{eq-cotlar-estimate}
by
\begin{equation}
    4M(H_rg)(x)+2^{22}Mg(x)+2^{15}Mg(x)\, .
\end{equation}
This proves the lemma.
\end{proof}

\begin{lemma}[simple nontangential Hilbert]\label{simple-nontangential-Hilbert}
\uses{Hardy-Littlewood,Hilbert-strong-2-2,Cotlar-estimate}
    For every $0<r<1$ and every bounded measurable function $g$ with bounded support we have
\begin{equation}\label{trzerobound}
    \|T_{r}g\|_2\le 2^{42}\|g\|_2,
\end{equation}
where
\begin{equation}\label{eq-simple--nontangential}
    T_{r} g(x):=\sup_{r<r_1<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_1<|x'-y|<1}
g(y) \kappa(x'-y)\, dy\right|\, .
\end{equation}
\end{lemma}
\begin{proof}
With \Cref{estimate-x-shift}
and the triangle inequality, we estimate
for every $x\in \R$
\begin{equation}
     T_{r} g(x)
     \le 2^{13} Mg(x)+\sup_{r<r_1<1}
     \frac 1{2\pi} \left|\int_{r_1<|x-y|<1}
g(y) \kappa(x-y)\, dy\right|\, .
\end{equation}
Using further \Cref{Cotlar-estimate},
we estimate
\begin{equation}
      T_{r} g(x)
     \le 2^{13} Mg(x)+2^{23}
     Mg(x)+2^{2}M(H_{r}g)(x)\, .
\end{equation}
Taking the $L^2$ norm and using \Cref{Hardy-Littlewood}with $a=4$ and $p_2=2$ and $p_1=1$ , we obtain
\begin{equation}
      \|T_{r} g\|_2
     \le 2^{24} \|Mg\|_2+2^{2}\|M(H_{r}g)\|_2
\end{equation}
\begin{equation}
     \le 2^{41} \|g\|_2+2^{19}\|H_{r}(g)\|_2\, .
\end{equation}
Applying \Cref{Hilbert-strong-2-2}, gives
\begin{equation}
      \|T_{r} g\|_2\le 2^{41} \|g\|_2+2^{32}\|g\|_2\, .
\end{equation}
This shows \eqref{trzerobound} and completes the proof of the lemma.
\end{proof}

\begin{proof}[Proof of \Cref{nontangential-Hilbert}]
    \proves{nontangential-Hilbert}
Fix $g$ as in the Lemma.
Applying \Cref{simple-nontangential-Hilbert} with a
sequence of $r$ tending to $0$ and using Lebesgue monotone convergence shows
\begin{equation}\label{tzerobound}
    \|T_{0}g\|_2\le 2^{42}\|g\|_2,
\end{equation}
where
\begin{equation}\label{eq-simpler--nontangential}
    T_{0} g(x):=\sup_{0<r_1<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_1<|x'-y|<1}
g(y) \kappa(x'-y)\, dy\right|\, .
\end{equation}
We now write by the triangle inequality
\begin{equation}\label{concretetstartriangle}
    T_* g(x)\le \sup_{0<r_1<r_2<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_1<|x'-y|<1}g(y) \kappa(x'-y)\, dy\right|
\end{equation}
    \begin{equation*}
+\sup_{0<r_1< r_2<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_2<|x'-y|<1} g(y) \kappa(x'-y)\, dy\right|\, .
\end{equation*}
Noting that the first integral does not depend on $r_2$ and
estimating the second integral by the larger supremum over all
$|x-x'|<r_2$, at which time the integral does not depend on $r_1$, we estimate \eqref{concretetstartriangle} by
\begin{equation}\label{concretetstartriangle2}
   \sup_{0<r_1<1}\sup_{|x-x'|<r_1}\frac 1{2\pi} \left|\int_{r_1<|x'-y|<1}g(y) \kappa(x'-y)\, dy\right|
\end{equation}
    \begin{equation*}
+\sup_{0< r_2<1}\sup_{|x-x'|<r_2}\frac 1{2\pi} \left|\int_{r_2<|x'-y|<1} g(y) \kappa(x'-y)\, dy\right|\, .
\end{equation*}
    Applying the triangle inequality on the left-hand side
    of \eqref{concretetstarbound} and applying
     \eqref{tzerobound} twice
    proves \eqref{concretetstarbound}.
    This completes the proof of \Cref{nontangential-Hilbert}.
\end{proof}





\section{The truncated Hilbert transform}
\label{10hilbert}





Let $M_n$ be the modulation operator
acting on measurable $2\pi$-periodic functions
defined by
\begin{equation}
    M_ng(x)=g(x) e^{inx}\, .
\end{equation}
Define the approximate Hilbert transform by
\begin{equation}
    L_N g=\frac 1N\sum_{n=0}^{N-1}
       M_{-n-N} S_{N+n}M_{N+n}g\, .
\end{equation}


\begin{lemma}[modulated averaged projection]
\label{modulated-averaged-projection}
\uses{spectral-projection-bound}
We have for every bounded measurable $2\pi$-periodic function $g$
\begin{equation}\label{lnbound}
    \|L_Ng\|_{L^2[-\pi, \pi]}\le \|g\|_{L^2[-\pi, \pi]}\,.
\end{equation}
\end{lemma}
\begin{proof}
    We have
    \begin{equation}\label{mnbound}
        \|M_ng\|_{L^2[-\pi, \pi]}^2=\int_{-\pi}^{\pi} |e^{inx}g(x)|^2\, dx
        =\int_{-\pi}^{\pi} |g(x)|^2\, dx=\|g\|_{L^2[-\pi, \pi]}^2\, .
    \end{equation}
     We have by the triangle inequality, the square root of the identity in \eqref{mnbound}, and \Cref{spectral-projection-bound}
    \begin{equation*}
        \|L_ng\|_{L^2[-\pi, \pi]}=\|\frac 1N\sum_{n=0}^{N-1}
       M_{-n-N} S_{N+n}M_{N+n}g\|_{L^2[-\pi, \pi]}
    \end{equation*}
    \begin{equation*}
        \le \frac 1N\sum_{n=0}^{N-1} \|
       M_{-n-N} S_{N+n}M_{N+n}g\|_{L^2[-\pi, \pi]}
         = \frac 1N\sum_{n=0}^{N-1} \|
    S_{N+n}M_{N+n}g\|_{L^2[-\pi, \pi]}
    \end{equation*}
       \begin{equation}
     \le \frac 1N\sum_{n=0}^{N-1} \|
 M_{N+n}g\|_{L^2[-\pi, \pi]} = \frac 1N\sum_{n=0}^{N-1} \|
g\|_{L^2[-\pi, \pi]} =\|g\|_{L^2[-\pi, \pi]}\, .
    \end{equation}
This proves \eqref{mnbound} and completes the proof of the lemma.
\end{proof}

\begin{lemma}[periodic domain shift]\label{periodic-domain-shift}
\lean{Function.Periodic.intervalIntegral_add_eq, intervalIntegral.integral_comp_sub_right}
\leanok
Let $f$ be a bounded $2\pi$-periodic function. We have for any
$0 \le x\le 2\pi$ that
\begin{equation}
 \int_0^{2\pi} f(y)\, dy= \int_{-x}^{2\pi -x} f(y)\, dy
 =\int_{-\pi}^{\pi} f(y-x)\, dy\,.
\end{equation}
\end{lemma}
\begin{proof}
\leanok
    We have by periodicity and change of variables
    \begin{equation}\label{eqhil9}
 \int_{-x}^{0} f(y)\, dy=\int_{-x}^{0} f(y+2\pi)\, dy= \int_{2\pi -x}^{2\pi} f(y)\, dy\, .
\end{equation}
We then have by breaking up the domain of integration
and using \eqref{eqhil9}
\begin{equation*}
 \int_0^{2\pi} f(y)\, dy= \int_0^{2\pi -x} f(y)\, dy+
 \int_{2\pi -x}^{2\pi} f(y)\, dy
 \end{equation*}
\begin{equation}
= \int_0^{2\pi -x} f(y)\, dy+
 \int_{ -x}^{0} f(y)\, dy
 = \int_{-x}^{2\pi-x} f(y)\, dy\, .
 \end{equation}
This proves the first identity of the lemma. The second identity follows by substitution of $y$ by $y-x$.
\end{proof}



\begin{lemma}[Young convolution]\label{Young-convolution}
\uses{periodic-domain-shift}
    Let $f$ and $g$ be two bounded non-negative measurable $2\pi$-periodic functions on $\R$. Then
    \begin{equation}\label{eqyoung}
        \left(\int_{-\pi}^{\pi} \left(\int_{-\pi}^{\pi}
        f(y)g(x-y)\, dy\right)^2\, dx\right)^{\frac 12}\le \|f\|_{L^2[-\pi, \pi]} \|g\|_{L^1[-\pi, \pi]}\, .
    \end{equation}
    \end{lemma}
\begin{proof}
Using Fubini and \Cref{periodic-domain-shift}, we observe
\begin{equation*}
  \int_{-\pi}^{\pi}\int_{-\pi}^{\pi}f(y)^2g(x-y)\, dy
    \, dx=\int_{-\pi}^{\pi}f(y)^2\int_{-\pi}^{\pi}g(x-y)\, dx
    \, dy
\end{equation*}
\begin{equation}\label{eqhil4}
=\int_{-\pi}^{\pi}f(y)^2\int_{-\pi}^{\pi}g(x) \, dx
     dy
=\|f\|_{L^2[-\pi, \pi]}^2\|g\|_{L^1[-\pi, \pi]}\, .
\end{equation}
   Let $h$ be the nonnegative square root of $g$, then
   $h$ is bounded and $2\pi$-periodic with $h^2=g$.
   We estimate the square of the left-hand side of
   \eqref{eqyoung} with Cauchy-Schwarz and then with
   \eqref{eqhil4} by
       \begin{equation*}
         \int_{-\pi}^{\pi} (\int_{-\pi}^{\pi}f(y)h(x-y)h(x-y)\, dy)^2\, dx
   \end{equation*}
\begin{equation*}
    \le \int_{-\pi}^{\pi}\left(\int_{-\pi}^{\pi}f(y)^2g(x-y)\, dy\right)
    \left(\int_{-\pi}^{\pi}g(x-y)\, dy\right)\, dx
\end{equation*}
\begin{equation*}
    = \|f\|_{L^2[-\pi, \pi]}^2\|g\|_{L^1[-\pi, \pi]}^2\, .
\end{equation*}
Taking square roots, this proves the lemma.
\end{proof}

For $0<r<1$, Define the kernel $k_r$ to be the $2\pi$-periodic function
\begin{equation}
    |k_r(x)|:=\min \left(r^{-1}, 1+\frac r{|1-e^{ix}|^2}\right)\, ,
\end{equation}
where the minimum is understood to be $r^{-1}$ in case $1=e^{ix}$.
\begin{lemma}[integrable bump convolution]
\label{integrable-bump-convolution}
\uses{Young-convolution}
Let $g,f$ be bounded measurable $2\pi$-periodic functions. Let $0<r<\pi$.
Assume we have for all $0\le x\le 2\pi$
\begin{equation}\label{ebump1}
    |g(x)|\le k_r(x)\, .
\end{equation}
Let
\begin{equation}
   h(x)= \int_{-\pi}^{\pi} f(y)g(x-y)\, dy \, .
\end{equation}
Then
\begin{equation}
   \|h\|_{L^2[-\pi, \pi]}\le 2^{5}\|f\|_{L^2[-\pi, \pi]} \, .
\end{equation}

\end{lemma}

\begin{proof}
From monotonicity of the integral and \eqref{ebump1},
\begin{equation}
    \|g\|_{L^1[-\pi, \pi]} \le \int_{-\pi}^{\pi}k_r(x)\, dx\,.
\end{equation}
Using the symmetry
$k_r(x)=k_r(-x)$, the assumption, and \Cref{lower-secant-bound}, the last display
is equal to
\begin{equation*}
    = 2 \int_0^\pi \min\left(\frac 1r, 1+\frac r{|1-e^{ix}|^2}\right)\, dx
\end{equation*}
\begin{equation*}
    \le 2\int_0^{r} \frac 1r \, dx+2\int_r^{\pi}1+\frac {64r}{x^2}\, dx
\end{equation*}
\begin{equation}
    \le 2+2\pi + 2\left(\frac {64r}r-\frac {64r}{\pi}\right)
    \le 2^{5}\, .
\end{equation}
    Together with \Cref{Young-convolution}, this proves the lemma.
\end{proof}

\begin{lemma}[dirichlet approximation]\label{dirichlet-approximation}
\uses{dirichlet-kernel,lower-secant-bound}
Let $0<r<1$. Let $N$ be the smallest
integer larger than $\frac 1r$.
There is a $2\pi$-periodic continuous function
 ${L'}$ on $\R$ that satisfies for all $-\pi\le x\le \pi$
and all $2\pi$-periodic bounded measurable functions $f$ on $\R$
\begin{equation}\label{lthroughlprime}
    L_Nf(x)=\frac 1{2\pi}\int_{-\pi}^{\pi}f(y) {L'}(x-y)\, dy
\end{equation}
and
\begin{equation}\label{eqdifflhil}
    \left|L'(x)-\mathbf{1}_{\{y:\, r<|y|<1\}} \kappa(x)\right|\le 2^{5}k_r(x)\, .
\end{equation}
\end{lemma}


\begin{proof}
We have by definition and \Cref{dirichlet-kernel}
\begin{equation}
    L_Ng(x)=
    \frac 1N\sum_{n=0}^{N-1}
       \int_{-\pi}^{\pi} e^{-i(N+n)x} K_{N+n}(x-y) e^{i(N+n)y}g(y)
\, dy \, .\end{equation}
This is of the form \eqref{lthroughlprime} with
the continuous function
\begin{equation}
    {L'}(x)= \frac 1N\sum_{n=0}^{N-1}
      K_{N+n}(x) e^{-i(N+n)x}\, .
\end{equation}
With \eqref{eqksumexp} of \Cref{dirichlet-kernel}
we have $|K_N(x)|\le N$ for every $x$ and thus
\begin{equation}\label{eqhil13}
    |{L'}(x)|\le \frac 1N\sum_{n=0}^{N-1}
      (N+n) \le 2N\le 2^2 r^{-1}\, .
\end{equation}
Therefore, for $|x|\in [0, r)\cup (1, \pi]$, we have
\begin{equation}
    \label{eqdiffzero}
    \left|L'(x)-\mathbf{1}_{\{y:\, r<|y|<1\}}(x)\kappa(x)\right|=|L'(x)|\leq 2^{2} r^{-1}.
\end{equation}
This proves \eqref{eqdifflhil} for $|x|\in [0, r)$ since $k_r(x)=r^{-1}$ in this case.

For $e^{ix'}\neq 1$
and may use the expression
\eqref{eqksumhil} for $K_N$
in \Cref{dirichlet-kernel} to obtain
\begin{equation*}
    {L'}(x)= \frac 1N\sum_{n=0}^{N-1}
     \left(\frac{e^{i(N+n)x}}{1-e^{-ix}}
      +\frac {e^{-i(N+n)x}}{1-e^{ix}}\right) e^{-i(N+n)x}
\end{equation*}
\begin{equation*}
    = \frac 1N\sum_{n=0}^{N-1}
    \left(\frac{1}{1-e^{-ix}}
      +\frac {e^{-i2(N+n)x}}{1-e^{ix}}\right)
\end{equation*}
\begin{equation}\label{eqhil3}
    = \frac{1}{1-e^{-ix}} +
     \frac 1N \frac {e^{-i2Nx}}{1-e^{ix}}
     \sum_{n=0}^{N-1}
    {e^{-i2nx}}
\end{equation}
and thus
\begin{equation}
\label{eq-L'L''}
  {L'}(x) -\mathbf{1}_{\{y:\, r<|y|<1\}}\kappa(x)=L''(x)+ \frac{1-\mathbf{1}_{{\{y:\, r<|y|<1\}}}(x)(1-|x|)}{1-e^{-ix}},
\end{equation}
where
$$L''(x):=\frac 1N \frac {e^{-i2Nx}}{1-e^{ix}}
     \sum_{n=0}^{N-1}
    {e^{-i2nx}}.$$
For $x\in [-\pi, r]\cup [r, \pi]$, we have using \Cref{lower-secant-bound} that
\begin{equation*}
   \left|\frac{1-\mathbf{1}_{{\{y:\, r<|y|<1\}}}(x)(1-|x|)}{1-e^{-ix}} \right|=\left|\frac{\min(|x|, 1)}{1-e^{-ix}} \right|\leq \frac{8\min(|x|, 1)}{|x|}
\end{equation*}
\begin{equation}
 \label{eq-diffzero2}
    \leq 2^3\cdot 1\leq 2^{3} k_r(x).
\end{equation}
Next, we need to estimate $L''(x)$. If the real part of
$e^{ix}$ is negative, we have
\begin{equation}
  1\le |1-e^{ix}|\le 2\, .
\end{equation}
and hence
\begin{equation}\label{eqhil12}
    |L''(x)|\le
     \frac 1N
     \sum_{n=0}^{N-1}
    1=1\le 1+\frac r{|1-e^{ix}|^2}\, .
\end{equation}
If the real part of $e^{ix}$ is positive and in particular while still $e^{ix}\neq \pm 1$, then we have by telescoping
\begin{equation}
 (1-e^{-2ix})
     \sum_{n=0}^{N-1}
    {e^{-i2nx}}=1-e^{-i2Nx}\, .
\end{equation}
As $e^{-2ix}\neq 1$, we may divide by $1-e^{-2ix}$ and insert this into
\eqref{eqhil3} to obtain
\begin{equation}
 L''(x)=
           \frac 1N \frac {e^{-i2Nx}}{1-e^{ix}}
     \frac{1-e^{-i2Nx}}{1-e^{-2ix}}\, .
\end{equation}
Hence, with \Cref{lower-secant-bound} and nonnegativity of the real part of $e^{ix}$
\begin{equation*}
    |L''(x)|
 \le \frac 2 N \frac {1}{|1-e^{ix}|}
     \frac{1}{|1-e^{-2ix}|}
 \end{equation*}
\begin{equation}\label{eqhil11}
    = \frac 2 N \frac {1}{|1-e^{ix}|^2}
     \frac{1}{|1+e^{ix}|}\le
 \frac {4r}{|1-e^{ix}|^2}\le 2^{2} \left (1+\frac {r}{|1-e^{ix}|^2}\right)
\end{equation}
Inequalities \eqref{eqhil13}, \eqref{eqdiffzero}, \eqref{eq-L'L''}, \eqref{eq-diffzero2}, \eqref{eqhil12}, and \eqref{eqhil11} prove \eqref{eqdifflhil}. This completes the proof of the lemma.
\end{proof}


We now prove \Cref{Hilbert-strong-2-2}.

\begin{proof}[Proof of \Cref{Hilbert-strong-2-2}]
    \proves{Hilbert-strong-2-2}
    We first show that if $f$ is supported in $[-3/2, 3/2]$, then
    \begin{equation}
        \label{eq-Hr-short-support}
        \|H_r f\|_{L^2(\R)} \le 2^{16} \|f\|_{L^2(\R)}\,.
    \end{equation}
    Let $\tilde{f}$ be the $2\pi$-periodic extension of $f$ to $\mathbb{R}$. Let $N$ be the smallest
    integer larger than $\frac 1r$. Then, by \Cref{dirichlet-approximation} and the triangle inequality, for $x\in [-\pi, \pi]$ we have
    \begin{equation*}
        |H_r \tilde{f}(x)|\leq 2\pi |L_N \tilde{f}(x)|+2^{5}\left|\int_{-\pi}^{\pi}k_r(x-y)\tilde{f}(y)\, dy\right|.
    \end{equation*}
    Taking $L^2$ norm over the interval $[-\pi, \pi]$ and using its sub-additivity, we get
    $$
         \|H_r \tilde{f}\|_{L^2([-\pi, \pi])}
    $$
    \begin{equation*}
       \leq 2\pi \|L_N \tilde{f}\|_{L^2([-\pi, \pi])}\, + 2^{5}\left(\int_{-\pi}^{\pi} \left|\int_{-\pi}^{\pi}k_r(x-y)\tilde{f}(y)\, dy\right|^2\, dx\right)^{\frac{1}{2}}.
    \end{equation*}
    Since $k_r$ is supported in $[-1,1]$, we have that $H_rf$ is supported in $[-5/2, 5/2]$ and agrees there with $H_r \tilde f(x)$.
    Using \Cref{modulated-averaged-projection} and \Cref{integrable-bump-convolution}, we conclude
    \begin{equation}
        \|H_r f\|_{L^2(\R)} \le \|H_r \tilde f\|_{L^2([-\pi, \pi])} \leq 2\pi \|f\|_{L^2(\R)} + 2^{10}\|f\|_{L^2(\R)}\,,
    \end{equation}
    which gives \eqref{eq-Hr-short-support}.

    Suppose now that $f$ is supported in $[c, c+3]$ for some $c \in \R$. Then the function $g(x) = f(c+ \frac{3}{2} +x)$ is supported in $[-3/2,3/2]$. By a change of variables in \eqref{def-H_r}, we have $H_r g(x ) = H_r f(c+ 3/2+x)$. Thus, by \eqref{eq-Hr-short-support}
    \begin{equation}
        \label{eq-Hr-short-support-2}
        \|H_rg\|_2 = \|H_r f\|_2 \le 2^{11} \|f\|_2 = \|g\|_2\,.
    \end{equation}

    Let now $f$ be arbitrary.
    Since $\kappa(x) = 0$ for $|x| > 1$, we have for all $x \in [c+1, c+2]$
    $$
        H_rf(x) = H_r(f \mathbf{1}_{[c, c+3]})(x)\,.
    $$
    Thus
    $$
        \int_{c+1}^{c+2} |H_r f(x)|^2 \, \mathrm{d}x \le \int_{\R} |H_r(f \mathbf{1}_{[c, c+3]})(x)|^2 \, \mathrm{d}x\,.
    $$
    Applying the bound \eqref{eq-Hr-short-support-2}, this is
    $$
        \le 2^{11} \int_{c}^{c+3} |f(x)|^2 \, \mathrm{d}x\,.
    $$
    Summing over all $c \in \mathbb{Z}$, we obtain
    $$
        \int_{\R} |H_rf(x)|^2 \, \mathrm{d}x \le 3 \cdot 2^{11} \int_{\R} |f(x)|^2 \, \mathrm{d}x\,.
    $$
    This completes the proof.
\end{proof}







\section{Calder\'on-Zygmund Decomposition}
\label{subsec-CZD}

For $I=[s, t)\subset \mathbb{R}$, we define
\begin{equation}
    \label{eq-bisec}
    \textrm{bi} (I):= \left\{\left[s, \frac{s+t}{2}\right), \left[\frac{s+t}{2}, t\right)\right\}.
\end{equation}

In what follows, we write $\mu$ for the Lebesgue measure on $\R$.

\begin{lemma}[interval bisection]
\label{interval-bisection}
    Let $I=[s, t)\subset \mathbb{R}$ be a bounded, right-open interval. Let $I_1, I_2\in \textrm{bi} (I)$ with $I_1\neq I_2$. Then
    \begin{equation}
        \label{eq-bi-size}
        \mu (I_1)=\mu(I_2)=\frac{\mu(I)}{2}.
    \end{equation}
    Further,
    \begin{equation}
        \label{eq-bi-union}
        I=I_1\cup I_2,
    \end{equation}
    and the intervals $I_1$ and $I_2$ are disjoint.
\end{lemma}
\begin{proof}
    This in some form can be taken from the Lean library.
\end{proof}
For a bounded interval $I=[a, b)\subset \mathbb{R}$ and a non-negative integer $n$, we inductively define
\begin{equation}
    \label{eq-ch-I}
    \textrm{ch}_0(I):=\{I\}, \qquad \textrm{ch}_n(I)=\cup_{J\in \textrm{ch}_{n-1}(J)} \textrm{bi} (J).
\end{equation}

\begin{lemma}[bisection children]
    \label{bisection-children}
    \uses{interval-bisection}
    Let $I=[s, t)$ and let $n$ be a non-negative integer. Then the intervals in $\textrm{ch}_n(I)$ are pairwise disjoint. For any $J\in \textrm{ch}_n(I)$,
    \begin{equation}
        \label{eq-ch-size}
        \mu(J)=\frac{\mu(I)}{2^{n}}=\frac{t-s}{2^n}.
    \end{equation}
    Further,
    \begin{equation}
        \label{eq-ch-cover}
        I= \cup_{J\in \textrm{ch}_n(I)} J
    \end{equation}
    and
    \begin{equation}
        \label{eq-ch-card}
        |\textrm{ch}_n(I)|= 2^{n+1}.
    \end{equation}
\end{lemma}
\begin{proof}
This follows by induction on $n$, using \Cref{interval-bisection}.
\end{proof}


\begin{lemma}[Lebesgue differentiation]
    \label{Lebesgue-differentiation}
    Let $f$ be a bounded measurable function with bounded support. Then for $\mu$ almost every $x$, we have
    $$\frac{1}{\mu(I_n)}\int_{I_n} f(y)\, dy= f(x),$$
    where $\{I_n\}_{n\geq 1}$ is a sequence of intervals such that $x\in I_n$ for each $n\geq 1$ and $$\lim_{n\to \infty} \mu(I_n)=0.$$
\end{lemma}
\begin{proof}
    This follows from the Lebesgue differentiation theorem, which is already formalized in Lean.
\end{proof}

\begin{lemma}[stopping time]
   \label{stopping-time}
   \uses{bisection-children,Lebesgue-differentiation}
   Let $f$ be a bounded, measurable function with bounded support on $\mathbb{R}$. Let $\alpha>0$. Then there exists $A\subset \mathbb{R}$ such that the following properties \eqref{eq-CZ-good-set}, \eqref{eq-CZ-good-set-comp}, \eqref{eq-CZ-bad-sets-1}, \eqref{eq-CZ-bad-sets-2}, and \eqref{eq-CZ-meas-b-set} are satisfied. For all $x\in A$
    \begin{equation}
    \label{eq-CZ-good-set}
        |f(x)|\leq \alpha.
    \end{equation}
    The set $\mathbb{R}\setminus A$ can be decomposed into a countable union of intervals
    \begin{equation}
        \label{eq-CZ-good-set-comp}
        \mathbb{R}\setminus A= \cup_{j} I_j= \cup_{j} [s_j, t_j),
    \end{equation}
    such that
   \begin{equation}
   \label{eq-CZ-bad-sets-1}
    [s_j, t_j)\cap [s_{j'}, t_{j'})=\emptyset \text{ for } j\neq j' \,.
   \end{equation}
   For each $j$,
   \begin{equation}
       \label{eq-CZ-bad-sets-2}
       \frac{\alpha}{2}\leq \frac{1}{t_j-s_j}\int_{s_j}^{t_j} |f(y)|\, dy\leq \alpha.
   \end{equation}
   Further,
   \begin{equation}
       \label{eq-CZ-meas-b-set}
        \sum_{j}(t_j-s_j)\leq \frac{2}{\alpha}\int |f(y)|\, dy\,.
   \end{equation}
\end{lemma}
\begin{proof}
    Since $f$ is bounded with bounded support, there exists a non-negative integer $\ell$ such that
    \begin{equation}
        \label{eq-f-supp}
        f(x)=0 \textrm{ for } x\not\in [-2^{\ell-1}, 2^{\ell-1})\,,
    \end{equation}
    and
    $$2^{-\ell}\int_{-2^{\ell-1}}^{2^{\ell-1}} |f(y)|\, dy< \alpha\,.$$
    Let $$I_0:=[-2^{\ell}, 2^{\ell}),\qquad \mathcal{Q}_0:=\{I_0\}\,,$$
    and
    $$\Tilde{\mathcal{Q}}_1:=\textrm{bi}(I_0).$$
    For $n\geq 1$, we inductively define
    \begin{equation*}
        {\mathcal{Q}}_n:=\left\{I\in \Tilde{\mathcal{Q}}_n: \frac{1}{\mu(I)}\int_{I} |f(y)|\, dy> \frac{\alpha}{2}\right\}\,,
    \end{equation*}
    and
    \begin{equation*}
     \Tilde{\mathcal{Q}}_{n+1}:=\cup_{I\in {\Tilde{\mathcal{Q}}}_n\setminus \mathcal{Q}_n} \textrm{bi} (I)\,.
    \end{equation*}
Finally, let
\begin{equation*}
    \mathcal{Q}:=\cup_{n\geq 1} \mathcal{Q}_n\,.
\end{equation*}

For each $n$ we have
$$\mathcal{Q}_n\subseteq \textrm{ch}_n(I_0).$$
Therefore, by \Cref{bisection-children},
$$|\mathcal{Q}_n|\leq \frac{\mu(I_0)}{2^n}= 2^{\ell+1-n}.$$
It follows that $\mathcal{Q}$ is a countable union of finite sets and hence, is countable itself. Let $\{I_j\}_{j\geq 1}$ be an enumeration of this set, with
$$I_j:=[s_j, t_j),$$
for $s_j, t_j\in I_0$ and $s_j<t_j$.
We set
\begin{equation*}
    A:=\mathbb{R}\setminus \cup_{j\geq 1} [s_j, t_j).
\end{equation*}
Then \eqref{eq-CZ-good-set-comp} holds by definition. We next show \eqref{eq-CZ-bad-sets-1}. Let $I_j, I_{j'}\in \mathcal{Q}$. Then, there exist $1\leq n, n'$ such that $I_j\in \mathcal{Q}_n$ and $I_{j'}\in \mathcal{Q}_{n'}$. If $n=n'$, \eqref{eq-CZ-bad-sets-1} follows from \Cref{bisection-children} since $\mathcal{Q}_n\subseteq \textrm{ch}_n(I_0).$ Otherwise, assume without loss of generality that $n<n'$. Then by construction, there exists $J\in \Tilde{\mathcal{Q}}_{n}\setminus {\mathcal{Q}_n}$ such that $I_{j'} \subset J$. Since $I_{j}\in \mathcal{Q}_n$, it follows that $I_j\neq J$. Since $I_j, J\in \Tilde{\mathcal{Q}}_{n}\subset \textrm{ch}_n(I_0)$, by \Cref{bisection-children}, we deduce that they are disjoint. Since $I_{j'}\subset J$, we conclude that $I_j$ and
$I_{j'}$ are disjoint as well. This proves \eqref{eq-CZ-bad-sets-1}.

To see \eqref{eq-CZ-bad-sets-2}, let $I_j=(s_j, t_j)\in \mathcal{Q}$. Then $I_j\in \mathcal{Q}_n$ for some $n\geq 1$. By definition of $\mathcal{Q}_n$, we have
$$\frac{\alpha}{2}<\frac{1}{\mu(I)}\int_{I} |f(y)|\, dy=\frac{1}{t_j-s_j}\int_{s_j}^{t_j} |f(y)|\, dy.$$
As $I_j\in \mathcal{Q}_n\subseteq \Tilde{\mathcal{Q}_{n}}$, by definition of the latter set, there exists $J\in \Tilde{\mathcal{Q}}_{n-1}\setminus \mathcal{Q}_{n-1}$ with $I\in \textrm{bi} (J)$. Since $J\not\in \mathcal{Q}_{n-1}$, we conclude that
$$\frac{1}{\mu(J)}\int_J |f(y)|\, dy\leq \frac{\alpha}{2}.$$
Using \Cref{interval-bisection} and the above, we get
$$\frac{1}{t_j-s_j}\int_{s_j}^{t_j} |f(y)|\, dy=\frac{1}{\mu(I)}\int_I |f(y)|\, dy\leq \frac{2}{\mu(J)} \int_J |f(y)|\, dy\leq \alpha.$$
This establishes \eqref{eq-CZ-bad-sets-2}. Using this, we see that for each $j$, we have
$$t_j-s_j\leq \frac{2}{\alpha}\int_{s_j}^{t_j} |f(y)|\, dy.$$
Summing up in $j$ and using the disjointedness property \eqref{eq-CZ-bad-sets-1}, we get
$$\sum_{j} (t_j-s_j)\leq \frac{2}{\alpha}\int_{s_j}^{t_j} |f(y)|\, dy= \frac{2}{\alpha}\int |f(y)|\, dy.$$

Finally, we show $\eqref{eq-CZ-good-set}$. Let $x\in A$. If $x\not \in [-2^{\ell}, 2^{\ell}]$, then by \eqref{eq-f-supp} that $f(x)=0$. Thus \eqref{eq-CZ-good-set} is true in this case. Alternately, let $x\in I_0\cap A$. Then for each $n$, there exists $I(n)\in \Tilde{\mathcal{Q}}_n$ such that $x\in I(n)$ and
\begin{equation}
    \label{eq-avg-In}
    \frac{1}{\mu(I(n))}\int_{I(n)} |f(y)| dy\leq {\alpha}.
\end{equation}
Since $\mu(I(n))=2^{\ell+1-n}$, we have
$$\lim_{n\to \infty} \mu(I(n))=0.$$
By \Cref{Lebesgue-differentiation}, we also have
\begin{equation*}
 \lim_{n\to \infty}\frac{1}{\mu(I(n))}\int_{I(n)} |f(y)| dy= |f(x)|
\end{equation*}
for almost every $x\in A$.
Combining the above with \eqref{eq-avg-In}, we conclude that
$$|f(x)|\leq \alpha.$$
This finishes the proof of \eqref{eq-CZ-good-set}, and hence the lemma.
\end{proof}

Calder\'on-Zygmund decomposition is a tool to extend $L^2$ bounds to $L^p$ bounds with $p<2$ or to the so-called weak $(1, 1)$ type endpoint bound.
It is classical and can be found in \cite{stein-book}.

\begin{lemma}[Calderon Zygmund decomposition]
    \label{Calderon-Zygmund-decomposition}
    \uses{stopping-time}
    Let $f$ be a bounded, measurable function with bounded support. Let $\alpha>0$ and $\gamma\in (0, 1)$. Then there exists a measurable functions $g$, a countable family of disjoint intervals $I_j = [s_j, t_j)$, and a countable family of measurable functions $\{g_j\}_{j\geq 1}$ such that for almost every $x \in \R$
    \begin{equation}
       \label{eq-gb-dec}
       f(x)= g(x)+ \sum_{j\geq 1} b_j(x)
    \end{equation}
    and such that the following holds. For almost every $x\in \mathbb{R}$,
    \begin{equation}
        \label{eq-g-max}
       |g(x)|\leq \gamma\alpha\,.
    \end{equation}
    We have
    \begin{equation}
        \label{eq-g-L1-norm}
        \int |g(y)|\, dy\leq \int |f(y)|\, dy.
    \end{equation}
    For every $j$
    \begin{equation}
        \label{eq-supp-bj}
        \operatorname{supp} b_j \subset I_j\,.
    \end{equation}
    For every $j$
    \begin{equation}
        \label{eq-bad-mean-zero}
        \int_{I_j} b_j(x)\, dx=0,
    \end{equation}
    and
     \begin{equation}
        \label{eq-bj-L1}
        \int_{I_j} |b_j(x)|\, dx \leq 2\gamma\alpha.
    \end{equation}
    We have
    \begin{equation}
        \label{eq-bset-length-sum}
        \sum_j (t_j-s_j)\leq \frac{2}{\gamma\alpha}\int |f(y)|\, dy
    \end{equation}
    and
    \begin{equation}
    \label{eq-b-L1}
    \sum_{j}\int_{I_j} |b_j(y)|\, dy\leq 2 \int |f(y)|\, dy\,.
    \end{equation}
\end{lemma}

\begin{proof}
    Applying \Cref{stopping-time} to $f$ and $\gamma\alpha$, we obtain a collection $I_j$ of intervals such that the conditions \eqref{eq-CZ-good-set}-\eqref{eq-CZ-meas-b-set} are satisfied. We set $A = \R \setminus \cup_j I_j$ and
\begin{equation}
    \label{eq-g-def}
    g(x):=\begin{cases}
     f(x), & x\in A,\\
     \frac{1}{\mu(I_j)}\int_{I_j} f(y)\, dy, &x\in (s_j, t_j),\\
     0, & x\in [s_j, t_j]\setminus (s_j, t_j),
    \end{cases}
\end{equation}
and, for each $j$,
\begin{equation}
    b_j(x):=\begin{cases}
        f(x)-\frac{1}{\mu(I_j)}\int_{I_j} f(y)\, dy, &x\in (s_j, t_j),\\
        0, & x\not\in (s_j, t_j).
    \end{cases}
\end{equation}
Then \eqref{eq-supp-bj} and \eqref{eq-bset-length-sum} are true by construction and \Cref{stopping-time}.
Further, let $b(x)=\sum_{j} b_j(x).$
Then
\begin{equation*}
    f(x)=g(x)+b(x)=g(x)+\sum_{j} b_j(x) ,
\end{equation*}
for all $x$ not in the measure zero set $\cup_j \{s_j, t_j\}.$

For almost every $x\in A$, we get using \eqref{eq-CZ-good-set}
$$|g(x)|\leq \gamma\alpha\,.$$ In the case when neither of the above is true, we have $g(x)=0$ by definition.
Thus, we obtain \eqref{eq-g-max}.

To prove \eqref{eq-g-L1-norm}, we estimate
$$\int |g(y)|\, dy\leq \int_A |f(y)|\, dy+ \sum_{j} \int_{I_j}\frac{1}{\mu(I_j)}\int_{I_j}|f(y)|\, dy.$$
Since the intervals $I_j$ are disjoint, and $A=\mathbb{R}\setminus \cup_j I_j$, we conclude
$$\int |g(y)|\, dy\leq \int_A |f(y)|\, dy+\sum_{j} \int_{I_j}|f(y)|\, dy= \int |f(y)|\, dy.$$
This establishes \eqref{eq-g-L1-norm}.
If $x\in I_j$ for some $j$, \eqref{eq-CZ-bad-sets-2} yields
$$|g(x)|\leq \frac{1}{\mu(I_j)}\int_{I_j}|f(y)|\, dy\leq \gamma\alpha.$$


Further, for each $j$, it follows from the definition of $t_j$ that
$$ \int_{I_j} b_j(x)\, dx= \int_{I_j} f(x)\, dx-\int_{I_j} \frac{1}{\mu(I_j)}\int_{I_j}f(y)\, dy\, dx$$
\begin{equation*}
    =\int_{I_j} f(x)\, dx- \int_{I_j}f(y)\, dy=0.
\end{equation*}
This establishes \eqref{eq-bad-mean-zero}.

Using the triangle inequality, we have that
\begin{equation*}
    \int_{I_j} |b_j(y)|\, dy\leq \int_{I_j} |f(y)|\, dy + \int_{I_j} \frac{1}{\mu(I_j)}\int_{I_j} |f(x)|\, dx\, dy.
\end{equation*}
\begin{equation}
    \label{eq-bj-int}
    =2 \int_{I_j} |f(y)|\, dy.
\end{equation}
Dividing both sides by $\mu(I_j)$ and using \eqref{eq-CZ-bad-sets-2}, we obtain \eqref{eq-bj-L1}.

Further, summing up \eqref{eq-bj-int} in $j$ yields
\begin{equation*}
    \sum_{j}\int_{I_j} |b_j(y)|\, dy\leq \sum_{j}\int_{I_j} |f(y)|\, dy + \sum_{j}\int_{I_j} \frac{1}{\mu(I_j)}\int_{I_j} |f(x)|\, dx\, dy.
\end{equation*}
Using the disjointedness of $(s_j, t_j)$, we get
\begin{equation*}
    \sum_{j}\int_{I_j} |b_j(y)|\, dy\leq 2 \int |f(y)|\, dy.
\end{equation*}
This proves \eqref{eq-b-L1}, and completes the proof.
\end{proof}

\begin{proof}[Proof of \Cref{Hilbert-weak-1-1}]
\proves{Hilbert-weak-1-1}
Using \Cref{Calderon-Zygmund-decomposition} for $f$ and $2^{-10}\alpha$, we obtain the decomposition
$$f=g+b=g+\sum_j b_j$$
such that the properties \eqref{eq-gb-dec}-\eqref{eq-b-L1} are satisfied with $\gamma=2^{-10}$. For each $j$, let
\begin{equation}
    \label{eq-Ij-cj}
    I_j=[s_j, t_j), \qquad c_j:=\frac{s_j+t_j}{2},
\end{equation}
and
\begin{equation}
    \label{eq-Ij*}
    I_j{^*}=\left[s_j-{2(t_j-s_j)}, t_j+2(t_j-s_j)\right].
\end{equation}
Then $I_j^*$ is an interval with the same center as $I_j$ but with
\begin{equation}
    \label{eq-Ij*-dim}
    \mu(I_j^*)=5(t_j-s_j)=5\mu(I_j).
\end{equation}
Let
\begin{equation}
    \label{eq-omega}
    \Omega:=\cup_j I_{j}^*.
\end{equation}
By definition, for each $x\in \mathbb{R}\setminus\Omega$ and $y\in I_j$,
\begin{equation}
    \label{eq-Om-cj}
    |x-c_j|>\frac{5(t_j-s_j)}{2}\geq 5|y-c_j|,
\end{equation}
and
\begin{equation}
    \label{eq-Om-y}
    |x-y|>{2(t_j-s_j)}.
\end{equation}
It follows by the triangle inequality and subadditivity of $\mu$ that
$$ \mu\left(\{x\in \mathbb{R}: |H_r f(x)|>\alpha\}\right) $$
\begin{equation}
\label{eq-set-dec-1}
 \le \mu\left(\{x\in \mathbb{R}: |H_r g(x)|>{\alpha}/2\}\right)+ \mu\left(\{x\in \mathbb{R}: |H_r b(x)|>{\alpha}/2\}\right).
\end{equation}
We estimate using monotonicity of the integral
$$ \mu\left(\{x\in \mathbb{R}: |H_r g(x)|>{\alpha}/2\}\right)\leq
\frac{4}{\alpha^2} \int |H_r g(y)|^2\, dy. $$
Using \Cref{Hilbert-strong-2-2} followed by \eqref{eq-g-max} and \eqref{eq-g-L1-norm}, we estimate the right hand side above by
$$\leq 2^{26}\frac{4}{\alpha^2} \int |g(y)|^2\, dy\leq \frac{2^{18}}{\alpha} \int |g(y)|\, dy\leq \frac{2^{18}}{\alpha} \int |f(y)|\, dy.$$
Thus, we conclude
\begin{equation}
    \label{eq-g-func-bd}
    \mu\left(\{x\in \mathbb{R}: |H_r g(x)|>{\alpha}/2\}\right)\leq
    \frac{2^{18}}{\alpha} \int |f(y)|\, dy.
\end{equation}
Next, we estimate
$$\mu\left(\{x\in \mathbb{R}: |H_r b(x)|>\alpha/2\}\right) $$
$$
    \le \mu (\Omega) + \mu\left(\{x\in \mathbb{R}\setminus\Omega: |H_r b(x)|>{\alpha}/2\}\right)\,.
$$
Using \eqref{eq-Ij*-dim} and \eqref{eq-bset-length-sum}, we conclude that
\begin{equation}
    \label{eq-omega-bd}
    \mu(\Omega) \le \sum_{j} \mu (I_j^*)
    = 5 \sum_{j} (t_j-s_j)\leq \frac{2^{13}}{\alpha} \int |f(y)|\, dy\,.
\end{equation}
We now focus on estimating the remaining term
$$\mu\left(\{x\in \mathbb{R}\setminus\Omega: |H_r b(x)|>{\alpha}/2\}\right)\,.$$
For $x\in \mathbb{R}\setminus\Omega$, define
\begin{align*}
    \mathcal{J}_1(x)&:=\{j\,:[s_j, t_j)\cap [x-r, x+r]=\emptyset \},\\
    \mathcal{J}_2(x)&:=\{j\,: |y-x|=r \text{ for some } y \in [s_j, t_j)\},\\
    \mathcal{J}_3(x)&:=\{j\,: [s_j, t_j)\subset [x-r, x+r]\}.
\end{align*}
Since $H_rb_j(x)=0$ for all $j\in \mathcal{J}_3(x)$, using the triangle inequality and the decomposition above, we get
\begin{equation}
    \label{eq-b-dec}
    |H_r b(x)|\leq \sum_{j\in \mathcal{J}_1(x)} |H_rb_j(x)|+\sum_{j\in \mathcal{J}_2(x)} |H_rb_j(x)|.
\end{equation}
Further, for $j\in \mathcal{J}_1(x)$, we have
$$H_rb_j(x)=\int_{I_j} \kappa (x-y)\mathbf{1}_{\{z:\, r<|z|<1\}}(x-y) b_j(y)\,dy=\int_{I_j} \kappa (x-y) b_j(y)\,dy\,.$$
Using \eqref{eq-bad-mean-zero}, the above is equal to
$$\int_{I_j} (\kappa (x-y)-\kappa(x-c_j)) b_j(y).$$
Thus, using the triangle inequality, \eqref{eq-Om-cj}, \eqref{eq-Om-y} and \Cref{Hilbert-kernel-regularity}, we can estimate
$$\sum_{j\in \mathcal{J}_1(x)} |H_rb_j(x)|\leq \sum_{j\in \mathcal{J}_1(x)}2^{10}\int_{I_j}\frac{|y-c_j|}{|x-c_j|^2} |b_j(y)|\, dy$$
\begin{equation}
    \label{eq-J1-diff-est}
    \leq 2^{10}\sum_{j} \frac{(t_j-s_j)}{|x-c_j|^2}\int_{I_j} |b_j(y)|\, dy:=F_1(x).
\end{equation}
Next, we estimate the second sum in \eqref{eq-b-dec}. For each $j\in \mathcal{J}_2(x)$, set
$$d_j:=\frac{1}{t_j-s_j}\int_{I_j} \mathbf{1}_{\{z:\, r<|z|<1\}}(x-y) b_j(y)\, dy.$$
Then by \eqref{eq-bj-L1}
\begin{equation}
    \label{eq-dj-est}
    |d_j|\leq 2\cdot 2^{-10} \alpha=2^{-9}\alpha.
\end{equation}
For each $j\in \mathcal{J}_2(x)$, we have
$$
H_r b_j(x)=\int_{I_j} \kappa(x-y) (\mathbf{1}_{\{z:\, r<|z|<1\}}(x-y)b_j(y)-d_j)\, dy$$
$$+ \int_{I_j} d_j \kappa(x-y) \, dy.
$$
$$=\int_{I_j} (\kappa(x-y)-\kappa(x-c_j)) (\mathbf{1}_{\{z:\, r<|z|<1\}}(x-y)b_j(y)-d_j)\, dy$$
$$+ \int_{I_j} d_j \kappa(x-y) \, dy.$$
Thus, using the triangle inequality, the estimate above and \eqref{eq-dj-est}, we obtain
$$|H_r b_j(x)|\leq $$
\begin{equation}
    \label{eq-J2-diff-est}
    \int_{I_j} |(\kappa(x-y)-\kappa(x-c_j)) \left(|b_j(y)|+2^{-9}\alpha\right)\, dy +2^{-9}\alpha \int_{I_j} |\kappa(x-y)| \, dy.
\end{equation}
Using \eqref{eq-Om-cj}, \eqref{eq-Om-y} and \Cref{Hilbert-kernel-regularity}, and arguing as in \eqref{eq-J1-diff-est}, we get the the first term above can be estimated by
\begin{equation}
    \label{eq-J2-diff-est-2}
    2^{10}\sum_{j} \frac{(t_j-s_j)}{|x-c_j|^2}\left(\int_{I_j} |b_j(y)|+2^{-9} \alpha (t_j-s_j)\right)=F_1(x)+F_2(x),
\end{equation}
with $F_1$ as in \eqref{eq-J1-diff-est} and
\begin{equation}
    \label{eq-def-F2}
    F_2(x):= 2\sum_{j} \frac{(t_j-s_j)}{|x-c_j|^2} \alpha (t_j-s_j).
\end{equation}
For each $j\in \mathcal{J}_2(x)$, let $y_j\in [s_j, t_j)$ be such that
$$|x-y_j|=r.$$ Using \eqref{eq-Om-y}, we have
$$r=|x-y_j|>2(t_j-s_j).$$
Further, using the triangle inequality, for each $y\in I_j$, we obtain
$$|x-y|\leq |x-y_j|+|y-y_j|\leq r+(t_j-s_j)<\frac{3r}{2},$$
and
$$|x-y|\geq |x-y_j|-|y-y_j|\geq r-(t_j-s_j)>\frac{r}{2}.$$
We conclude that
$$[s_j, t_j)\subset \left\{y\,: \frac{r}{2}<|x-y|<\frac{3r}{2}\right\}.$$
Using this and \Cref{Hilbert-kernel-bound}, we get
\begin{equation}
    \label{eq-J2-diff-est-4}
    \int_{I_j}|\kappa(x-y)|\,dy \leq \int_{\{y\,: \frac{r}{2}<|x-y|<\frac{3r}{2}\}}\frac{8}{|x-y|}\, dy\leq 32\,.
\end{equation}

Combining \eqref{eq-b-dec}, \eqref{eq-J1-diff-est}, \eqref{eq-J2-diff-est}, \eqref{eq-J2-diff-est-2} and \eqref{eq-J2-diff-est-4}, we get
\begin{equation*}
    |H_rb(x)|\leq 2F_1(x)+F_2(x)+2^{-4}\alpha.
\end{equation*}
Using the triangle inequality, we deduce that
$$\mu({\{x\in \Omega: |H_r b(x)|>\alpha/4\}})\leq $$
\begin{equation}
    \label{eq-set-dec-3}
    \mu(\{x\in \Omega: |F_1(x)|> 2^{-4} \alpha\})+\mu(\{x\in \Omega: | F_2(x)|> 2^{-4}\alpha\}).
\end{equation}

We estimate
\begin{equation}
    \label{eq-F1-est-1}
    \mu(\{x\in \Omega: |F_1(x)|> 2^{-4}\alpha\})\leq \frac{2^{14}}{\alpha}\sum_{j} \int_{I_j} |b_j(y)|\, dy\int_{\Omega} \frac{(t_j-s_j)}{|x-c_j|^2}\, dx.
\end{equation}
Using \eqref{eq-Om-cj}, we can bound
\begin{equation}
    \label{eq-Om-int}
    \int_{\Omega} \frac{(t_j-s_j)}{|x-c_j|^2}\, dx \le 2(t_j - s_j) \int_{5|t_j - s_j|}^\infty \frac{1}{t^2} \, \mathrm{d}t = \frac{2}{5}\,.
\end{equation}
Plugging \eqref{eq-Om-int} into \eqref{eq-F1-est-1} and using \eqref{eq-b-L1}, we conclude that
\begin{equation}
    \label{eq-F1-est-2}
    \mu(\{x\in \Omega: |F_1(x)|>2^{-4}\alpha\})\leq \frac{2^{14}}{\alpha}\int |f(y)|\,dy\,.
\end{equation}

Similarly, we estimate
$$\mu(\{x\in \Omega: |F_2(x)|>2^{-4} \alpha\})\leq \frac{2^{5}}{\alpha}\sum_{j} \alpha (t_j-s_j)\, \int_{\Omega} \frac{(t_j-s_j)}{|x-c_j|^2}\, dx.$$
Using \eqref{eq-Om-int} and \eqref{eq-bset-length-sum}, this is bounded by
\begin{equation}
\label{eq-F2-est}
2^{4}\sum_{j} (t_j-s_j)\leq \frac{2^{15}}{\alpha}\int |f(y)|\, dy.
\end{equation}

Combining estimates \eqref{eq-set-dec-1}, \eqref{eq-g-func-bd}, \eqref{eq-omega-bd}, \eqref{eq-set-dec-3}, \eqref{eq-F1-est-2} and \eqref{eq-F2-est} yields \eqref{eq-weak-1-1}.
\end{proof}
















































\section{The proof of the van der Corput Lemma}
\label{10vandercorput}

\begin{proof}[Proof of \Cref{van-der-Corput}]
\proves{van-der-Corput}
Let $g$ be a Lipschitz continuous function as in the lemma. We have
$$
    e^{in(x + \pi/n)} = -e^{inx}\,.
$$
Using this, we write
$$
    \int_\alpha^\beta g(x) e^{-inx} \, \mathrm{d}x
    = \frac{1}{2} \int_\alpha^\beta g(x) e^{inx} \, \mathrm{d}x - \frac{1}{2} \int_\alpha^\beta g(x) e^{in(x + \pi/n)}) \, \mathrm{d}x\,.
$$
We split the the first integral at $\alpha + \frac{\pi}{n}$ and the second one at $\beta - \frac{\pi}{n}$, and make a change of variables in the second part of the first integral to obtain
$$
    = \frac{1}{2} \int_{\alpha}^{\alpha + \frac{\pi}{n}} g(x) e^{inx} \, \mathrm{d}x - \frac{1}{2} \int_{\beta - \frac{\pi}{n}}^{\beta} g(x) e^{in(x + \pi/n)} \, \mathrm{d}x
$$
$$
    + \frac{1}{2} \int_{\alpha + \frac{\pi}{n}}^{\beta} (g(x) - g(x - \frac{\pi}{n})) e^{inx} \, \mathrm{d}x\,.
$$
The sum of the first two terms is by the triangle inequality bounded by
$$
    \frac{\pi}{n} \sup_{x \in [\alpha,\beta]} |g(x)|\,.
$$
The third term is by the triangle inequality at most
$$
    \frac{1}{2} \int_{\alpha + \frac{\pi}{n}}^\beta |g(x) - g(x - \frac{\pi}{n})| \, \mathrm{d}x
$$
$$
    \le \frac{\pi}{2n} \sup_{\alpha \le x < y \le \beta} \frac{|g(x) - g(y)|}{|x-y|} |\beta-\alpha|\,.
$$
Adding the two terms, we obtain
$$
    \left|\int_\alpha^\beta g(x) e^{-inx} \, \mathrm{d}x\right| \le \frac{\pi}{n} \|g\|_{\mathrm{Lip}(\alpha,\beta)}\,.
$$
By the triangle inequality, we also have
$$
    \left|\int_\alpha^\beta g(x) e^{-inx} \, \mathrm{d}x\right| \le |\beta -\alpha| \sup_{x \in [\alpha,\beta]} |g(x)| \le |\beta-\alpha| \|g\|_{\mathrm{Lip}(\alpha,\beta)}\,.
$$
This completes the proof of the lemma, using that
$$
    \min\{|\beta-\alpha|, \frac{\pi}{n}\} \le 2 \pi |\beta-\alpha|(1 + n|\beta-\alpha|)^{-1}\,.
$$
\end{proof}




\section{Partial sums as orthogonal projections}
\label{10projection}

This subsection proves \Cref{spectral-projection-bound}






\begin{lemma}[partial sum projection]
\label{partial-sum-projection}
\uses{mean-zero-oscillation}
  Let $f$ be a bounded $2\pi$-periodic measurable function. Then, for all $N\ge 0$
   \begin{equation}\label{projection}
   S_N(S_N f)=S_Nf\, .
   \end{equation}
   \end{lemma}
\begin{proof}
Let $N>0$ be given. With $K_N$ as in \Cref{dirichlet-kernel},
\begin{equation*}
S_N (S_Nf) (x)=
\frac{1}{2\pi} \int_0^{2\pi} S_Nf(y)K_N(x-y)\, dy
\end{equation*}
\begin{equation}\label{eqhil1}
=
\frac{1}{(2\pi)^2}\int_0^{2\pi} \int_0^{2\pi} f(y')K_N(y-y') K_N(x-y)\, \, dy' dy\, .
\end{equation}
We have by \Cref{dirichlet-kernel}
\begin{equation*}
\frac{1}{2\pi}\int_0^{2\pi} K_N(y-y') K_N(x-y)\, dy
\end{equation*}
\begin{equation*}
=\frac{1}{2\pi}\sum_{n=-N}^N\sum_{n'=-N}^N
\int_0^{2\pi} e^{in(y-y')}e^{in'(x-y)}\, dy
\end{equation*}
\begin{equation}\label{eqhil6}
=\frac{1}{2\pi}\sum_{n=-N}^N\sum_{n'=-N}^N
e^{i(n'x-ny')}\int_0^{2\pi} e^{i(n-n')y}\, dy\, .
\end{equation}
By \Cref{mean-zero-oscillation}, the summands for $n\neq n'$ vanish.
We obtain for \eqref{eqhil6}
\begin{equation}\label{eqhil2}
=\frac{1}{2\pi}\sum_{n=-N}^N
e^{in(x-y')}\int_0^{2\pi} \, dy=K_N(x-y')\, .
\end{equation}
Applying Fubini in \eqref{eqhil1} and using
\eqref{eqhil2} gives
\begin{equation}
S_N(S_Nf)(x)=
\frac{1}{2\pi} \int_0^{2\pi} f(y')K(x-y') \, dy'=S_N f(x)
\end{equation}
This proves the lemma.
\end{proof}
\begin{lemma}[partial sum selfadjoint]
\label{partial-sum-selfadjoint}
\uses{dirichlet-kernel}
    We have for any $2\pi$-periodic bounded measurable $g,f$ that
    \begin{equation}
       \int_0^{2\pi} \overline{S_Nf(x)} g(x)=\int_0^{2\pi} \overline{f(x)} S_Ng(x)\, dx\, .
    \end{equation}
\end{lemma}
\begin{proof}
  We have with $K_N$ as in \Cref{dirichlet-kernel} for every $x$
  \begin{equation}
      \overline{K_N(x)}=\sum_{n=-N}^N\overline{ e^{in x}}=
      {\sum_{n=-N}^N e^{-in x}}=K_N(-x)\, .
  \end{equation}
 Further, with \Cref{dirichlet-kernel} and Fubini
\begin{equation*}
\int_0^{2\pi} \overline{S_Nf(x)} g(x)
= \frac 1{2\pi} \int_0^{2\pi} \int_{-\pi}^{\pi}\overline{f(y) K_N(x-y)} g(x)\, dy dx
 \end{equation*}
 \begin{equation}
=
\frac 1{2\pi} \int_0^{2\pi} \int_{-\pi}^{\pi}\overline{f(y)} K_N(y-x)
g(x)\, dx dy
=\int_0^{2\pi} \overline{f(x)} S_Ng(x)\, dx
\, .
\end{equation}
 This proves the lemma.
\end{proof}


We turn to the proof of Lemma
\ref{spectral-projection-bound}.

We have with \Cref{partial-sum-selfadjoint}, then \Cref{partial-sum-projection} and the \Cref{partial-sum-selfadjoint} again
\begin{equation*}
 \int_0^{2\pi} S_Nf(x)\overline{S_Nf(x)}\, dx
 \int_0^{2\pi} f(x)\overline{S_N(S_Nf)(x)}\, dx
\end{equation*}
\begin{equation}\label{eqhil7}
 =\int_0^{2\pi} f(x)\overline{S_Nf(x)}\, dx=
 \int_0^{2\pi} S_N f(x)\overline{f(x)}\, dx\, .
\end{equation}

We have by the distributive law
\begin{equation}\label{diffnorm}
    \int_0^{2\pi} (f(x)-S_Nf(x))(\overline{f(x)-S_Nf(x)})\, dx=
\end{equation}
\begin{equation*}
 \int_0^{2\pi} f(x)\overline{f(x)}
    -S_Nf(x)\overline{f(x)}
   -f(x)\overline{S_Nf(x)}
     + S_Nf(x)\overline{S_Nf(x)}\, dx
\end{equation*}
Using the various identities expressed in \eqref{eqhil7}, this becomes
\begin{equation}
 =\int_0^{2\pi} f(x)\overline{f(x)}\, dx
    -
   \int_0^{2\pi} S_Nf(x)\overline{S_Nf(x)}\, dx\, .
\end{equation}
As \eqref{diffnorm} has nonnegative integrand and is thus nonnegative, we conclude
\begin{equation}
  \int_0^{2\pi} S_Nf(x)\overline{S_Nf(x)}\, dx\le
 \int_0^{2\pi} f(x)\overline{f(x)})\, dx\, .
\end{equation}
As both sides are positive, we may take the square root of this inequality.
This completes the proof of the lemma.





\section{The error bound}
\label{10difference}

%\begin{lemma}
%\label{control-approximation-effect}
%Let $h : \R \to \C$ be measurable, $2\pi$-periodic and
%\end{lemma}

\begin{proof}[Proof of \Cref{control-approximation-effect}]
\leanok
Define
$$
    E := \{x \in [0, 2\pi) \ : \ \sup_{N > 0} |S_N f(x) - S_N f_0(x)| > \frac{\epsilon}{4} \}\,.
$$
Then \eqref{eq-max-partial-sum-diff} clearly holds, and it remains to show that $|E| \le \frac{\epsilon}{2}$. This will follow from \Cref{real-Carleson}.

Let $x \in E$. Then there exists $N > 0$ with
$$
    |S_N f(x) - S_N f_0(x)| > \frac{\epsilon}{4}\,,
$$
pick such $N$. We have with \Cref{dirichlet-kernel}
$$
    \frac{\epsilon}{4} < |S_N f(x) - S_N f_0(x)| = \frac{1}{2\pi} \left| \int_0^{2\pi} (f(y) - f_0(y)) K_N(x-y) \, dy\right|\,.
$$
We make a change of variables, replacing $y$ by $x -y$. Then we use $2\pi$-periodicity of $f$, $f_0$ and $K_N$ to shift the domain of integration to obtain
$$
    = \frac{1}{2\pi} \left|\int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) K_N(y) \, dy\right|\,.
$$
Using the triangle inequality, we split this as
$$
    \le \frac{1}{2\pi} \left|\int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) \max(1 - |y|, 0) K_N(y) \, dy\right|
$$
$$
    + \frac{1}{2\pi} \left|\int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) \min(|y|, 1) K_N(y) \, dy\right|\,.
$$
Note that all integrals are well defined, since $K_N$ is by \eqref{eqksumexp} bounded by $2N+1$.
Using \eqref{eqksumhil} and the definition \eqref{eq-hilker} of $\kappa$, we rewrite the two terms and obtain
\begin{equation}
    \label{eq-diff-singular}
    \frac{\epsilon}{4} < \frac{1}{2\pi} \left| \int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) (e^{iNy} \overline{\kappa}(y) + e^{-iNy}\kappa(y)) \, dy\right|
\end{equation}
\begin{equation}
    \label{eq-diff-integrable}
    + \frac{1}{2\pi} \left|\int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) ( e^{iNy} \frac{\min\{|y|, 1\} }{1 - e^{-iy}} + e^{-iNy} \frac{\min\{|y|, 1\} }{1 - e^{iy}}) \, dy \right|\,.
\end{equation}
By \Cref{lower-secant-bound} with $\eta = |y|$, we have for $-1 \le y \le 1$
$$
    |e^{iNy}\frac{\min\{|y|, 1\} }{1 - e^{-iy}}| = \frac{|y|}{|1 - e^{iy}|} \le \frac \pi 2 \,.
$$
By \Cref{lower-secant-bound} with $\eta = 1$, we have for $1 \le |y| \le \pi$
$$
    |e^{iNy}\frac{\min\{|y|, 1\} }{1 - e^{-iy}}| = \frac{1}{|1 - e^{iy}|} \le \frac \pi 2 \,.
$$
Thus we obtain using the triangle inequality and \eqref{eq-ffzero}
$$
    \eqref{eq-diff-integrable} \le \frac{1}{2} \int_{-\pi}^{\pi} |f(x-y) - f_0(x-y)| \, dy \le \pi\epsilon'.
$$
Consequently, we have that
$$
    \frac{\epsilon}{4} - \pi\epsilon' \le \frac{1}{2\pi} \left| \int_{-\pi}^{\pi} (f(x-y) - f_0(x-y)) (e^{iNy} \overline{\kappa}(y) + e^{-iNy}\kappa(y)) \, dy\right|\,.
$$
By dominated convergence and since $\kappa(y) = 0$ for $|y| > 1$, this equals
$$
     = \frac{1}{2\pi} \lim_{r \to 0^+} \left| \int_{r < |y| < 1} (f(x-y) - f_0(x-y)) (e^{iNy} \overline{\kappa}(y) + e^{-iNy}\kappa(y)) \, dy\right|\,.
$$
Let $h = (f - f_0) \mathbf{1}_{[-\pi, 3\pi]}$. Since $x \in [0, 2\pi]$, the above integral does not change if we replace $(f - f_0)$ by $h$. We do that, apply the triangle inequality and bound the limits by suprema
$$
    \le \frac{1}{2\pi} \sup_{r > 0} \left| \int_{r < |y| < 1} h(x-y) e^{-iNy} \kappa(y) \, dy\right|
$$
$$
    + \frac{1}{2\pi} \sup_{r > 0} \left| \int_{r < |y| < 1} \overline{h}(x-y) e^{-iNy} \kappa(y) \, dy\right|\,.
$$
By the definition \eqref{define-T-carleson} of $T$, this is
$$
    \le \frac{1}{2\pi} (Th(x) + T\bar{h}(x))\,.
$$
Thus for each $x \in E$, at least one of $Th(x)$ and $T\bar h(x)$ is larger than $\frac{\pi(\epsilon - 4 \pi\epsilon')}{4}$.
Thus at least one of $Th$ and $T\bar h$ is $\ge \frac{\pi(\epsilon - 4 \pi\epsilon')}{4}$ on a subset $E'$ of $E$ with $2|E'| \ge |E|$. Without loss of generality this is $Th$. By assumption \eqref{eq-ffzero}, we have $|2^{2^{50}}\epsilon^{-2} h| \le \mathbf{1}_{[-\pi, 3\pi]}$. Applying \Cref{real-Carleson} with $F = [-\pi, 3\pi]$ and $G = E'$, it follows that
$$
    \frac{\pi(\epsilon - 4 \pi\epsilon')}{4} |E'| \le \int_{E'} Th(x) \, dx = \epsilon' \int_{E'} T(\epsilon'^{-1} h)(x) \, dx
$$
$$
    \le \epsilon' \cdot C_{4,2} |F|^{\frac{1}{2}} |E'|^{\frac{1}{2}} \le (4\pi)^\frac{1}{2} C_{4,2} \epsilon' \cdot |E'|^{\frac{1}{2}}\,.
$$
Rearranging, we obtain
$$
    |E'| \le \left(\frac{4 (4\pi)^\frac{1}{2} C_{4,2} \epsilon'}{\pi(\epsilon - 4 \pi\epsilon')}\right)^2 = \frac{\epsilon}{2}\,.
$$
This completes the proof using $|E| \le 2|E'|$.
\end{proof}




\section{Carleson on the real line}
\label{10carleson}

We prove \Cref{real-Carleson}.

Consider the standard distance function
\begin{equation}
    \rho(x,y)=|x-y|
\end{equation}
on the real line $\R$.
\begin{lemma}[real line metric]
\label{real-line-metric}
The space $(\R,\rho)$ is a complete locally compact metric space.
\end{lemma}
\begin{proof}
    This is part of the Lean library.
\end{proof}
\begin{lemma}[real line ball]
\label{real-line-ball}
    \lean{Real.ball_eq_Ioo}
    \leanok
    For $x\in R$ and $R>0$, the ball $B(x,R)$ is the interval $(x-R,x+R)$
\end{lemma}
\begin{proof}
\leanok
Let $x'\in B(x,R)$. By definition of the ball,
$|x'-x|<R$. It follows that $x'-x<R$ and $x-x'<R$.
It follows $x'<x+R$ and $x'>x-R$. This implies
$x'\in (x-R,x+R)$.
Conversely, let $x'\in (x-R,x+R)$. Then
$x'<x+R$ and $x'>x-R$. It follows that
$x'-x<R$ and $x-x'<R$. It follows that $|x'-x|<R$,
hence $x'\in B(x,R)$.
This proves the lemma.
\end{proof}
We consider the Lebesgue measure $\mu$ on $\R$.
\begin{lemma}[real line measure]
\label{real-line-measure}
    The measure $\mu$ is a sigma-finite non-zero
    Radon-Borel measure on $\R$.
\end{lemma}
\begin{proof}
    This is part of the Lean library.
\end{proof}
\begin{lemma}[real line ball measure]
\label{real-line-ball-measure}
\uses{real-line-ball}
    \lean{Real.volume_ball}
    \leanok
    We have for every $x\in \R$ and $R>0$
    \begin{equation}
        \mu(B(x,R))=2R\, .
    \end{equation}
\end{lemma}
\begin{proof}
\leanok
We have with \Cref{real-line-ball}
\begin{equation}
    \mu(B(x,R))=\mu((x-R,x+R))=2R\, .
\end{equation}
\end{proof}

\begin{lemma}[real line doubling]
\label{real-line-doubling}
\uses{real-line-ball-measure}
    We have for every $x\in \R$ and $R>0$
    \begin{equation}
        \mu(B(x,2R))=2\mu(B(x,R))\, .
    \end{equation}
\end{lemma}
\begin{proof}
    We have with \Cref{real-line-ball-measure}
\begin{equation}
    \mu(B(x,2R)=4R=2\mu(B(x,R)\, .
\end{equation}
This proves the lemma.
\end{proof}


The preceding four lemmas show that $(\R, \rho, \mu, 4)$ is a doubling metric measure space. Indeed, we even show
that $(\R, \rho, \mu, 1)$ is a doubling metric measure space, but we may relax the estimate in \Cref{real-line-doubling} to conclude that $(\R, \rho, \mu, 4)$
is a doubling metric measure space.


For each $n\in \mathbb{Z}$ define
$\mfa_n:\R\to \R$ by
\begin{equation}
    \mfa_n(x)=nx\, .
\end{equation}


Let $\Mf$ be the collection $\{\mfa_n, n\in \mathbb{Z}\}$.
Note that for every $n\in \mathbb{Z}$ we have $\mfa_n(0)=0$.
Define
\begin{equation}
    \label{eqcarl4}
    d_{B(x,R)}(\mfa_n, \mfa_m) := 2R|n-m|\,.
\end{equation}

\begin{lemma}[frequency metric]
    \label{frequency-metric}
    For every $R > 0$ and $x \in X$, the function $d_{B(x,R)}$ is a metric on $\Mf$.
\end{lemma}

\begin{proof}
    This follows immediately from the fact that the standard metric on $\mathbb{Z}$ is a metric.
\end{proof}

\begin{lemma}[oscillation control]
    \label{oscillation-control}
    For every $R > 0$ and $x \in X$, and for all $n, m \in \mathbb{Z}$, we have
    \begin{equation}\label{eqcarl2}
       \sup_{y,y'\in B(x,R)}|ny-ny'-my+my'|\le 2|n-m|R\, .
    \end{equation}
\end{lemma}

\begin{proof}
    The right hand side of \eqref{eqcarl2} equals
    $$
        \sup_{y,y'\in B(x,R)}|(n-m)(y-x)-(n-m)(y'-x)|\,.
    $$
    The lemma then follows from the triangle inequality.
\end{proof}

\begin{lemma}[frequency monotone]
\label{frequency-monotone}

    For any $x, x' \in X$ and $R, R' > 0$ with $B(x,R) \subset B(x, R')$, and for any $n, m \in \mathbb{Z}$
    $$
        d_{B(x,R)}(\mfa_n, \mfa_m) \le d_{B(x',R')}(\mfa_n, \mfa_m)\,.
    $$
\end{lemma}

\begin{proof}
    This follows immediately from the definition \eqref{eqcarl4} and $R \le R'$.
\end{proof}

\begin{lemma}[frequency ball doubling]
\label{frequency-ball-doubling}
\uses{frequency-metric}
  For any $x,x'\in \R$ and $R>0$ with
   $x\in B(x',2R)$ and any $n,m\in \mathbb{Z}$, we have
\begin{equation}\label{firstdb1}
    d_{B(x',2R)}(\mfa_n,\mfa_m)\le 2 d_{B(x,R)}(\mfa_n,\mfa_m) \, .
\end{equation}
\end{lemma}
\begin{proof}
With \eqref{eqcarl4}, both sides of \eqref{firstdb1} are equal to $4R|n-m|$. This proves the lemma.
\end{proof}

\begin{lemma}[frequency ball growth]
\label{frequency-ball-growth}
    For any $x,x'\in \R$ and $R>0$ with
   $B(x,R)\subset B(x',2R)$ and any $n,m\in \mathbb{Z}$, we have
\begin{equation}\label{seconddb1}
    2d_{B(x,R)}(\mfa_n,\mfa_m)\le d_{B(x',2R)}(\mfa_n,\mfa_m) \, .
\end{equation}
\end{lemma}
\begin{proof}
With \eqref{eqcarl4}, both sides of \eqref{firstdb1} are equal to $4R|n-m|$. This proves the lemma.
\end{proof}

\begin{lemma}[integer ball cover]
\label{integer-ball-cover}
    For every $x\in \R$ and $R>0$ and every
    $n\in \mathbb{Z}$ and $R'>0$,
    there exist $m_1, m_2, m_3\in \mathbb{Z}$
    such that
    \begin{equation}\label{eqcarl5}
        B'\subset B_1\cup B_2\cup B_3\, ,
    \end{equation}
where
\begin{equation}
B'= \{ \mfa \in \Mf: d_{B(x,R)}(\mfa, \mfa_n)<2R'\}
\end{equation}
and for $j=1,2,3$
\begin{equation}
  B_j=
     \{ \mfa \in \Mf: d_{B(x,R)}(\mfa, \mfa_{m_j})<R'\}
     \, .
\end{equation}

\end{lemma}
\begin{proof}
Let $m_1$ be the largest integer smaller than
or equal to
$n- \frac {R'} {2R}$.
Let $m_2=n$.
Let $m_3$ be the smallest integer larger than
or equal to $n+ \frac {R'} {2R}$.

Let $\mfa_{n'}\in B'$, then with \eqref{eqcarl4},
we have
\begin{equation}\label{eqcarl6}
    2R|n-n'|< 2R'\, .
\end{equation}

Assume first $n'\le m_1$. With \eqref{eqcarl6}
we have
\begin{equation*}
    R|m_1-n'|=R(m_1-n')=R(m_1-n)+R(n-n')
\end{equation*}
\begin{equation}
    < -\frac{R'}2+R'=-\frac{R'}2\, .
\end{equation}
We conclude $\mfa_{n'}\in B_1$.

Assume next $m_1<n'<m_3$. Then
$\mfa_{n'}\in B_2$.

Assume finally that $m_3\le n'$. With \eqref{eqcarl6}
we have
\begin{equation*}
    R|m_3-n'|=R(n'-m_3)=R(n'-n)+R(n-m_3)
\end{equation*}
\begin{equation}
    < R' -\frac{R'}2=-\frac{R'}2\, .
\end{equation}
We conclude $\mfa_{n'}\in B_1$.
This completes the proof of the lemma.
\end{proof}


\begin{lemma}[real van der Corput]
\label{real-van-der-Corput}
\uses{van-der-Corput}
    For any $x\in \R$ and $R>0$ and any
    function $\varphi: X\to \C$ supported on $B'=B(x,R)$
    such that
\begin{equation}
    \|\varphi\|_{\Lip(B')} = \sup_{x \in B'} |\varphi(x)| + R \sup_{x,y \in B', x \neq y} \frac{|\varphi(x) - \varphi(y)|}{\rho(x,y)}
\end{equation}
is finite and for any $n,m\in \mathbb{Z}$, we have
\begin{equation}
    \label{eq-vdc-cond1}
    \left|\int_{B'} e(\mfa_n(x)-{\mfa_m(x)}) \varphi(x) d\mu(x)\right|\le 2\pi \mu(B')\frac{\|\varphi\|_{\Lip(B')}}{1+d_{B'}(\mfa_n,\mfa_m)}
\, .
\end{equation}
\end{lemma}
\begin{proof}
Set $n'=n-m$. Then we have to prove
\begin{equation}
    \label{eq-vdc-cond2}
    \left|\int_{x-R}^{x+R} e^{in'y}\varphi(y) dy\right|\le 4\pi R\|\varphi\|_{\Lip(B')}
(1+2R|n'|)^{-1}\, .
\end{equation}
This follows from \Cref{van-der-Corput} with $\alpha = x - R$ and $\beta = x + R$.
\end{proof}

The preceding chain of lemmas establish that $\Mf$ is a cancellative, compatible collection of functions on $(\R, \rho, \mu, 4)$. Again, some of the statements in these lemmas are stronger than what is needed for $a=4$, but can be relaxed to give the desired conclusion for $a=4$.




With $\kappa$ as near \eqref{eq-hilker}, define
the function $K:\R\times \R\to \mathbb{C}$ as in Theorem
\ref{metric-space-Carleson} by
\begin{equation}
    K(x,y):=\kappa(x-y)\, .
\end{equation}
The function $K$ is continuous outside the diagonal
$x=y$ and vanishes on the diagonal. Hence it is measurable.


By the Lemmas \ref{Hilbert-kernel-bound} and \ref{Hilbert-kernel-regularity}, it follows that $K$ is a one-sided Calder\'on--Zygmund kernel on $(\R,\rho,\mu,4)$.


The operator $T^*$ defined in \eqref{def-tang-unm-op} coincides in our setting with the operator $T^*$ defined in \eqref{concretetstar}. By \Cref{nontangential-Hilbert}, this operator satisfies the bound \eqref{nontanbound}.




Thus the assumptions of \Cref{metric-space-Carleson} are all satisfied. Applying the Theorem, \Cref{real-Carleson} follows.

\printbibliography
